### 2016-06-29 paper.tex
intro

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Evidence of the necissity of isotopic precise calculation in fuel cycle
calculation}
\author{Baptiste Mouginot$^{*}$ Paul, P.H. Wilson$^{*}$}

\institute{
$^{*}$University of Wisconsin-Madison, WI
\and
%$^{\dagger}$State Capitol Building, Springfield, IL
}

\email{mouginot@wisc.edu \and paul.wilson@wisc.edu}

% Optional disclaimer: remove this command to hide
\disclaimer{Notice: this manuscript is a work of fiction. Any resemblance to
actual articles, living or dead, is purely coincidental.}

%%%% packages and definitions (optional)
\usepackage{graphicx} % allows inclusion of graphics
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF

\newcommand{\SN}{S$_N$}
\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
\newcommand{\grad}{\vec{\nabla}} % gradient
\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

This work is part of the evaluation study of the transition analysis
\cite{Bo-fengpaper?} identify as the ``Evaluation Group 29'' or ``EG29'', in the
recently-published Evaluation and Screening (E\&S) \cite{ES}.  The EG29 fuel
cycle corresponds to a double strata fleet. The first stratum is composed by
sodium-cooled fast reactor (SFRs) multi-recycling the plutonium. The surplus
amounts of plutonium is send to the second stratum composed of pressurized water
reactor with full mixed oxide (U/Pu)O$_{2}$ cores (MOX-PWRs).  The PWR stratum
is also multi recycling its plutonium. The target energy generation ratio for
the final EG29 system is 70:30 (SFR:PWR), with a 1\% annual growth in nuclear
energy demand.

The purpose of this study is to enlighten the importance of the isotopic
composition for the plutonium, on PWR MOX fuel fabrication and the effect of its
evolution. Two main effect can modify the isotopic composition of the plutonium
used to build the PWR-MOX fuel: decay and depletion.

\section{Study description}
This works compares the plutonium amount require to build the fresh MOX fuel
using 3 different fabrication modeling: ``fixed mixing ratio'', ``plutonium
equivalent theory'', ``Neural network \cite{CLASS_MLP}'', considering or not
decay, and using recipe reactor or recalculation the depletion for each loaded
fuel.

The first part of the study in focused on the effect of the decay on the
isotopic composition of the reprocessed plutonium and its implication of fuel
fabrication depending on the fabrication modeling.
The second part of the study, compares 2 recipes compositions versus recalculated
depletion using the neural network fuel fabrication modeling.

\subsection{Cycle}
The cycle used for the following study is a very simple cycle implying a single
PWR reactor using MOX fuel. After irradiation the uranium and the plutonium are
separated and re-processed to fuel the next batch of MOX fuel for the PWR.

A stream of ``good'' quality plutonium coming from an hypothetical irradiated
SFR blanket is represented by a storage. The impact of the decay on this storage
is limited, as the content in $^{241}$Pu is almost negligible.  In order to
build the first batch of fuel, an initial storage has also been set.  In order
to limit the effect of decay of this storage the initial inventory have been
tuned to be as small as possible (preventing any unnecessary plutonium pilling
up).

\subsection{Fabrication model}
Three different way to model the fuel fabrication have been used: ``fix mixing
ratio'', ``Pu-equivalent`` and ''Neural Network``.
The fix mixing ratio used pre-set ratio for the different stream mixing. The
''Pu-equivalent`` model try to fix the best mixing ratio allowing to reproduce
the initial reactivity of the requested MOX fuel. As the requested fuel
composition correspond to the fuel composition built with the ''fix mixing
ratio`` model, the results of those 2 models are expected to be close.
The last model use a different approach to mix the different stream: the
$<k_{infty}>$, the mean infinity neutronic multiplication factor, have to reach
a threshold at the end of the irradiation ($50~$GWd/t in this study). The
$<k_{infty}>$ used in this study is 1.034 \cite{???}. The Neural Network in this
model have been pre-trained on several different depletion calculation,
allowing it to predict the correct plutonium enrichment required.

Because of all those model have not necessary been tuned on exactly the same
PWR configuration and parameter, only the behavior differences between the
different calculations should be analysed..

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Decay impact}

To measure the impact of the decay on the fuel fabrication process, $2\times3$
different calculations have been performed, each using a different way to model
the fuel fabrication, with and without decay activated:

\begin{itemize}
  \item fixed mixing ratio,
  \item plutonium equivalent theory,
  \item Neural network \cite{CLASS_MLP}.
\end{itemize}

The fixed mixing ratio corresponds to a simple mix of the different stream to
build the fresh MOX fuel. The mixing ratio remain fix regardless to the isotopic
composition evolution resulting of the decay process.

The second calculation uses the plutonium equivalent theory to determine the
proper mixing ratio between the different stream. In this case the model is
tuned to build a MOX fuel with the same initial reactivity as the fuel loaded
with the fixed mixing ratio model.

The last model based on pre-trained neural network, determine the mixing ratio
in order to build a MOX fuel that will reach a $<k_{\infty}>$ of $1.034$ at the
end of irradiation (i.e.: $50~$GWd/t). (The $<k_{\infty}>$ corresponds to the mean
$k_{\infty}$ of the tree batches of the reactor)

In order to discriminate between the depletion calculation effect and the decay
consequences, in each case the reactor use the same output composition for the
spent fuel despite the change in fresh MOX fuel composition.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Irradiation calculation impact}

This part is dedicated to the evaluation of the impact of non recalculation of
the MOX fuel evolution during irradiation.

Two additional calculation have been performed. Those calculations use the
neural network for the fuel fabrication modeling as well as for the
recalculation of the MOX fuel depletion calculation: for each MOX fuel loaded in
the reactor, a dedicated depletion calculation also to update the output recipe
used for the spent MOX fuel.

The difference between the fix recipe reactor calculation and the more precise
reactor are show in the following part.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

The included ANS style file and this clear example file are a panacea for
the hours of headache that invariably results from formatting a document in
Microsoft Word.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Appendix}

Numbering in the appendix is different:
\begin{equation} \label{eq:appendix}
  2 + 2 = 5\,.
\end{equation}
and another equation:
\begin{equation} \label{eq:appendix2}
  a + b = c\,.
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
This material is based upon work supported a Department of Energy Nuclear
Energy University Programs Graduate Fellowship.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{ans}
\bibliography{bibliography}
\end{document}

### 2016-06-29 paper.tex
first darft

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Evidence of the necissity of isotopic precise calculation in fuel cycle
+\title{Evidence of the necessity of isotopic precise calculation in fuel cycle
 calculation}
-\author{Baptiste Mouginot$^{*}$ Paul, P.H. Wilson$^{*}$}
+\author{Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$, Meghan B. McGarry$^{*}$,
+Arrielle C. Opotowsky$^{*}$ }
 
@@
 % Optional disclaimer: remove this command to hide
-\disclaimer{Notice: this manuscript is a work of fiction. Any resemblance to
-actual articles, living or dead, is purely coincidental.}
+%\disclaimer{Notice: this manuscript is a work of fiction. Any resemblance to
+%actual articles, living or dead, is purely coincidental.}
 
@@
 
+All the calculation of this study have been performed using the Cyclus fuel cycle
+tool\cite{CYCLUS}. The model used are coming from the Cycamore package, developed by the
+Cyclus team (containing the Pu-Equivalent fuel fabrication modeling as well as
+the simple fix mixing ratio fuel fabrication). The neural network model have
+been included into the Cyclus environment using the cyCLASS tool, allowing to
+using all the fuel fabrication model and the depletion model from the CLASS tool
+\cite{CLASS} in Cyclus.
+
 \section{Study description}
@@
 separated and re-processed to fuel the next batch of MOX fuel for the PWR.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{flow}
+  \caption{Schematic representation of the fuel cycle. Quantities on the row
+  represents the cumulative amount in kg of material exchanged between two
+facilities in the calculation using ``pu-equivalent'' for fuel fabrication
+modeling with decay activated.}
+  \label{fig:flow}
+\end{figure}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Decay impact}
-
-To measure the impact of the decay on the fuel fabrication process, $2\times3$
-different calculations have been performed, each using a different way to model
-the fuel fabrication, with and without decay activated:
-
-\begin{itemize}
-  \item fixed mixing ratio,
-  \item plutonium equivalent theory,
-  \item Neural network \cite{CLASS_MLP}.
-\end{itemize}
-
-The fixed mixing ratio corresponds to a simple mix of the different stream to
-build the fresh MOX fuel. The mixing ratio remain fix regardless to the isotopic
-composition evolution resulting of the decay process.
-
-The second calculation uses the plutonium equivalent theory to determine the
-proper mixing ratio between the different stream. In this case the model is
-tuned to build a MOX fuel with the same initial reactivity as the fuel loaded
-with the fixed mixing ratio model.
-
-The last model based on pre-trained neural network, determine the mixing ratio
-in order to build a MOX fuel that will reach a $<k_{\infty}>$ of $1.034$ at the
-end of irradiation (i.e.: $50~$GWd/t). (The $<k_{\infty}>$ corresponds to the mean
-$k_{\infty}$ of the tree batches of the reactor)
-
-In order to discriminate between the depletion calculation effect and the decay
-consequences, in each case the reactor use the same output composition for the
-spent fuel despite the change in fresh MOX fuel composition.
+The second part of the study compares the amount of plutonium require to build
+the PWR-MOX fuel (using the neural network modeling for fuel fabrication) for
+the recipe based output composition versus the depletion calculation one.
+To redo the depletion calculation for each fuel loaded in the PWR reactor, an
+other neural network is used to predict the macroscopic cross section of the
+fuel \cite{NN_CLASS} (only fission, capture and n,2n reactions are considered). The
+depletion calculation is done renormalizing the neutron flux to maintain a
+constant power in the reactor.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Irradiation calculation impact}
+\section{Decay}
 
-This part is dedicated to the evaluation of the impact of non recalculation of
-the MOX fuel evolution during irradiation.
+As observed on Fig. \ref{fig:nod}, despite the different model were not tuned to
+describe the exact same PWR concept, the results without decay process are very
+close. They all predict a constant plutonium fraction around $8\%$ of plutonium
+in the fresh PWR-MOX fuel.
 
-Two additional calculation have been performed. Those calculations use the
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{nodecay_pu_contribution.png}
+  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
+  using the 3 predicted models, without considering decay.}
+  \label{fig:nod}
+\end{figure}
+
+Activating decay, see Fig. \ref{fig:d}, results for the ``fix mixing ratio''
+calculation in a small decrease of the fraction of plutonium in the fuel,
+corresponding to the decay of $^{241}$Pu into $^{241}$Am. For the
+``Pu-equivalent'' modeling we can observe a slight increase of the fraction of
+plutonium, which is required to compensate for the negative reactivity effect
+coming with the $^{241}$Am. For the calculation using ``Neural network'' fuel
+fabrication modeling the effect is very quickly increasing to $13\%$ and then
+slowing stabilising while the plutonium inventory reach an equilibrium\ldots
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{decay_pu_contribution.png}
+  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
+  using the 3 prediction models, with and without decay enable.}
+  \label{fig:d}
+\end{figure}
+
+As the calculation using ``Neural Network'' fabrication modeling, requires more
+plutonium than the cycle can produce, the initial inventory has been set to an
+higher values, increasing the plutonium decay effect. Nevertheless this shows
+the strong impact of the presence of $^{241}$Am with the plutonium used for the
+PWR-MOX fuel fabrication.
+
+A last calculation, on decay have been performed using the ``Pu-equivalent''
+fabrication model, increasing by a factor 2, 5 and 10 the amount of plutonium in
+the startup inventory, trying to mimic different degree of a plutonium pill-up.
+This calculation shoes an change from 10 to 30\% in the mixing ratio required to
+build the proper PWR-MOX fuel. Those kind of plutonium pilling up can
+unexpectedly occurs in a real fuel cycle and might need to be considered in a
+complete fuel cycle transition study.
+
+The decay process tends to change to composition of the plutonium vector, and
+then of the plutonium enrichment require to build a proper PWR-MOX fuel. Those
+composition change in the MOX fuel will impact the individual cross section:
+specially in thermal reactor where the macroscopic cross section are very
+dependent on the shape of the thermal part of the neutron spectrum, which is
+strongly driven by the fuel isotopic composition.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Depletion vs Recipe}
+
+This part is dedicated to the evaluation of the impact of the depletion
+calculation in a fuel cycle macroscopic level.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{irradiation_pu_contribution.png}
+  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
+  using the ``Neural Network'' prediction models, with decay enable using recipe
+based spent fuel composition and recalculated spent fuel composition.}
+  \label{fig:depletion}
+\end{figure}
+
+Two additional calculations have been performed. Those calculations use the
 neural network for the fuel fabrication modeling as well as for the
@@
 
-The difference between the fix recipe reactor calculation and the more precise
-reactor are show in the following part.
+As shown on Fig. \ref{fig:depletion}, the equilibrium values for recipe based
+calculation and the depletion calculation are not the same. Moreover,
+recalculating the fuel spent fuel composition for each loaded fuel allows the
+cycle to reach faster its equilibrium.
+
+This is led by the slight change in the composition in the available plutonium
+(see Fig. \ref{fig:depletioncompo}): in the case of the depletion calculation
+the available plutonium contain $68\%$ of $^{239}$Pu versus $64\%$ in the recipe
+based case, and also significantly less $^{241}$Pu leading to less $^{242}$Pu in
+the cycle. The amount of the other nuclide are very close.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{MOX_pu_composition.png}
+  \caption{Evolution of the composition of the plutonium in the fresh PWR-MOX fuel
+  using the ``Neural Network'' prediction models, with decay enable using recipe
+based spent fuel composition and recalculated spent fuel composition.}
+  \label{fig:depletioncompo}
+\end{figure}
+
+Those slight change in the output composition, lead to an overall decrease of
+the amount of $^{241}$Am in the fresh PWR-MOX fuel and an increase of the
+$^{239}$Pu, allowing to build fuel with a lower plutonium enrichment.
 
@@
 
-The included ANS style file and this clear example file are a panacea for
-the hours of headache that invariably results from formatting a document in
-Microsoft Word.
+This study have shown the potential impact of the decay process on the MOX-PWR fuel
+fabrication process, increasing the required amount from $1\%$ to $4\%$
+depending on the fuel fabrication modelization. The recalculation of the 
+depletion of each loaded fuel has for consequences the change of the equilibrium
+state of the calculation: the reduction of fraction of $^{241}$Am and the increase of the
+fraction $^{239}$Pu in the available plutonium allows to reduce the amount of
+plutonium at an alternate level (between the no-decay calculation and the recipe
+based calculation).
+
+This work has shown the strong influence of the isotopic composition on a LWR
+cycle involving plutonium recycling. Similar analysis will be conducted in the
+near future on the FBR part of the EG29 fuel cycle, which should be less
+impacted by those isotopic changes, as fast spectrum reactor are less sensitive
+to those change.
+
+Moreover this study has shown the potential of a agent based fuel cycle tool
+such as Cyclus. Not only Cyclus follows every isotopes in the cycle,
+but its modularity allows also to add modules based on other tool technology such
+as the Neural networks model developed for the French fuel cycle tool, CLASS.
+Those quality made of Cyclus a great platform to do such comparative study
+allowing to only change a specific aspect of the fuel cycle description while
+keeping every thing else identical.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Appendix}
-
-Numbering in the appendix is different:
-\begin{equation} \label{eq:appendix}
-  2 + 2 = 5\,.
-\end{equation}
-and another equation:
-\begin{equation} \label{eq:appendix2}
-  a + b = c\,.
-\end{equation}
+%\appendix
+%\section{Appendix}
+%
+%Numbering in the appendix is different:
+%\begin{equation} \label{eq:appendix}
+%  2 + 2 = 5\,.
+%\end{equation}
+%and another equation:
+%\begin{equation} \label{eq:appendix2}
+%  a + b = c\,.
+%\end{equation}
 
@@
 \section{Acknowledgments}
-This material is based upon work supported a Department of Energy Nuclear
-Energy University Programs Graduate Fellowship.
+Shall we acknowledge anyone ? DOE ? FCO ?
 

### 2016-06-30 paper.tex
adding Bo ref

--- 2016-06-29 paper.tex
@@
 
-This work is part of the evaluation study of the transition analysis
-\cite{Bo-fengpaper?} identify as the ``Evaluation Group 29'' or ``EG29'', in the
-recently-published Evaluation and Screening (E\&S) \cite{ES}.  The EG29 fuel
-cycle corresponds to a double strata fleet. The first stratum is composed by
-sodium-cooled fast reactor (SFRs) multi-recycling the plutonium. The surplus
-amounts of plutonium is send to the second stratum composed of pressurized water
-reactor with full mixed oxide (U/Pu)O$_{2}$ cores (MOX-PWRs).  The PWR stratum
-is also multi recycling its plutonium. The target energy generation ratio for
+The purpose of this study is to examine the importance of the isotopic
+composition of plutonium on PWR MOX fuel fabrication as part of a multi-tiered
+fuel cycle, and the effect of its evolution during a transition. Two main
+effects can modify the isotopic composition of the plutonium used to build the
+PWR-MOX fuel: decay and depletion.
+
+This analysis is based on a transition of the nuclear fuel cycle
+to a configuration identified as ``Evaluation Group 29'' or ``EG29'', in the
+recently-published Evaluation and Screening (E\&S) report \cite{ES}.  The EG29 fuel
+cycle corresponds to a double strata fleet. The first stratum is composed of
+sodium-cooled fast reactors (SFRs) multi-recycling plutonium. Surplus
+plutonium is sent to the second stratum composed of pressurized water
+reactors with full mixed oxide (U/Pu)O$_{2}$ cores (MOX-PWRs).  The PWR stratum
+is also multi-recycling its plutonium. The target energy generation ratio for
 the final EG29 system is 70:30 (SFR:PWR), with a 1\% annual growth in nuclear
@@
 
-The purpose of this study is to enlighten the importance of the isotopic
-composition for the plutonium, on PWR MOX fuel fabrication and the effect of its
-evolution. Two main effect can modify the isotopic composition of the plutonium
-used to build the PWR-MOX fuel: decay and depletion.
+%% PPHW: Can we add the official FCDP images
+
+All the calculation of this study have been performed using the Cyclus fuel cycle
+tool\cite{CYCLUS}. The facility models are from the Cycamore package, developed by the
+Cyclus team, and containing a Pu-equivalent fuel fabrication model as well as
+a simple fixed mixing ratio fuel fabrication model. A new neural network model has
+also been contributed to the Cyclus environment using the cyCLASS tool\cite{cyCLASS}, 
+allowing the use of the fuel fabrication and depletion models from the CLASS tool
+\cite{CLASS} in Cyclus.
+
+%% PPHW: Need a reference to cyCLASS - perhaps tag a version and put a zip
+%% file on figshare with a DOI.
 
 \section{Study description}
-This works compares the plutonium amount require to build the fresh MOX fuel
-using 3 different fabrication modeling: ``fixed mixing ratio'', ``plutonium
-equivalent theory'', ``Neural network \cite{CLASS_MLP}'', considering or not
-decay, and using recipe reactor or recalculation the depletion for each loaded
-fuel.
-
-The first part of the study in focused on the effect of the decay on the
-isotopic composition of the reprocessed plutonium and its implication of fuel
-fabrication depending on the fabrication modeling.
-The second part of the study, compares 2 recipes compositions versus recalculated
-depletion using the neural network fuel fabrication modeling.
+This work compares the plutonium fraction required to build fresh MOX fuel
+using three different stream mixing models in fuel fabrication: ``fixed mixing
+ratio'', ``plutonium equivalent theory'', ``neural network'' \cite{CLASS_MLP}.
+The first part of the study in focuses on the effect of decay on the isotopic
+composition of the reprocessed plutonium and its impact on fuel fabrication
+depending on the chosen stream mixing model.  The second part of the study,
+compares the impact on fresh fuel compositions when used fuel is based on a
+depletion calculation instead of a fixed recipe, using the neural network fuel
+fabrication model, also including the impact of decay.
 
 \subsection{Cycle}
-The cycle used for the following study is a very simple cycle implying a single
+This analysis is focused only on the second strata of EG29, represented by a single
 PWR reactor using MOX fuel. After irradiation the uranium and the plutonium are
-separated and re-processed to fuel the next batch of MOX fuel for the PWR.
+separated and reprocessed to fuel the next batch of MOX fuel for the PWR.
+%% PPHW - must provide the separation parameters/efficiencies
 
-A stream of ``good'' quality plutonium coming from an hypothetical irradiated
-SFR blanket is represented by a storage. The impact of the decay on this storage
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{flow}
+  \caption{Schematic representation of the fuel cycle. Quantities on the row
+  represents the cumulative amount in kg of material exchanged between two
+facilities in the calculation using ``pu-equivalent'' for fuel fabrication
+modeling with decay activated.}
+  \label{fig:flow}
+\end{figure}
+
+%% PPHW - must provide the composition of the ``good'' Pu
+A stream of ``good'' quality plutonium coming from a hypothetical irradiated
+SFR blanket is represented by a storage facility. 
+%% PPHW - which facility?  which label - there are two.
+The impact of the decay on this stored Pu
 is limited, as the content in $^{241}$Pu is almost negligible.  In order to
-build the first batch of fuel, an initial storage has also been set.  In order
-to limit the effect of decay of this storage the initial inventory have been
-tuned to be as small as possible (preventing any unnecessary plutonium pilling
-up).
+build the first batch of fuel, an initial quantity of stored Pu has also been provided.
+%% PPHW - how much?
+In order to limit the effect of decay of this storage the initial inventory have been
+tuned to be as small as possible, preventing any unnecessary accumulation of plutonium.
+%% PPHW - is this about the initial inventory or the capacity of the storage facility
+%%      - the latter seems to be about capacity
 
 \subsection{Fabrication model}
-Three different way to model the fuel fabrication have been used: ``fix mixing
-ratio'', ``Pu-equivalent`` and ''Neural Network``.
-The fix mixing ratio used pre-set ratio for the different stream mixing. The
-''Pu-equivalent`` model try to fix the best mixing ratio allowing to reproduce
-the initial reactivity of the requested MOX fuel. As the requested fuel
-composition correspond to the fuel composition built with the ''fix mixing
-ratio`` model, the results of those 2 models are expected to be close.
-The last model use a different approach to mix the different stream: the
-$<k_{infty}>$, the mean infinity neutronic multiplication factor, have to reach
-a threshold at the end of the irradiation ($50~$GWd/t in this study). The
-$<k_{infty}>$ used in this study is 1.034 \cite{???}. The Neural Network in this
-model have been pre-trained on several different depletion calculation,
-allowing it to predict the correct plutonium enrichment required.
+Three different ways to model the fuel fabrication have been used: ``fix mixing
+ratio'', ``Pu-equivalent'' and ``neural network''.
+The fix mixing ratio is based on a user-defined ratio for the different stream mixing. The
+``Pu-equivalent'' model finds the mixing ratio that results in an initial reactivity
+that matches that of the requested MOX fuel recipe.  This ratio may change as the 
+composition of the incoming streams changes.  As the requested fuel
+composition corresponds to the fuel composition built with the ''fix mixing
+ratio`` model, the results of those 2 models are expected to be similar.
+The ``neural network'' model attempts to achieve a given reactivity at the end of a 
+life for a given batch of fuel ($50~$GWd/t in this study). The
+$<k_{infty}>$ used in this study is 1.034 \cite{???}. The neural network in this
+model has been pre-trained on several different depletion calculations,
+allowing it to predict the correct plutonium fraction required, depending
+on the composition of that plutonium.
 
-Because of all those model have not necessary been tuned on exactly the same
-PWR configuration and parameter, only the behavior differences between the
-different calculations should be analysed..
+%% PPHW - is this end of cycle reactivity of the whole core for a multi-batch core?
+%%      - or is it end of life reactivity for a given batch?
+%%      - 1.034 and 50 GWd/t don't seem to go together
+
+Because of these models have not necessary been tuned on exactly the same
+PWR configuration and parameters, this analysis focuses on the differences
+in the results due to the change in model rather than the results themselves.
+
+The second part of the study compares the amount of plutonium require to build
+the PWR-MOX fuel (using the neural network modeling for fuel fabrication) for
+the recipe based output composition versus a compisition calculated by depletion.
+To caluclate the depletion for each fuel batch loaded in the PWR reactor, another 
+neural network is used to predict the macroscopic cross section of the
+fuel \cite{NN_CLASS} (only fission, capture and n,2n reactions are considered). The
+depletion calculation is done renormalizing the neutron flux to maintain a
+constant power in the reactor.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Decay impact}
+\section{Decay}
 
-To measure the impact of the decay on the fuel fabrication process, $2\times3$
-different calculations have been performed, each using a different way to model
-the fuel fabrication, with and without decay activated:
+As observed in Fig. \ref{fig:nod}, despite the fact that the different models 
+were not tuned to
+describe the exact same PWR concept, the results without decay are very
+close. They all predict a constant plutonium fraction around $8\%$ of plutonium
+in the fresh PWR-MOX fuel.
 
-\begin{itemize}
-  \item fixed mixing ratio,
-  \item plutonium equivalent theory,
-  \item Neural network \cite{CLASS_MLP}.
-\end{itemize}
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{nodecay_pu_contribution.png}
+  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
+  using the 3 predicted models, without considering decay.}
+  \label{fig:nod}
+\end{figure}
 
-The fixed mixing ratio corresponds to a simple mix of the different stream to
-build the fresh MOX fuel. The mixing ratio remain fix regardless to the isotopic
-composition evolution resulting of the decay process.
+%% PPHW - need better figure legend text so that readers know what they are
+%% looking at
 
-The second calculation uses the plutonium equivalent theory to determine the
-proper mixing ratio between the different stream. In this case the model is
-tuned to build a MOX fuel with the same initial reactivity as the fuel loaded
-with the fixed mixing ratio model.
+With decay turned on, see Fig. \ref{fig:d}, results for the ``fix mixing ratio''
+calculation see a small decrease of the fraction of plutonium in the fuel,
+corresponding to the decay of $^{241}$Pu into $^{241}$Am.  For the
+``Pu-equivalent'' modeling we can observe a slight increase of the fraction of
+plutonium, which is required to compensate for the negative reactivity effect
+coming from the $^{241}$Am. For the calculation using ``neural network'' fuel
+fabrication modeling the effect is very quickly increasing to $13\%$ and then
+slowing stabilizing as the plutonium composition approaches an equilibrium.
 
-The last model based on pre-trained neural network, determine the mixing ratio
-in order to build a MOX fuel that will reach a $<k_{\infty}>$ of $1.034$ at the
-end of irradiation (i.e.: $50~$GWd/t). (The $<k_{\infty}>$ corresponds to the mean
-$k_{\infty}$ of the tree batches of the reactor)
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{decay_pu_contribution.png}
+  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
+  using the 3 prediction models, with and without decay enable.}
+  \label{fig:d}
+\end{figure}
 
-In order to discriminate between the depletion calculation effect and the decay
-consequences, in each case the reactor use the same output composition for the
-spent fuel despite the change in fresh MOX fuel composition.
+%% PPHW - need better color and symbol choices to facilitate comparison
+%%      - different models use different colors and decay/no decay uses
+%%      -  different symbols (for example)
+
+As the calculation using ``neural network'' fabrication modeling requires more
+plutonium than the cycle can produce, the initial inventory has been set to a
+higher values, increasing the plutonium decay effect. Nevertheless this shows
+the strong impact of the presence of $^{241}$Am with the plutonium used for the
+PWR-MOX fuel fabrication.
+
+%% PPHW: why is the Pu-equiavlent model so bad?
+
+A last calculation, on decay have been performed using the ``Pu-equivalent''
+fabrication model, increasing by a factor 2, 5 and 10 the amount of plutonium in
+the startup inventory.  This mimics different degrees of a plutonium accumulation,
+and thus different impacts from the decay of this plutonium.
+This calculation shows a change from 10 to 30\% in the mixing ratio required to
+build the proper PWR-MOX fuel. This kind of plutonium accumulation can
+unexpectedly occur in a real fuel cycle and might need to be considered in a
+complete fuel cycle transition study.
+%% PPHW - do you plot results for this?
+
+The decay process tends to change to composition of the plutonium vector, and
+then of the plutonium enrichment required to build a proper PWR-MOX fuel.  Such
+composition change in the MOX fuel will impact the individual cross sections:
+particularly in thermal reactors where the macroscopic cross sections are very
+dependent on the shape of the thermal part of the neutron spectrum, which is
+strongly driven by the fuel isotopic composition.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Irradiation calculation impact}
+\section{Depletion vs Recipe}
 
-This part is dedicated to the evaluation of the impact of non recalculation of
-the MOX fuel evolution during irradiation.
+Another analysis was performed to evaluate the impact of the depletion
+calculation on a fuel cycle macroscopic (???) level.
 
-Two additional calculation have been performed. Those calculations use the
-neural network for the fuel fabrication modeling as well as for the
-recalculation of the MOX fuel depletion calculation: for each MOX fuel loaded in
-the reactor, a dedicated depletion calculation also to update the output recipe
-used for the spent MOX fuel.
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{irradiation_pu_contribution.png}
+  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
+  using the ``neural network'' prediction models, with decay enable using recipe
+based spent fuel composition and recalculated spent fuel composition.}
+  \label{fig:depletion}
+\end{figure}
 
-The difference between the fix recipe reactor calculation and the more precise
-reactor are show in the following part.
+%% PPHW: - I don't know which answer is which !?!?  bad legend labels!
+
+%% PPHW: I don't know what the difference between these calculations is!!!
+%% You have 4 results but haven't made clear what the variations are. Do they
+%% all have decay?  I think the following is correct, but I'm not sure...
+
+Four simulations were carried out representing variations across two problem
+dimensions.  One variation compares how reactor models determine the recipe of
+used fuel.  The standard recipe reactor model produces used fuel of a fixed
+composition, regardless of the composition of the incoming fuel.  The
+alternative is a neural network depletion model provided by the cyCLASS
+package.  This model determines the composition of the used fuel depending on
+its initial composition and discharge burnup.  Both of these models were used
+without decay and with decay.
+
+As shown on Fig. \ref{fig:depletion}, the equilibrium values for recipe based
+calculation and the depletion calculation are not the same. Moreover,
+recalculating the fuel spent fuel composition for each fuel batch allows the
+cycle to reach equilibrium faster.
+
+This is caused by the slight change in the composition in the available plutonium
+(see Fig. \ref{fig:depletioncompo}): in the case of the depletion calculation
+the available plutonium contain $68\%$ of $^{239}$Pu versus $64\%$ in the recipe
+based case, and also significantly less $^{241}$Pu leading to less $^{242}$Pu in
+the cycle. The amounts of the other nuclides are very close.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{MOX_pu_composition.png}
+  \caption{Evolution of the composition of the plutonium in the fresh PWR-MOX fuel
+  using the ``neural network'' prediction models, with decay enable using recipe
+based spent fuel composition and recalculated spent fuel composition.}
+  \label{fig:depletioncompo}
+\end{figure}
+
+Those slight change in the output composition, lead to an overall decrease in
+the amount of $^{241}$Am in the fresh PWR-MOX fuel and an increase of the
+$^{239}$Pu, allowing to build fuel with a lower plutonium enrichment.
 
@@
 
-The included ANS style file and this clear example file are a panacea for
-the hours of headache that invariably results from formatting a document in
-Microsoft Word.
+This study has shown the potential impact of the decay process on the MOX-PWR fuel
+fabrication process, increasing the required amount from $1\%$ to $4\%$
+depending on the fuel fabrication model choice. The recalculation of the 
+depletion of each loaded fuel batch has consequences on the equilibrium
+state of the calculation: the reduction of fraction of $^{241}$Am and the increase of the
+fraction $^{239}$Pu in the available plutonium allows a reduction in the amount of
+plutonium in the fuel.
+
+This work has shown the strong influence of the isotopic composition on a LWR
+cycle involving plutonium recycling. Similar analysis will be conducted in the
+near future on the SFR strata of the EG29 fuel cycle, which should be less
+impacted by those isotopic changes, as fast spectrum reactor are less sensitive
+to those change.
+
+Moreover this study has demonstrated the value of the modular design of
+Cyclus, able to investigate differences between the physics fidelity of
+facility models in an isolated fashion, with other fuel cycle components
+unchanged.  In this case, additional fidelity was introduced rapidly by
+wrapping the existing neural network models made available by CLASS.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Appendix}
-
-Numbering in the appendix is different:
-\begin{equation} \label{eq:appendix}
-  2 + 2 = 5\,.
-\end{equation}
-and another equation:
-\begin{equation} \label{eq:appendix2}
-  a + b = c\,.
-\end{equation}
+%\appendix
+%\section{Appendix}
+%
+%Numbering in the appendix is different:
+%\begin{equation} \label{eq:appendix}
+%  2 + 2 = 5\,.
+%\end{equation}
+%and another equation:
+%\begin{equation} \label{eq:appendix2}
+%  a + b = c\,.
+%\end{equation}
 

### 2016-07-01 paper.tex
re-add caption on figure, add sep efficiency, stream composition, cyCLASS ref, facility labels, inventory explanation and value, clarify? the nn explanation

@@
 calculation}
-\author{Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$, Meghan B. McGarry$^{*}$,
-Arrielle C. Opotowsky$^{*}$ }
+\author{ Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$ }
 
@@
 
-%% PPHW: Need a reference to cyCLASS - perhaps tag a version and put a zip
-%% file on figshare with a DOI.
+\section{Study description}
 
-\section{Study description}
 This work compares the plutonium fraction required to build fresh MOX fuel
 using three different stream mixing models in fuel fabrication: ``fixed mixing
-ratio'', ``plutonium equivalent theory'', ``neural network'' \cite{CLASS_MLP}.
+ratio'', ``plutonium equivalent theory'', ``neural network'' \cite{Leniau2015125}.
 The first part of the study in focuses on the effect of decay on the isotopic
@@
 \subsection{Cycle}
-This analysis is focused only on the second strata of EG29, represented by a single
-PWR reactor using MOX fuel. After irradiation the uranium and the plutonium are
-separated and reprocessed to fuel the next batch of MOX fuel for the PWR.
-%% PPHW - must provide the separation parameters/efficiencies
+
+This analysis is focused only on the second strata of EG29, represented by a
+single PWR reactor using MOX fuel. After irradiation the uranium and the
+plutonium are separated and reprocessed to fuel the next batch of MOX fuel for
+the PWR. The separation efficiency is $0.988$. The separated U/Pu (``J1''
+stream) is then separated into two sub-stream, one used for new PWR deployment
+(``J1\_prime\_storage'' on Fig. \ref{fig:flow}) and the other one for the
+production the new batch of MOX fuel (``J1\_second\_storage''). The respective
+fraction of those sub-stream are $0.105$ and $0.895$.
 
@@
 
-%% PPHW - must provide the composition of the ``good'' Pu
-A stream of ``good'' quality plutonium coming from a hypothetical irradiated
-SFR blanket is represented by a storage facility. 
-%% PPHW - which facility?  which label - there are two.
-The impact of the decay on this stored Pu
-is limited, as the content in $^{241}$Pu is almost negligible.  In order to
-build the first batch of fuel, an initial quantity of stored Pu has also been provided.
-%% PPHW - how much?
-In order to limit the effect of decay of this storage the initial inventory have been
-tuned to be as small as possible, preventing any unnecessary accumulation of plutonium.
-%% PPHW - is this about the initial inventory or the capacity of the storage facility
-%%      - the latter seems to be about capacity
+A stream (``E3'') of ``good'' quality plutonium coming from a hypothetical irradiated
+SFR blanket is represented by a storage facility
+(``E3\_second\_limited\_storage`` on Fig. \ref{fig:flow}).
+
+\begin{table*}[htb]
+  \centering
+  \begin{tabular}{llllllllllll}\toprule
+    Stream 
+    & $^{234}$U   & $^{235}$U   & $^{236}$U   & $^{238}$U   
+    & $^{238}$Pu  & $^{239}$Pu  & $^{240}$Pu  & $^{241}$Pu  & $^{242}$Pu 
+    & $^{241}$Am  & F.P. \\ \midrule
+    E3 [\%]
+    & $0.002$   & $0.203$    & $0.083$   & $81.082$
+    & $0.0087$  & $17.9764$  & $0.6166$  & $0.0216$  & $0.0007$
+    & $0$         & $0$ \\
+    J1 [\%]
+    & $0$       & $0$        & $0$       & $93.632$
+    & $0.1216$  & $2.7058$   & $1.8193$  & $0.7402$  & $0.6833$
+    & $0.2978$  & $0$ \\
+    \bottomrule
+  \end{tabular}
+  \caption{Streams compositions in percentage by mass.}
+  \label{tab:strem_compo}
+\end{table*}
+
+The impact of the decay on this stored Pu is limited, as the content in
+$^{241}$Pu is almost negligible (see Tab. \ref{tab:stream_compo}).
+
+In order to build the first batches of fuel, an initial quantity of 225t has
+also been provided in the ``J1\_second\_storage'', which corresponds to 3 times
+the requirement on ``J1'' stream to build the PWR-MOX fuel for full PWR
+core.
 
@@
 ratio'', ``Pu-equivalent'' and ``neural network''.
-The fix mixing ratio is based on a user-defined ratio for the different stream mixing. The
-``Pu-equivalent'' model finds the mixing ratio that results in an initial reactivity
-that matches that of the requested MOX fuel recipe.  This ratio may change as the 
-composition of the incoming streams changes.  As the requested fuel
-composition corresponds to the fuel composition built with the ''fix mixing
-ratio`` model, the results of those 2 models are expected to be similar.
-The ``neural network'' model attempts to achieve a given reactivity at the end of a 
-life for a given batch of fuel ($50~$GWd/t in this study). The
-$<k_{infty}>$ used in this study is 1.034 \cite{???}. The neural network in this
-model has been pre-trained on several different depletion calculations,
-allowing it to predict the correct plutonium fraction required, depending
-on the composition of that plutonium.
+The fix mixing ratio is based on a user-defined ratio for the J1 and E3 stream
+mixing. The respective mixing ratio used for J1 and E3 stream are 
+$0.8357$ and $0.1643$.
+The ``Pu-equivalent'' model finds the mixing ratio that results in an initial
+reactivity that matches that of the requested MOX fuel recipe.  This ratio may
+change as the composition of the incoming streams changes.  As the requested
+fuel composition corresponds to the fuel composition built with the ''fix mixing
+ratio`` model, the results of those 2 models are expected to be similar.  The
+``neural network'' model attempts to achieve a given reactivity at the  end of
+cycle reactivity of the whole core for a multi-batch core ($50~$GWd/t in this
+study). The $k_{infty}$ used in this study is 1.034, assuming the reactivity of
+the full core is the mean reactivity of the batches. The neural network in this
+model has been pre-trained on several different depletion calculations, allowing
+it to predict the correct plutonium fraction required, depending on the
+composition of that plutonium.
 
-%% PPHW - is this end of cycle reactivity of the whole core for a multi-batch core?
-%%      - or is it end of life reactivity for a given batch?
-%%      - 1.034 and 50 GWd/t don't seem to go together
+Because the neural network model allows only to mix a plutonium stream into a
+uranium stream, slight modification have been made on the cycle: in both ``J1''
+and ``E3'' streams uranium and plutonium are separated, the uranium and
+plutonium sub-streams are mix together to build one stream of pure uranium and
+one stream of pure plutonium.
 
@@
 the PWR-MOX fuel (using the neural network modeling for fuel fabrication) for
-the recipe based output composition versus a compisition calculated by depletion.
-To caluclate the depletion for each fuel batch loaded in the PWR reactor, another 
+the recipe based output composition versus a composition calculated by depletion.
+To calculate the depletion for each fuel batch loaded in the PWR reactor, another 
 neural network is used to predict the macroscopic cross section of the
-fuel \cite{NN_CLASS} (only fission, capture and n,2n reactions are considered). The
+fuel \cite{Leniau2015125} (only fission, capture and n,2n reactions are considered). The
 depletion calculation is done renormalizing the neutron flux to maintain a
@@
   \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
-  using the 3 predicted models, without considering decay.}
+  using the 3 predicted models: ``fix mixing ratio'' (``fix'', blue), ``Pu-equivalent''
+  (``Pu-eq'', green) and ``Neural Network'' (``NN'', red), without considering decay.}
   \label{fig:nod}
 \end{figure}
-
-%% PPHW - need better figure legend text so that readers know what they are
-%% looking at
 
@@
   \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
-  using the 3 prediction models, with and without decay enable.}
+    using the 3 prediction models: ``fix mixing ratio'' (``fix'', blue),
+    ``Pu-equivalent'' (``Pu-eq'', green) and ``Neural Network'' (``NN'', red),
+    with (plain line) and without (dash line) decay enable.} 
   \label{fig:d}
 \end{figure}
-
-%% PPHW - need better color and symbol choices to facilitate comparison
-%%      - different models use different colors and decay/no decay uses
-%%      -  different symbols (for example)
 
@@
   \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
-  using the ``neural network'' prediction models, with decay enable using recipe
-based spent fuel composition and recalculated spent fuel composition.}
+    using the ``Neural Network'' prediction models, using recipe based spent
+    fuel composition (red) and recalculated spent fuel composition (orange),
+    with (plain line) and without (dash line) decay enable.}
   \label{fig:depletion}
@@
   \caption{Evolution of the composition of the plutonium in the fresh PWR-MOX fuel
-  using the ``neural network'' prediction models, with decay enable using recipe
-based spent fuel composition and recalculated spent fuel composition.}
+  using the ``Neural Network'' prediction models, with decay enable using recipe
+  based spent fuel composition (plain line) and recalculated spent fuel
+  composition (dash line).}
   \label{fig:depletioncompo}

### 2016-07-01 paper.tex
correction on depletion discussion

@@
 the PWR-MOX fuel (using the neural network modeling for fuel fabrication) for
-the recipe based output composition versus a composition calculated by depletion.
-To calculate the depletion for each fuel batch loaded in the PWR reactor, another 
-neural network is used to predict the macroscopic cross section of the
-fuel \cite{Leniau2015125} (only fission, capture and n,2n reactions are considered). The
-depletion calculation is done renormalizing the neutron flux to maintain a
-constant power in the reactor.
+the recipe based output composition versus a composition calculated by
+depletion.  To calculate the depletion for each fuel batch loaded in the PWR
+reactor, another neural network is used to predict the macroscopic cross section
+of the fuel \cite{Leniau2015125} (only fission, capture and n,2n reactions are
+considered). The depletion calculation is done renormalizing the neutron flux to
+maintain a constant power in the reactor.
 
@@
 As observed in Fig. \ref{fig:nod}, despite the fact that the different models
-were not tuned to
-describe the exact same PWR concept, the results without decay are very
-close. They all predict a constant plutonium fraction around $8\%$ of plutonium
-in the fresh PWR-MOX fuel.
+were not tuned to describe the exact same PWR concept, the results without decay
+are very close. They all predict a constant plutonium fraction around $8\%$ of
+plutonium in the fresh PWR-MOX fuel.
 
@@
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
   \centering
@@
     ``Pu-equivalent'' (``Pu-eq'', green) and ``Neural Network'' (``NN'', red),
-    with (plain line) and without (dash line) decay enable.} 
+    with (solid line) and without (dash line) decay enable.} 
   \label{fig:d}
@@
     fuel composition (red) and recalculated spent fuel composition (orange),
-    with (plain line) and without (dash line) decay enable.}
+    with (solid line) and without (dash line) decay enable.}
   \label{fig:depletion}
 \end{figure}
-
-%% PPHW: - I don't know which answer is which !?!?  bad legend labels!
-
-%% PPHW: I don't know what the difference between these calculations is!!!
-%% You have 4 results but haven't made clear what the variations are. Do they
-%% all have decay?  I think the following is correct, but I'm not sure...
 
@@
 
-This is caused by the slight change in the composition in the available plutonium
-(see Fig. \ref{fig:depletioncompo}): in the case of the depletion calculation
-the available plutonium contain $68\%$ of $^{239}$Pu versus $64\%$ in the recipe
-based case, and also significantly less $^{241}$Pu leading to less $^{242}$Pu in
-the cycle. The amounts of the other nuclides are very close.
+This is caused by the slight change in the composition in the available
+plutonium (see Fig. \ref{fig:depletioncompo}): in the case of the depletion
+calculation the available plutonium contain $68\%$ of $^{239}$Pu versus $64\%$
+in the recipe based case, and also less $^{242}$Pu and $^{241}$Am, respectively
+$4.8\%$ and $5.4\%$ in the depletion case versus $7.3\%$ and $6.7\%$. The
+amounts of the other nuclides are very close.
 

### 2016-07-01 paper.tex
first add of FCDP cycle
increase line size for figure, add NEUP logo and Acknowledgments

@@
 $^{*}$University of Wisconsin-Madison, WI
-\and
-%$^{\dagger}$State Capitol Building, Springfield, IL
 }
@@
 
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.48\textwidth]{FCDP_cycle}
+  \caption{Schematic representation of the EG29 fuel cycle taken from \cite{FCDP}.}
+  \label{fig:FCDP}
+\end{figure}
 %% PPHW: Can we add the official FCDP images
@@
 plutonium sub-streams are mix together to build one stream of pure uranium and
-one stream of pure plutonium.
+one stream of pure plutonium. That is why, when comparing the different fuel
+fabrication models only the total plutonium enrichement are compared.
 
@@
 and thus different impacts from the decay of this plutonium.
-This calculation shows a change from 10 to 30\% in the mixing ratio required to
-build the proper PWR-MOX fuel. This kind of plutonium accumulation can
+This calculation results in a change in the mixing ratio required to build the
+PWR-MOX fuel of 10 to 30\%. This kind of plutonium accumulation can
 unexpectedly occur in a real fuel cycle and might need to be considered in a
 complete fuel cycle transition study.
-%% PPHW - do you plot results for this?
 
@@
 \section{Acknowledgments} 
-Shall we acknowledge anyone ? DOE ? FCO ?
+This work was funded in part by the Nuclear Energy University Program 
+(DE-NE0000673) and Idaho National Laboratory (154956).
+\begin{center}
+\includegraphics[width=1.5in]{neup_logo_large.jpg}
+\end{center}
 

### 2016-07-01 paper.tex
remove nad lines...
correct 1 typo...

@@
 one stream of pure plutonium. That is why, when comparing the different fuel
-fabrication models only the total plutonium enrichement are compared.
+fabrication models only the total plutonium enrichment are compared.
 
@@
 
-Another analysis was performed to evaluate the impact of the depletion
-calculation on a fuel cycle macroscopic (???) level.
+Four simulations were carried out representing variations across two problem
+dimensions.  One variation compares how reactor models determine the recipe of
+used fuel.  The standard recipe reactor model produces used fuel of a fixed
+composition, regardless of the composition of the incoming fuel.  The
+alternative is a neural network depletion model provided by the cyCLASS
+package.  This model determines the composition of the used fuel depending on
+its initial composition and discharge burnup.  Both of these models were used
+without decay and with decay.
 
@@
 \end{figure}
-
-Four simulations were carried out representing variations across two problem
-dimensions.  One variation compares how reactor models determine the recipe of
-used fuel.  The standard recipe reactor model produces used fuel of a fixed
-composition, regardless of the composition of the incoming fuel.  The
-alternative is a neural network depletion model provided by the cyCLASS
-package.  This model determines the composition of the used fuel depending on
-its initial composition and discharge burnup.  Both of these models were used
-without decay and with decay.
 

### 2016-07-01 paper.tex
final edits

@@
 All the calculation of this study have been performed using the Cyclus fuel cycle
-tool\cite{CYCLUS}. The facility models are from the Cycamore package, developed by the
+simulator framework\cite{CYCLUS}. The facility models are from the Cycamore package, developed by the
 Cyclus team, and containing a Pu-equivalent fuel fabrication model as well as
@@
 ratio'', ``plutonium equivalent theory'', ``neural network'' \cite{Leniau2015125}.
-The first part of the study in focuses on the effect of decay on the isotopic
+The first part of the study focuses on the effect of decay on the isotopic
 composition of the reprocessed plutonium and its impact on fuel fabrication
@@
 ratio'', ``Pu-equivalent'' and ``neural network''.
-The fix mixing ratio is based on a user-defined ratio for the J1 and E3 stream
-mixing. The respective mixing ratio used for J1 and E3 stream are 
-$0.8357$ and $0.1643$.
+The fixed mixing ratio is based on a user-defined ratio for the J1 and E3 stream
+mixing, with mixing ratio of $0.8357$ and $0.1643$, respectively.
 The ``Pu-equivalent'' model finds the mixing ratio that results in an initial
@@
 change as the composition of the incoming streams changes.  As the requested
-fuel composition corresponds to the fuel composition built with the ''fix mixing
-ratio`` model, the results of those 2 models are expected to be similar.  The
-``neural network'' model attempts to achieve a given reactivity at the  end of
-cycle reactivity of the whole core for a multi-batch core ($50~$GWd/t in this
+fuel composition corresponds to the fuel composition built with the ``fix mixing
+ratio'' model, the results of those 2 models are expected to be similar.  The
+``neural network'' model attempts to achieve a given whole core end of cycle 
+reactivity for a multi-batch core with specified discharge burnup ($50~$GWd/t in this
 study). The $k_{infty}$ used in this study is 1.034, assuming the reactivity of
@@
 
-Because the neural network model allows only to mix a plutonium stream into a
+Because the neural network model allows only mixing of a plutonium stream into a
 uranium stream, slight modification have been made on the cycle: in both ``J1''
@@
 
-Because of these models have not necessary been tuned on exactly the same
+Because these models have not necessarily been tuned on exactly the same
 PWR configuration and parameters, this analysis focuses on the differences
@@
 
-The second part of the study compares the amount of plutonium require to build
+The second part of the study compares the amount of plutonium required to build
 the PWR-MOX fuel (using the neural network modeling for fuel fabrication) for
@@
   using the 3 predicted models: ``fix mixing ratio'' (``fix'', blue), ``Pu-equivalent''
-  (``Pu-eq'', green) and ``Neural Network'' (``NN'', red), without considering decay.}
+  (``Pu-eq'', green) and ``neural network'' (``NN'', red), without considering decay.}
   \label{fig:nod}
@@
     using the 3 prediction models: ``fix mixing ratio'' (``fix'', blue),
-    ``Pu-equivalent'' (``Pu-eq'', green) and ``Neural Network'' (``NN'', red),
+    ``Pu-equivalent'' (``Pu-eq'', green) and ``neural network'' (``NN'', red),
     with (solid line) and without (dash line) decay enable.} 
@@
 
-A last calculation, on decay have been performed using the ``Pu-equivalent''
+Finally, a set of calculations with decay have been performed using the ``Pu-equivalent''
 fabrication model, increasing by a factor 2, 5 and 10 the amount of plutonium in
@@
 used fuel.  The standard recipe reactor model produces used fuel of a fixed
-composition, regardless of the composition of the incoming fuel.  The
+composition, regardless of the composition of the incoming fuel.  In this case, the
 alternative is a neural network depletion model provided by the cyCLASS
-package.  This model determines the composition of the used fuel depending on
-its initial composition and discharge burnup.  Both of these models were used
+package.  This model determines the macroscopic cross sections of the fuel as a
+function of burnup depending on its initial composition and discharge burnup. It then
+performs a simple calculation to allow the composition to evolve. Both of these models were used
 without decay and with decay.
@@
   \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
-    using the ``Neural Network'' prediction models, using recipe based spent
+    using the ``neural network'' prediction models, using recipe based spent
     fuel composition (red) and recalculated spent fuel composition (orange),
@@
 calculation the available plutonium contain $68\%$ of $^{239}$Pu versus $64\%$
-in the recipe based case, and also less $^{242}$Pu and $^{241}$Am, respectively
+in the recipe based case, and also less $^{242}$Pu and $^{241}$Am: respectively
 $4.8\%$ and $5.4\%$ in the depletion case versus $7.3\%$ and $6.7\%$. The
@@
   \caption{Evolution of the composition of the plutonium in the fresh PWR-MOX fuel
-  using the ``Neural Network'' prediction models, with decay enable using recipe
+  using the ``neural network'' prediction models, with decay enable using recipe
   based spent fuel composition (plain line) and recalculated spent fuel
@@
 the amount of $^{241}$Am in the fresh PWR-MOX fuel and an increase of the
-$^{239}$Pu, allowing to build fuel with a lower plutonium enrichment.
+$^{239}$Pu, allowing fuel to be built with a lower plutonium enrichment.
 

### 2016-08-09 paper.tex
update title
correction of Tab label name
fix major issue with non referenced numbers

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Evidence of the necessity of isotopic precise calculation in fuel cycle
-calculation}
+\title{Impact of Isotope Fidelity on Fuel Cycle Calculations}
 \author{ Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$ }
@@
 \usepackage{microtype} % improves typography for PDF
+\usepackage{hyperref}
 
@@
 
-All the calculation of this study have been performed using the Cyclus fuel cycle
-simulator framework\cite{CYCLUS}. The facility models are from the Cycamore package, developed by the
-Cyclus team, and containing a Pu-equivalent fuel fabrication model as well as
-a simple fixed mixing ratio fuel fabrication model. A new neural network model has
-also been contributed to the Cyclus environment using the cyCLASS tool\cite{cyCLASS}, 
-allowing the use of the fuel fabrication and depletion models from the CLASS tool
-\cite{CLASS} in Cyclus.
+All the calculation of this study have been performed using the Cyclus fuel
+cycle simulator framework\cite{CYCLUS}. The facility models are from the
+Cycamore package, developed by the Cyclus team, and containing a Pu-equivalent
+fuel fabrication model as well as a simple fixed mixing ratio fuel fabrication
+model. A new neural network model has also been contributed to the Cyclus
+environment using the cyCLASS tool\cite{cyCLASS}, allowing the use of the fuel
+fabrication and depletion models from the CLASS tool \cite{CLASS} in Cyclus.
 
@@
 plutonium are separated and reprocessed to fuel the next batch of MOX fuel for
-the PWR. The separation efficiency is $0.988$. The separated U/Pu (``J1''
-stream) is then separated into two sub-stream, one used for new PWR deployment
-(``J1\_prime\_storage'' on Fig. \ref{fig:flow}) and the other one for the
-production the new batch of MOX fuel (``J1\_second\_storage''). The respective
-fraction of those sub-stream are $0.105$ and $0.895$.
+the PWR. As no loss are associated to the fabrication process, the separation
+efficiency is set at $0.988$, which corresponding to the $1\%$ loss in
+separation and the $0.2\%$ during fabrication as specified in \cite{FCDP}).
+About $10\%$ of this U/Pu stream (``J1`` stream) is arbitrary set aside in order
+to support an hypothetical new PWR deployment (``J1\_prime\_storage), the
+remaining $90\%$ is used for the production the new batch of MOX fuel
+(``J1\_second\_storage'').
 
@@
   \centering
+  \caption{Streams compositions in percentage by mass.}
   \begin{tabular}{llllllllllll}\toprule
@@
   \end{tabular}
-  \caption{Streams compositions in percentage by mass.}
-  \label{tab:strem_compo}
+  \label{tab:stream_compo}
 \end{table*}

### 2016-08-09 paper.tex
addresing minor issues

@@
   \caption{Schematic representation of the fuel cycle. Quantities on the row
-  represents the cumulative amount in kg of material exchanged between two
+  represent the cumulative amount in kg of material exchanged between two
   facilities in the calculation using ``pu-equivalent'' for fuel fabrication
@@
 coming from the $^{241}$Am. For the calculation using ``neural network'' fuel
-fabrication modeling the effect is very quickly increasing to $13\%$ and then
+fabrication modeling the effect very quickly increases to $13\%$ and then
 slowing stabilizing as the plutonium composition approaches an equilibrium.
@@
 PWR-MOX fuel fabrication.
-
-%% PPHW: why is the Pu-equiavlent model so bad?
 

### 2018-01-25 paper.tex
adding the theory

--- 2016-07-01 paper.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Evidence of the necessity of isotopic precise calculation in fuel cycle
-calculation}
-\author{ Baptiste Mouginot$^{*}$, Paul P.H. Wilson$^{*}$, Robert W. Carlsen$^{*}$ }
+\title{An Improved ANS Transaction Template}
+\author{Baptiste Mouginot,$^{*}$ Kathie Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
 
@@
 
-\email{mouginot@wisc.edu \and paul.wilson@wisc.edu}
+\email{mouginot@wisc.edu \and mummah@wisc.edu \and paul.wilson@wisc.edu}
 
 % Optional disclaimer: remove this command to hide
-%\disclaimer{Notice: this manuscript is a work of fiction. Any resemblance to
-%actual articles, living or dead, is purely coincidental.}
+% \disclaimer{Notice: this manuscript is a work of fiction. Any resemblance to
+% actual articles, living or dead, is purely coincidental.}
 
@@
 
-The purpose of this study is to examine the importance of the isotopic
-composition of plutonium on PWR MOX fuel fabrication as part of a multi-tiered
-fuel cycle, and the effect of its evolution during a transition. Two main
-effects can modify the isotopic composition of the plutonium used to build the
-PWR-MOX fuel: decay and depletion.
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
 
-This analysis is based on a transition of the nuclear fuel cycle
-to a configuration identified as ``Evaluation Group 29'' or ``EG29'', in the
-recently-published Evaluation and Screening (E\&S) report \cite{ES}.  The EG29 fuel
-cycle corresponds to a double strata fleet. The first stratum is composed of
-sodium-cooled fast reactors (SFRs) multi-recycling plutonium. Surplus
-plutonium is sent to the second stratum composed of pressurized water
-reactors with full mixed oxide (U/Pu)O$_{2}$ cores (MOX-PWRs).  The PWR stratum
-is also multi-recycling its plutonium. The target energy generation ratio for
-the final EG29 system is 70:30 (SFR:PWR), with a 1\% annual growth in nuclear
-energy demand.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Theory}
+
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+Some text for introduction etc\ldots
+
+\section{Cascade Enrich Construction}
+\subsection{Centrifuge properties}
+In the present work, the analytical solution by R\"aetz \cite{ref} of the
+differential equation for the gas centrifuge as described in \cite{Glaser2008}
+is used. The different parameter of the centrifuges, such as average temperature
+of the gas, rotation speed, height, feed flow rate, diameter, pressure ratio,
+countercurent ratio, efficiency have been choosen to match the cascade design
+describe in \cite{glaser2008} and \cite{Walker2017} using P-1 centrifuges and
+repect the JCPOA aggrement.
+
+\subsection{Cascade Design}
+
+The cascade build as an ideal cascade, taht is to day, $\alpha =\beta = const$
+for all stage of the cascade, where $\alpha$ and $\beta$ respectively represent
+the feed to product and the feed to tail enrichment factors. 
+$\alpha$ can be expressed as a function of the feed rate $F$, $\delta U(\theta)$ and $\theta$,
+and $\beta$ as a function of $alpha$ and $\theta$: 
+\begin{subequations} \label{eqs:alphabeta}
+    \begin{equation} \label{eq:alpha}
+    \alpha = \sqrt{\frac{2\delta U}{F} \frac{1-\theta}{\theta}}+1
+\end{equation}
+\\
+\begin{equation}\label{eq:beta}
+    \beta = R 
+              \dfrac{1 - \dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
+                   {\dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}} 
+\end{equation}
+\end{subequations}
+
+From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine the cut value
+(all other centrifuge parameters been fixed) allowing the have $\alpha=\beta$
+required to build an ideal cascade.
+
+As an ideal cascade is build, we only need to determine the proper cut value of
+each stages, $\theta_{i}$, the value of $\alpha_{i}$ and $\beta_{i}$ remain
+constant over the different stages.
+It can be shown that $\theta_{i}$ can be computed from $\alpha$,
+$\beta$ values and the feed assay, $N_{i}$:
+\begin{eqnarray}
+    \theta_{i} &=& \dfrac{N_{i} - N''_{i}}{N'_{i}-N''_{i}}\nonumber\\
+           &=& \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
+           \dfrac{1}{1 + \beta/R_{i}}} 
+\end{eqnarray}
+
+This algorithm assumes that the corresponding $\delta U$ (not re-computed) can be
+achieve with the centrifuges.  With $\theta_{i}$ determined it is possible to
+compute the product and the tail assay from $\alpha$ and $\beta$.
+The design of the cascade is performed through 2 steps. First one determines the
+number of stages and their configuration, adding stages following the previously
+described procedure, until $N'_{last} > N'_{requested}$ and $N''_{last} <
+N''_{requested}$. (Note that $N'_{last}$ corresponds to the product assay of the
+last enrichment stage, and $N''_{last}$ to the tail assay of the last stripping
+stage). This allows to determine the number of enriching and stripping stages as
+well as their enrichment properties ($N_{i}$, $N'_{i}$,
+$N''_{i}$,$\theta_{i}$i).
+
+The second steps is dedicated on populating the cascade with centrifuges. One
+first solves the linear flow equation to determine the theoretical flow in the
+cascade:
+\begin{strip}
+\begin{equation}
+\setcounter{MaxMatrixCols}{20}
+\begin{bmatrix}
+-1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
+\theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
+           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
+0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
+           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
+0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
+0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
+\end{bmatrix}
+\times 
+\begin{bmatrix}
+     F_{S}   \\
+     F_{S+1} \\
+     \cdots  \\
+     F_{0}   \\
+    \cdots   \\
+    F_{E-1}  \\
+    F_{E}
+\end{bmatrix}
+=
+\begin{bmatrix}
+     0   \\
+     0 \\
+     \cdots  \\
+     F   \\
+    \cdots   \\
+    0  \\
+    0
+\end{bmatrix}
+\label{eq:flow}
+\end{equation}
+\end{strip}
+Once the relative flow on the different stages $F_{i}$ have been determined, the
+cascade can be populated with actual machines, feeling up the different stages
+until either the maximum number available of machines, either the maximum feed
+flow is reached.
+
+\subsection{Response to an non-ideal feed - $\theta_{i} = const$ hypothesis}
+
+As it is practically impossible to get reliable information about tuning a
+cascade when feed with a different feed assay than the one used for its design.
+Two different tuning have been considered, the first one makes the hypothesis
+that no physical change are made to the different centrifuges: the cut on the
+machine remains the same at every stage. The second considered tuning option,
+keep the enrichment factor constant implying to modify the cuts and then the
+different flows.
+
+The first tuning method assumes the cut of each stages are constant. As $\delta
+U$ and $\alpha$ do not depend on the stage feed assay $N'$,the feed to product
+ratio $\alpha$ do not change across the different stages. According to equation
+\eqref{eq:beta} , when $\alpha$ and $\theta$ remaining, if the feed assay,
+$N$, change $\beta$ has to change accordingly.  This will lead to brake of the
+ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.
+
+In order to compute the stage proper product and tails assay at each stages, one
+need to blend the tails and the product from respectively the next and the
+previous stage in order to determine the correct stage feed assay. As this is a
+obvious cycling problem, it has been chosen to solve it iteratively: all feed
+assay are iteratively updated, blending the proper product and tail, then using
+the updated feed assay, the new product and tail assay are recomputed. This
+process it repeated until the change in the different assays is smaller than the
+set precision (1e-8 by default).
+
+Other hypothesis will be explored in the future, such as maintaining the ideal
+stage of the cascade through a tunning of the cuts values $\theta_{i}$ of each
+stage of the cascade, or maintaining $\alpha\beta = const$ as described in
+\cite{walker2017}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results and Analysis}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Subsection Goes Here}
+\begin{equation} \label{eq:marshak}
+  4 J^- = \phi + 2 D \vec{n} \vd \grad \phi \,.
+\end{equation}
+If we so choose, we can effortlessly reference the equation later.
 
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{FCDP_cycle}
-  \caption{Schematic representation of the EG29 fuel cycle taken from \cite{FCDP}.}
-  \label{fig:FCDP}
-\end{figure}
-%% PPHW: Can we add the official FCDP images
-
-All the calculation of this study have been performed using the Cyclus fuel cycle
-simulator framework\cite{CYCLUS}. The facility models are from the Cycamore package, developed by the
-Cyclus team, and containing a Pu-equivalent fuel fabrication model as well as
-a simple fixed mixing ratio fuel fabrication model. A new neural network model has
-also been contributed to the Cyclus environment using the cyCLASS tool\cite{cyCLASS}, 
-allowing the use of the fuel fabrication and depletion models from the CLASS tool
-\cite{CLASS} in Cyclus.
-
-\section{Study description}
-
-This work compares the plutonium fraction required to build fresh MOX fuel
-using three different stream mixing models in fuel fabrication: ``fixed mixing
-ratio'', ``plutonium equivalent theory'', ``neural network'' \cite{Leniau2015125}.
-The first part of the study focuses on the effect of decay on the isotopic
-composition of the reprocessed plutonium and its impact on fuel fabrication
-depending on the chosen stream mixing model.  The second part of the study,
-compares the impact on fresh fuel compositions when used fuel is based on a
-depletion calculation instead of a fixed recipe, using the neural network fuel
-fabrication model, also including the impact of decay.
-
-\subsection{Cycle}
-
-This analysis is focused only on the second strata of EG29, represented by a
-single PWR reactor using MOX fuel. After irradiation the uranium and the
-plutonium are separated and reprocessed to fuel the next batch of MOX fuel for
-the PWR. The separation efficiency is $0.988$. The separated U/Pu (``J1''
-stream) is then separated into two sub-stream, one used for new PWR deployment
-(``J1\_prime\_storage'' on Fig. \ref{fig:flow}) and the other one for the
-production the new batch of MOX fuel (``J1\_second\_storage''). The respective
-fraction of those sub-stream are $0.105$ and $0.895$.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.48\textwidth]{flow}
-  \caption{Schematic representation of the fuel cycle. Quantities on the row
-  represents the cumulative amount in kg of material exchanged between two
-  facilities in the calculation using ``pu-equivalent'' for fuel fabrication
-  modeling with decay activated.}
-  \label{fig:flow}
+  \includegraphics{example_figure}
+  \caption{Captions are flush with the left.}
+  \label{fig:voltage}
 \end{figure}
 
-A stream (``E3'') of ``good'' quality plutonium coming from a hypothetical irradiated
-SFR blanket is represented by a storage facility
-(``E3\_second\_limited\_storage`` on Fig. \ref{fig:flow}).
-
+Later on, we can include a table, even one that spans two columns such as
+Table~\ref{tab:widetable}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table*}[htb]
   \centering
-  \begin{tabular}{llllllllllll}\toprule
-    Stream 
-    & $^{234}$U   & $^{235}$U   & $^{236}$U   & $^{238}$U   
-    & $^{238}$Pu  & $^{239}$Pu  & $^{240}$Pu  & $^{241}$Pu  & $^{242}$Pu 
-    & $^{241}$Am  & F.P. \\ \midrule
-    E3 [\%]
-    & $0.002$   & $0.203$    & $0.083$   & $81.082$
-    & $0.0087$  & $17.9764$  & $0.6166$  & $0.0216$  & $0.0007$
-    & $0$         & $0$ \\
-    J1 [\%]
-    & $0$       & $0$        & $0$       & $93.632$
-    & $0.1216$  & $2.7058$   & $1.8193$  & $0.7402$  & $0.6833$
-    & $0.2978$  & $0$ \\
+\begin{tabular}{llllllllll}\toprule
+      & $\phi_T(0)$      & $\phi_T(10)$      & $\phi_T(20)$      &
+      $\phi_D(0)$      & $\phi_D(10)$      & $\phi_D(20)$      & $\rho$      &
+      $\varepsilon$      & $N_\text{it}$
+\\ \midrule
+$c=0.999$  & 0.9038 & 20.63 & 31.24 & 0.9087 & 20.63 & 31.23 & 0.2192 & $10^{-7}$ & 15
+\\
+$c=0.990$  & 0.3675 & 13.04 & 24.7 & 0.3696 & 13.04 & 24.69 & 0.2184 & $10^{-7}$ & 15
+\\
+$c=0.900$  & 0.009909 & 4.776 & 17.64 & 0.009984 & 4.786 & 17.63 & 0.2118 & $10^{-7}$ & 14
+\\
+$c=0.500$  & $6.069\times 10^{-5}$ & 2.212 & 15.53 & 6.213$\times 10^{-5}$ & 2.239 & 15.53 & 0.2068 & $10^{-7}$ & 13
+\\
 \bottomrule
 \end{tabular}
-  \caption{Streams compositions in percentage by mass.}
-  \label{tab:strem_compo}
+  \caption{This is an example of a really wide table which might not normally
+  fit in the document.}
+  \label{tab:widetable}
 \end{table*}
-
-The impact of the decay on this stored Pu is limited, as the content in
-$^{241}$Pu is almost negligible (see Tab. \ref{tab:stream_compo}).
-
-In order to build the first batches of fuel, an initial quantity of 225t has
-also been provided in the ``J1\_second\_storage'', which corresponds to 3 times
-the requirement on ``J1'' stream to build the PWR-MOX fuel for full PWR
-core.
-
-\subsection{Fabrication model}
-Three different ways to model the fuel fabrication have been used: ``fix mixing
-ratio'', ``Pu-equivalent'' and ``neural network''.
-The fixed mixing ratio is based on a user-defined ratio for the J1 and E3 stream
-mixing, with mixing ratio of $0.8357$ and $0.1643$, respectively.
-The ``Pu-equivalent'' model finds the mixing ratio that results in an initial
-reactivity that matches that of the requested MOX fuel recipe.  This ratio may
-change as the composition of the incoming streams changes.  As the requested
-fuel composition corresponds to the fuel composition built with the ``fix mixing
-ratio'' model, the results of those 2 models are expected to be similar.  The
-``neural network'' model attempts to achieve a given whole core end of cycle 
-reactivity for a multi-batch core with specified discharge burnup ($50~$GWd/t in this
-study). The $k_{infty}$ used in this study is 1.034, assuming the reactivity of
-the full core is the mean reactivity of the batches. The neural network in this
-model has been pre-trained on several different depletion calculations, allowing
-it to predict the correct plutonium fraction required, depending on the
-composition of that plutonium.
-
-Because the neural network model allows only mixing of a plutonium stream into a
-uranium stream, slight modification have been made on the cycle: in both ``J1''
-and ``E3'' streams uranium and plutonium are separated, the uranium and
-plutonium sub-streams are mix together to build one stream of pure uranium and
-one stream of pure plutonium. That is why, when comparing the different fuel
-fabrication models only the total plutonium enrichment are compared.
-
-Because these models have not necessarily been tuned on exactly the same
-PWR configuration and parameters, this analysis focuses on the differences
-in the results due to the change in model rather than the results themselves.
-
-The second part of the study compares the amount of plutonium required to build
-the PWR-MOX fuel (using the neural network modeling for fuel fabrication) for
-the recipe based output composition versus a composition calculated by
-depletion.  To calculate the depletion for each fuel batch loaded in the PWR
-reactor, another neural network is used to predict the macroscopic cross section
-of the fuel \cite{Leniau2015125} (only fission, capture and n,2n reactions are
-considered). The depletion calculation is done renormalizing the neutron flux to
-maintain a constant power in the reactor.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Notice how the table reference uses a Roman numeral
+for its numbering scheme, whereas the figure reference uses an Arabic numeral.
+For one-column tables, use the \verb|table| environment; two-column tables use
+\verb|table*|. The same applies to figures.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Decay}
+\subsection{Another Subsection}
+Excessive sectioning in a three-page document is discouraged, but here are more
+subsections to demonstrate compliance with the ANS formatting guidelines.
 
-As observed in Fig. \ref{fig:nod}, despite the fact that the different models
-were not tuned to describe the exact same PWR concept, the results without decay
-are very close. They all predict a constant plutonium fraction around $8\%$ of
-plutonium in the fresh PWR-MOX fuel.
+\subsubsection{Third-level Heading}
+This subsubsection shows compliance with the ANS-specified standard. This level
+of heading should be used rarely.
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.48\textwidth]{nodecay_pu_contribution.png}
-  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
-  using the 3 predicted models: ``fix mixing ratio'' (``fix'', blue), ``Pu-equivalent''
-  (``Pu-eq'', green) and ``neural network'' (``NN'', red), without considering decay.}
-  \label{fig:nod}
-\end{figure}
-
-With decay turned on, see Fig. \ref{fig:d}, results for the ``fix mixing ratio''
-calculation see a small decrease of the fraction of plutonium in the fuel,
-corresponding to the decay of $^{241}$Pu into $^{241}$Am.  For the
-``Pu-equivalent'' modeling we can observe a slight increase of the fraction of
-plutonium, which is required to compensate for the negative reactivity effect
-coming from the $^{241}$Am. For the calculation using ``neural network'' fuel
-fabrication modeling the effect is very quickly increasing to $13\%$ and then
-slowing stabilizing as the plutonium composition approaches an equilibrium.
-
-\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.48\textwidth]{decay_pu_contribution.png}
-  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
-    using the 3 prediction models: ``fix mixing ratio'' (``fix'', blue),
-    ``Pu-equivalent'' (``Pu-eq'', green) and ``neural network'' (``NN'', red),
-    with (solid line) and without (dash line) decay enable.} 
-  \label{fig:d}
-\end{figure}
-
-As the calculation using ``neural network'' fabrication modeling requires more
-plutonium than the cycle can produce, the initial inventory has been set to a
-higher values, increasing the plutonium decay effect. Nevertheless this shows
-the strong impact of the presence of $^{241}$Am with the plutonium used for the
-PWR-MOX fuel fabrication.
-
-%% PPHW: why is the Pu-equiavlent model so bad?
-
-Finally, a set of calculations with decay have been performed using the ``Pu-equivalent''
-fabrication model, increasing by a factor 2, 5 and 10 the amount of plutonium in
-the startup inventory. This mimics different degrees of a plutonium accumulation,
-and thus different impacts from the decay of this plutonium.
-This calculation results in a change in the mixing ratio required to build the
-PWR-MOX fuel of 10 to 30\%. This kind of plutonium accumulation can
-unexpectedly occur in a real fuel cycle and might need to be considered in a
-complete fuel cycle transition study.
-
-The decay process tends to change to composition of the plutonium vector, and
-then of the plutonium enrichment required to build a proper PWR-MOX fuel.  Such
-composition change in the MOX fuel will impact the individual cross sections:
-particularly in thermal reactors where the macroscopic cross sections are very
-dependent on the shape of the thermal part of the neutron spectrum, which is
-strongly driven by the fuel isotopic composition.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Depletion vs Recipe}
-
-Four simulations were carried out representing variations across two problem
-dimensions.  One variation compares how reactor models determine the recipe of
-used fuel.  The standard recipe reactor model produces used fuel of a fixed
-composition, regardless of the composition of the incoming fuel.  In this case, the
-alternative is a neural network depletion model provided by the cyCLASS
-package.  This model determines the macroscopic cross sections of the fuel as a
-function of burnup depending on its initial composition and discharge burnup. It then
-performs a simple calculation to allow the composition to evolve. Both of these models were used
-without decay and with decay.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.48\textwidth]{irradiation_pu_contribution.png}
-  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
-    using the ``neural network'' prediction models, using recipe based spent
-    fuel composition (red) and recalculated spent fuel composition (orange),
-    with (solid line) and without (dash line) decay enable.}
-  \label{fig:depletion}
-\end{figure}
-
-As shown on Fig. \ref{fig:depletion}, the equilibrium values for recipe based
-calculation and the depletion calculation are not the same. Moreover,
-recalculating the fuel spent fuel composition for each fuel batch allows the
-cycle to reach equilibrium faster.
-
-This is caused by the slight change in the composition in the available
-plutonium (see Fig. \ref{fig:depletioncompo}): in the case of the depletion
-calculation the available plutonium contain $68\%$ of $^{239}$Pu versus $64\%$
-in the recipe based case, and also less $^{242}$Pu and $^{241}$Am: respectively
-$4.8\%$ and $5.4\%$ in the depletion case versus $7.3\%$ and $6.7\%$. The
-amounts of the other nuclides are very close.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.48\textwidth]{MOX_pu_composition.png}
-  \caption{Evolution of the composition of the plutonium in the fresh PWR-MOX fuel
-  using the ``neural network'' prediction models, with decay enable using recipe
-  based spent fuel composition (plain line) and recalculated spent fuel
-  composition (dash line).}
-  \label{fig:depletioncompo}
-\end{figure}
-
-Those slight change in the output composition, lead to an overall decrease in
-the amount of $^{241}$Am in the fresh PWR-MOX fuel and an increase of the
-$^{239}$Pu, allowing fuel to be built with a lower plutonium enrichment.
+\subsubsection{Another Such Heading}
+And, if you really think you need a third-level heading, you should make sure
+that your subsection needs at least two of them.
 
@@
 
-This study has shown the potential impact of the decay process on the MOX-PWR fuel
-fabrication process, increasing the required amount from $1\%$ to $4\%$
-depending on the fuel fabrication model choice. The recalculation of the 
-depletion of each loaded fuel batch has consequences on the equilibrium
-state of the calculation: the reduction of fraction of $^{241}$Am and the increase of the
-fraction $^{239}$Pu in the available plutonium allows a reduction in the amount of
-plutonium in the fuel.
-
-This work has shown the strong influence of the isotopic composition on a LWR
-cycle involving plutonium recycling. Similar analysis will be conducted in the
-near future on the SFR strata of the EG29 fuel cycle, which should be less
-impacted by those isotopic changes, as fast spectrum reactor are less sensitive
-to those change.
-
-Moreover this study has demonstrated the value of the modular design of
-Cyclus, able to investigate differences between the physics fidelity of
-facility models in an isolated fashion, with other fuel cycle components
-unchanged.  In this case, additional fidelity was introduced rapidly by
-wrapping the existing neural network models made available by CLASS.
+The included ANS style file and this clear example file are a panacea for
+the hours of headache that invariably results from formatting a document in
+Microsoft Word.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\appendix
-%\section{Appendix}
-%
-%Numbering in the appendix is different:
-%\begin{equation} \label{eq:appendix}
-%  2 + 2 = 5\,.
-%\end{equation}
-%and another equation:
-%\begin{equation} \label{eq:appendix2}
-%  a + b = c\,.
-%\end{equation}
+\appendix
+\section{Appendix}
+
+Numbering in the appendix is different:
+\begin{equation} \label{eq:appendix}
+  2 + 2 = 5\,.
+\end{equation}
+and another equation:
+\begin{equation} \label{eq:appendix2}
+  a + b = c\,.
+\end{equation}
 
@@
 \section{Acknowledgments}
-This work was funded in part by the Nuclear Energy University Program 
-(DE-NE0000673) and Idaho National Laboratory (154956).
-\begin{center}
-\includegraphics[width=1.5in]{neup_logo_large.jpg}
-\end{center}
+This material is based upon work supported a Department of Energy Nuclear
+Energy University Programs Graduate Fellowship.
 

### 2018-01-25 paper.tex
adding ref case description

@@
 Other hypothesis will be explored in the future, such as maintaining the ideal
-stage of the cascade through a tunning of the cuts values $\theta_{i}$ of each
+stage of the cascade through a tuning of the cuts values $\theta_{i}$ of each
 stage of the cascade, or maintaining $\alpha\beta = const$ as described in
 \cite{walker2017}.
+
+Note that as a consequence of our design method, the cascade product and tail
+assay will not necessary match the targeted values, and usually slightly over
+enrich and over strip the product and the tail.
+
+\section{The experiment}
+
+As explain previously, the goal of this work is to assess the rate of the HEU
+production using enrichment cascade designed within the JCPOA agreement
+constrains. For this work two different cases will be investigated and compare
+to the reference case.
+
+\subsection{Reference Case}
+The reference case corresponds to a cascade design include all the 5060
+centrifuges available within JCPOA targeting an enriched product at $90\%$ of U-235,
+stripping the tail product up to 0.28 $\%$ from a feed of natural uranium. 
+The design cascade in this case, includes 4 stripping stages, and 38 enriching
+stages. The Feed/Product/Tail (F/P/T) assay are respectively
+0.0071/0.903/0.0028.
+
+\subsection{Case 1}
+\subsection{Case 2}
+
+Both case 1 and 2 will be simulation without and with tail recycling. In the
+tail recycling cases, the tails of the cascade level $N$ are blended in the feed
+of cascade level $N-1$.
 

### 2018-01-25 paper.tex
fix the flow

@@
 cascade when feed with a different feed assay than the one used for its design.
-Two different tuning have been considered, the first one makes the hypothesis
-that no physical change are made to the different centrifuges: the cut on the
-machine remains the same at every stage. The second considered tuning option,
-keep the enrichment factor constant implying to modify the cuts and then the
-different flows.
+Hypothesis have been made to design the response of the cascade: no physical
+change are made to the different centrifuges: the cut on the machine remains the
+same at every stage.
 
-The first tuning method assumes the cut of each stages are constant. As $\delta
+This tuning method assumes the cut of each stages are constant. As $\delta
 U$ and $\alpha$ do not depend on the stage feed assay $N'$,the feed to product
@@
 \subsection{Case 1}
+The case 1 is design to allow configure 30 cascades in the scenario (limit of
+the JCPOA agreement), all design the same way. The design properties are:\\
+- less than 169 centrifuges per cascade,\\
+- F/P/T assays: 0.0071/0.035/0.003.\\
+The corresponding design is:\\
+- 167 centrifuges,\\
+- F/P/T assays: 0.0071/0.0412842/0.00290548.\\
+
 \subsection{Case 2}

### 2018-01-25 paper.tex
fix the flow
preparing pres of case3

@@
 cascade when feed with a different feed assay than the one used for its design.
-Hypothesis have been made to design the response of the cascade: no physical
-change are made to the different centrifuges: the cut on the machine remains the
-same at every stage.
 
@@
 \subsection{Case 2}
+The case 2 is design is also limited to 30 cascades in the scenario (limit of
+the JCPOA agreement), all design the same way. In thsi case the explored design
+aims to reproduce the different stage of the reference case over the different
+level of cascade enrichment: the goal is to have the tails assay of a stage to
+match the feed assay of the previous stage. To do so instead of aiming for a
+S/E stages of 4/10, a S/E stages repartition of 6/7 was targeted.:w
+
+The design properties are:\\
+- less than 169 centrifuges per cascade,\\
+- F/P/T assays: 0.0071/0.0296/0.002.\\% to be correct with the correct value --
+                                      % this corresponds to a S/E of 5/6
+The corresponding design is:\\
+- 167 centrifuges,\\
+- F/P/T assays: 0.0071/0.0260104/0.0019111.\\
 

### 2018-01-26 paper.tex
update

@@
 to the reference case.
-
-\subsection{Reference Case}
+i
+\subsection{the studied cases}
+\subsubsection{Reference Case}
 The reference case corresponds to a cascade design include all the 5060
@@
 
-\subsection{Case 1}
+\subsubsection{Case 1}
 The case 1 is design to allow configure 30 cascades in the scenario (limit of
@@
 
-\subsection{Case 2}
+\subsubsection{Case 2}
 The case 2 is design is also limited to 30 cascades in the scenario (limit of
@@
 of cascade level $N-1$.
+
+\subsection{the simulation}
+The simulation is build to layer up the different cascade in order to produce
+HEU. The different layers of cascade will be called levels in the following. The
+first task has been to determine the number of level required to produce HEU.
+The optimum number of cascade per level is determine (the same way) that the
+centrifuges are distributed on the different cascade stages.
+Once both the number of levels and the number of cascades per level is
+determined, the simulation is ran.
 

### 2018-01-26 paper.tex
not inspired/tired... stopping for the night
starting case 1 description

@@
 
+\section{Results}
+
+\subsection{Assays}
+\subsubsection{Case 1}
+As shows on Figure \ref{ }, without tails recycling, the number of cascade level
+required to enrich the uranium up to $90\%$ are respectively 5 for the
+first case considered. Recycling the tails, allow to reduce the number of
+enrichment levels required to enrich natural uranium up to a high enrich level
+to 3.
+
+This bump in enrichment can easily be explained, as the cascade don't have the
+same number of stages, there is less stripping enrichment work, than enriching
+work. That is to say that even work in an ideal case (where the stripping work of a
+stage is the exact inverse of the enrich work), with an cascade with less
+stripping stage than enriching stage will produce tail with a higher enrichment
+than the feed of the previous level of
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-26 paper.tex
adding table case 2

@@
 The case 2 is design is also limited to 30 cascades in the scenario (limit of
-the JCPOA agreement), all design the same way. In thsi case the explored design
-aims to reproduce the different stage of the reference case over the different
-level of cascade enrichment: the goal is to have the tails assay of a stage to
-match the feed assay of the previous stage. To do so instead of aiming for a
-S/E stages of 4/10, a S/E stages repartition of 6/7 was targeted.:w
+the JCPOA agreement), but this time each level of cascade are designed to get
+feed with the previous level product and to have 4 stripping stages and 10
+enriching stages. The configuration of the different level of cascade can be
+found in table \ref{}
+\begin{table}[htb]
+\centering
+\begin{tabular}{lllll}
+\toprule
 
-The design properties are:\\
-- less than 169 centrifuges per cascade,\\
-- F/P/T assays: 0.0071/0.0296/0.002.\\% to be correct with the correct value --
-                                      % this corresponds to a S/E of 5/6
-The corresponding design is:\\
-- 167 centrifuges,\\
-- F/P/T assays: 0.0071/0.0260104/0.0019111.\\
+Level   &           & Assay     &       & Machines  \\ 
+        & Feed      & Product   & Feed  &           \\
+\midrule
+1       & 0.0071    & 0.0413    & 0.0029 & 167       \\
+2       & 0.0413    & 0.2043    & 0.0173 & 169       \\
+3       & 0.2043    & 0.5941    & 0.0971 & 168       \\
+4       & 0.5941    & 0.8834    & 0.3915 & 168       \\
+5       & 0.8834    & 0.9735    & 0.7746 & 169       \\
 
-Both case 1 and 2 will be simulation without and with tail recycling. In the
-tail recycling cases, the tails of the cascade level $N$ are blended in the feed
-of cascade level $N-1$.
+\bottomrule
+\end{tabular}
+  \caption{Summary of the different properties of the different level of cascade.}
+  \label{tab:widetable}
+\end{table}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}[htb]
-  \centering
-\begin{tabular}{llllllllll}\toprule
-      & $\phi_T(0)$      & $\phi_T(10)$      & $\phi_T(20)$      &
-      $\phi_D(0)$      & $\phi_D(10)$      & $\phi_D(20)$      & $\rho$      &
-      $\varepsilon$      & $N_\text{it}$
-\\ \midrule
-$c=0.999$  & 0.9038 & 20.63 & 31.24 & 0.9087 & 20.63 & 31.23 & 0.2192 & $10^{-7}$ & 15
-\\
-$c=0.990$  & 0.3675 & 13.04 & 24.7 & 0.3696 & 13.04 & 24.69 & 0.2184 & $10^{-7}$ & 15
-\\
-$c=0.900$  & 0.009909 & 4.776 & 17.64 & 0.009984 & 4.786 & 17.63 & 0.2118 & $10^{-7}$ & 14
-\\
-$c=0.500$  & $6.069\times 10^{-5}$ & 2.212 & 15.53 & 6.213$\times 10^{-5}$ & 2.239 & 15.53 & 0.2068 & $10^{-7}$ & 13
-\\
-\bottomrule
-\end{tabular}
-  \caption{This is an example of a really wide table which might not normally
-  fit in the document.}
-  \label{tab:widetable}
-\end{table*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-26 paper.tex
suggested edits up until experiment section

--- 2018-01-26 paper.tex
@@
 \title{An Improved ANS Transaction Template}
-\author{Baptiste Mouginot,$^{*}$ Kathie Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
+\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
 
@@
 \usepackage{microtype} % improves typography for PDF
+\usepackage{float}
 
@@
 \subsection{Centrifuge properties}
-In the present work, the analytical solution by R\"aetz \cite{ref} of the
-differential equation for the gas centrifuge as described in \cite{Glaser2008}
-is used. The different parameter of the centrifuges, such as average temperature
-of the gas, rotation speed, height, feed flow rate, diameter, pressure ratio,
-countercurent ratio, efficiency have been choosen to match the cascade design
-describe in \cite{glaser2008} and \cite{Walker2017} using P-1 centrifuges and
-repect the JCPOA aggrement.
+The present work uses the analytical solution by R\"aetz \cite{ref} of the
+differential equation for the gas centrifuge as described in \cite{Glaser2008}.
+Centrifuge parameters, such as average gas temperature, rotation speed, height, feed flow rate, diameter, pressure ratio,
+counter-current flow ratio, and efficiency have been chosen to match the cascade design
+describe in \cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type centrifuge are used to estimate the Joint Comprehensive Plan of Action (JCPOA)-compliant IR-1 centrifuge.
 
@@
 
-The cascade build as an ideal cascade, taht is to day, $\alpha =\beta = const$
+The cascade is built to be ideal, defined by $\alpha =\beta = const$
 for all stage of the cascade, where $\alpha$ and $\beta$ respectively represent
 the feed to product and the feed to tail enrichment factors.
-$\alpha$ can be expressed as a function of the feed rate $F$, $\delta U(\theta)$ and $\theta$,
+$\alpha$ can be expressed as a function of the feed rate $F$, the separative performance $\delta U(\theta)$ and $\theta$,
 and $\beta$ as a function of $alpha$ and $\theta$:
@@
 
-From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine the cut value
-(all other centrifuge parameters been fixed) allowing the have $\alpha=\beta$
+From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine the cut, or the ratio of product flow to feed flow.
+%(all other centrifuge parameters been fixed) allowing the have $\alpha=\beta$
 required to build an ideal cascade.
 
-As an ideal cascade is build, we only need to determine the proper cut value of
-each stages, $\theta_{i}$, the value of $\alpha_{i}$ and $\beta_{i}$ remain
-constant over the different stages.
+Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut, $\theta_{i}$, changes in each stage of a cascade.
+
 It can be shown that $\theta_{i}$ can be computed from $\alpha$,
-$\beta$ values and the feed assay, $N_{i}$:
+$\beta$ values and the feed assay, $N_{i}$ \cite{ref}:
 \begin{eqnarray}
@@
 
-This algorithm assumes that the corresponding $\delta U$ (not re-computed) can be
-achieve with the centrifuges.  With $\theta_{i}$ determined it is possible to
-compute the product and the tail assay from $\alpha$ and $\beta$.
+This algorithm assumes that the corresponding separative power $\delta U$ (not re-computed) can be
+achieved with the chosen centrifuge design. Once $\theta_{i}$ determined, it is possible to
+compute the product and the tail assay.
+
 The design of the cascade is performed through 2 steps. First one determines the
-number of stages and their configuration, adding stages following the previously
+configuration and number of stages, adding stages following the previously
 described procedure, until $N'_{last} > N'_{requested}$ and $N''_{last} <
@@
 $N''_{i}$,$\theta_{i}$i).
+% might be more useful to the reader to say this in words instead of variables, i.e.
+adding stages until the product assay of the final stage is greater than or equal to than the desired assay, and the tails assay is similarly less than or equal to the desired tails assay
 
-The second steps is dedicated on populating the cascade with centrifuges. One
-first solves the linear flow equation to determine the theoretical flow in the
+The second step determines how to populate the cascade with the user-defined maximum number of centrifuges. One first solves the linear flow equation to determine the theoretical flow in the
 cascade:
@@
 \end{bmatrix}
+\caption{caption needed!}
 \label{eq:flow}
@@
 \end{strip}
-Once the relative flow on the different stages $F_{i}$ have been determined, the
-cascade can be populated with actual machines, feeling up the different stages
-until either the maximum number available of machines, either the maximum feed
+Once the relative flow of each stage, $F_{i}$, has been determined, the
+cascade can be populated with actual machines up the stages
+until either the maximum number available of machines or the maximum feed
 flow is reached.
@@
 
-As it is practically impossible to get reliable information about tuning a
-cascade when feed with a different feed assay than the one used for its design.
+Little information is available about the optimum way to tune a cascade that is being fed a feed enrichment that does not match its ideal enrichment.
 
-This tuning method assumes the cut of each stages are constant. As $\delta
-U$ and $\alpha$ do not depend on the stage feed assay $N'$,the feed to product
-ratio $\alpha$ do not change across the different stages. According to equation
-\eqref{eq:beta} , when $\alpha$ and $\theta$ remaining, if the feed assay,
-$N$, change $\beta$ has to change accordingly.  This will lead to brake of the
+The tuning method outlined here does not re-optimize $\theta_i$ based on the true flow enrichment. As $\delta
+U$ and $\alpha$ do not depend on the stage feed assay $N'$ and the feed to product
+ratio $\alpha$ do not change from stage to stage. According to equation
+\eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, if the feed assay,
+$N$ changes, then $\beta$ will change accordingly.  This brakes the
 ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.
 
-In order to compute the stage proper product and tails assay at each stages, one
-need to blend the tails and the product from respectively the next and the
-previous stage in order to determine the correct stage feed assay. As this is a
+In order to compute the proper product and tails assay at each stages\, the tails and the product from respectively the next and the
+previous stage must be blended in order to determine the correct stage feed assay. As this is a
 obvious cycling problem, it has been chosen to solve it iteratively: all feed
@@
 the updated feed assay, the new product and tail assay are recomputed. This
-process it repeated until the change in the different assays is smaller than the
+process is repeated until the change in assays is smaller than the
 set precision (1e-8 by default).
 
-Other hypothesis will be explored in the future, such as maintaining the ideal
-stage of the cascade through a tuning of the cuts values $\theta_{i}$ of each
-stage of the cascade, or maintaining $\alpha\beta = const$ as described in
+Other hypotheses will be explored in the future, such as maintaining the ideal
+stage of the cascade through tuning the cut values $\theta_{i}$ of each
+stage of the cascade, or maintaining $\alpha*\beta = const$ as described in
 \cite{walker2017}.
@@
 assay will not necessary match the targeted values, and usually slightly over
-enrich and over strip the product and the tail.
+enrich and over strip the product and the tail respectively.
 
@@
 
-As explain previously, the goal of this work is to assess the rate of the HEU
-production using enrichment cascade designed within the JCPOA agreement
-constrains. For this work two different cases will be investigated and compare
+As explained previously, the goal of this work is to assess the rate of the highly-enriched uranium (HEU)
+production using enrichment cascades designed within the JCPOA agreement
+constraints. For this work, two different cases will be investigated and compared
 to the reference case.
-i
-\subsection{the studied cases}
+
+\subsection{Relevant Cases}
 \subsubsection{Reference Case}
-The reference case corresponds to a cascade design include all the 5060
-centrifuges available within JCPOA targeting an enriched product at $90\%$ of U-235,
+The reference case corresponds to the most ideal cascade design--utilizing all the 5060
+centrifuges available within JCPOA to produce an enriched product at >$90\%$ of U-235,
 stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
@@
 0.0071/0.903/0.0028.
+%maybe include some cascade shape figures?
 
@@
 
-This bump in enrichment can easily be explained, as the cascade don't have the
+This bump in enrichment can easily be explained, as the cascade does not have the
 same number of stages, there is less stripping enrichment work, than enriching
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Nomenclature}
+
+\begin{table}[H]
+    \centering
+    \begin{tabular}{l|l}
+%         &  \\
+        $N$ & Feed assay \\
+        $N'$ & Product assay \\
+        $N''$ & Tails assay \\
+        $\alpha$ & Feed to product enrichment factor \\
+        $\beta$ & Feed to tail enrichment factor \\
+        $\theta$ & Cut
+    \end{tabular}
+%    \caption{Caption}
+    \label{tab:my_label}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Acknowledgments}

### 2018-01-26 paper.tex
done with the experiement description

--- 2018-01-26 paper.tex
@@
 enriching stages. The configuration of the different level of cascade can be
-found in table \ref{}
+found in table \ref{tab:cascadelvl}. The different cascades don't have the same
+geometry: the number of centrifuges per stage depends on their own design and
+varies slightly from a level to another.
+
 \begin{table}[htb]
@@
   \caption{Summary of the different properties of the different level of cascade.}
-  \label{tab:widetable}
+  \label{tab:cascadelvl}
 \end{table}

### 2018-01-26 paper.tex

--- 2018-01-26 paper.tex
@@
 The case 2 is design is also limited to 30 cascades in the scenario (limit of
-the JCPOA agreement), all design the same way. In thsi case the explored design
-aims to reproduce the different stage of the reference case over the different
-level of cascade enrichment: the goal is to have the tails assay of a stage to
-match the feed assay of the previous stage. To do so instead of aiming for a
-S/E stages of 4/10, a S/E stages repartition of 6/7 was targeted.:w
+the JCPOA agreement), but this time each level of cascade are designed to get
+feed with the previous level product and to have 4 stripping stages and 10
+enriching stages. The configuration of the different level of cascade can be
+found in table \ref{tab:cascadelvl}. The different cascades don't have the same
+geometry: the number of centrifuges per stage depends on their own design and
+varies slightly from a level to another.
 
-The design properties are:\\
-- less than 169 centrifuges per cascade,\\
-- F/P/T assays: 0.0071/0.0296/0.002.\\% to be correct with the correct value --
-                                      % this corresponds to a S/E of 5/6
-The corresponding design is:\\
-- 167 centrifuges,\\
-- F/P/T assays: 0.0071/0.0260104/0.0019111.\\
+\begin{table}[htb]
+\centering
+\begin{tabular}{lllll}
+\toprule
 
-Both case 1 and 2 will be simulation without and with tail recycling. In the
-tail recycling cases, the tails of the cascade level $N$ are blended in the feed
-of cascade level $N-1$.
+Level   &           & Assay     &       & Machines  \\ 
+        & Feed      & Product   & Feed  &           \\
+\midrule
+1       & 0.0071    & 0.0413    & 0.0029 & 167       \\
+2       & 0.0413    & 0.2043    & 0.0173 & 169       \\
+3       & 0.2043    & 0.5941    & 0.0971 & 168       \\
+4       & 0.5941    & 0.8834    & 0.3915 & 168       \\
+5       & 0.8834    & 0.9735    & 0.7746 & 169       \\
+
+\bottomrule
+\end{tabular}
+  \caption{Summary of the different properties of the different level of cascade.}
+  \label{tab:cascadelvl}
+\end{table}
 

### 2018-01-26 paper.tex
done with the experiement description

@@
 
-\subsection{the simulation}
-The simulation is build to layer up the different cascade in order to produce
-HEU. The different layers of cascade will be called levels in the following. The
-first task has been to determine the number of level required to produce HEU.
-The optimum number of cascade per level is determine (the same way) that the
-centrifuges are distributed on the different cascade stages.
-Once both the number of levels and the number of cascades per level is
-determined, the simulation is ran.
+\subsection{Level optimisation}
+A last round of optimisation if then ran in order to limit the number of cascade
+level to the amount of level required produce HEU, and then to populate the
+different level with a total of 30 cascades in order to maximize the HEU
+production rate.
 

### 2018-01-26 paper.tex
adding a table

@@
 \end{bmatrix}
-\caption{caption needed!}
+%\caption{caption needed!}
 \label{eq:flow}
@@
 \centering
-\begin{tabular}{lllll}
+\begin{tabular}{cllll}
 \toprule
@@
 \section{Results}
+
+\subsection{wWithout tail recycling}
+Despite the reconfiguration of each level occuring in the second case, the case
+1 is way more effective to produce HEU than case 1.
+Indeed as observed on Figure \ref{} and \ref{}, the first case is able to
+produce a an uranium product enrich at $98\%$ while the second case is only able
+to reach an enrichment of $88.3\%$.
+This is the consequence of the usage of un-touched cascade in the case 1:
+because the cut value at each stage is unchanged it artificially produces over
+enricht tails when feeded with higher enriched materials compared to a cascade
+feed with the same feed assay but with a cascade designed for it.
+The effective cut values for each cascade can be computed as :
+\begin{equation}\label{eq:theta_eff}
+    \theta = \dfrac{N - N''}{N'-N''}
+\end{equation}
+
+\begin{table}[htb]
+\centering
+\begin{tabular}{cll}
+\toprule
+
+Level   &  $\theta_{eff}^{C1}$   & $\theta_{eff}^{C2}$ \\ 
+\midrule
+1       & 0.109375               & 0.109375     \\
+2       & 0.109375               & 0.128342     \\
+3       & 0.109375               & 0.215694     \\
+4       & 0.109375               & 0.411872     \\
+5       & 0.109375               & 0.547009     \\
+
+\bottomrule
+\end{tabular}
+  \caption{Summary of the different properties of the different level of cascade.}
+  \label{tab:cascadelvl}
+\end{table}
+
+    Looks at the effective $\theta$ values of the cascade at the third level in both
+case
 

### 2018-01-26 paper.tex
adding a table

@@
 \end{tabular}
-  \caption{Summary of the different properties of the different level of cascade.}
-  \label{tab:cascadelvl}
+  \caption{Cascade effective $\theta$ as a function of the cascade level and the
+  case considered.}
+  \label{tab:cascade_theta}
 \end{table}
-
-    Looks at the effective $\theta$ values of the cascade at the third level in both
-case
+As illustrated on Table \ref{tab:cascade_theta} the effecive cut of the the
+different level increase up to $0.54$ for the fifth stage on case 2. The high
+effecive cut value increase the product production rate but decrease the
+enrichment ratio.
 

### 2018-01-26 paper.tex
adding some figures

@@
 
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[scale=0.7]{flow_case_2_recy.pdf}
+  \caption{Illustraction of the different cascade level materials flow with tail
+  recycling.}
+  \label{fig:flow}
+\end{figure}
+
 \subsubsection{Case 1}
@@
 \section{Results}
-
-\subsection{wWithout tail recycling}
+\subsection{Enrichment}
+\subsubsection{Without tail recycling}
 Despite the reconfiguration of each level occuring in the second case, the case
@@
 
-\subsection{Assays}
+\subsubsection{tails recycling}
 \subsubsection{Case 1}

### 2018-01-26 paper.tex
some update about the flow

--- 2018-01-26 paper.tex
@@
 
+All cases will be considered with and without tail recycling. Figure
+\ref{fig:flow} shows the different flows between the different facilities in the
+fleet, in a configuration with two different levels of cascade without tail
+recycling. When considering the tail recycling, all the flow going from a
+cascade to the waste, are going from the cascade $i$ to the cascade $i-1$.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[scale=0.7]{flow_case_2_no_recy.pdf}
+  \caption{Illustration of the material flow between the different level of
+      cascades without tail recycling, in this diagram, nu\_src correspond to an
+      infinite source of natural uranium, cascade\_ $n$ and storage\_ $n$
+      corresponds respectively to the cascades, and the storage getting the
+  products of the cascades at the level $n$.}\label{fig:flow}
+\end{figure}
+
 \subsection{Relevant Cases}
@@
 The reference case corresponds to the most ideal cascade design--utilizing all the 5060
-centrifuges available within JCPOA to produce an enriched product at >$90\%$ of U-235,
+centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
 stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
@@
 \midrule
-1       & 0.0071    & 0.0413    & 0.0029 & 167       \\
-2       & 0.0413    & 0.2043    & 0.0173 & 169       \\
-3       & 0.2043    & 0.5941    & 0.0971 & 168       \\
-4       & 0.5941    & 0.8834    & 0.3915 & 168       \\
-5       & 0.8834    & 0.9735    & 0.7746 & 169       \\
+0       & 0.0071    & 0.0413    & 0.0029 & 167       \\
+1       & 0.0413    & 0.2043    & 0.0173 & 169       \\
+2       & 0.2043    & 0.5941    & 0.0971 & 168       \\
+3       & 0.5941    & 0.8834    & 0.3915 & 168       \\
+4       & 0.8834    & 0.9735    & 0.7746 & 169       \\
 
@@
 \section{Results}
+\subsection{Enrichment}
+\subsubsection{Without tail recycling}
+Despite the reconfiguration of each level occuring in the second case, the case
+1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
+\ref{} and \ref{}, the first case is able to produce a an uranium product enrich
+at $98\%$ while the second case is only able to reach an enrichment of $88.3\%$.
 
-\subsection{wWithout tail recycling}
-Despite the reconfiguration of each level occuring in the second case, the case
-1 is way more effective to produce HEU than case 1.
-Indeed as observed on Figure \ref{} and \ref{}, the first case is able to
-produce a an uranium product enrich at $98\%$ while the second case is only able
-to reach an enrichment of $88.3\%$.
-This is the consequence of the usage of un-touched cascade in the case 1:
-because the cut value at each stage is unchanged it artificially produces over
-enricht tails when feeded with higher enriched materials compared to a cascade
-feed with the same feed assay but with a cascade designed for it.
-The effective cut values for each cascade can be computed as :
+Because the cut value at each stage is unchanged it artificially produces over
+enriched tails when feed with higher enriched materials compared to a cascade
+feed with the same feed assay but with a cascade designed for it.  The effective
+cut values for each cascade can be computed as :
+
 \begin{equation}\label{eq:theta_eff}
@@
 \end{tabular}
-  \caption{Summary of the different properties of the different level of cascade.}
-  \label{tab:cascadelvl}
+  \caption{Cascade effective $\theta$ as a function of the cascade level and the
+  case considered.}
+  \label{tab:cascade_theta}
 \end{table}
+As illustrated on Table \ref{tab:cascade_theta} the effective cut of the
+different level increase up to $0.54$ for the fifth stage on case 2. The high
+effective cut value increase the product production rate but decrease the
+enrichment ratio.
 
-    Looks at the effective $\theta$ values of the cascade at the third level in both
-case
+\subsubsection{tails recycling}
 
-\subsection{Assays}
 \subsubsection{Case 1}

### 2018-01-26 paper.tex
adding a snetce about storage
adding assay no recycling figs, cleanig bottom of the file

@@
 cascade to the waste, are going from the cascade $i$ to the cascade $i-1$. 
+The Storage are not required in Cyclus they have been added to ensure the
+proper material flow between the facilities (if a receiver facility input buffer
+is full then the sender facility will stop sending material to it, and will stop
+working when its own output buffer will be filled).
 
@@
 \subsubsection{Without tail recycling}
-Despite the reconfiguration of each level occuring in the second case, the case
+Despite the reconfiguration of each level occurring in the second case, the case
 1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
-\ref{} and \ref{}, the first case is able to produce a an uranium product enrich
-at $98\%$ while the second case is only able to reach an enrichment of $88.3\%$.
+\ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
+produce an uranium product enrich at $98\%$ while the second case is only able
+to reach an enrichment of $88.3\%$.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
+  \caption{Evolution of the different product assays at each cascade level for
+  the case 1 without recycling.}\label{fig:assay_c1_nc}
+\end{figure}
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
+  \caption{Evolution of the different product assays at each cascade level for
+  the case 2 without recycling.}\label{fig:assay_c2_nc}
+\end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Subsection Goes Here}
-\begin{equation} \label{eq:marshak}
-  4 J^- = \phi + 2 D \vec{n} \vd \grad \phi \,.
-\end{equation}
-If we so choose, we can effortlessly reference the equation later.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics{example_figure}
-  \caption{Captions are flush with the left.}
-  \label{fig:voltage}
-\end{figure}
-
-Later on, we can include a table, even one that spans two columns such as
-Table~\ref{tab:widetable}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Notice how the table reference uses a Roman numeral
-for its numbering scheme, whereas the figure reference uses an Arabic numeral.
-For one-column tables, use the \verb|table| environment; two-column tables use
-\verb|table*|. The same applies to figures.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Another Subsection}
-Excessive sectioning in a three-page document is discouraged, but here are more
-subsections to demonstrate compliance with the ANS formatting guidelines.
-
-\subsubsection{Third-level Heading}
-This subsubsection shows compliance with the ANS-specified standard. This level
-of heading should be used rarely.
-
-\subsubsection{Another Such Heading}
-And, if you really think you need a third-level heading, you should make sure
-that your subsection needs at least two of them.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-26 paper.tex
adding rec assay evol to the repo
some more changes

--- 2018-01-26 paper.tex
@@
 The design cascade in this case, includes 4 stripping stages, and 38 enriching
-stages. The Feed/Product/Tail (F/P/T) assay are respectively
+stages. The Feed/Product/Tail (F/P/T) assays are respectively
 0.0071/0.903/0.0028.
@@
 \subsubsection{Case 1}
-The case 1 is design to allow configure 30 cascades in the scenario (limit of
-the JCPOA agreement), all design the same way. The design properties are:\\
+The case 1 is designed to configure 30 cascades in the scenario (the maximum allowable under
+the JCPOA agreement), all designed the same way. The basic properties are:\\
 - less than 169 centrifuges per cascade,\\
@@
 \subsubsection{Case 2}
-The case 2 is design is also limited to 30 cascades in the scenario (limit of
+Case 2 also limited to 30 cascades in the scenario (the maximum allowable under
 the JCPOA agreement), but this time each level of cascade are designed to get
@@
 varies slightly from a level to another.
+%we haven't defined a level
 

### 2018-01-26 paper.tex
done with the assay section

--- 2018-01-26 paper.tex
@@
 
-\subsection{Relevant Cases}
+\subsection{Explored Cases}
 \subsubsection{Reference Case}
@@
 1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
-\ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
+\ref{fig:assay_c1_nr} and \ref{fig:assay_c2_nr}, the first case is able to
 produce an uranium product enrich at $98\%$ while the second case is only able
@@
   \caption{Evolution of the different product assays at each cascade level for
-  the case 1 without recycling.}\label{fig:assay_c1_nc}
+  the case 1 without recycling. The blue line represents the $90\%$ enrichment
+  threshold.}\label{fig:assay_c1_nr}
 \end{figure}
@@
   \caption{Evolution of the different product assays at each cascade level for
-  the case 2 without recycling.}\label{fig:assay_c2_nc}
+  the case 2 without recycling. The blue line represents the $90\%$ enrichment
+  threshold.}\label{fig:assay_c2_nr}
 \end{figure}
@@
 \end{tabular}
-  \caption{Cascade effective $\theta$ as a function of the cascade level and the
-  case considered.}
+  \caption{Cascade effective $\theta$ by the level and the case.}
   \label{tab:cascade_theta}
@@
 \subsubsection{tails recycling}
+When recycling the tails from the different cascade levels, both cases behave
+the same way. As the tails have an higher enrichment than the product then are
+blended to, recycling the tail has the effect to bump up the enrichment of the
+product at each level (see Figure \ref{fig:assay_c1_r} and \ref{fig:assay_c2_r}).
 
-\subsubsection{Case 1}
-As shows on Figure \ref{ }, without tails recycling, the number of cascade level
-required to enrich the uranium up to $90\%$ are respectively 5 for the
-first case considered. Recycling the tails, allow to reduce the number of
-enrichment levels required to enrich natural uranium up to a high enrich level
-to 3.
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.5\textwidth]{assay_case_1_rec.png}
+  \caption{Evolution of the different product assays at each cascade level for
+  the case 1 with recycling. The blue line represents the $90\%$ enrichment
+  threshold.}\label{fig:assay_c1_r}
+\end{figure}
 
-This bump in enrichment can easily be explained, as the cascade does not have the
-same number of stages, there is less stripping enrichment work, than enriching
-work. That is to say that even work in an ideal case (where the stripping work of a
-stage is the exact inverse of the enrich work), with an cascade with less
-stripping stage than enriching stage will produce tail with a higher enrichment
-than the feed of the previous level of
+Note that for the case 2, where the fourth stage could appear as useless only the
+blending of its tail allows the product of the third one to pass the $90\%$ threshold.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results and Analysis}
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.5\textwidth]{assay_case_2_rec.png}
+  \caption{Evolution of the different product assays at each cascade level for
+  the case 2 with recycling. The blue line represents the $90\%$ enrichment
+  threshold.}\label{fig:assay_c2_r}
+\end{figure}
+
+\subsection{HEU flow rate}
 

### 2018-01-26 paper.tex
more changes

--- 2018-01-26 paper.tex
@@
 \subsubsection{Reference Case}
-The reference case corresponds to the most ideal cascade design--utilizing all the 5060
+The reference case corresponds to the most ideal cascade design--utilizing all of the 5060
 centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
@@
 
-\subsubsection{Case 2}
-Case 2 also limited to 30 cascades in the scenario (the maximum allowable under
-the JCPOA agreement), but this time each level of cascade are designed to get
-feed with the previous level product and to have 4 stripping stages and 10
-enriching stages. The configuration of the different level of cascade can be
-found in table \ref{tab:cascadelvl}. The different cascades don't have the same
-geometry: the number of centrifuges per stage depends on their own design and
-varies slightly from a level to another.
+\subsubsection{Case 2} Case 2 also limited to 30 cascades in the scenario (the
+maximum allowable under the JCPOA agreement), but this time each level of
+cascades are designed to take feed from the previous level's product. Each
+cascade has 4 stripping stages and 10 enriching stages. The configuration of
+cascade levels can be found in table \ref{tab:cascadelvl}. Unlike case 1, the
+organization of centrifuges varies from level to level. Each level is re-optimized
+to have the most efficient number of centrifuges in each stage, although the total number
+of stages remains constant. T
+
  %we haven't defined a level
@@
 \end{tabular}
-  \caption{Summary of the different properties of the different level of cascade.}
+  \caption{Summary of cascade properties for each level}
   \label{tab:cascadelvl}
@@
 
-\subsection{Level optimisation}
-A last round of optimisation if then ran in order to limit the number of cascade
+\subsection{Level optimization}
+A last round of optimization if then ran in order to limit the number of cascade
 level to the amount of level required produce HEU, and then to populate the
@@
 Despite the reconfiguration of each level occurring in the second case, the case
-1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
+1 is notably more effective in producing HEU than case 1. Indeed, as observed in Figure
 \ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
 produce an uranium product enrich at $98\%$ while the second case is only able
-to reach an enrichment of $88.3\%$.
+to reach an enrichment of $88.3\%$ with the same number of levels.
 
@@
 
-Because the cut value at each stage is unchanged it artificially produces over
-enriched tails when feed with higher enriched materials compared to a cascade
-feed with the same feed assay but with a cascade designed for it.  The effective
-cut values for each cascade can be computed as :
+Because the cut value $\theta_i$ at each stage is unchanged, case 2 artificially
+produces over-enriched tails when fed with higher enriched materials compared
+to a cascade feed with the same feed assay but with a cascade designed for it.
+
+% ^ the above paragraph is confusing but I don't understand it enough to fix it
+
+The effective cut values for each cascade can be computed as :
 
@@
 
-\bottomrule
-\end{tabular}
-  \caption{Cascade effective $\theta$ as a function of the cascade level and the
-  case considered.}
-  \label{tab:cascade_theta}
-\end{table}
-As illustrated on Table \ref{tab:cascade_theta} the effective cut of the
-different level increase up to $0.54$ for the fifth stage on case 2. The high
+\bottomrule \end{tabular} \caption{Cascade effective $\theta$ as a function of
+the cascade level and the case considered.} \label{tab:cascade_theta}
+\end{table} As illustrated in Table \ref{tab:cascade_theta}, the effective cut
+of each level increases up to $0.54$ for the fifth stage for case 2. The high
 effective cut value increase the product production rate but decrease the
@@
 \subsubsection{Case 1}
-As shows on Figure \ref{ }, without tails recycling, the number of cascade level
-required to enrich the uranium up to $90\%$ are respectively 5 for the
-first case considered. Recycling the tails, allow to reduce the number of
-enrichment levels required to enrich natural uranium up to a high enrich level
-to 3.
+As shows on Figure \ref{ }, without tails recycling, the number of cascade levels
+required to enrich uranium up to $90\%$ is 5 for the
+first case considered. Recycling the tails allows for a reduction in the number of
+enrichment levels down to only 3.
 
-This bump in enrichment can easily be explained, as the cascade does not have the
-same number of stages, there is less stripping enrichment work, than enriching
-work. That is to say that even work in an ideal case (where the stripping work of a
-stage is the exact inverse of the enrich work), with an cascade with less
-stripping stage than enriching stage will produce tail with a higher enrichment
-than the feed of the previous level of
+This bump in enrichment can easily be explained, as the cascade does not have
+the same number of stages, less work is spent on stripping as opposed to
+enriching. Even compared to an ideal case, where the stripping
+work of a stage is the exact inverse of the enriching work, a cascade with
+less stripping stages will produce tails with a higher
+enrichment than the feed of the previous level of
+
+%Did you commit in the middle of a sentence or did you forget to finish?
 

### 2018-01-26 paper.tex

@@
 1 is notably more effective in producing HEU than case 1. Indeed, as observed in Figure
-\ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
+\ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able to
 produce an uranium product enrich at $98\%$ while the second case is only able
@@
 
-\bottomrule \end{tabular} \caption{Cascade effective $\theta$ as a function of
-the cascade level and the case considered.} \label{tab:cascade_theta}
-\end{table} As illustrated in Table \ref{tab:cascade_theta}, the effective cut
+\bottomrule
+\end{tabular}
+  \caption{Cascade effective $\theta$ by the level and case.}
+  \label{tab:cascade_theta}
+\end{table}
+\end{table} 
+As illustrated in Table \ref{tab:cascade_theta}, the effective cut
 of each level increases up to $0.54$ for the fifth stage for case 2. The high
@@
 \subsubsection{tails recycling}
+When recycling the tails from the different cascade levels, both cases behave
+the same way. As the tails have an higher enrichment than the product then are
+blended to, recycling the tail has the effect to bump up the enrichment of the
+product at each level (see Figure \ref{fig:assay_c1_r} and \ref{fig:assay_c2_r}).
 
-\subsubsection{Case 1}
-As shows on Figure \ref{ }, without tails recycling, the number of cascade levels
-required to enrich uranium up to $90\%$ is 5 for the
-first case considered. Recycling the tails allows for a reduction in the number of
-enrichment levels down to only 3.
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.5\textwidth]{assay_case_1_rec.png}
+  \caption{Evolution of the different product assays at each cascade level for
+  the case 1 with recycling. The blue line represents the $90\%$ enrichment
+  threshold.}\label{fig:assay_c1_r}
+\end{figure}
 
-This bump in enrichment can easily be explained, as the cascade does not have
-the same number of stages, less work is spent on stripping as opposed to
-enriching. Even compared to an ideal case, where the stripping
-work of a stage is the exact inverse of the enriching work, a cascade with
-less stripping stages will produce tails with a higher
-enrichment than the feed of the previous level of
+Note that for the case 2, where the fourth stage could appear as useless only the
+blending of its tail allows the product of the third one to pass the $90\%$ threshold.
 
-%Did you commit in the middle of a sentence or did you forget to finish?
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.5\textwidth]{assay_case_2_rec.png}
+  \caption{Evolution of the different product assays at each cascade level for
+  the case 2 with recycling. The blue line represents the $90\%$ enrichment
+  threshold.}\label{fig:assay_c2_r}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results and Analysis}
+\subsection{HEU flow rate}
 

### 2018-01-27 paper.tex
empty commit
good fig size
add introduction

@@
 
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
+The Joint Comprehensive Plan of Action (JCPOA)\cite{ref} %cite JCPOA
+agreement limits the Iranian nuclear program and, in return, lifts many of the economic sanctions that had been placed on Iran.
+Under the JCPOA, Iran is severely limited in its ability to enrich Uranium.
+This paper presents a model to probe the enriching ability of various cascade configurations that are related to JCPOA agreement limits.
+This analysis was performed using the Cyclus fuel cycle simulator\cite{ref} %cite Fundamental concepts in the Cyclus nuclear fuel cycle simulation framework
+in order to demonstrate that such analysis can be integrated into a fuel cycle with material flowing among multiple facilities.
+
+The Cyclus fuel cycle simulator is designed to support the dynamic addition novel facility models into fuel cycles both declared and undeclared facilities.
+The CascadeEnrich archetype\cite{ref} was developed to model gas centrifuge enrichment cascades at a higher fidelity than previous enrichment models, relying on individual centrifuge and cascade design parameters to build an ideal cascade configuration instead of integral facility parameters.
+Once a CascadeEnrich facility is deployed, it may be asked to participate in the fuel cycle at a variety of flow rates and enrichments over time, constrained by the initial design of the cascade.
+
+This analysis introduces a facility with parameters consistent with the JCPOA-defined capacity and explores its performance when asked to enrich material above JCPOA limits.
+Although the analytical aspect of this analysis can be performed using other tools, a fuel cycle simulator provides value in further extensions of this work.
+Studying the internal behavior of a cascade, or rather a set of cascades organized into levels that feed into each other, identifies the most effective ways that enrichments higher than the JCPOA-allowed 3.67\% U-235 could be produced.
+However, this is only one step in a safeguards program.
+
+Performing enrichment cascade analysis within a fuel cycle simulator offers the opportunity to study the \textit{external} behavior of an enrichment facility as well as internal.
+When an enrichment facility that is not complying with the JCPOA is forced to participate in a larger fuel cycle---where it must purchase natural uranium and interact with outside facilities, it will act differently than an enrichment facility that \textit{is} fully complying with the JCPOA.
+The levels of cascades developed in this paper will ultimately be used to probe these differences and reveal patterns useful for a safeguards program.
 
@@
 counter-current flow ratio, and efficiency have been chosen to match the cascade design
-describe in \cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type centrifuge are used to estimate the Joint Comprehensive Plan of Action (JCPOA)-compliant IR-1 centrifuge.
+describe in \cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.
 

### 2018-01-27 paper.tex
almost done with the results

--- 2018-01-26 paper.tex
@@
 \end{table}
-\end{table} 
 As illustrated in Table \ref{tab:cascade_theta}, the effective cut
@@
 \subsection{HEU flow rate}
+As shown Figure \ref{fig:heu_prod}, if using all the centrifuges available to
+build a big cascade dedicated to HEU production, only 8 months are required to
+produce 1 Significant Quantity (SQ) of HEU. Also it take significantly longer to
+build 1 SQ of HEU, without recycling the tails respectively 13 years and 3.5 year
+for the case 1 and 2 versus about 2 years with tail recycling.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[width=0.5\textwidth]{HEU_prod.png}
+  \caption{Evolution of the amount of HEU in the storage. The blue line
+  correspond to one significant quantity of HEU ($25~$kg). CX correpsonds to the
+  case number(1 or 2), RT and NRT the tail reprocessing or not ones. W/X/Y/Z represent the
+  number of cascade per level. REF corresponds to the reference
+  case.}\label{fig:heu_prod}
+\end{figure}
+
+It is also interresting to note that despite requiering more level of cascade to
+reach an enrichment of $90\%$ the second case with tial recycling produces HEU
+at a equivalent rate than the case 1. The production rate seems to be faster but
+require more time to reach the maximum production rate (the material have to
+flow through more levels to reach the final level).
 

### 2018-01-27 paper.tex

--- 2018-01-27 paper.tex
@@
 \end{table}
-\end{table}
 As illustrated in Table \ref{tab:cascade_theta}, the effective cut

### 2018-01-27 paper.tex
formating, cleaning

@@
 
-The Joint Comprehensive Plan of Action (JCPOA)\cite{ref} %cite JCPOA
-agreement limits the Iranian nuclear program and, in return, lifts many of the economic sanctions that had been placed on Iran.
-Under the JCPOA, Iran is severely limited in its ability to enrich Uranium.
-This paper presents a model to probe the enriching ability of various cascade configurations that are related to JCPOA agreement limits.
-This analysis was performed using the Cyclus fuel cycle simulator\cite{ref} %cite Fundamental concepts in the Cyclus nuclear fuel cycle simulation framework
-in order to demonstrate that such analysis can be integrated into a fuel cycle with material flowing among multiple facilities.
+The Joint Comprehensive Plan of Action (JCPOA)\cite{ref} %cite JCPOA agreement
+limits the Iranian nuclear program and, in return, lifts many of the economic
+sanctions that had been placed on Iran. Under the JCPOA, Iran is severely
+limited in its ability to enrich Uranium. This paper presents a model to probe
+the enriching ability of various cascade configurations that are related to
+JCPOA agreement limits. This analysis was performed using the Cyclus fuel cycle
+simulator\cite{ref} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
+simulation framework in order to demonstrate that such analysis can be
+integrated into a fuel cycle with material flowing among multiple facilities.
 
-The Cyclus fuel cycle simulator is designed to support the dynamic addition novel facility models into fuel cycles both declared and undeclared facilities.
-The CascadeEnrich archetype\cite{ref} was developed to model gas centrifuge enrichment cascades at a higher fidelity than previous enrichment models, relying on individual centrifuge and cascade design parameters to build an ideal cascade configuration instead of integral facility parameters.
-Once a CascadeEnrich facility is deployed, it may be asked to participate in the fuel cycle at a variety of flow rates and enrichments over time, constrained by the initial design of the cascade.
+The Cyclus fuel cycle simulator is designed to support the dynamic addition
+novel facility models into fuel cycles both declared and undeclared facilities.
+The CascadeEnrich archetype\cite{ref} was developed to model gas centrifuge
+enrichment cascades at a higher fidelity than previous enrichment models,
+relying on individual centrifuge and cascade design parameters to build an ideal
+cascade configuration instead of integral facility parameters. Once a
+CascadeEnrich facility is deployed, it may be asked to participate in the fuel
+cycle at a variety of flow rates and enrichments over time, constrained by the
+initial design of the cascade.
 
-This analysis introduces a facility with parameters consistent with the JCPOA-defined capacity and explores its performance when asked to enrich material above JCPOA limits.
-Although the analytical aspect of this analysis can be performed using other tools, a fuel cycle simulator provides value in further extensions of this work.
-Studying the internal behavior of a cascade, or rather a set of cascades organized into levels that feed into each other, identifies the most effective ways that enrichments higher than the JCPOA-allowed 3.67\% U-235 could be produced.
-However, this is only one step in a safeguards program.
+This analysis introduces a facility with parameters consistent with the
+JCPOA-defined capacity and explores its performance when asked to enrich
+material above JCPOA limits. Although the analytical aspect of this analysis can
+be performed using other tools, a fuel cycle simulator provides value in further
+extensions of this work. Studying the internal behavior of a cascade, or rather
+a set of cascades organized into levels that feed into each other, identifies
+the most effective ways that enrichments higher than the JCPOA-allowed 3.67\%
+U-235 could be produced. However, this is only one step in a safeguards program.
 
-Performing enrichment cascade analysis within a fuel cycle simulator offers the opportunity to study the \textit{external} behavior of an enrichment facility as well as internal.
-When an enrichment facility that is not complying with the JCPOA is forced to participate in a larger fuel cycle---where it must purchase natural uranium and interact with outside facilities, it will act differently than an enrichment facility that \textit{is} fully complying with the JCPOA.
-The levels of cascades developed in this paper will ultimately be used to probe these differences and reveal patterns useful for a safeguards program.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Theory}
-
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
-Some text for introduction etc\ldots
+Performing enrichment cascade analysis within a fuel cycle simulator offers the
+opportunity to study the \textit{external} behavior of an enrichment facility as
+well as internal. When an enrichment facility that is not complying with the
+JCPOA is forced to participate in a larger fuel cycle---where it must purchase
+natural uranium and interact with outside facilities, it will act differently
+than an enrichment facility that \textit{is} fully complying with the JCPOA. The
+levels of cascades developed in this paper will ultimately be used to probe
+these differences and reveal patterns useful for a safeguards program.
 
@@
 \subsection{Centrifuge properties}
+
 The present work uses the analytical solution by R\"aetz \cite{ref} of the
 differential equation for the gas centrifuge as described in \cite{Glaser2008}.
-Centrifuge parameters, such as average gas temperature, rotation speed, height, feed flow rate, diameter, pressure ratio,
-counter-current flow ratio, and efficiency have been chosen to match the cascade design
-describe in \cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.
+Centrifuge parameters, such as average gas temperature, rotation speed, height,
+feed flow rate, diameter, pressure ratio, counter-current flow ratio, and
+efficiency have been chosen to match the cascade design describe in
+\cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type
+centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.
 
@@
 
-The cascade is built to be ideal, defined by $\alpha =\beta = const$
-for all stage of the cascade, where $\alpha$ and $\beta$ respectively represent
-the feed to product and the feed to tail enrichment factors.
-$\alpha$ can be expressed as a function of the feed rate $F$, the separative performance $\delta U(\theta)$ and $\theta$,
-and $\beta$ as a function of $alpha$ and $\theta$:
+The cascade is built to be ideal, defined by $\alpha =\beta = const$ for all
+stage of the cascade, where $\alpha$ and $\beta$ respectively represent the feed
+to product and the feed to tail enrichment factors.  $\alpha$ can be expressed
+as a function of the feed rate $F$, the separative performance $\delta
+U(\theta)$ and $\theta$, and $\beta$ as a function of $alpha$ and $\theta$:
+
 \begin{subequations} \label{eqs:alphabeta}
@@
 
-From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine the cut, or the ratio of product flow to feed flow.
+From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
+the cut, or the ratio of product flow to feed flow.
 %(all other centrifuge parameters been fixed) allowing the have $\alpha=\beta$
@@
 
-Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut, $\theta_{i}$, changes in each stage of a cascade.
+Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
+$\theta_{i}$, changes in each stage of a cascade.
 
@@
 
-This algorithm assumes that the corresponding separative power $\delta U$ (not re-computed) can be
-achieved with the chosen centrifuge design. Once $\theta_{i}$ determined, it is possible to
-compute the product and the tail assay.
+This algorithm assumes that the corresponding separative power $\delta U$ (not
+re-computed) can be achieved with the chosen centrifuge design. Once
+$\theta_{i}$ determined, it is possible to compute the product and the tail
+assay.
 
@@
 $N''_{i}$,$\theta_{i}$i).
-% might be more useful to the reader to say this in words instead of variables, i.e.
-adding stages until the product assay of the final stage is greater than or equal to than the desired assay, and the tails assay is similarly less than or equal to the desired tails assay
+% might be more useful to the reader to say this in words instead of variables,
+% i.e. adding stages until the product assay of the final stage is greater than
+% or equal to than the desired assay, and the tails assay is similarly less than
+% or equal to the desired tails assay
 
-The second step determines how to populate the cascade with the user-defined maximum number of centrifuges. One first solves the linear flow equation to determine the theoretical flow in the
-cascade:
+The second step determines how to populate the cascade with the user-defined
+maximum number of centrifuges. One first solves the linear flow equation to
+determine the theoretical flow in the cascade:
+
 \begin{strip}
@@
 
-Little information is available about the optimum way to tune a cascade that is being fed a feed enrichment that does not match its ideal enrichment.
+Little information is available about the optimum way to tune a cascade that is
+being fed a feed enrichment that does not match its ideal enrichment.
 
-The tuning method outlined here does not re-optimize $\theta_i$ based on the true flow enrichment. As $\delta
-U$ and $\alpha$ do not depend on the stage feed assay $N'$ and the feed to product
-ratio $\alpha$ do not change from stage to stage. According to equation
-\eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, if the feed assay,
-$N$ changes, then $\beta$ will change accordingly.  This brakes the
-ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.
+The tuning method outlined here does not re-optimize $\theta_i$ based on the
+true flow enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed
+assay $N'$ and the feed to product ratio $\alpha$ do not change from stage to
+stage. According to equation \eqref{eq:beta}, when $\alpha$ and $\theta$ are
+fixed, if the feed assay, $N$ changes, then $\beta$ will change accordingly.
+This brakes the ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq
+N''_{i+1}$.
 
-In order to compute the proper product and tails assay at each stages\, the tails and the product from respectively the next and the
-previous stage must be blended in order to determine the correct stage feed assay. As this is a
-obvious cycling problem, it has been chosen to solve it iteratively: all feed
-assay are iteratively updated, blending the proper product and tail, then using
-the updated feed assay, the new product and tail assay are recomputed. This
-process is repeated until the change in assays is smaller than the
-set precision (1e-8 by default).
+In order to compute the proper product and tails assay at each stages\, the
+tails and the product from respectively the next and the previous stage must be
+blended in order to determine the correct stage feed assay. As this is a obvious
+cycling problem, it has been chosen to solve it iteratively: all feed assay are
+iteratively updated, blending the proper product and tail, then using the
+updated feed assay, the new product and tail assay are recomputed. This process
+is repeated until the change in assays is smaller than the set precision (1e-8
+by default).
 
 Other hypotheses will be explored in the future, such as maintaining the ideal
-stage of the cascade through tuning the cut values $\theta_{i}$ of each
-stage of the cascade, or maintaining $\alpha*\beta = const$ as described in
+stage of the cascade through tuning the cut values $\theta_{i}$ of each stage of
+the cascade, or maintaining $\alpha*\beta = const$ as described in
 \cite{walker2017}.
@@
 
-As explained previously, the goal of this work is to assess the rate of the highly-enriched uranium (HEU)
-production using enrichment cascades designed within the JCPOA agreement
-constraints. For this work, two different cases will be investigated and compared
-to the reference case.
+As explained previously, the goal of this work is to assess the rate of the
+highly-enriched uranium (HEU) production using enrichment cascades designed
+within the JCPOA agreement constraints. For this work, two different cases will
+be investigated and compared to the reference case.
 
@@
 recycling. When considering the tail recycling, all the flow going from a
-cascade to the waste, are going from the cascade $i$ to the cascade $i-1$.
-The Storage are not required in Cyclus they have been added to ensure the
-proper material flow between the facilities (if a receiver facility input buffer
-is full then the sender facility will stop sending material to it, and will stop
+cascade to the waste, are going from the cascade $i$ to the cascade $i-1$.  The
+Storage are not required in Cyclus they have been added to ensure the proper
+material flow between the facilities (if a receiver facility input buffer is
+full then the sender facility will stop sending material to it, and will stop
 working when its own output buffer will be filled).
@@
 \subsubsection{Reference Case}
-The reference case corresponds to the most ideal cascade design--utilizing all of the 5060
-centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
-stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
-The design cascade in this case, includes 4 stripping stages, and 38 enriching
-stages. The Feed/Product/Tail (F/P/T) assays are respectively
+
+The reference case corresponds to the most ideal cascade design--utilizing all
+of the 5060 centrifuges available within JCPOA to produce an enriched product at
+$>90\%$ of U-235, stripping the tail product up to 0.28 $\%$ from a feed of
+natural uranium.  The design cascade in this case, includes 4 stripping stages,
+and 38 enriching stages. The Feed/Product/Tail (F/P/T) assays are respectively
 0.0071/0.903/0.0028.
-%maybe include some cascade shape figures?
 
 \subsubsection{Case 1}
-The case 1 is designed to configure 30 cascades in the scenario (the maximum allowable under
-the JCPOA agreement), all designed the same way. The basic properties are:\\
-- less than 169 centrifuges per cascade,\\
-- F/P/T assays: 0.0071/0.035/0.003.\\
-The corresponding design is:\\
-- 167 centrifuges,\\
-- F/P/T assays: 0.0071/0.0412842/0.00290548.\\
 
-\subsubsection{Case 2} Case 2 also limited to 30 cascades in the scenario (the
-maximum allowable under the JCPOA agreement), but this time each level of
-cascades are designed to take feed from the previous level's product. Each
-cascade has 4 stripping stages and 10 enriching stages. The configuration of
-cascade levels can be found in table \ref{tab:cascadelvl}. Unlike case 1, the
-organization of centrifuges varies from level to level. Each level is re-optimized
-to have the most efficient number of centrifuges in each stage, although the total number
-of stages remains constant. T
+The case 1 is designed to configure 30 cascades in the scenario (the maximum
+allowable under the JCPOA agreement), all designed the same way. The basic
+properties are: less than 169 centrifuges per cascade, F/P/T assays of
+0.0071/0.035/0.003. The corresponding design includes 167 centrifuges, with
+respective F/P/T assays of 0.0071/0.0412842/0.00290548.
 
- %we haven't defined a level
+\subsubsection{Case 2}
+
+Case 2 also limited to 30 cascades in the scenario (the maximum allowable under
+the JCPOA agreement), but this time each level of cascades are designed to take
+feed from the previous level's product. Each cascade has 4 stripping stages and
+10 enriching stages.
 
@@
 
+The configuration of cascade levels can be found in table
+\ref{tab:cascadelvl}. Unlike case 1, the organization of centrifuges varies from
+level to level. Each level is re-optimized to have the most efficient number of
+centrifuges in each stage, although the total number of stages remains constant.
+
 \subsection{Level optimization}
+
 A last round of optimization if then ran in order to limit the number of cascade
@@
 \subsubsection{Without tail recycling}
+
 Despite the reconfiguration of each level occurring in the second case, the case
-1 is notably more effective in producing HEU than case 1. Indeed, as observed in Figure
-\ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able to
-produce an uranium product enrich at $98\%$ while the second case is only able
-to reach an enrichment of $88.3\%$ with the same number of levels.
+1 is notably more effective in producing HEU than case 1. Indeed, as observed in
+Figure \ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able
+to produce an uranium product enrich at $98\%$ while the second case is only
+able to reach an enrichment of $88.3\%$ with the same number of levels.
 
@@
   \caption{Evolution of the different product assays at each cascade level for
-  the case 2 without recycling. The blue line represents the $90\%$ enrichment
-  threshold.}\label{fig:assay_c2_nr}
+  the case 2 without recycling. }\label{fig:assay_c2_nr}
 \end{figure}
@@
   \caption{Evolution of the different product assays at each cascade level for
-  the case 1 with recycling. The blue line represents the $90\%$ enrichment
-  threshold.}\label{fig:assay_c1_r}
+  the case 1 with recycling. }\label{fig:assay_c1_r}
 \end{figure}
@@
   \caption{Evolution of the different product assays at each cascade level for
-  the case 2 with recycling. The blue line represents the $90\%$ enrichment
-  threshold.}\label{fig:assay_c2_r}
+  the case 2 with recycling.}\label{fig:assay_c2_r}
 \end{figure}
@@
   \caption{Evolution of the amount of HEU in the storage. The blue line
-  correspond to one significant quantity of HEU ($25~$kg). CX correpsonds to the
-  case number(1 or 2), RT and NRT the tail reprocessing or not ones. W/X/Y/Z represent the
-  number of cascade per level. REF corresponds to the reference
-  case.}\label{fig:heu_prod}
+      correspond to one significant quantity of HEU ($25~$kg). CX correpsonds to
+      the case number(1 or 2), RT and NRT the tail reprocessing or not ones.
+      W/X/Y/Z represent the number of cascade per level. REF corresponds to the
+      reference case.}\label{fig:heu_prod}
 \end{figure}
@@
 
-The included ANS style file and this clear example file are a panacea for
-the hours of headache that invariably results from formatting a document in
-Microsoft Word.
+Where the JCPOA aggrement
 

### 2018-01-27 paper.tex
comment nomenclature
commenting apendix
conclusion draft + Acknowledgments

@@
 
-Where the JCPOA aggrement
+The JCPOA aggrement limits to 5060 runing centrifuges in the Natanz Fuel
+Enrichment Plant (NFEP) so about $10\%$ of its design capacity, the reference
+case allows to build $1$ SQ of HEU in 8 months (versus in 24 days without the JCPOA
+agrement limitations). While using directly the 5060 centrifuges to produce 1 SQ
+of HEU take about 8 months, case 1 and the case 2 will produce it in 2 years.
+Nevertheless the diversion scenario from case 1 or 2 will be hard if not
+impossible to detect from the cascasde configuration.
+
+While the results of this work might be limited, it aims to develop a
+methodology to study diversion scenarios, from the fuel cycle perspective.
+Futhermore, additional methods to compute the CascadeEnrich response to
+non-ideal feed assay will be investigated.  The CascadeEnrich facility used will
+also be improved in order to take advantage of the dynamical flow managment of
+the Cyclus framework, allowing for example to automatically assign the cascade
+to the different level as the need evolve.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Appendix}
-
-Numbering in the appendix is different:
-\begin{equation} \label{eq:appendix}
-  2 + 2 = 5\,.
-\end{equation}
-and another equation:
-\begin{equation} \label{eq:appendix2}
-  a + b = c\,.
-\end{equation}
-
+%% \appendix
+%% \section{Appendix}
+%% 
+%% Numbering in the appendix is different:
+%% \begin{equation} \label{eq:appendix}
+%%   2 + 2 = 5\,.
+%% \end{equation}
+%% and another equation:
+%% \begin{equation} \label{eq:appendix2}
+%%   a + b = c\,.
+%% \end{equation}
+%% 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Nomenclature}
-
-\begin{table}[H]
-    \centering
-    \begin{tabular}{l|l}
-%         &  \\
-        $N$ & Feed assay \\
-        $N'$ & Product assay \\
-        $N''$ & Tails assay \\
-        $\alpha$ & Feed to product enrichment factor \\
-        $\beta$ & Feed to tail enrichment factor \\
-        $\theta$ & Cut
-    \end{tabular}
-%    \caption{Caption}
-    \label{tab:my_label}
-\end{table}
+%% \section{Nomenclature}
+%%
+%% \begin{table}[H]
+%%     \centering
+%%     \begin{tabular}{l|l}
+%% %         &  \\
+%%         $N$ & Feed assay \\
+%%         $N'$ & Product assay \\
+%%         $N''$ & Tails assay \\
+%%         $\alpha$ & Feed to product enrichment factor \\
+%%         $\beta$ & Feed to tail enrichment factor \\
+%%         $\theta$ & Cut
+%%     \end{tabular}
+%% %    \caption{Caption}
+%%     \label{tab:my_label}
+%% \end{table}
 
@@
 \section{Acknowledgments} 
-This material is based upon work supported a Department of Energy Nuclear
-Energy University Programs Graduate Fellowship.
+This work was funded by the Consortium for Verification Technology under
+Department of Energy National Nuclear Security Administration award number
+DE-NA0002534
 

### 2018-01-27 paper.tex
adding refs

@@
 
-The Joint Comprehensive Plan of Action (JCPOA)\cite{ref} %cite JCPOA agreement
+The Joint Comprehensive Plan of Action (JCPOA)\cite{jcpoa} %cite JCPOA agreement
 limits the Iranian nuclear program and, in return, lifts many of the economic
@@
 JCPOA agreement limits. This analysis was performed using the Cyclus fuel cycle
-simulator\cite{ref} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
+simulator\cite{cyclus} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
 simulation framework in order to demonstrate that such analysis can be
@@
 novel facility models into fuel cycles both declared and undeclared facilities.
-The CascadeEnrich archetype\cite{ref} was developed to model gas centrifuge
+The CascadeEnrich archetype\cite{mbmore.2018} was developed to model gas centrifuge
 enrichment cascades at a higher fidelity than previous enrichment models,
@@
 
-The present work uses the analytical solution by R\"aetz \cite{ref} of the
-differential equation for the gas centrifuge as described in \cite{Glaser2008}.
+The present work uses the analytical solution by R\"aetz \cite{raetz.phd} of the
+differential equation for the gas centrifuge as described in \cite{glaser.2008}.
 Centrifuge parameters, such as average gas temperature, rotation speed, height,
@@
 efficiency have been chosen to match the cascade design describe in
-\cite{glaser2008} and \cite{Walker2017}. These parameters for a P1-type
+\cite{glaser.2008} and \cite{walker.2017}. These parameters for a P1-type
 centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.
@@
 It can be shown that $\theta_{i}$ can be computed from $\alpha$,
-$\beta$ values and the feed assay, $N_{i}$ \cite{ref}:
+$\beta$ values and the feed assay, $N_{i}$:
 \begin{eqnarray}
@@
 the cascade, or maintaining $\alpha*\beta = const$ as described in
-\cite{walker2017}.
+\cite{walker.2017}.
 

### 2018-01-27 paper.tex
updated conclusion

--- 2018-01-27 paper.tex
@@
 
-The JCPOA aggrement limits to 5060 runing centrifuges in the Natanz Fuel
-Enrichment Plant (NFEP) so about $10\%$ of its design capacity, the reference
-case allows to build $1$ SQ of HEU in 8 months (versus in 24 days without the JCPOA
-agrement limitations). While using directly the 5060 centrifuges to produce 1 SQ
-of HEU take about 8 months, case 1 and the case 2 will produce it in 2 years.
-Nevertheless the diversion scenario from case 1 or 2 will be hard if not
-impossible to detect from the cascasde configuration.
+The JCPOA agreement limits the Natanz Fuel Enrichment Plant (NFEP) to 5060 operating centrifuges, or about $10\%$ of its design capacity.
+The reference case, using all 5060 centrifuges in a single cascade, would lead to a stockpile of approximately $1$ SQ of HEU in 8 months, as opposed to 24 days without the
+JCPOA agreement limitations.
+However, the more realistic case 1 and the case 2 will produce a $1$ SQ in about 2 years.
+Nevertheless, the diversion scenario from case 1 or 2 would be much more difficult to detect from the cascade configuration.
 
 While the results of this work might be limited, it aims to develop a
-methodology to study diversion scenarios, from the fuel cycle perspective.
-Futhermore, additional methods to compute the CascadeEnrich response to
-non-ideal feed assay will be investigated.  The CascadeEnrich facility used will
-also be improved in order to take advantage of the dynamical flow managment of
-the Cyclus framework, allowing for example to automatically assign the cascade
-to the different level as the need evolve.
+methodology to study diversion scenarios from the fuel cycle perspective.
+Furthermore, additional methods to compute the CascadeEnrich response to non-ideal feed assays will be investigated in the future.
+The CascadeEnrich facility will be improved in order to take advantage of the dynamic flow management of the Cyclus framework.
+This will include automatic cascade level assignment to optimize the analysis workflow.
 

### 2018-01-27 paper.tex
removing flow equation

--- 2018-01-27 paper.tex
@@
 maximum number of centrifuges. One first solves the linear flow equation to
-determine the theoretical flow in the cascade:
-
-\begin{strip}
-\begin{equation}
-\setcounter{MaxMatrixCols}{20}
-\begin{bmatrix}
--1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
-\theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
-           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
-0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
-           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
-0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
-0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
-\end{bmatrix}
-\times
-\begin{bmatrix}
-     F_{S}   \\
-     F_{S+1} \\
-     \cdots  \\
-     F_{0}   \\
-    \cdots   \\
-    F_{E-1}  \\
-    F_{E}
-\end{bmatrix}
-=
-\begin{bmatrix}
-     0   \\
-     0 \\
-     \cdots  \\
-     F   \\
-    \cdots   \\
-    0  \\
-    0
-\end{bmatrix}
-%\caption{caption needed!}
-\label{eq:flow}
-\end{equation}
-\end{strip}
-Once the relative flow of each stage, $F_{i}$, has been determined, the
+determine the theoretical flow in the cascade.
+%% 
+%% \begin{strip}
+%% \begin{equation}
+%% \setcounter{MaxMatrixCols}{20}
+%% \begin{bmatrix}
+%% -1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
+%% \theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
+%%            &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
+%% 0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
+%%            &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
+%% 0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
+%% 0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
+%% \end{bmatrix}
+%% \times
+%% \begin{bmatrix}
+%%      F_{S}   \\
+%%      F_{S+1} \\
+%%      \cdots  \\
+%%      F_{0}   \\
+%%     \cdots   \\
+%%     F_{E-1}  \\
+%%     F_{E}
+%% \end{bmatrix}
+%% =
+%% \begin{bmatrix}
+%%      0   \\
+%%      0 \\
+%%      \cdots  \\
+%%      F   \\
+%%     \cdots   \\
+%%     0  \\
+%%     0
+%% \end{bmatrix}
+%% %\caption{caption needed!}
+%% \label{eq:flow}
+%% \end{equation}
+%% \end{strip}
+Once the relative flow of each stage has been determined, the
 cascade can be populated with actual machines up the stages

### 2018-01-27 paper.tex
title draft some light change

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{An Improved ANS Transaction Template}
+\title{Modeling potential JCPOA breakout scenarios using Cyclus}
 \author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
@@
 \subsection{Explored Cases}
-\subsubsection{Reference Case}
+%\subsubsection{Reference Case}
 
@@
 
-\subsubsection{Case 1}
+%\subsubsection{Case 1}
 
@@
 
-\subsubsection{Case 2}
+%\subsubsection{Case 2}
 
@@
 
-Despite the reconfiguration of each level occurring in the second case, the case
-1 is notably more effective in producing HEU than case 1. Indeed, as observed in
-Figure \ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able
-to produce an uranium product enrich at $98\%$ while the second case is only
-able to reach an enrichment of $88.3\%$ with the same number of levels.
-
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
@@
 \end{figure}
+Despite the reconfiguration of each level occurring in the second case, the case
+1 is notably more effective in producing HEU than case 1. Indeed, as observed in
+Figure \ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able
+to produce an uranium product enrich at $98\%$ while the second case is only
+able to reach an enrichment of $88.3\%$ with the same number of levels.
+
+Because the cut value $\theta_i$ at each stage is unchanged, case 2 artificially
+produces over-enriched tails when fed with higher enriched materials compared
+to a cascade feed with the same feed assay but with a cascade designed for it.
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
@@
 \end{figure}
-
-Because the cut value $\theta_i$ at each stage is unchanged, case 2 artificially
-produces over-enriched tails when fed with higher enriched materials compared
-to a cascade feed with the same feed assay but with a cascade designed for it.
 
@@
 
+As illustrated in Table \ref{tab:cascade_theta}, the effective cut
+of each level increases up to $0.54$ for the fifth stage for case 2. The high
+effective cut value increase the product production rate but decrease the
+enrichment ratio.
 \begin{table}[htb]
@@
 \end{table}
-As illustrated in Table \ref{tab:cascade_theta}, the effective cut
-of each level increases up to $0.54$ for the fifth stage for case 2. The high
-effective cut value increase the product production rate but decrease the
-enrichment ratio.
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{HEU_prod.png}
-  \caption{Evolution of the amount of HEU in the storage. The blue line
-      correspond to one significant quantity of HEU ($25~$kg). CX correpsonds to
-      the case number(1 or 2), RT and NRT the tail reprocessing or not ones.
-      W/X/Y/Z represent the number of cascade per level. REF corresponds to the
-      reference case.}\label{fig:heu_prod}
+  \includegraphics[width=0.5\textwidth]{HEU_prod.png} \caption{Evolution of the
+  amount of HEU in the storage. The blue line correspond to 1 SQ of HEU
+  ($25~$kg). Cx, RT(NRT) represents the different cases with (no)tail recycling
+  with the cascade population per level and REF the reference
+  case.}\label{fig:heu_prod}
 \end{figure}
 
-It is also interresting to note that despite requiering more level of cascade to
-reach an enrichment of $90\%$ the second case with tial recycling produces HEU
+It is also interesting to note that despite requiring more level of cascade to
+reach an enrichment of $90\%$ the second case with tail recycling produces HEU
 at a equivalent rate than the case 1. The production rate seems to be faster but
@@
 
-The JCPOA agreement limits the Natanz Fuel Enrichment Plant (NFEP) to 5060 operating centrifuges, or about $10\%$ of its design capacity.
-The reference case, using all 5060 centrifuges in a single cascade, would lead to a stockpile of approximately $1$ SQ of HEU in 8 months, as opposed to 24 days without the
-JCPOA agreement limitations.
-However, the more realistic case 1 and the case 2 will produce a $1$ SQ in about 2 years.
-Nevertheless, the diversion scenario from case 1 or 2 would be much more difficult to detect from the cascade configuration.
+The JCPOA agreement limits the Natanz Fuel Enrichment Plant (NFEP) to 5060
+operating centrifuges, or about $10\%$ of its design capacity. The reference
+case, using all 5060 centrifuges in a single cascade, would lead to a stockpile
+of approximately $1$ SQ of HEU in 8 months, as opposed to 24 days without the
+JCPOA agreement limitations. However, the more realistic case 1 and the case 2
+will produce a $1$ SQ in about 2 years. Nevertheless, the diversion scenario
+from case 1 or 2 would be much more difficult to detect from the cascade
+configuration.
 
@@
 methodology to study diversion scenarios from the fuel cycle perspective.
-Furthermore, additional methods to compute the CascadeEnrich response to non-ideal feed assays will be investigated in the future.
-The CascadeEnrich facility will be improved in order to take advantage of the dynamic flow management of the Cyclus framework.
-This will include automatic cascade level assignment to optimize the analysis workflow.
+Furthermore, additional methods to compute the CascadeEnrich response to
+non-ideal feed assays will be investigated in the future.  The CascadeEnrich
+facility will be improved in order to take advantage of the dynamic flow
+management of the Cyclus framework. This will include automatic cascade level
+assignment to optimize the analysis workflow.
 

### 2018-01-27 paper.tex
human readable assay :)

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Modeling potential JCPOA breakout scenarios using Cyclus}
+\title{Modeling potential JCPOA diversion scenarios using Cyclus}
 \author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
@@
   \centering
-  \includegraphics[scale=0.7]{flow_case_2_no_recy.pdf}
+  \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
   \caption{Illustration of the material flow between the different level of
-      cascades without tail recycling, in this diagram, nu\_src correspond to an
-      infinite source of natural uranium, cascade\_ $n$ and storage\_ $n$
-      corresponds respectively to the cascades, and the storage getting the
-  products of the cascades at the level $n$.}\label{fig:flow}
+      cascades without tail recycling, in this diagram, nu\_src corresponds to an
+  infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_ $\{n\}$
+      corresponds to the cascade and the storage getting the
+      products of the cascades at the level $\{n\}$.}\label{fig:flow}
 \end{figure}
@@
 0.0071/0.035/0.003. The corresponding design includes 167 centrifuges, with
-respective F/P/T assays of 0.0071/0.0412842/0.00290548.
+respective F/P/T assays of 0.0071/0.0413/0.0029.
 
@@
 1 is notably more effective in producing HEU than case 1. Indeed, as observed in
-Figure \ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able
+Figure \ref{fig:assay_c1_nr} and \ref{fig:assay_c2_nr}, the first case is able
 to produce an uranium product enrich at $98\%$ while the second case is only

### 2018-01-27 paper.tex
simplify caption

@@
   \caption{Illustration of the material flow between the different level of
-      cascades without tail recycling, in this diagram, nu\_src corresponds to an
-  infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_ $\{n\}$
-      corresponds to the cascade and the storage getting the
-      products of the cascades at the level $\{n\}$.}\label{fig:flow}
+      cascades without tail recycling, in this diagram, nu\_src corresponds to
+      an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
+      $\{n\}$ to the cascade and the storage getting the products of the
+      cascades at the level $\{n\}$.}\label{fig:flow}
 \end{figure}

### 2018-01-27 paper.tex
small changes and review of entire paper

--- 2018-01-27 paper.tex
@@
 sanctions that had been placed on Iran. Under the JCPOA, Iran is severely
-limited in its ability to enrich Uranium. This paper presents a model to probe
+limited in its ability to enrich uranium. This paper presents a model to probe
 the enriching ability of various cascade configurations that are related to
-JCPOA agreement limits. This analysis was performed using the Cyclus fuel cycle
-simulator\cite{cyclus} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
+JCPOA agreement limits. The analysis was performed using the Cyclus fuel cycle
+\cite{cyclus} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
 simulation framework in order to demonstrate that such analysis can be
@@
 
-The Cyclus fuel cycle simulator is designed to support the dynamic addition
-novel facility models into fuel cycles both declared and undeclared facilities.
+The Cyclus fuel cycle simulator is designed to support the dynamic addition of
+novel facility models into fuel cycles with both declared and undeclared facilities.
 The CascadeEnrich archetype\cite{mbmore.2018} was developed to model gas centrifuge
@@
 as a function of the feed rate $F$, the separative performance $\delta
-U(\theta)$ and $\theta$, and $\beta$ as a function of $alpha$ and $\theta$:
+U(\theta)$, the cut $\theta$, and $\beta$ as a function of $alpha$ and $\theta$:
 
@@
 From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
-the cut, or the ratio of product flow to feed flow.
+the cut, or the ratio of product flow to feed flow
 %(all other centrifuge parameters been fixed) allowing the have $\alpha=\beta$
@@
 Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
-$\theta_{i}$, changes in each stage of a cascade.
+$\theta_{i}$, changes in each stage $i$ of a cascade.
 
@@
 re-computed) can be achieved with the chosen centrifuge design. Once
-$\theta_{i}$ determined, it is possible to compute the product and the tail
+$\theta_{i}$ is determined, it is possible to compute the product and the tail
 assay.
@@
 The design of the cascade is performed through 2 steps. First one determines the
-configuration and number of stages, adding stages following the previously
-described procedure, until $N'_{last} > N'_{requested}$ and $N''_{last} <
-N''_{requested}$. (Note that $N'_{last}$ corresponds to the product assay of the
-last enrichment stage, and $N''_{last}$ to the tail assay of the last stripping
-stage). This allows to determine the number of enriching and stripping stages as
+configuration and number of stages, adding stages until the product assay of the final stage is greater than or equal to than the desired assay, and the tails assay is similarly less than or equal to the desired tails assay.
+This determines the number of enriching and stripping stages as
 well as their enrichment properties ($N_{i}$, $N'_{i}$,
 $N''_{i}$,$\theta_{i}$i).
-% might be more useful to the reader to say this in words instead of variables,
-% i.e. adding stages until the product assay of the final stage is greater than
-% or equal to than the desired assay, and the tails assay is similarly less than
-% or equal to the desired tails assay
 
 The second step determines how to populate the cascade with the user-defined
-maximum number of centrifuges. One first solves the linear flow equation to
+maximum number of centrifuges. One then solves the linear flow equation to
 determine the theoretical flow in the cascade.
@@
 true flow enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed
-assay $N'$ and the feed to product ratio $\alpha$ do not change from stage to
+assay ($N'$), they do not change from stage to
 stage. According to equation \eqref{eq:beta}, when $\alpha$ and $\theta$ are
-fixed, if the feed assay, $N$ changes, then $\beta$ will change accordingly.
-This brakes the ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq
+fixed, whenthe feed assay ($N$) changes, then $\beta$ will change accordingly.
+This breaks the ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq
 N''_{i+1}$.
 
-In order to compute the proper product and tails assay at each stages\, the
+In order to compute the proper product and tails assay at each stage, the
 tails and the product from respectively the next and the previous stage must be
 blended in order to determine the correct stage feed assay. As this is a obvious
-cycling problem, it has been chosen to solve it iteratively: all feed assay are
-iteratively updated, blending the proper product and tail, then using the
-updated feed assay, the new product and tail assay are recomputed. This process
+cycling problem, an iterative solution has been chosen: all feed assays are
+iteratively updated, blending the proper product and tails, then using the
+updated feed assay, the new product and tail assays are recomputed. This process
 is repeated until the change in assays is smaller than the set precision (1e-8
@@
 
-As explained previously, the goal of this work is to assess the rate of the
+As explained previously, the goal of this work is to assess the rate of
 highly-enriched uranium (HEU) production using enrichment cascades designed
-within the JCPOA agreement constraints. For this work, two different cases will
-be investigated and compared to the reference case.
+near, but not within, the JCPOA agreement constraints. For this work, two different cases will
+be investigated and compared to a reference case that is based on the most efficient use of the 5060 available centrifuges.
 
 All cases will be considered with and without tail recycling. Figure
-\ref{fig:flow} shows the different flows between the different facilities in the
-fleet, in a configuration with two different levels of cascade without tail
-recycling. When considering the tail recycling, all the flow going from a
+\ref{fig:flow} shows the material flows between the different facilities in the
+fleet, in a configuration with two "levels" of cascades without tail
+recycling. When considering the tail recycling, all of the flow going from a
 cascade to the waste, are going from the cascade $i$ to the cascade $i-1$.  The
-Storage are not required in Cyclus they have been added to ensure the proper
-material flow between the facilities (if a receiver facility input buffer is
-full then the sender facility will stop sending material to it, and will stop
-working when its own output buffer will be filled).
+Storage facilities are not required in Cyclus, but they have been added to ensure the proper
+material flow between the facilities.
+
+% you don't need this unless you want to explain how a buffer works (if a receiver facility input buffer is full then the sender facility will stop sending material to it, and will stop working when its own output buffer will be filled).
 
@@
 
-The reference case corresponds to the most ideal cascade design--utilizing all
-of the 5060 centrifuges available within JCPOA to produce an enriched product at
+The reference case corresponds to the most efficient cascade design--utilizing all
+of the 5060 centrifuges available within JCPOA in a single large cascade to produce an enriched product at
 $>90\%$ of U-235, stripping the tail product up to 0.28 $\%$ from a feed of
@@
 
-The case 1 is designed to configure 30 cascades in the scenario (the maximum
-allowable under the JCPOA agreement), all designed the same way. The basic
+The case 1 is designed to configure identical 30 cascades in the scenario (the maximum
+allowable under the JCPOA agreement). The basic
 properties are: less than 169 centrifuges per cascade, F/P/T assays of
-0.0071/0.035/0.003. The corresponding design includes 167 centrifuges, with
+0.0071/0.035/0.003. The corresponding cascade design includes 167 centrifuges, with
 respective F/P/T assays of 0.0071/0.0412842/0.00290548.
@@
 
-Case 2 also limited to 30 cascades in the scenario (the maximum allowable under
-the JCPOA agreement), but this time each level of cascades are designed to take
-feed from the previous level's product. Each cascade has 4 stripping stages and
+Case 2 is also limited to 30 cascades in the scenario (the maximum allowable under
+the JCPOA agreement), but this time each level of cascades are optimized for the feed they recieve from the previous level's product. Each cascade has 4 stripping stages and
 10 enriching stages.
@@
 \centering
+  \caption{Summary of cascade properties for each level}
 \begin{tabular}{cllll}
@@
 \end{tabular}
-  \caption{Summary of cascade properties for each level}
+
   \label{tab:cascadelvl}
@@
 
-A last round of optimization if then ran in order to limit the number of cascade
-level to the amount of level required produce HEU, and then to populate the
-different level with a total of 30 cascades in order to maximize the HEU
-production rate.
+One last round of optimization limits the number of cascade
+levels to the number of level required produce HEU, and then to populate each level with a total of 30 cascades in order to maximize the HEU production rate.
 
@@
 \centering
+\caption{Cascade effective $\theta$ by the level and case.}
 \begin{tabular}{cll}
@@
 \end{tabular}
-  \caption{Cascade effective $\theta$ by the level and case.}
+
   \label{tab:cascade_theta}
@@
 
-\subsubsection{tails recycling}
-When recycling the tails from the different cascade levels, both cases behave
-the same way. As the tails have an higher enrichment than the product then are
-blended to, recycling the tail has the effect to bump up the enrichment of the
+\subsubsection{Recycling tails}
+When recycling the tails from the each cascade level, both cases behave
+the same way. As the tails have an higher enrichment than the product they are
+blended to, recycling the tails has bumps up the enrichment of the
 product at each level (see Figure \ref{fig:assay_c1_r} and \ref{fig:assay_c2_r}).
@@
 
-Note that for the case 2, where the fourth stage could appear as useless only the
-blending of its tail allows the product of the third one to pass the $90\%$ threshold.
+Note that for case 2, a fourth level is needed while blending the tails for the product of the third level to pass the $90\%$ threshold.
 
@@
 \subsection{HEU flow rate}
-As shown Figure \ref{fig:heu_prod}, if using all the centrifuges available to
-build a big cascade dedicated to HEU production, only 8 months are required to
-produce 1 Significant Quantity (SQ) of HEU. Also it take significantly longer to
-build 1 SQ of HEU, without recycling the tails respectively 13 years and 3.5 year
+As shown Figure \ref{fig:heu_prod}, if all of the available centrifuges are dedicated to HEU production in one massive cascade, only 8 months are required to
+produce 1 Significant Quantity (SQ) of HEU. It also takes significantly longer to
+stockpile 1 SQ of HEU without recycling the tails, respectively 13 years and 3.5 years
 for the case 1 and 2 versus about 2 years with tail recycling.
@@
 
-It is also interesting to note that despite requiring more level of cascade to
-reach an enrichment of $90\%$ the second case with tail recycling produces HEU
-at a equivalent rate than the case 1. The production rate seems to be faster but
-require more time to reach the maximum production rate (the material have to
-flow through more levels to reach the final level).
+Despite requiring more levels of cascades to
+reach an enrichment of $90\%$, the second case with tail recycling produces HEU
+at a equivalent rate to case 1. The production rate is faster, but
+require more times to reach the maximum production rate. This is because the material has to
+flow through more levels to reach its final level.
 

### 2018-01-27 paper.tex

@@
   \centering
-  \includegraphics[scale=0.7]{flow_case_2_no_recy.pdf}
+  \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
   \caption{Illustration of the material flow between the different level of
-      cascades without tail recycling, in this diagram, nu\_src correspond to an
-      infinite source of natural uranium, cascade\_ $n$ and storage\_ $n$
-      corresponds respectively to the cascades, and the storage getting the
-  products of the cascades at the level $n$.}\label{fig:flow}
+      cascades without tail recycling, in this diagram, nu\_src corresponds to
+      an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
+      $\{n\}$ to the cascade and the storage getting the products of the
+      cascades at the level $\{n\}$.}\label{fig:flow}
 \end{figure}
@@
 0.0071/0.035/0.003. The corresponding cascade design includes 167 centrifuges, with
-respective F/P/T assays of 0.0071/0.0412842/0.00290548.
+respective F/P/T assays of 0.0071/0.0413/0.002.
 

### 2018-01-27 paper.tex
...
1 typo + formating

@@
 stage. According to equation \eqref{eq:beta}, when $\alpha$ and $\theta$ are
-fixed, whenthe feed assay ($N$) changes, then $\beta$ will change accordingly.
+fixed, when the feed assay ($N$) changes, then $\beta$ will change accordingly.
 This breaks the ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq
@@
 highly-enriched uranium (HEU) production using enrichment cascades designed
-near, but not within, the JCPOA agreement constraints. For this work, two different cases will
-be investigated and compared to a reference case that is based on the most efficient use of the 5060 available centrifuges.
+near, but not within, the JCPOA agreement constraints. For this work, two
+different cases will be investigated and compared to a reference case that is
+based on the most efficient use of the 5060 available centrifuges.
 
@@
 \ref{fig:flow} shows the material flows between the different facilities in the
-fleet, in a configuration with two "levels" of cascades without tail
-recycling. When considering the tail recycling, all of the flow going from a
-cascade to the waste, are going from the cascade $i$ to the cascade $i-1$.  The
-Storage facilities are not required in Cyclus, but they have been added to ensure the proper
-material flow between the facilities.
+fleet, in a configuration with two "levels" of cascades without tail recycling.
+When considering the tail recycling, all of the flow going from a cascade to the
+waste, are going from the cascade $i$ to the cascade $i-1$.  The Storage
+facilities are not required in Cyclus, but they have been added to ensure the
+proper material flow between the facilities.
 
@@
 
-The reference case corresponds to the most efficient cascade design--utilizing all
-of the 5060 centrifuges available within JCPOA in a single large cascade to produce an enriched product at
-$>90\%$ of U-235, stripping the tail product up to 0.28 $\%$ from a feed of
-natural uranium.  The design cascade in this case, includes 4 stripping stages,
-and 38 enriching stages. The Feed/Product/Tail (F/P/T) assays are respectively
-0.0071/0.903/0.0028.
+The reference case corresponds to the most efficient cascade design--utilizing
+all of the 5060 centrifuges available within JCPOA in a single large cascade to
+produce an enriched product at $>90\%$ of U-235, stripping the tail product up
+to 0.28 $\%$ from a feed of natural uranium.  The design cascade in this case,
+includes 4 stripping stages, and 38 enriching stages. The Feed/Product/Tail
+(F/P/T) assays are respectively 0.0071/0.903/0.0028.
 
@@
 
-Case 2 is also limited to 30 cascades in the scenario (the maximum allowable under
-the JCPOA agreement), but this time each level of cascades are optimized for the feed they recieve from the previous level's product. Each cascade has 4 stripping stages and
-10 enriching stages.
+Case 2 is also limited to 30 cascades in the scenario (the maximum allowable
+under the JCPOA agreement), but this time each level of cascades are optimized
+for the feed they receive from the previous level's product. Each cascade has 4
+stripping stages and 10 enriching stages.
 
@@
 
-One last round of optimization limits the number of cascade
-levels to the number of level required produce HEU, and then to populate each level with a total of 30 cascades in order to maximize the HEU production rate.
+One last round of optimization limits the number of cascade levels to the number
+of level required produce HEU, and then to populate each level with a total of
+30 cascades in order to maximize the HEU production rate.
 
@@
 
-Note that for case 2, a fourth level is needed while blending the tails for the product of the third level to pass the $90\%$ threshold.
+Note that for case 2, a fourth level is needed while blending the tails for the
+product of the third level to pass the $90\%$ threshold.
 
@@
 \subsection{HEU flow rate}
-As shown Figure \ref{fig:heu_prod}, if all of the available centrifuges are dedicated to HEU production in one massive cascade, only 8 months are required to
-produce 1 Significant Quantity (SQ) of HEU. It also takes significantly longer to
-stockpile 1 SQ of HEU without recycling the tails, respectively 13 years and 3.5 years
-for the case 1 and 2 versus about 2 years with tail recycling.
+As shown Figure \ref{fig:heu_prod}, if all of the available centrifuges are
+dedicated to HEU production in one massive cascade, only 8 months are required
+to produce 1 Significant Quantity (SQ) of HEU. It also takes significantly
+longer to stockpile 1 SQ of HEU without recycling the tails, respectively 13
+years and 3.5 years for the case 1 and 2 versus about 2 years with tail
+recycling.
 
@@
 
-Despite requiring more levels of cascades to
-reach an enrichment of $90\%$, the second case with tail recycling produces HEU
-at a equivalent rate to case 1. The production rate is faster, but
-require more times to reach the maximum production rate. This is because the material has to
-flow through more levels to reach its final level.
+Despite requiring more levels of cascades to reach an enrichment of $90\%$, the
+second case with tail recycling produces HEU at a equivalent rate to case 1. The
+production rate is faster, but require more times to reach the maximum
+production rate. This is because the material has to flow through more levels to
+reach its final level.
 

### 2018-01-27 paper.tex
adding paper.pdf

@@
 \cite{cyclus} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
-simulation framework in order to demonstrate that such analysis can be
+simulation simulator in order to demonstrate that such analysis can be
 integrated into a fuel cycle with material flowing among multiple facilities.

### 2018-01-27 paper.tex
adding centrifuge parameter table

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Modeling potential JCPOA diversion scenarios using Cyclus}
+\title{Enrichment Cascade Alternatives under JCPOA}
 \author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
@@
 differential equation for the gas centrifuge as described in \cite{glaser.2008}.
-Centrifuge parameters, such as average gas temperature, rotation speed, height,
-feed flow rate, diameter, pressure ratio, counter-current flow ratio, and
-efficiency have been chosen to match the cascade design describe in
+Centrifuge parameters, such as average gas temperature, $T$, peripheral speed,
+$v$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
+counter-current flow ratio, $L/P$, and efficiency, $e$ have been chosen (Table
+\ref{tab:centrifuges}) to match the cascade design describe in
 \cite{glaser.2008} and \cite{walker.2017}.  These parameters for a P1-type
 centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.
+
+\begin{table}[htb]
+\centering
+\caption{Summary of the centrifuge parameters.}
+\begin{tabular}{cccccccc}
+\toprule
+$T$[K] & $v$[m/s]    & $h$[m] & $d$[m]   & $x$   & $F$[mg/s]  & $L/F$ & $e$  \\
+\midrule
+320    & $320$           & $1.8$ & $0.105$ & $1e3$  & $13$      & 2     & 1.0  \\
+\bottomrule
+\end{tabular}
+
+  \label{tab:centrifuges}
+\end{table}
 
@@
 \begin{equation}\label{eq:beta}
-    \beta = R
-              \dfrac{1 - \dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
-                   {\dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
+    \beta =   \left(1 - \dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 -
+              \theta}\right)
+              \left(\dfrac{R}{\dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1
+              - \theta}}\right)
 \end{equation}
@@
 \begin{eqnarray}
-    \theta_{i} &=& \dfrac{N_{i} - N''_{i}}{N'_{i}-N''_{i}}\nonumber\\
-           &=& \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
+    \theta_{i} = \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
            \dfrac{1}{1 + \beta/R_{i}}}
+%%    \theta_{i} &=& \dfrac{N_{i} - N''_{i}}{N'_{i}-N''_{i}}\nonumber\\
+%%           &=& \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
+%%           \dfrac{1}{1 + \beta/R_{i}}}
 \end{eqnarray}

### 2018-01-27 paper.tex
update fig, fix caption

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Enrichment Cascade Alternatives under JCPOA}
+\title{Modeling potential JCPOA diversion scenarios with Cyclus}
 \author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
@@
 \centering
-  \caption{Summary of cascade properties for each level}
+  \caption{Summary of cascade properties for each level.}
 \begin{tabular}{cllll}
@@
 
-\subsubsection{Recycling tails}
+\subsubsection{With tail recycling}
 When recycling the tails from the each cascade level, both cases behave

### 2018-05-03 paper.tex
cleaning

--- 2018-01-27 paper.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Modeling potential JCPOA diversion scenarios using Cyclus}
+\title{Modeling potential JCPOA diversion scenarios with Cyclus}
 \author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
@@
 
-The Joint Comprehensive Plan of Action (JCPOA)\cite{jcpoa} %cite JCPOA agreement
-limits the Iranian nuclear program and, in return, lifts many of the economic
-sanctions that had been placed on Iran. Under the JCPOA, Iran is severely
-limited in its ability to enrich uranium. This paper presents a model to probe
-the enriching ability of various cascade configurations that are related to
-JCPOA agreement limits. The analysis was performed using the Cyclus fuel cycle
-\cite{cyclus} %cite Fundamental concepts in the Cyclus nuclear fuel cycle
-simulation simulator in order to demonstrate that such analysis can be
-integrated into a fuel cycle with material flowing among multiple facilities.
-
-The Cyclus fuel cycle simulator is designed to support the dynamic addition of
-novel facility models into fuel cycles with both declared and undeclared facilities.
-The CascadeEnrich archetype\cite{mbmore.2018} was developed to model gas centrifuge
-enrichment cascades at a higher fidelity than previous enrichment models,
-relying on individual centrifuge and cascade design parameters to build an ideal
-cascade configuration instead of integral facility parameters. Once a
-CascadeEnrich facility is deployed, it may be asked to participate in the fuel
-cycle at a variety of flow rates and enrichments over time, constrained by the
-initial design of the cascade.
-
-This analysis introduces a facility with parameters consistent with the
-JCPOA-defined capacity and explores its performance when asked to enrich
-material above JCPOA limits. Although the analytical aspect of this analysis can
-be performed using other tools, a fuel cycle simulator provides value in further
-extensions of this work. Studying the internal behavior of a cascade, or rather
-a set of cascades organized into levels that feed into each other, identifies
-the most effective ways that enrichments higher than the JCPOA-allowed 3.67\%
-U-235 could be produced. However, this is only one step in a safeguards program.
-
-Performing enrichment cascade analysis within a fuel cycle simulator offers the
-opportunity to study the \textit{external} behavior of an enrichment facility as
-well as internal. When an enrichment facility that is not complying with the
-JCPOA is forced to participate in a larger fuel cycle---where it must purchase
-natural uranium and interact with outside facilities, it will act differently
-than an enrichment facility that \textit{is} fully complying with the JCPOA. The
-levels of cascades developed in this paper will ultimately be used to probe
-these differences and reveal patterns useful for a safeguards program.
-
 \section{Cascade Enrich Construction}
@@
 
-The present work uses the analytical solution by R\"aetz \cite{raetz.phd} of the
-differential equation for the gas centrifuge as described in \cite{glaser.2008}.
-Centrifuge parameters, such as average gas temperature, rotation speed, height,
-feed flow rate, diameter, pressure ratio, counter-current flow ratio, and
-efficiency have been chosen to match the cascade design describe in
-\cite{glaser.2008} and \cite{walker.2017}. These parameters for a P1-type
-centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.
-
-\subsection{Cascade Design}
-
-The cascade is built to be ideal, defined by $\alpha =\beta = const$ for all
-stage of the cascade, where $\alpha$ and $\beta$ respectively represent the feed
-to product and the feed to tail enrichment factors.  $\alpha$ can be expressed
-as a function of the feed rate $F$, the separative performance $\delta
-U(\theta)$, the cut $\theta$, and $\beta$ as a function of $alpha$ and $\theta$:
-
-\begin{subequations} \label{eqs:alphabeta}
-    \begin{equation} \label{eq:alpha}
-    \alpha = \sqrt{\frac{2\delta U}{F} \frac{1-\theta}{\theta}}+1
-\end{equation}
-\\
-\begin{equation}\label{eq:beta}
-    \beta = R
-              \dfrac{1 - \dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
-                   {\dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 - \theta}}
-\end{equation}
-\end{subequations}
-
-From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
-the cut, or the ratio of product flow to feed flow
-%(all other centrifuge parameters been fixed) allowing the have $\alpha=\beta$
-required to build an ideal cascade.
-
-Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
-$\theta_{i}$, changes in each stage $i$ of a cascade.
-
-It can be shown that $\theta_{i}$ can be computed from $\alpha$,
-$\beta$ values and the feed assay, $N_{i}$:
-\begin{eqnarray}
-    \theta_{i} &=& \dfrac{N_{i} - N''_{i}}{N'_{i}-N''_{i}}\nonumber\\
-           &=& \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
-           \dfrac{1}{1 + \beta/R_{i}}}
-\end{eqnarray}
-
-This algorithm assumes that the corresponding separative power $\delta U$ (not
-re-computed) can be achieved with the chosen centrifuge design. Once
-$\theta_{i}$ is determined, it is possible to compute the product and the tail
-assay.
-
-The design of the cascade is performed through 2 steps. First one determines the
-configuration and number of stages, adding stages until the product assay of the final stage is greater than or equal to than the desired assay, and the tails assay is similarly less than or equal to the desired tails assay.
-This determines the number of enriching and stripping stages as
-well as their enrichment properties ($N_{i}$, $N'_{i}$,
-$N''_{i}$,$\theta_{i}$i).
-
-The second step determines how to populate the cascade with the user-defined
-maximum number of centrifuges. One then solves the linear flow equation to
-determine the theoretical flow in the cascade.
-%%
-%% \begin{strip}
-%% \begin{equation}
-%% \setcounter{MaxMatrixCols}{20}
-%% \begin{bmatrix}
-%% -1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
-%% \theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
-%%            &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
-%% 0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
-%%            &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
-%% 0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
-%% 0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
-%% \end{bmatrix}
-%% \times
-%% \begin{bmatrix}
-%%      F_{S}   \\
-%%      F_{S+1} \\
-%%      \cdots  \\
-%%      F_{0}   \\
-%%     \cdots   \\
-%%     F_{E-1}  \\
-%%     F_{E}
-%% \end{bmatrix}
-%% =
-%% \begin{bmatrix}
-%%      0   \\
-%%      0 \\
-%%      \cdots  \\
-%%      F   \\
-%%     \cdots   \\
-%%     0  \\
-%%     0
-%% \end{bmatrix}
-%% %\caption{caption needed!}
-%% \label{eq:flow}
-%% \end{equation}
-%% \end{strip}
-Once the relative flow of each stage has been determined, the
-cascade can be populated with actual machines up the stages
-until either the maximum number available of machines or the maximum feed
-flow is reached.
-
-\subsection{Response to an non-ideal feed - $\theta_{i} = const$ hypothesis}
-
-Little information is available about the optimum way to tune a cascade that is
-being fed a feed enrichment that does not match its ideal enrichment.
-
-The tuning method outlined here does not re-optimize $\theta_i$ based on the
-true flow enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed
-assay ($N'$), they do not change from stage to
-stage. According to equation \eqref{eq:beta}, when $\alpha$ and $\theta$ are
-fixed, when the feed assay ($N$) changes, then $\beta$ will change accordingly.
-This breaks the ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq
-N''_{i+1}$.
-
-In order to compute the proper product and tails assay at each stage, the
-tails and the product from respectively the next and the previous stage must be
-blended in order to determine the correct stage feed assay. As this is a obvious
-cycling problem, an iterative solution has been chosen: all feed assays are
-iteratively updated, blending the proper product and tails, then using the
-updated feed assay, the new product and tail assays are recomputed. This process
-is repeated until the change in assays is smaller than the set precision (1e-8
-by default).
-
-Other hypotheses will be explored in the future, such as maintaining the ideal
-stage of the cascade through tuning the cut values $\theta_{i}$ of each stage of
-the cascade, or maintaining $\alpha*\beta = const$ as described in
-\cite{walker.2017}.
-
-Note that as a consequence of our design method, the cascade product and tail
-assay will not necessary match the targeted values, and usually slightly over
-enrich and over strip the product and the tail respectively.
-
-\section{The experiment}
-
-As explained previously, the goal of this work is to assess the rate of
-highly-enriched uranium (HEU) production using enrichment cascades designed
-near, but not within, the JCPOA agreement constraints. For this work, two
-different cases will be investigated and compared to a reference case that is
-based on the most efficient use of the 5060 available centrifuges.
-
-All cases will be considered with and without tail recycling. Figure
-\ref{fig:flow} shows the material flows between the different facilities in the
-fleet, in a configuration with two "levels" of cascades without tail recycling.
-When considering the tail recycling, all of the flow going from a cascade to the
-waste, are going from the cascade $i$ to the cascade $i-1$.  The Storage
-facilities are not required in Cyclus, but they have been added to ensure the
-proper material flow between the facilities.
-
-% you don't need this unless you want to explain how a buffer works (if a receiver facility input buffer is full then the sender facility will stop sending material to it, and will stop working when its own output buffer will be filled).
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
-  \caption{Illustration of the material flow between the different level of
-      cascades without tail recycling, in this diagram, nu\_src corresponds to
-      an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
-      $\{n\}$ to the cascade and the storage getting the products of the
-      cascades at the level $\{n\}$.}\label{fig:flow}
-\end{figure}
-
 \subsection{Explored Cases}
-%\subsubsection{Reference Case}
-
-The reference case corresponds to the most efficient cascade design--utilizing
-all of the 5060 centrifuges available within JCPOA in a single large cascade to
-produce an enriched product at $>90\%$ of U-235, stripping the tail product up
-to 0.28 $\%$ from a feed of natural uranium.  The design cascade in this case,
-includes 4 stripping stages, and 38 enriching stages. The Feed/Product/Tail
-(F/P/T) assays are respectively 0.0071/0.903/0.0028.
-
-%\subsubsection{Case 1}
-
-The case 1 is designed to configure identical 30 cascades in the scenario (the maximum
-allowable under the JCPOA agreement). The basic
-properties are: less than 169 centrifuges per cascade, F/P/T assays of
-0.0071/0.035/0.003. The corresponding cascade design includes 167 centrifuges, with
-respective F/P/T assays of 0.0071/0.0413/0.002.
-
-%\subsubsection{Case 2}
-
-Case 2 is also limited to 30 cascades in the scenario (the maximum allowable
-under the JCPOA agreement), but this time each level of cascades are optimized
-for the feed they receive from the previous level's product. Each cascade has 4
-stripping stages and 10 enriching stages.
-
-\begin{table}[htb]
-\centering
-  \caption{Summary of cascade properties for each level}
-\begin{tabular}{cllll}
-\toprule
-
-Level   &           & Assay     &       & Machines  \\
-        & Feed      & Product   & Feed  &           \\
-\midrule
-0       & 0.0071    & 0.0413    & 0.0029 & 167       \\
-1       & 0.0413    & 0.2043    & 0.0173 & 169       \\
-2       & 0.2043    & 0.5941    & 0.0971 & 168       \\
-3       & 0.5941    & 0.8834    & 0.3915 & 168       \\
-4       & 0.8834    & 0.9735    & 0.7746 & 169       \\
-
-\bottomrule
-\end{tabular}
-
-  \label{tab:cascadelvl}
-\end{table}
-
-The configuration of cascade levels can be found in table
-\ref{tab:cascadelvl}. Unlike case 1, the organization of centrifuges varies from
-level to level. Each level is re-optimized to have the most efficient number of
-centrifuges in each stage, although the total number of stages remains constant.
-
-\subsection{Level optimization}
-
-One last round of optimization limits the number of cascade levels to the number
-of level required produce HEU, and then to populate each level with a total of
-30 cascades in order to maximize the HEU production rate.
-
-\section{Results}
-\subsection{Enrichment}
-\subsubsection{Without tail recycling}
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
-  \caption{Evolution of the different product assays at each cascade level for
-  the case 1 without recycling. The blue line represents the $90\%$ enrichment
-  threshold.}\label{fig:assay_c1_nr}
-\end{figure}
-Despite the reconfiguration of each level occurring in the second case, the case
-1 is notably more effective in producing HEU than case 1. Indeed, as observed in
-Figure \ref{fig:assay_c1_nr} and \ref{fig:assay_c2_nr}, the first case is able
-to produce an uranium product enrich at $98\%$ while the second case is only
-able to reach an enrichment of $88.3\%$ with the same number of levels.
-
-Because the cut value $\theta_i$ at each stage is unchanged, case 2 artificially
-produces over-enriched tails when fed with higher enriched materials compared
-to a cascade feed with the same feed assay but with a cascade designed for it.
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
-  \caption{Evolution of the different product assays at each cascade level for
-  the case 2 without recycling. }\label{fig:assay_c2_nr}
-\end{figure}
-
-% ^ the above paragraph is confusing but I don't understand it enough to fix it
-
-The effective cut values for each cascade can be computed as :
-
-\begin{equation}\label{eq:theta_eff}
-    \theta = \dfrac{N - N''}{N'-N''}
-\end{equation}
-
-As illustrated in Table \ref{tab:cascade_theta}, the effective cut
-of each level increases up to $0.54$ for the fifth stage for case 2. The high
-effective cut value increase the product production rate but decrease the
-enrichment ratio.
-\begin{table}[htb]
-\centering
-\caption{Cascade effective $\theta$ by the level and case.}
-\begin{tabular}{cll}
-\toprule
-
-Level   &  $\theta_{eff}^{C1}$   & $\theta_{eff}^{C2}$ \\
-\midrule
-1       & 0.109375               & 0.109375     \\
-2       & 0.109375               & 0.128342     \\
-3       & 0.109375               & 0.215694     \\
-4       & 0.109375               & 0.411872     \\
-5       & 0.109375               & 0.547009     \\
-
-\bottomrule
-\end{tabular}
-
-  \label{tab:cascade_theta}
-\end{table}
-
-\subsubsection{Recycling tails}
-When recycling the tails from the each cascade level, both cases behave
-the same way. As the tails have an higher enrichment than the product they are
-blended to, recycling the tails has bumps up the enrichment of the
-product at each level (see Figure \ref{fig:assay_c1_r} and \ref{fig:assay_c2_r}).
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.5\textwidth]{assay_case_1_rec.png}
-  \caption{Evolution of the different product assays at each cascade level for
-  the case 1 with recycling. }\label{fig:assay_c1_r}
-\end{figure}
-
-Note that for case 2, a fourth level is needed while blending the tails for the
-product of the third level to pass the $90\%$ threshold.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.5\textwidth]{assay_case_2_rec.png}
-  \caption{Evolution of the different product assays at each cascade level for
-  the case 2 with recycling.}\label{fig:assay_c2_r}
-\end{figure}
-
-\subsection{HEU flow rate}
-As shown Figure \ref{fig:heu_prod}, if all of the available centrifuges are
-dedicated to HEU production in one massive cascade, only 8 months are required
-to produce 1 Significant Quantity (SQ) of HEU. It also takes significantly
-longer to stockpile 1 SQ of HEU without recycling the tails, respectively 13
-years and 3.5 years for the case 1 and 2 versus about 2 years with tail
-recycling.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[width=0.5\textwidth]{HEU_prod.png} \caption{Evolution of the
-  amount of HEU in the storage. The blue line correspond to 1 SQ of HEU
-  ($25~$kg). Cx, RT(NRT) represents the different cases with (no)tail recycling
-  with the cascade population per level and REF the reference
-  case.}\label{fig:heu_prod}
-\end{figure}
-
-Despite requiring more levels of cascades to reach an enrichment of $90\%$, the
-second case with tail recycling produces HEU at a equivalent rate to case 1. The
-production rate is faster, but require more times to reach the maximum
-production rate. This is because the material has to flow through more levels to
-reach its final level.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-The JCPOA agreement limits the Natanz Fuel Enrichment Plant (NFEP) to 5060
-operating centrifuges, or about $10\%$ of its design capacity. The reference
-case, using all 5060 centrifuges in a single cascade, would lead to a stockpile
-of approximately $1$ SQ of HEU in 8 months, as opposed to 24 days without the
-JCPOA agreement limitations. However, the more realistic case 1 and the case 2
-will produce a $1$ SQ in about 2 years. Nevertheless, the diversion scenario
-from case 1 or 2 would be much more difficult to detect from the cascade
-configuration.
-
-While the results of this work might be limited, it aims to develop a
-methodology to study diversion scenarios from the fuel cycle perspective.
-Furthermore, additional methods to compute the CascadeEnrich response to
-non-ideal feed assays will be investigated in the future.  The CascadeEnrich
-facility will be improved in order to take advantage of the dynamic flow
-management of the Cyclus framework. This will include automatic cascade level
-assignment to optimize the analysis workflow.
 
@@
 
+%% \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+%%   \centering
+%%   \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
+%%   \caption{Illustration of the material flow between the different level of
+%%       cascades without tail recycling, in this diagram, nu\_src corresponds to
+%%       an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
+%%       $\{n\}$ to the cascade and the storage getting the products of the
+%%       cascades at the level $\{n\}$.}\label{fig:flow}
+%% \end{figure}
+
+%% \begin{table}[htb]
+%% \centering
+%%   \caption{Summary of cascade properties for each level.}
+%% \begin{tabular}{cllll}
+%% \toprule
+%% 
+%% Level   &           & Assay     &       & Machines  \\
+%%         & Feed      & Product   & Feed  &           \\
+%% \midrule
+%% 0       & 0.0071    & 0.0413    & 0.0029 & 167       \\
+%% 1       & 0.0413    & 0.2043    & 0.0173 & 169       \\
+%% 2       & 0.2043    & 0.5941    & 0.0971 & 168       \\
+%% 3       & 0.5941    & 0.8834    & 0.3915 & 168       \\
+%% 4       & 0.8834    & 0.9735    & 0.7746 & 169       \\
+%% 
+%% \bottomrule
+%% \end{tabular}
+%% 
+%%   \label{tab:cascadelvl}
+%% \end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-05-03 paper.tex
first draft of introduction

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Modeling potential JCPOA diversion scenarios with Cyclus}
+\title{}
 \author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}
@@
 
-\section{Cascade Enrich Construction}
-\subsection{Centrifuge properties}
+Fuel cycle simulations, as any simulation process, do not produce results
+without errors. Those errors have different sources: data uncertainties (when
+the simulation relies on previously estimated/measured metrics), modeling
+uncertainties (produced by the simplification made by the simulator) and the
+``functional`` uncertainty (uncertainty on the operation parameters of the
+different facilities).
 
-\subsection{Explored Cases}
+Some treaty verification scenarios require estimating historical fissile
+material production based on records of facility operation and material
+transfer.  If the measurements of facility operation and material transfer are
+subject to uncertainty, the total production quantities will then also be
+uncertain, creating an opportunity for undetected diversion.  This study seeks
+to understand which measures of facility operation have the most impact on the
+uncertainty of fissile material production across a complete fuel cycle.  A
+``Total Monte Carlo'' approach will be applied to the Cyclus fuel cycle simulator
+\cite{cyclus} to estimate output metrics uncertainty caused by individual
+facility uncertainties.
+
+\section{Method}
+
+To estimate the uncertainty on fuel cycle output metrics, a ``Total Monte
+Carlo'' approach has been applied. In the following, output metric uncertainty
+corresponds to the Standard Deviation of the output metrics over about 200
+different simulations. For each uncertainty associated parameter, an
+artificially large uncertainty of $10\%$ have been Normally distributed.
+
+To pursuit this work, both the Cycamore\cite{cycamore} package and the
+CyCLASS\cite{cyclass} have been updated to deal with uncertainty in different
+operational parameters of their different facility.  Table
+\ref{tab:package_uncertainty} summarize all the modification implemented in the
+different facilities present in Cycamore and CyCLASS.
+
+ \begin{table}[htb]
+ \centering
+   \caption{Summary of facility modification per source package.}
+ \begin{tabular}{cll}
+ \toprule
+
+ Packae   & Facility   & Parameters                \\
+ \midrule
+ Cycamore & Enrichment & Tail Assay                \\
+          & Separation & Separation efficiency     \\
+          & Storage    & Residence Time            \\
+ \midrule
+ CyCLASS  & Reactor    & Cycle Length              \\
+          &            & Power                     \\
+          &            & Fuel Enrichment (PWR-UOX) \\
+
+ \bottomrule
+ \end{tabular}
+
+   \label{tab:package_uncertainty}
+ \end{table}
+
+\section{The Experiment}
 

### 2018-05-03 paper.tex
done with Uncertainty measurement section

@@
 \newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
+
+\usepackage[acronym]{glossaries}
+\newacronym{UOX}{UOX}{uranium oxide fuel}
+\newacronym{MOX}{MOX}{mixed oxide fuel}
+\newacronym{LWR}{LWR}{light water reactor}
+\newacronym{FBR}{FBR}{fast breeder reactor}
 
@@
 
- Packae   & Facility   & Parameters                \\
+Package   & Facility   & Parameters                \\
 \midrule
@@
 \section{The Experiment}
+\subsection{The Fuel Cycle}
+This work aims to assess the impact of the functional uncertainties of a
+simple transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening And
+Evaluation Group\cite{FCO}: a transition from light water reactors fleet loaded
+with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX} fuel, considering an
+$1\%/$y grows of the generated power (Figure \ref{fig:power}).
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[scale=0.31]{cycle.png}
+  \caption{Illustration of the material flow between the different facilities,
+  with in green each operational parameters associated with an
+  uncertainty.}\label{fig:cycle}
+\end{figure}
+
+As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
+fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
+transition starts around year 35, with the deployment of \glspl{FBR}, loaded
+with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
+uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
+\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
+ratio.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+  \centering
+  \includegraphics[scale=0.32]{power.png}
+  \caption{Electric power generated over time, with in blue the full production,
+      in orange the \glspl{LWR} contribution, in green the hight breeding ratio
+    \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}
+    \label{fig:power}
+\end{figure}
+
+The plutonium, required for the \glspl{MOX} fabrication, is reprocessed
+from all used fuel, at first only used UOX, then used MOX fuel as they start to
+be available for reprocessing.
+
+Both fuel reprocessing and fabrication are done at a constant rate (constrained
+by the feed materials availabilities). The enrichment of the UOX is processed on
+demand. Buffer storages (not shown on Figure \ref{fig:cycle}) is present between
+all facilities with constant processing rates.
+
+\subsection{Uncertainty Measurements}
+In this specific study, one will only focus on the uncertainty on the produced
+electric power as a function of time, on the total quantity of natural uranium
+used and on the total unused fissile inventory (unused reprocessed plutonium).
+In order to estimate the total uncertainty on those 3 parameters as well as the
+individual contribution of the operational parameters several set of (199) simulations
+have been completed.
+
+In addition to the set with all parameters are sampled according to their
+uncertainty, a set a have been computed for each parameter, with all the other
+remaining fixed to the reference value.
 

### 2018-05-03 paper.tex
add power uncertainty section

@@
 
+\subsection{Generated Power}
+By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the generated power is expected. The
+transition scenario has been design to allow all the reactors to receive the
+fuel as needed allowing them to be producing power all the time.
+ \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+   \centering
+   \includegraphics[scale=0.37]{power_full}
+   \caption{Electric power generated as a function of time. The black line
+   represents the reference calculation(wihtout uncertainty), and the blue zone
+   represents the 1 $\sigma$ distribution uncertainty induced by the
+   uncertainty of all the operational parameters.}\label{fig:power_full}
+ \end{figure}
+ %%  \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+ %%    \centering
+ %%    \includegraphics[scale=0.37]{power_uncer}
+ %%    \caption{}\label{fig:power_uncer}
+ %%  \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-05-03 paper.tex
upadte power section

--- 2018-05-03 paper.tex
@@
         in orange the \glspl{LWR} contribution, in green the hight breeding ratio
-    \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}
-    \label{fig:power}
+        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
 \end{figure}
@@
 In order to estimate the total uncertainty on those 3 parameters as well as the
-individual contribution of the operational parameters several set of (199) simulations
-have been completed.
+individual contribution of the operational parameters several set of (199)
+simulations have been completed.  All uncertainty are computed as the standard
+deviation over over all the calculations in the set.
 
@@
 remaining fixed to the reference value.
+
+\subsection{Generated Power}
+By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
+generated power is expected.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.35]{power_full}
+    \caption{Electric power generated as a function of time. The black line
+        represents the reference calculation and the blue zone
+        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
+\end{figure}
+
+Indeed the transition scenario has been design to allow
+all the reactors to receive the fuel as needed allowing them to be producing
+power all the time. This ensure that the uncertainty measured on other
+parameters are not influence by the reactors miss-loadings.
+
+%%  \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+%%    \centering
+%%    \includegraphics[scale=0.37]{power_uncer}
+%%    \caption{}\label{fig:power_uncer}
+%%  \end{figure}
+
+\subsection{Natural Uranium Consumption}
+
+Figure \ref{fig:unat_full}| represents the cumulative natural uranium
+consumption as a function of time.
 

### 2018-05-03 paper.tex
adding unat figures

@@
 
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.35]{power_full}
+    \caption{Cumulative consumption of natural uranium as a function of time. The black line
+        represents the reference calculation and the blue zone
+        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:unat_full}
+\end{figure}
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.37]{unat_uncer}
+    \caption{Cumulative natural uranium consumption relative uncertainty, with
+    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
+    contribution of each parameter: cooling time (blue), fuel enrichment (red),
+    cycle time (green), thermal power(brown), separation efficiency (light blue)}
+    \label{fig:unatr_uncer}
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-05-04 paper.tex
update u nat uencrtainty

--- 2018-05-03 paper.tex
@@
 
-Figure \ref{fig:unat_full}| represents the cumulative natural uranium
-consumption as a function of time.
+Figure \ref{fig:unat_full} represents the cumulative natural uranium
+consumption as a function of time. The uncertainty on the cumulative uranium
+consumption grows as expected with the time and the loading of the \glspl{LWR}.
+The increase stops around year 125y with the decommissioning of the last
+\glspl{LWR}.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.35]{unat_full}
+    \caption{Cumulative consumption of natural uranium as a function of time. The black line
+        represents the reference calculation and the blue zone
+        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:unat_full}
+\end{figure}
+
+The fluctuation of the full relative uncertainty at low time are because of the
+sensitivity to the fuel loading: all reactors at the beginning have synchronised
+cycle, this phenomenon disappear with the gradual decommissioning of the initial
+reactor, spread on 50 years.
+
+\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.35]{unat_uncer}
+    \caption{Cumulative natural uranium consumption relative uncertainty, with
+    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
+    contribution of each parameter: cooling time (blue), fuel enrichment (red),
+    cycle time (green), thermal power(brown), separation efficiency (light
+    blue).}\label{fig:unatr_uncer}
+\end{figure}
+The relative uncertainty of the total uranium consumption starts at about
+$5.5\%$ a slowly drops and stabilise around $3\%$.
+
+As expected, cooling time, separation efficiency and thermal power does
+not affect the natural uranium consumption.
+The uncertainty on the natural uranium consumption is dominated by the
+\glspl{LWR} cycle length: shorter the cycle length is, the more fuel will be
+loaded.
+
+As the number of deployed \glspl{LWR} reactors increases, as each parameters is
+sampled once for each facilities, the average length of the cycle (as well as
+the number of loaded batches) converges to the reference value.
+The fuel enrichment and the tail assay contribution follow a smoother behavior,
+so as the total relative uncertainty decrease, their contribution increases over
+time.
 

### 2018-05-04 paper.tex
pu uncerintainty + adding discussion

@@
 \end{table}
+
+Note: the fuel enrichment is determined by a fuel fabrication model\cite{leniau} which
+express a fissile fraction required in the fuel to reach a target
+burnup at the end of irradiation. In this study, the uncertainty on the fuel
+enrichment is not applied directly on the effective enrichment but on the target
+parameter (the burnup), which leads to to a fuel enrichment uncertainty close to
+$10\%$.
 
@@
 sensitivity to the fuel loading: all reactors at the beginning have synchronised
-cycle, this phenomenon disappear with the gradual decommissioning of the initial
+cycle, this phenomenon disappears with the gradual decommissioning of the initial
 reactor, spread on 50 years.
@@
 time.
+
+\subsection{Fissile Inventory}
+As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow on
+year 40, with the deployment of the first reprocessing facility. It grows
+during the first period of the \glspl{LWR} to \glspl{FBR}-A transition until
+year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
+When he steady state is reached (full \glspl{FBR} fleet), the plutonium
+inventory starts to increase, as the breading ratio of the \glspl{FBR} is higher
+than the deployment needs.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.35]{pu_full}
+    \caption{Fissile (plutonium) inventory as a function of time. The black line
+        represents the reference calculation and the blue zone
+        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:pu_full}
+\end{figure}
+
+\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.35]{pu_uncer}
+    \caption{Fissile (plutonium) inventory relative uncertainty, with
+    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
+    contribution of each parameter: cooling time (blue), fuel enrichment (red),
+    cycle time (green), thermal power(brown), separation efficiency (light
+    blue).}\label{fig:pu_uncer}
+\end{figure}
+
+Regarding the uncertainty, beside the low inventory artefact observable around
+year 40, the relative uncertainty starts at about $5\%$, and grows until year
+125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
+it will reach an equilibrium between $5$ and $10\%$...
+Between year 40 and 70, the main contributor to the fissile inventory
+uncertainty is the cycle length, as for the uranium needs, lower cycle length
+implies more fuel loads. Never the less, around year 65 (see Figure
+\ref{fig:used_fuel}), the stock of used fuel available for reprocessing starts
+to lack, and the availability of the used fuel starts to dictate the evolution
+of fissile in storage. The uncertainty weight is then slowly transferred from
+the cycle length to the fuel cooling time.
+
+\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.17]{used_fuel}
+    \caption{Used fuel inventory.}\label{fig:used_fuel}
+\end{figure}
+Between year 90 and 120, the \glspl{FBR} deployment speed increases, it has to
+compensate the non replacement of the decommissioned \glspl{LWR} as well as
+follow the power demand. During this period the needs in plutonium are higher
+than its productions, explaining the observed decrease of the total amount, and
+the increase associated relative uncertainty.
+
+As the transition ends, the plutonium breed from the \glspl{FBR} starts to be
+sufficient to sustain the new \glspl{FBR} deployment to follow the power demand.
+
+It is also interesting to note that, the uncertainty contribution from the cycle
+length are conversion toward the power contribution, such as the increase of
+fuel loads effect tends to vanish and let its place to a discharge burnup
+effect (the power uncertainty only affects the burnup of the fuel at discharge).
+
+\section{Discussion}
+
+Even if for the two output metric analysed there is no surprise such as the
+identified uncertainty contributions, it is very interesting to be able to
+measure them and rank them.
+
+In this study, we can estimate than the cycle length uncertainty of $10\%$
+varies from $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
+on the enrichment implies a almost flat uncertainty of $2\%$, and the enrichment
+tails uncertainty have an even lower contributions of $1\%$.
+
+It is also very interesting to observe that while the plutonium inventory uncertainty
+reach a pick at $30\%$, lead by the cooling time uncertainty contribution, the reactor
+parameters seems to have a lower contribution, the cycle time contribution
+picking at $10\%$ and stabilizing with the power contribution around $1\%$
+
+Two main points can be deduced from this work. First of all, in a transitional
+fuel cycle, the uncertainty contributions to an output metric can vary over time
+depending of various factors: deployment schedule artifact or pressure point in
+the material flows.
 

### 2018-05-04 paper.tex
conclusion?!

@@
 corresponds to the Standard Deviation of the output metrics over about 200
-different simulations. For each uncertainty associated parameter, an
-artificially large uncertainty of $10\%$ have been Normally distributed.
+different simulations. For each deployed facilities, the uncertainty associated
+parameters have been a normally distributed with an artificially large standard
+deviation of $10\%$.
 
@@
 
-The plutonium, required for the \glspl{MOX} fabrication, is reprocessed
-from all used fuel, at first only used UOX, then used MOX fuel as they start to
-be available for reprocessing.
+The plutonium, required for the \glspl{MOX} fabrication, is reprocessed from all
+used fuel, at first only used UOX, then used MOX fuel as they start to be
+available for reprocessing.
 
@@
 
-Indeed the transition scenario has been design to allow
-all the reactors to receive the fuel as needed allowing them to be producing
-power all the time. This ensure that the uncertainty measured on other
-parameters are not influence by the reactors miss-loadings.
+Indeed the transition scenario has been design to allow all the reactors to
+receive the fuel as needed allowing them to be producing power all the time.
+This ensure that the uncertainty measured on other parameters are not influence
+by the reactors miss-loadings.
 
@@
 
-As expected, cooling time, separation efficiency and thermal power does
-not affect the natural uranium consumption.
-The uncertainty on the natural uranium consumption is dominated by the
-\glspl{LWR} cycle length: shorter the cycle length is, the more fuel will be
-loaded.
+As expected, cooling time, separation efficiency and thermal power does not
+affect the natural uranium consumption.  The uncertainty on the natural uranium
+consumption is dominated by the \glspl{LWR} cycle length: shorter the cycle
+length is, the more fuel will be loaded.
 
@@
 
-Two main points can be deduced from this work. First of all, in a transitional
+\section{Conclusion}
+
+Two main points can be deduced from this work. Firstly, in a transitional
 fuel cycle, the uncertainty contributions to an output metric can vary over time
@@
 the material flows.
+
+Secondly, it is important to note the special character of the time related
+parameters uncertainty in a fuel cycle study, such as cooling time and cycle
+length. As the cycle length impact the discharge fuel burnup, it also affects
+the frequency of the fuel loads, this, as well as the cooling may imply a
+uncertainty on the material availability, which could lead to a large
+uncertainty. Those kind of uncertainties will need a special treatment on further
+uncertainty analysis.
+
+This study aims to be a proof-of-principle for uncertainty propagation in
+potential commercial fuel cycle transition and will to be extended to random
+uncertainty.
+
+While the parameters contributing to natural uranium needs and fissile inventory
+uncertainties might be obvious, such study allows to estimate each parameters
+contribution, it could be less obvious for other parameters, such as
+plutonium quality, waste compositions. Such studies could also provide research
+guidance for nuclear archeology works, which aims to precisely estimate past
+fissile production by the different nuclear countries.
 

### 2018-05-04 paper.tex

@@
 to understand which measures of facility operation have the most impact on the
-uncertainty of fissile material production across a complete fuel cycle.  A
-``Total Monte Carlo'' approach will be applied to the Cyclus fuel cycle simulator
+uncertainty of fissile material production across a complete fuel cycle.  An
+approaching using Total Monte Carlo methodology will be applied to the Cyclus
+fuel cycle simulator
 \cite{cyclus} to estimate output metrics uncertainty caused by individual
@@
 
+% I don't think Total Monte Carlo should be in quotes
+
 \section{Method}
 
-To estimate the uncertainty on fuel cycle output metrics, a ``Total Monte
-Carlo'' approach has been applied. In the following, output metric uncertainty
+To estimate the uncertainty on fuel cycle output metrics, a Total Monte
+Carlo approach has been applied. In the following, output metric uncertainty
 corresponds to the Standard Deviation of the output metrics over about 200
@@
 To pursuit this work, both the Cycamore\cite{cycamore} package and the
-CyCLASS\cite{cyclass} have been updated to deal with uncertainty in different
-operational parameters of their different facility.  Table
-\ref{tab:package_uncertainty} summarize all the modification implemented in the
-different facilities present in Cycamore and CyCLASS.
+CyCLASS\cite{cyclass} have been updated to deal with uncertainty in several
+operational parameters of their associated facilities.  Table
+\ref{tab:package_uncertainty} summarizes all modificatiosn implemented in the
+range of facilities present in Cycamore and CyCLASS.
 
@@
 
-Note: the fuel enrichment is determined by a fuel fabrication model\cite{leniau} which
-express a fissile fraction required in the fuel to reach a target
+It must be noted that for this work, the fuel enrichment was determined by a
+fuel fabrication model\cite{leniau} which
+calculates the fissile fraction required in the fuel to reach a target
 burnup at the end of irradiation. In this study, the uncertainty on the fuel

### 2018-05-04 paper.tex
some rearanging

--- 2018-05-04 paper.tex
@@
 \subsection{The Fuel Cycle}
-This work aims to assess the impact of the functional uncertainties of a
-simple transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening And
-Evaluation Group\cite{FCO}: a transition from light water reactors fleet loaded
-with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX} fuel, considering an
-$1\%/$y grows of the generated power (Figure \ref{fig:power}).
+This work estimates the impact of the operationnal parameters uncertainty on a simple
+transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening
+And Evaluation Group\cite{FCO}: a transition from light water reactors fleet
+loaded with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX}
+fuel, considering an $1\%/$y grows of the generated power (Figure
+\ref{fig:power}).
+
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
@@
 with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
-uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
-\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
-ratio.
+uranium.
 
@@
     \centering
-    \includegraphics[scale=0.32]{power.png}
+    \includegraphics[scale=0.18]{power.png}
     \caption{Electric power generated over time, with in blue the full production,
-        in orange the \glspl{LWR} contribution, in green the hight breeding ratio
-        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
+        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}\label{fig:power}
 \end{figure}
@@
 
-\subsection{Uncertainty Measurements}
+\section{Results}
 In this specific study, one will only focus on the uncertainty on the produced
@@
 \subsection{Generated Power}
-By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
-generated power is expected.
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
     \centering
@@
 \end{figure}
+By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
+generated power is expected.
 
@@
 
-\section{Discussion}
+\subsection{Discussion}
 

### 2018-05-04 paper.tex

@@
 \subsection{Generated Power}
+By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
+generated power is expected.
 
@@
 \end{figure}
-By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
-generated power is expected.
 

### 2018-05-04 paper.tex
update experiment

--- 2018-05-04 paper.tex
@@
 This work aims to assess the impact of the functional uncertainties of a
-simple transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening And
-Evaluation Group\cite{FCO}: a transition from light water reactors fleet loaded
-with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX} fuel, considering an
-$1\%/$y grows of the generated power (Figure \ref{fig:power}).
+simple transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{FCO}: a transition from light water reactors fleet loaded
+with \glspl{UOX} fuel to a sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an
+$1\%/$y growth of the generated power (Figure \ref{fig:power}).
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
@@
 
-As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
-fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
+As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
+fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
 transition starts around year 35, with the deployment of \glspl{FBR}, loaded
-with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
+with \glspl{MOX}, consisting of plutonium blended with natural
 uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
@@
 
-The plutonium, required for the \glspl{MOX} fabrication, is reprocessed from all
-used fuel, at first only used UOX, then used MOX fuel as they start to be
+The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
+used fuel. At first , it is sourced only from UOX, then used MOX fuel as it becomes
 available for reprocessing.

### 2018-05-04 paper.tex
simple fixes

@@
     \centering
-    \includegraphics[scale=0.32]{power.png}
+    \includegraphics[scale=0.18]{power.png}
     \caption{Electric power generated over time, with in blue the full production,
@@
 
-\subsection{Uncertainty Measurements}
+\subsection{Results}
 In this specific study, one will only focus on the uncertainty on the produced
@@
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
     \centering
@@
 
-\section{Conclusion}
+\subsection{Conclusion}
 

### 2018-05-04 paper.tex
trying to not mess things up

@@
 
-\subsection{Results}
+\section{Results}
 In this specific study, one will only focus on the uncertainty on the produced
@@
 
-\subsection{Conclusion}
+\section{Conclusion}
 

### 2018-05-04 paper.tex
add bibliography

@@
 approaching using Total Monte Carlo methodology will be applied to the Cyclus
-fuel cycle simulator
-\cite{cyclus} to estimate output metrics uncertainty caused by individual
-facility uncertainties.
+fuel cycle simulator \cite{cyclus} to estimate output metrics uncertainty caused
+by individual facility uncertainties.
 
 % I don't think Total Monte Carlo should be in quotes
+\section{The Experiment}
 
-\section{Method}
+\subsection{Method}
 
@@
 
-To pursuit this work, both the Cycamore\cite{cycamore} package and the
-CyCLASS\cite{cyclass} have been updated to deal with uncertainty in several
+To pursuit this work, both the Cycamore\cite{cycamore} package\footnote{Low
+fidelity facilities package for Cyclus} and the
+CyCLASS\footnote{Reactor and Fuel fabrication facility based on
+    CLASS\cite{CLASS}  models} have been
+updated\cite{mouginot_2018, cyclass} to deal with uncertainty in several
 operational parameters of their associated facilities.  Table
-\ref{tab:package_uncertainty} summarizes all modificatiosn implemented in the
+\ref{tab:package_uncertainty} summarizes all modification implemented in the
 range of facilities present in Cycamore and CyCLASS.
@@
 \midrule
-Cycamore & Enrichment & Tail Assay                \\
-         & Separation & Separation efficiency     \\
+Cycamore & Separation & Separation efficiency     \\
          & Storage    & Residence Time            \\
@@
 It must be noted that for this work, the fuel enrichment was determined by a
-fuel fabrication model\cite{leniau} which
+fuel fabrication model\cite{Leniau2015125} which
 calculates the fissile fraction required in the fuel to reach a target
@@
 
-\section{The Experiment}
 \subsection{The Fuel Cycle}
-This work aims to assess the impact of the functional uncertainties of a
-simple transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{FCO}: a transition from light water reactors fleet loaded
-with \glspl{UOX} fuel to a sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an
-$1\%/$y growth of the generated power (Figure \ref{fig:power}).
+This work estimates the impact of the operational parameters uncertainty on a simple
+transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening
+And Evaluation Group\cite{ES}: a transition from light water reactors fleet
+loaded with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX}
+fuel, considering an $1\%/$y grows of the generated power (Figure
+\ref{fig:power}).
+
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
@@
 
-As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
-fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
+As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
+fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
 transition starts around year 35, with the deployment of \glspl{FBR}, loaded
-with \glspl{MOX}, consisting of plutonium blended with natural
-uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
-\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
-ratio.
+with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
+uranium.
 
@@
     \caption{Electric power generated over time, with in blue the full production,
-        in orange the \glspl{LWR} contribution, in green the hight breeding ratio
-        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
+        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}\label{fig:power}
 \end{figure}
 
-The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
-used fuel. At first , it is sourced only from UOX, then used MOX fuel as it becomes
+The plutonium, required for the \glspl{MOX} fabrication, is reprocessed from all
+used fuel, at first only used UOX, then used MOX fuel as they start to be
 available for reprocessing.
@@
 the number of loaded batches) converges to the reference value.
-The fuel enrichment and the tail assay contribution follow a smoother behavior,
-so as the total relative uncertainty decrease, their contribution increases over
-time.
+The fuel enrichment contribution follow a smoother behavior, so as the total
+relative uncertainty decrease, their contribution increases over time.
 
@@
     \centering
-    \includegraphics[scale=0.17]{used_fuel}
+    \includegraphics[scale=0.18]{used_fuel}
     \caption{Used fuel inventory.}\label{fig:used_fuel}

### 2018-05-04 paper.tex

@@
 \subsection{The Fuel Cycle}
-This work estimates the impact of the operational parameters uncertainty on a simple
-transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening
-And Evaluation Group\cite{ES}: a transition from light water reactors fleet
-loaded with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX}
-fuel, considering an $1\%/$y grows of the generated power (Figure
-\ref{fig:power}).
-
+This work aims to assess the impact of the functional uncertainties of a simple
+transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle
+of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}: a
+transition from light water reactors fleet loaded with \glspl{UOX} fuel to a
+sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an $1\%/$y growth
+of the generated power (Figure \ref{fig:power}).
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
@@
 
-As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
-fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
+As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
+fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
 transition starts around year 35, with the deployment of \glspl{FBR}, loaded
-with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
-uranium.
+with \glspl{MOX}, consisting of plutonium blended with natural
+uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
+\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
+ratio.
 
@@
     \caption{Electric power generated over time, with in blue the full production,
-        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}\label{fig:power}
+        in orange the \glspl{LWR} contribution, in green the hight breeding ratio
+        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
 \end{figure}
 
-The plutonium, required for the \glspl{MOX} fabrication, is reprocessed from all
-used fuel, at first only used UOX, then used MOX fuel as they start to be
+The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
+used fuel. At first , it is sourced only from UOX, then used MOX fuel as it becomes
 available for reprocessing.

### 2018-05-15 paper.tex
some work with the flow

@@
 uncertainties (produced by the simplification made by the simulator) and the
-``functional`` uncertainty (uncertainty on the operation parameters of the
+``operational`` uncertainty (uncertainty on the operation parameters of the
 different facilities).
@@
 enrichment is not applied directly on the effective enrichment but on the target
-parameter (the burnup), which leads to to a fuel enrichment uncertainty close to
+parameter (the burnup), which leads to a fuel enrichment uncertainty close to
 $10\%$.
@@
 \subsection{The Fuel Cycle}
-This work aims to assess the impact of the functional uncertainties of a simple
+This work aims to assess the impact of the operational uncertainties of a simple
 transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle
@@
 with \glspl{MOX}, consisting of plutonium blended with natural
-uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
-\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
-ratio.
+uranium.
 
@@
     \caption{Electric power generated over time, with in blue the full production,
-        in orange the \glspl{LWR} contribution, in green the hight breeding ratio
-        \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}\label{fig:power}
+        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}
+    \label{fig:power}
 \end{figure}
@@
 receive the fuel as needed allowing them to be producing power all the time.
-This ensure that the uncertainty measured on other parameters are not influence
-by the reactors miss-loadings.
+This ensures that the uncertainty measured any other parameters is not
+influenced by the reactors miss-loadings.
 
@@
 
-\subsection{Natural Uranium Consumption}
+\subsection{Natural Uranium Consumption dedicated to PWR-UOX fabrication}
 
-Figure \ref{fig:unat_full} represents the cumulative natural uranium
-consumption as a function of time. The uncertainty on the cumulative uranium
-consumption grows as expected with the time and the loading of the \glspl{LWR}.
-The increase stops around year 125y with the decommissioning of the last
-\glspl{LWR}.
+Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
+dedicated to PWR-UOX fuel fabrication as a function of time.  The uncertainty on
+the cumulative uranium consumption grows as expected with the time and the
+loading of the \glspl{LWR}.  The increase stops around year 125y with the
+decommissioning of the last \glspl{LWR}.
 
@@
 
-The fluctuation of the full relative uncertainty at low time are because of the
-sensitivity to the fuel loading: all reactors at the beginning have synchronised
-cycle, this phenomenon disappears with the gradual decommissioning of the initial
-reactor, spread on 50 years.
+The fluctuation of the full relative uncertainty at low time are induced by the
+fuel loading: all reactors at the beginning of the simulation have synchronised
+cycle, this phenomenon disappears with the gradual decommissioning of the
+initial reactors, spread on 50 years.
 
@@
 
-As expected, cooling time, separation efficiency and thermal power does not
+As expected, cooling time, separation efficiency and thermal power don't
 affect the natural uranium consumption.  The uncertainty on the natural uranium
@@
 
-As the number of deployed \glspl{LWR} reactors increases, as each parameters is
-sampled once for each facilities, the average length of the cycle (as well as
-the number of loaded batches) converges to the reference value.
-The fuel enrichment contribution follow a smoother behavior, so as the total
-relative uncertainty decrease, their contribution increases over time.
+With the increase of deployed reactors, the number of batches of \glspl{PWR}
+fuel loaded converges to the references one (a random cycle length
+values if randomly determined for each deployed reactors), reducing its impact
+on the uncertainty on the total uranium consumption.
+The fuel enrichment contribution follow a close to constant uncertainty
+contribution of $2\%$, so as the total relative uncertainty decrease, its
+relative contribution increases over time.
 
 \subsection{Fissile Inventory}
+The fissile inventory corresponds to the amount on separated fissile waiting to
+be blend with natural uranium in order to produce the \glspl{FBR} MOX fuel.
+
 As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow on
@@
 125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
-it will reach an equilibrium between $5$ and $10\%$...
+it would have reached an equilibrium between $5$ and $10\%$ with longer
+simulations...
 Between year 40 and 70, the main contributor to the fissile inventory
@@
 It is also interesting to note that, the uncertainty contribution from the cycle
-length are conversion toward the power contribution, such as the increase of
-fuel loads effect tends to vanish and let its place to a discharge burnup
-effect (the power uncertainty only affects the burnup of the fuel at discharge).
+length is between year 40 and 70 comes mainly from fuel batch loading
+frequencies, and after it relative contributions follows closely the thermal
+power one, suggesting a contributions through fuel discharge burnup (i.e. fuel
+discharge composition).
 
@@
 
-Even if for the two output metric analysed there is no surprise such as the
-identified uncertainty contributions, it is very interesting to be able to
-measure them and rank them.
+Uranium consumption and separated fissile inventory are two important metrics
+regarding to non proliferation and nuclear archaeology. In this study, we have
+been able to estimate than the cycle length uncertainty of $10\%$ implies a
+variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
+on the enrichment implies a almost flat uncertainty of $2\%$.
 
-In this study, we can estimate than the cycle length uncertainty of $10\%$
-varies from $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
-on the enrichment implies a almost flat uncertainty of $2\%$, and the enrichment
-tails uncertainty have an even lower contributions of $1\%$.
-
-It is also very interesting to observe that while the plutonium inventory uncertainty
-reach a pick at $30\%$, lead by the cooling time uncertainty contribution, the reactor
-parameters seems to have a lower contribution, the cycle time contribution
-picking at $10\%$ and stabilizing with the power contribution around $1\%$
+Regarding the reprocessed fissile inventory, this study has shown the limited
+impact of the reprocessed fuel compositions (through burnup variations) it
+limited to $5\%$, where fuel availability constrains, fuel loading frequency (cycle
+time), or fissile materials available for fuel fabrication (cooling time) can lead to higher
+uncertainties, respectively up to $10\%$ and to $30\%$. Moreover it is very
+interesting to observe the pressure transition from one to the other around
+year 70.
 
@@
 parameters uncertainty in a fuel cycle study, such as cooling time and cycle
-length. As the cycle length impact the discharge fuel burnup, it also affects
+length. Where some of those time related parameter will on the first order only
+impact material availability (as the cooling time will do), some other, like
+cycle length, will also have a impact as physical parameters such as fuel enrichment or thermal
+power.
+
+Those time related parameters can not only impact the uncertainty as
+physical parameters (for example the cycle lenght impacting the fuel discharge
+burnup and composition)
+
+Cycle length impacts the discharge fuel burnup, it also affects
 the frequency of the fuel loads, this, as well as the cooling may imply a

### 2018-05-15 paper.tex
pdf update as well

@@
 
-With the increase of deployed reactors, the number of batches of \glspl{PWR}
+With the increase of deployed reactors, the number of batches of \glspl{LWR}
 fuel loaded converges to the references one (a random cycle length

### 2018-05-15 paper.tex
some work on the conclusion

@@
 Those time related parameters can not only impact the uncertainty as
-physical parameters (for example the cycle lenght impacting the fuel discharge
+physical parameters (for example the cycle length impacting the fuel discharge
 burnup and composition)
 
-Cycle length impacts the discharge fuel burnup, it also affects
-the frequency of the fuel loads, this, as well as the cooling may imply a
-uncertainty on the material availability, which could lead to a large
-uncertainty.  Those kind of uncertainties will need a special treatment on further
-uncertainty analysis.
+Cycle length impacts the discharge fuel burnup, it also affects the frequency of
+the fuel loads, this, as well as the cooling may imply a uncertainty on the
+material availability, which could lead to an artificially large uncertainty.
+Those kind of time related uncertainties will require a careful analysis on further
+uncertainty analysis, in order to understand and measure accurately their
+contributions on uncertainties.
 
 This study aims to be a proof-of-principle for uncertainty propagation in
-potential commercial fuel cycle transition and will to be extended to random
-uncertainty.
+potential commercial fuel cycle transition. While it has demonstrated the
+capability to measure the uncertainty on output fuel cycle metrics and relative
+contributions, it has only been applied to systematic uncertainties per
+facilities (parameters randomly generated at each new facility deployment).
+This kind of study will to be extended to random uncertainty (new parameter
+values at each occurrence) and completely systematic uncertainty (shared by all the
+facilities of a kind).
 
@@
 plutonium quality, waste compositions.  Such studies could also provide research
-guidance for nuclear archeology works, which aims to precisely estimate past
+guidance for nuclear archaeology works, which aims to precisely estimate past
 fissile production by the different nuclear countries.

### 2018-05-15 paper.tex
add explanation on uncertainty

@@
 \end{table}
+
+The uncertainty on the different parameters have been considered for this study
+as systematic for each new deployed facilities: each time a new facility is
+deployed (such as a reactor or a fuel fabrication facility) a new set a
+parameter is computed.
 
@@
 impact material availability (as the cooling time will do), some other, like
-cycle length, will also have a impact as physical parameters such as fuel enrichment or thermal
-power.
+cycle length, will also have a impact as physical parameters such as fuel
+enrichment or thermal power.
 
@@
 potential commercial fuel cycle transition. While it has demonstrated the
-capability to measure the uncertainty on output fuel cycle metrics and relative
-contributions, it has only been applied to systematic uncertainties per
+capability to measure the uncertainty on output fuel cycle metrics and their
+relative contributions, it has only been applied to systematic uncertainties per
 facilities (parameters randomly generated at each new facility deployment).
 This kind of study will to be extended to random uncertainty (new parameter
-values at each occurrence) and completely systematic uncertainty (shared by all the
-facilities of a kind).
+values at each occurrence) and completely systematic uncertainty (shared by all
+the facilities of a kind).
 

### 2018-05-15 paper.tex
remove old paragraph
rework uncertainty measurement description

@@
 \section{Results}
-In this specific study, one will only focus on the uncertainty on the produced
-electric power as a function of time, on the total quantity of natural uranium
-used and on the total unused fissile inventory (unused reprocessed plutonium).
-In order to estimate the total uncertainty on those 3 parameters as well as the
-individual contribution of the operational parameters several set of (199)
-simulations have been completed.  All uncertainty are computed as the standard
-deviation over over all the calculations in the set.
 
-In addition to the set with all parameters are sampled according to their
-uncertainty, a set a have been computed for each parameter, with all the other
-remaining fixed to the reference value.
+As nuclear archaeology main interests are high enrich uranium production and
+fissile inventories, this specific study will mainly focus on the uncertainty on
+the total quantity of natural uranium used and on the total unused fissile
+inventory (unused reprocessed plutonium).
+
+Generated power will briefly being investigated to ensure the overall
+uncertainty study will not be contaminated with fuel miss loading, which could
+be interesting but are not the focus on this work.
+
+For this study 6 set of 199 simulations, and a reference calculation have been
+computed: One for each of the 5 uncertain parameters, one varying parameter the
+4 others remaining fix, one with all 5 parameters varying and one single
+simulation where all the 5 parameters were fixed at the mean value.
+
+All uncertainty have been computed as the standard deviation over over all the
+calculations in a single set.
 
 \subsection{Generated Power}
+
 By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
@@
 
-Those time related parameters can not only impact the uncertainty as
-physical parameters (for example the cycle length impacting the fuel discharge
-burnup and composition)
-
 Cycle length impacts the discharge fuel burnup, it also affects the frequency of

### 2018-05-15 paper.tex
add uncertainty measurement description

@@
 
+In this works, a time step of 1 month have been considered.
+
 \section{Results}
@@
 
-All uncertainty have been computed as the standard deviation over over all the
-calculations in a single set.
+In the following, each total uncertainty is reported at $\pm1\sigma$ around the
+mean values of the corresponding uncertainty set at each time step. The time
+dependant relative uncertainty are computed as the standard deviation of a
+single set over its mean value at the corresponding time.
 

### 2018-05-15 paper.tex
mention no decay
formating

@@
 The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
-used fuel.  At first , it is sourced only from UOX, then used MOX fuel as it becomes
-available for reprocessing.
+used fuel.  At first , it is sourced only from \glspl{UOX}, then used MOX fuel
+as it becomes available for reprocessing.
 
 Both fuel reprocessing and fabrication are done at a constant rate (constrained
-by the feed materials availabilities).  The enrichment of the UOX is processed on
-demand.  Buffer storages (not shown on Figure \ref{fig:cycle}) is present between
-all facilities with constant processing rates.
+by the feed materials availabilities).  The enrichment of the UOX is processed
+on demand.  Buffer storages (not shown on Figure \ref{fig:cycle}) is present
+between all facilities with constant processing rates.
 
-In this works, a time step of 1 month have been considered.
+In this works, a time step of 1 month have been considered, i.e. each output
+metrics are reported one each month and decay process have not be taking into
+account.
 
@@
     \centering
-    \includegraphics[scale=0.35]{power_full}
+    \includegraphics[scale=0.36]{power_full}
     \caption{Electric power generated as a function of time.  The black line

### 2018-05-16 paper.tex
including Pat comments

@@
 the simulation relies on previously estimated/measured metrics), modeling
-uncertainties (produced by the simplification made by the simulator) and the
+uncertainties (produced by the simplifications made by the simulator) and the
 ``operational`` uncertainty (uncertainty on the operation parameters of the
@@
 Carlo approach has been applied.  In the following, output metric uncertainty
-corresponds to the Standard Deviation of the output metrics over about 200
+corresponds to the standard deviation of the output metrics 199
 different simulations.  For each deployed facilities, the uncertainty associated
@@
 
-To pursuit this work, both the Cycamore\cite{cycamore} package\footnote{Low
-fidelity facilities package for Cyclus} and the
-CyCLASS\footnote{Reactor and Fuel fabrication facility based on
-    CLASS\cite{CLASS}  models} have been
+To pursue this work, both the Cycamore\cite{cycamore} package\footnote{Low
+fidelity facilities package for Cyclus} and the CyCLASS\footnote{Reactor and
+Fuel fabrication facility based on CLASS\cite{CLASS}  models} have been
 updated\cite{mouginot_2018, cyclass} to deal with uncertainty in several
@@
 as systematic for each new deployed facilities: each time a new facility is
-deployed (such as a reactor or a fuel fabrication facility) a new set a
+deployed (such as a reactor or a fuel fabrication facility) a new set of
 parameter is computed.
 
-It must be noted that for this work, the fuel enrichment was determined by a
-fuel fabrication model\cite{Leniau2015125} which
-calculates the fissile fraction required in the fuel to reach a target
-burnup at the end of irradiation.  In this study, the uncertainty on the fuel
-enrichment is not applied directly on the effective enrichment but on the target
-parameter (the burnup), which leads to a fuel enrichment uncertainty close to
-$10\%$.
-
-\subsection{The Fuel Cycle}
+\subsection{The Fuel Cycle Scenario}
 This work aims to assess the impact of the operational uncertainties of a simple
@@
 
-In this works, a time step of 1 month have been considered, i.e. each output
+In this work, a time step of 1 month have been considered, i.e.  each output
 metrics are reported one each month and decay process have not be taking into
 account.
+
+It must be noted that for this work, the fuel enrichment was determined by a
+fuel fabrication model\cite{Leniau2015125} which
+calculates the fissile fraction required in the fuel to reach a target
+burnup at the end of irradiation.  In this study, the uncertainty on the fuel
+enrichment is not applied directly on the effective enrichment but on the target
+parameter (the burnup), which leads to a fuel enrichment uncertainty close to
+$10\%$.
 
@@
 For this study 6 set of 199 simulations, and a reference calculation have been
-computed: One for each of the 5 uncertain parameters, one varying parameter the
-4 others remaining fix, one with all 5 parameters varying and one single
+computed: One for each of the 5 uncertain parameters,Tab.
+\ref{tab:package_uncertainty}  (separation efficiency, residence time, UOX fuel
+enrichment, reactor cycle length, reactor thermal power), one varying parameter
+the 4 others remaining fix, one with all 5 parameters varying and one single
 simulation where all the 5 parameters were fixed at the mean value.
@@
 mean values of the corresponding uncertainty set at each time step.  The time
-dependant relative uncertainty are computed as the standard deviation of a
+dependant relative uncertainties are computed as the standard deviation of a
 single set over its mean value at the corresponding time.
@@
 
-Indeed the transition scenario has been design to allow all the reactors to
+Indeed the transition scenario has been designed to allow all the reactors to
 receive the fuel as needed allowing them to be producing power all the time.
 This ensures that the uncertainty measured any other parameters is not
-influenced by the reactors miss-loadings.
-
-%%  \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-%%    \centering
-%%    \includegraphics[scale=0.37]{power_uncer}
-%%    \caption{}\label{fig:power_uncer}
-%%  \end{figure}
+influenced by the reactors miss-loadings.  As \glspl{FBR} fuel is built from
+reprocessed used fuels, the availability of those used fuels may impact the
+capability to build the required MOX-FBR fuel.  Having reactor miss-loads, may
+impact more miss-loading later during a simulation and lead to a snow-ball
+effect.  Having a small uncertainty on the power generation ensures large miss
+load effects are not to be considered here.
 
@@
 
-The fluctuation of the full relative uncertainty at low time are induced by the
-fuel loading: all reactors at the beginning of the simulation have synchronised
-cycle, this phenomenon disappears with the gradual decommissioning of the
-initial reactors, spread on 50 years.
+As expected, cooling time, separation efficiency and thermal power don't
+affect the natural uranium consumption.  The uncertainty on the natural uranium
+consumption is dominated by the \glspl{LWR} cycle length: shorter the cycle
+length is, the more fuel will be loaded.
 
@@
 
-As expected, cooling time, separation efficiency and thermal power don't
-affect the natural uranium consumption.  The uncertainty on the natural uranium
-consumption is dominated by the \glspl{LWR} cycle length: shorter the cycle
-length is, the more fuel will be loaded.
+Uncertainty fluctuation of the full relative uncertainty can be observed before
+year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
+beginning of the simulation have synchronised cycle, this phenomenon disappears
+with the gradual decommissioning of the initial reactors, spread on 50 years.
 
-With the increase of deployed reactors, the number of batches of \glspl{LWR}
-fuel loaded converges to the references one (a random cycle length
-values if randomly determined for each deployed reactors), reducing its impact
-on the uncertainty on the total uranium consumption.
+The decrease of the cycle time uncertainty contribution, from year 30 to year
+90, can be understand as an averaging effect.  As the uncertainty are considered
+as systematic per deployed facility, each reactor will have a different cycle
+length value, so a different number of loaded batches per year.With the increase
+of deployed reactors, the number of batches of \glspl{LWR} fuel loaded converges
+to the references one, reducing its impact on the uncertainty on the total
+uranium consumption.
+
 The fuel enrichment contribution follow a close to constant uncertainty
@@
     \includegraphics[scale=0.18]{used_fuel}
-    \caption{Used fuel inventory.}\label{fig:used_fuel}
+    \caption{Used fuel inventory, corresponding to the amount of used
+    \glspl{LWR} and \glspl{FBR} fuel, cooled and waiting to be reprocessed.}
+    \label{fig:used_fuel}
 \end{figure}
@@
 year 70.
+
+This preliminary study may suggest that the most important contribution to
+natural uranium consumption and fissile inventory is coming from the time when
+occurs the different material exchange between facilities, and not necessary
+from the physical parameters such as thermal power or fuel enrichment. Further
+analysis should allow us to confirm or denies it.
 

### 2018-05-16 paper.tex
intro and method

--- 2018-05-15 paper.tex
@@
 
-Fuel cycle simulations, as any simulation process, do not produce results
-without errors.  Those errors have different sources: data uncertainties (when
-the simulation relies on previously estimated/measured metrics), modeling
-uncertainties (produced by the simplification made by the simulator) and the
-``operational`` uncertainty (uncertainty on the operation parameters of the
+Fuel cycle simulations, as with any simulation process, do not produce results
+without errors.  Those errors have different sources: data uncertainties (from
+the simulator's reliance on previously estimated/measured metrics), modeling
+uncertainties (from simplifications made by the simulator) and the
+``operational`` uncertainty (from the operation parameter uncertainties of
 different facilities).
 
-Some treaty verification scenarios require estimating historical fissile
+Simulation errors are important in the context of treaty verification. 
+Some scenarios require estimating historical fissile
 material production based on records of facility operation and material
@@
 to understand which measures of facility operation have the most impact on the
-uncertainty of fissile material production across a complete fuel cycle.  An
-approaching using Total Monte Carlo methodology will be applied to the Cyclus
-fuel cycle simulator \cite{cyclus} to estimate output metrics uncertainty caused
-by individual facility uncertainties.
+uncertainty of fissile material production across a complete fuel cycle.
+To accomplish this, a Total Monte Carlo methodology will be applied to the Cyclus
+fuel cycle simulator \cite{cyclus} to estimate the effect of individual facility uncertainties on the output metrics.
 
@@
 Carlo approach has been applied.  In the following, output metric uncertainty
-corresponds to the Standard Deviation of the output metrics over about 200
-different simulations.  For each deployed facilities, the uncertainty associated
-parameters have been a normally distributed with an artificially large standard
+corresponds to the standard deviation of the output metrics over about 200
+different simulations.  For each deployed facility, the
+parameters are normally distributed with an artificially large standard
 deviation of $10\%$.
 
-To pursuit this work, both the Cycamore\cite{cycamore} package\footnote{Low
+To pursue this work, both the Cycamore\cite{cycamore} package\footnote{Low
 fidelity facilities package for Cyclus} and the
-CyCLASS\footnote{Reactor and Fuel fabrication facility based on
-    CLASS\cite{CLASS}  models} have been
-updated\cite{mouginot_2018, cyclass} to deal with uncertainty in several
-operational parameters of their associated facilities.  Table
-\ref{tab:package_uncertainty} summarizes all modification implemented in the
-range of facilities present in Cycamore and CyCLASS.
+CyCLASS\footnote{Reactor and fuel fabrication facility based on
+    CLASS\cite{CLASS}  models} were
+updated\cite{mouginot_2018, cyclass} to evaluate uncertainty of several
+operational parameters in their associated facilities.  Table
+\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
+facilities of Cycamore and CyCLASS.
 
@@
 \centering
-  \caption{Summary of facility modification per source package.}
+  \caption{Summary of facility modifications according to their source package.}
 \begin{tabular}{cll}
@@
 
-The uncertainty on the different parameters have been considered for this study
-as systematic for each new deployed facilities: each time a new facility is
-deployed (such as a reactor or a fuel fabrication facility) a new set a
-parameter is computed.
+The uncertainty of the different parameters in this study
+are systematic for each new deployed facility: each time a new facility is
+deployed (such as a reactor or a fuel fabrication facility) a new set of
+parameters are computed.
 
@@
 calculates the fissile fraction required in the fuel to reach a target
-burnup at the end of irradiation.  In this study, the uncertainty on the fuel
-enrichment is not applied directly on the effective enrichment but on the target
-parameter (the burnup), which leads to a fuel enrichment uncertainty close to
+burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
+enrichment is not applied directly to the effective enrichment. It is instead applied to the
+burnup, which leads to a fuel enrichment uncertainty close to
 $10\%$.

### 2018-05-16 paper.tex
fuel cycle edits

@@
 This work aims to assess the impact of the operational uncertainties of a simple
-transition as shown in Figure \ref{fig:cycle}, inspired from the EG23 fuel cycle
-of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}: a
-transition from light water reactors fleet loaded with \glspl{UOX} fuel to a
-sodium fast reactor fleet loaded \glspl{MOX} fuel, considering an $1\%/$y growth
+transition, inspired from the EG23 fuel cycle
+of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. As shown in Figure \ref{fig:cycle}, this is a
+transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
+sodium fast reactor fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
 of the generated power (Figure \ref{fig:power}).
@@
   \caption{Illustration of the material flow between the different facilities,
-  with in green each operational parameters associated with an
-  uncertainty.}\label{fig:cycle}
+  with each operational parameter associated with an
+  uncertainty labeled in green.}\label{fig:cycle}
 \end{figure}
@@
 As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
-fully composed of \glspl{LWR} loaded with enriched \glspl{UOX} fuel.  The actual
-transition starts around year 35, with the deployment of \glspl{FBR}, loaded
-with \glspl{MOX}, consisting of plutonium blended with natural
+composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
+transition starts around year 35, with the deployment of \glspl{FBR}. The \glspl{FBR} are loaded
+with \gls{MOX}, which consists of plutonium blended with natural
 uranium.
@@
     \includegraphics[scale=0.18]{power.png}
-    \caption{Electric power generated over time, with in blue the full production,
-        in orange the \glspl{LWR} contribution, in green the \glspl{FBR}.}
+    \caption{Electric power generated over time, with the full production,
+        the \glspl{LWR} contribution, the \glspl{FBR} labelled in blue, orange, and green, respectively.}
     \label{fig:power}
@@
 
-The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
-used fuel.  At first , it is sourced only from \glspl{UOX}, then used MOX fuel
+The plutonium, required for \gls{MOX} fabrication, is reprocessed from all
+used fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel
 as it becomes available for reprocessing.
@@
 Both fuel reprocessing and fabrication are done at a constant rate (constrained
-by the feed materials availabilities).  The enrichment of the UOX is processed
-on demand.  Buffer storages (not shown on Figure \ref{fig:cycle}) is present
+by the feed material availability).  The enrichment of the \gls{UOX} is processed
+on demand.  Buffer storages (not shown in Figure \ref{fig:cycle}) is present
 between all facilities with constant processing rates.
 
-In this works, a time step of 1 month have been considered, i.e. each output
-metrics are reported one each month and decay process have not be taking into
+In this work, a time step of 1 month has been considered, i.e., each output
+metric is reported once per month. Additionally, decay processes have not be taken into
 account.

### 2018-05-16 paper.tex

@@
 Carlo approach has been applied.  In the following, output metric uncertainty
-corresponds to the standard deviation of the output metrics over about 200
+corresponds to the standard deviation of the output metrics 199
 different simulations.  For each deployed facility, the
@@
 fidelity facilities package for Cyclus} and the
-CyCLASS\footnote{Reactor and fuel fabrication facility based on
-    CLASS\cite{CLASS}  models} were
+CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models} were
 updated\cite{mouginot_2018, cyclass} to evaluate uncertainty of several
@@
 
-\subsection{The Fuel Cycle}
+\subsection{The Fuel Cycle Scenario}
 This work aims to assess the impact of the operational uncertainties of a simple
@@
 
+It must be noted that for this work, the fuel enrichment was determined by a
+fuel fabrication model\cite{Leniau2015125} which
+calculates the fissile fraction required in the fuel to reach a target
+burnup at the end of irradiation.  In this study, the uncertainty on the fuel
+enrichment is not applied directly on the effective enrichment but on the target
+parameter (the burnup), which leads to a fuel enrichment uncertainty close to
+$10\%$.
+
 \section{Results}

### 2018-05-16 paper.tex

@@
 
-To estimate the uncertainty on fuel cycle output metrics, a Total Monte
+To estimate the uncertainty of fuel cycle output metrics, a Total Monte
 Carlo approach has been applied.  In the following, output metric uncertainty
-corresponds to the standard deviation of the output metrics 199
+corresponds to the standard deviation of the output metrics from 199
 different simulations.  For each deployed facility, the
@@
 CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models} were
-updated\cite{mouginot_2018, cyclass} to evaluate uncertainty of several
+updated\cite{mouginot_2018, cyclass} to evaluate the uncertainty of several
 operational parameters in their associated facilities.  Table
@@
 
-It must be noted that for this work, the fuel enrichment was determined by a
-fuel fabrication model\cite{Leniau2015125} which
-calculates the fissile fraction required in the fuel to reach a target
-burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
-enrichment is not applied directly to the effective enrichment. It is instead applied to the
-burnup, which leads to a fuel enrichment uncertainty close to
-$10\%$.
-
 \subsection{The Fuel Cycle Scenario}
@@
 transition, inspired from the EG23 fuel cycle
-of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. As shown in Figure \ref{fig:cycle}, this is a
+of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. Pictured in Figure \ref{fig:cycle}, this is a
 transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
@@
     \caption{Electric power generated over time, with the full production,
-        the \glspl{LWR} contribution, the \glspl{FBR} labelled in blue, orange, and green, respectively.}
+        the \gls{LWR} contribution, and the \gls{FBR} contribution labeled in blue, orange, and green, respectively.}
     \label{fig:power}
@@
 by the feed material availability).  The enrichment of the \gls{UOX} is processed
-on demand.  Buffer storages (not shown in Figure \ref{fig:cycle}) is present
+on demand.  Buffer storages (not shown in Figure \ref{fig:cycle}) are present
 between all facilities with constant processing rates.
@@
 
-As nuclear archaeology main interests are high enrich uranium production and
-fissile inventories, this specific study will mainly focus on the uncertainty on
-the total quantity of natural uranium used and on the total unused fissile
+The main interests of nuclear archaeology involve highly enriched uranium production and
+fissile inventories, so this study mainly focuses on the uncertainties of
+the total quantity of natural uranium used and the total unused fissile
 inventory (unused reprocessed plutonium).  
+Generated power is also briefly being investigated to ensure the overall
+uncertainty is not contaminated with a missed fuel loading, which could
+be interesting but is not the focus of this work.
 
-Generated power will briefly being investigated to ensure the overall
-uncertainty study will not be contaminated with fuel miss loading, which could
-be interesting but are not the focus on this work.
-
-For this study 6 set of 199 simulations, and a reference calculation have been
-computed: One for each of the 5 uncertain parameters,Tab.
-\ref{tab:package_uncertainty}  (separation efficiency, residence time, UOX fuel
-enrichment, reactor cycle length, reactor thermal power), one varying parameter
-the 4 others remaining fix, one with all 5 parameters varying and one single
-simulation where all the 5 parameters were fixed at the mean value.
+For this study, the 199 simulations were performed six times, and a reference calculation was also
+computed. With the five parameters in Table
+\ref{tab:package_uncertainty} (separation efficiency, residence time, \gls{UOX} fuel
+enrichment, reactor cycle length, reactor thermal power) being tracked, the six sets are divided as follows: five sets where a single parameter is varied and 
+the four others remain fixed, and one with all five parameters being varied. 
+The reference calculation is a single
+simulation with all five parameters fixed at the mean value.
 
 In the following, each total uncertainty is reported at $\pm1\sigma$ around the
-mean values of the corresponding uncertainty set at each time step.  The time
-dependant relative uncertainties are computed as the standard deviation of a
+mean values of the corresponding uncertainty set at each time step.  The 
+time-dependant relative uncertainties are computed as the standard deviation of a
 single set over its mean value at the corresponding time.

### 2018-05-21 abstract.tex
first addition

\begin{abstract}

This work compares and evaluates different computational approaches for modeling
off-normal operation of a gas centrifuge enrichment cascade.

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades to design more effective and efficient
international safeguards approaches.  While it is straightforward to design an
enrichment cascade under ideal conditions as a function of the theoretical feed,
product and tails assays, it is very difficult to find reliable information
about the behavior of a given cascade when the feed assay does not match the
design value. Several methods have been developed to assess the behavior of an
enrichment cascade in such circumstances, those methods evaluate the cut, the
feed to product, feed to tail and the product to tail enrichment ratio,
respectively, alpha, beta and gamma, as a function of the cascade feed assay. As
those four parameters depends on each other, determining two of them allows to
compute the other.  The first approach consists of fixing the cut and alpha
recomputing the corresponding assays at each stages of the cascade. The second
one maintains the ideal condition of the cascade (alpha and beta fixed across
the whole cascade), modifying the cut value at each stage accordingly. Both
approaches have been implemented into the Cyclus fuel cycle
simulator\cite{cyclus, mbmore.2018}. The
third fixes the cut and gamma, using both alpha and beta at each stage as free
parameters. The third method has been investigated in \cite{walker.2017}.

Following a description of each method and an evaluation of differences between
each approach, this work compares the results produced by these methods within
scenarios involving misuse of enrichment cascades simulated using the dynamic
nuclear fuel cycle simulator, Cyclus.

\end{abstract}

### 2018-05-21 discuss.tex
first addition

\section{Discussion: Limitations of the Framework}
\label{s_discuss}
The use of historical data to develop a forward model has several limitations. The biggest limitation is in the size of this data set, both in terms of the number of states and in the range of years that are included.  With only 10 states that have acquired nuclear weapons in the historical record, there is large uncertainty in any quantitative analysis. As a result, while the analysis has identified factors that are correlated to weapons programs, there is insufficient data to confirm causal relationships.

Since the data set already includes all states that have pursued nuclear weapons, the missing states would only be relevant to the likelihood analysis if they had pursuit scores of 4 or larger, thus reducing the time-integrated likelihood of pursuit associated with such scores. Due to the influence of nuclear technology, a non-nuclear state could theoretically have a maximum pursuit score of 7. Considering that the majority of states that have high potential military spending and major historical conflicts have already been incorporated, this further reduces the potential maximum score to below 5, even if all other factors are maximized.  A large fraction of states in the world are expected to have scores on the order of 1-3, and thus not alter the distribution shown in \ref{fig:likely}.

A more important addition to the database would be data for each state for all years between 1940 (before the first historical pursuit) and the year of pursuit and/or aquisition.  This would allow the direct calculation of an annual probability of pursuit as a function of the pursuit score.  The current model for converting a time-integrated likelihood to an annual probability inherently assumes that the pursuit score for the states in the data set is constant for all the years prior to the decision to pursue nuclear weapons.  An effort to assemble this data would be a valuable contribution to this modeling effort.

### 2018-05-21 introduction.tex
first addition

\section{Introduction}
\label{s_motive}

%An effective treaty verification regime must synthesize knowledge from the realms of political science, international relations, nuclear physics and engineering, and even behavioral psychology.  Figure \ref{fig:cyclus_diagram} illustrates  the role of a fuel cycle simulator such as \Cyclus in bringing together these disparate fields to provide insights into proposed verification technologies. A fuel cycle simulator tracks the flow of nuclear material through the facilities in a fuel cycle\cite{gidden_agent-based_2015}.  Uranium enrichment and spent fuel reprocessing are two particularly sensitive parts of the fuel cycle, but correlated signatures of illicit activity are likely to be present across the fuel cycle. A fuel cycle simulator creates synthetic data, such as what would be available to an inspector, for many different facilities simultaneously while incorporating a system-level perspective of proliferation scenarios. This synthetic data can then be used as a testbed to investigate the efficacy of new detection and analysis techniques and illucidate the strengths and weaknesses of various verification strategies.

Progress in preventing the spread of nuclear weapons is contigent both upon limiting access to the required technology as well as disincentivizing weapons programs. An effective global nonproliferation regime must synthesize knowledge from the realms of political science, international relations, nuclear physics and engineering, and even behavioral psychology. An understanding of when and why states proliferate can inform future treaties and agreements to minimize this risk. For example, the concept of multilateral enrichment, in which multiple states co-own and operate an enrichment facility, has the potential to reduce the spread of enrichment technology. However, detractors risks associated with international networking opportunities inherent in multinational organizations as a path for increased proliferation\cite{albright_2005, obeidi2005bomb}. A multi-state modeling framework to compare the relative risk between proposed treaty paradigms and the status quo can help inform the discussion and potentially identify ways to reduce global risk of nuclear proliferation.

As part of the Consortium for Verification Technology, the Cyclus fuel cycle simulator is being used as a test-bed for the development of such new technologies and approaches to treaty development. Cyclus is a systems-level nuclear fuel cycle simulator that models the interactions between actors in the nuclear arena\cite{cyclus_v1_5, huff_open_2011, huff_fundamental_2016}. While designed to track the flow of nuclear material between facilities, Cyclus also incorporates an innovative Region-Institution-Facility hierarchy that can capture the dynamics of regional-level interactions between states.  We have developed a forward model in which a set of hypothetical states can be given individual political and technical attributes. This model then tracks whether each state develops nuclear weapons over time based on how these attributes evolve in time, including feedback on conflict levels between states.

### 2018-05-21 paper.tex
add empty files

--- 2018-05-16 paper.tex
@@
-\documentclass{anstrans}
+\documentclass[12pt]{paper}
+\usepackage{mathptmx} % Nearly Times New Roman
+\usepackage[acronym,toc]{glossaries}
+\include{acros}
+%\makeglossaries
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{}
-\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H.  Wilson$^{*}$}
 
-\institute{
-$^{*}$University of Wisconsin-Madison, WI
+\usepackage{color}
+\usepackage{subcaption}
+\usepackage{graphicx}
+\usepackage{booktabs} % nice rules for tables
+\usepackage{microtype} % if using PDF
+\usepackage{xspace}
+\usepackage{listings}
+\usepackage{textcomp}
+\usepackage{multicol,tabularx,capt-of}
+\usepackage{multirow}
+%\usepackage{ulem}
+\usepackage{pdflscape}
+% Page length commands go here in the preamble
+\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
+\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
+\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
+\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in
+
+\definecolor{listinggray}{gray}{0.9}
+\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
+\definecolor{burgundy}{rgb}{0.5, 0.0, 0.13}
+\definecolor{burntorange}{rgb}{0.8, 0.33, 0.0}
+\definecolor{chromeyellow}{rgb}{1.0, 0.65, 0.0}
+\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
+
+\lstset{
+    %backgroundcolor=\color{lbcolor},
+    language={C++},
+    tabsize=4,
+    rulecolor=\color{black},
+    upquote=true,
+    aboveskip={1.5\baselineskip},
+    belowskip={1.5\baselineskip},
+    columns=fixed,
+    extendedchars=true,
+    breaklines=true,
+    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
+    frame=single,
+    showtabs=false,
+    showspaces=false,
+    showstringspaces=false,
+    basicstyle=\scriptsize\ttfamily\color{green!40!black},
+    keywordstyle=\color[rgb]{0,0,1.0},
+    commentstyle=\color[rgb]{0.133,0.545,0.133},
+    stringstyle=\color[rgb]{0.627,0.126,0.941},
+    numberstyle=\color[rgb]{0,1,0},
+    identifierstyle=\color{black},
+    captionpos=t,
 }
 
-\email{mouginot@wisc.edu \and mummah@wisc.edu \and paul.wilson@wisc.edu}
+\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily\color{green!40!black}]|#1|}
+\newcommand{\units}[1] {\:\text{#1}}%
+\newcommand{\SN}{S$_N$}
+\newcommand{\cyclus}{\textsc{Cyclus}\xspace}
+\newcommand{\Cyclus}{\cyclus}
+\newcommand{\citeme}{\textcolor{red}{CITE}\xspace}
+\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%
 
-% Optional disclaimer: remove this command to hide
-% \disclaimer{Notice: this manuscript is a work of fiction.  Any resemblance to
-% actual articles, living or dead, is purely coincidental.}
+\newcommand{\comment}[1]{{\color{green}\textbf{#1}}}
 
-%%%% packages and definitions (optional)
-\usepackage{graphicx} % allows inclusion of graphics
-\usepackage{booktabs} % nice rules (thick lines) for tables
-\usepackage{microtype} % improves typography for PDF
-\usepackage{float}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
 
-\newcommand{\SN}{S$_N$}
-\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
-\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
-\newcommand{\grad}{\vec{\nabla}} % gradient
-\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
+%\begin{frontmatter}
+\title{Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades}
 
-\usepackage[acronym]{glossaries}
-\newacronym{UOX}{UOX}{uranium oxide fuel}
-\newacronym{MOX}{MOX}{mixed oxide fuel}
-\newacronym{LWR}{LWR}{light water reactor}
-\newacronym{FBR}{FBR}{fast breeder reactor}
+% Authors. Separated by commas
+\input{authors}
+\date{}
+% Institutes of the authors
+\input{institutions}
+\maketitle
 
-\begin{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+% I.   Motivation
+\include{motivation}
+% II.  Theory
+%   a. cascade design
+%   b. miss-use model
+%       i.   case A
+%       ii.  case B
+%       iii. case C
+\include{theory}
+% III. Experiement
+%   a.  cycle 
+%   b.  cascade per level optimisation
+\include{experiement}
+% IV.  results
+%   a. time step effects
+%   b. no tail recycling
+%   c. tail recycling
+\include{results}
+% V.  Discussion
+% VI. Conclusions and future plan
+\include{dis_clusion}
 
-Fuel cycle simulations, as with any simulation process, do not produce results
-without errors.  Those errors have different sources: data uncertainties (from
-the simulator's reliance on previously estimated/measured metrics), modeling
-uncertainties (from simplifications made by the simulator) and the
-``operational`` uncertainty (from the operation parameter uncertainties of
-different facilities).
+\input{abstract}
 
-Simulation errors are important in the context of treaty verification. 
-Some scenarios require estimating historical fissile
-material production based on records of facility operation and material
-transfer.  If the measurements of facility operation and material transfer are
-subject to uncertainty, the total production quantities will then also be
-uncertain, creating an opportunity for undetected diversion.  This study seeks
-to understand which measures of facility operation have the most impact on the
-uncertainty of fissile material production across a complete fuel cycle.
-To accomplish this, a Total Monte Carlo methodology will be applied to the Cyclus
-fuel cycle simulator \cite{cyclus} to estimate the effect of individual facility uncertainties on the output metrics.
+%\end{frontmatter}
 
-% I don't think Total Monte Carlo should be in quotes
-\section{The Experiment}
-
-\subsection{Method}
-
-To estimate the uncertainty on fuel cycle output metrics, a Total Monte
-Carlo approach has been applied.  In the following, output metric uncertainty
-corresponds to the standard deviation of the output metrics over about 200
-different simulations.  For each deployed facility, the
-parameters are normally distributed with an artificially large standard
-deviation of $10\%$.
-
-To pursue this work, both the Cycamore\cite{cycamore} package\footnote{Low
-fidelity facilities package for Cyclus} and the
-CyCLASS\footnote{Reactor and fuel fabrication facility based on
-    CLASS\cite{CLASS}  models} were
-updated\cite{mouginot_2018, cyclass} to evaluate uncertainty of several
-operational parameters in their associated facilities.  Table
-\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
-facilities of Cycamore and CyCLASS.
-
-\begin{table}[htb]
-\centering
-  \caption{Summary of facility modifications according to their source package.}
-\begin{tabular}{cll}
-\toprule
-
-Package   & Facility   & Parameters                \\
-\midrule
-Cycamore & Separation & Separation efficiency     \\
-         & Storage    & Residence Time            \\
-\midrule
-CyCLASS  & Reactor    & Cycle Length              \\
-         &            & Power                     \\
-         &            & Fuel Enrichment (PWR-UOX) \\
-
-\bottomrule
-\end{tabular}
-
-  \label{tab:package_uncertainty}
-\end{table}
-
-The uncertainty of the different parameters in this study
-are systematic for each new deployed facility: each time a new facility is
-deployed (such as a reactor or a fuel fabrication facility) a new set of
-parameters are computed.
-
-It must be noted that for this work, the fuel enrichment was determined by a
-fuel fabrication model\cite{Leniau2015125} which
-calculates the fissile fraction required in the fuel to reach a target
-burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
-enrichment is not applied directly to the effective enrichment. It is instead applied to the
-burnup, which leads to a fuel enrichment uncertainty close to
-$10\%$.
-
-\subsection{The Fuel Cycle}
-This work aims to assess the impact of the operational uncertainties of a simple
-transition, inspired from the EG23 fuel cycle
-of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. As shown in Figure \ref{fig:cycle}, this is a
-transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
-sodium fast reactor fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
-of the generated power (Figure \ref{fig:power}).
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[scale=0.31]{cycle.png}
-  \caption{Illustration of the material flow between the different facilities,
-  with each operational parameter associated with an
-  uncertainty labeled in green.}\label{fig:cycle}
-\end{figure}
-
-As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
-composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
-transition starts around year 35, with the deployment of \glspl{FBR}. The \glspl{FBR} are loaded
-with \gls{MOX}, which consists of plutonium blended with natural
-uranium.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.18]{power.png}
-    \caption{Electric power generated over time, with the full production,
-        the \glspl{LWR} contribution, the \glspl{FBR} labelled in blue, orange, and green, respectively.}
-    \label{fig:power}
-\end{figure}
-
-The plutonium, required for \gls{MOX} fabrication, is reprocessed from all
-used fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel
-as it becomes available for reprocessing.
-
-Both fuel reprocessing and fabrication are done at a constant rate (constrained
-by the feed material availability).  The enrichment of the \gls{UOX} is processed
-on demand.  Buffer storages (not shown in Figure \ref{fig:cycle}) is present
-between all facilities with constant processing rates.
-
-In this work, a time step of 1 month has been considered, i.e., each output
-metric is reported once per month. Additionally, decay processes have not be taken into
-account.
-
-\section{Results}
-
-As nuclear archaeology main interests are high enrich uranium production and
-fissile inventories, this specific study will mainly focus on the uncertainty on
-the total quantity of natural uranium used and on the total unused fissile
-inventory (unused reprocessed plutonium).
-
-Generated power will briefly being investigated to ensure the overall
-uncertainty study will not be contaminated with fuel miss loading, which could
-be interesting but are not the focus on this work.
-
-For this study 6 set of 199 simulations, and a reference calculation have been
-computed: One for each of the 5 uncertain parameters, one varying parameter the
-4 others remaining fix, one with all 5 parameters varying and one single
-simulation where all the 5 parameters were fixed at the mean value.
-
-In the following, each total uncertainty is reported at $\pm1\sigma$ around the
-mean values of the corresponding uncertainty set at each time step. The time
-dependant relative uncertainty are computed as the standard deviation of a
-single set over its mean value at the corresponding time.
-
-\subsection{Generated Power}
-
-By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
-generated power is expected.
-
-\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.36]{power_full}
-    \caption{Electric power generated as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
-\end{figure}
-
-Indeed the transition scenario has been design to allow all the reactors to
-receive the fuel as needed allowing them to be producing power all the time.
-This ensures that the uncertainty measured any other parameters is not
-influenced by the reactors miss-loadings.
-
-%%  \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-%%    \centering
-%%    \includegraphics[scale=0.37]{power_uncer}
-%%    \caption{}\label{fig:power_uncer}
-%%  \end{figure}
-
-\subsection{Natural Uranium Consumption dedicated to PWR-UOX fabrication}
-
-Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
-dedicated to PWR-UOX fuel fabrication as a function of time.  The uncertainty on
-the cumulative uranium consumption grows as expected with the time and the
-loading of the \glspl{LWR}.  The increase stops around year 125y with the
-decommissioning of the last \glspl{LWR}.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.35]{unat_full}
-    \caption{Cumulative consumption of natural uranium as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:unat_full}
-\end{figure}
-
-The fluctuation of the full relative uncertainty at low time are induced by the
-fuel loading: all reactors at the beginning of the simulation have synchronised
-cycle, this phenomenon disappears with the gradual decommissioning of the
-initial reactors, spread on 50 years.
-
-\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.35]{unat_uncer}
-    \caption{Cumulative natural uranium consumption relative uncertainty, with
-    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
-    contribution of each parameter: cooling time (blue), fuel enrichment (red),
-    cycle time (green), thermal power(brown), separation efficiency (light
-    blue).}\label{fig:unatr_uncer}
-\end{figure}
-The relative uncertainty of the total uranium consumption starts at about
-$5.5\%$ a slowly drops and stabilise around $3\%$.
-
-As expected, cooling time, separation efficiency and thermal power don't
-affect the natural uranium consumption.  The uncertainty on the natural uranium
-consumption is dominated by the \glspl{LWR} cycle length: shorter the cycle
-length is, the more fuel will be loaded.
-
-With the increase of deployed reactors, the number of batches of \glspl{LWR}
-fuel loaded converges to the references one (a random cycle length
-values if randomly determined for each deployed reactors), reducing its impact
-on the uncertainty on the total uranium consumption.
-The fuel enrichment contribution follow a close to constant uncertainty
-contribution of $2\%$, so as the total relative uncertainty decrease, its
-relative contribution increases over time.
-
-\subsection{Fissile Inventory}
-The fissile inventory corresponds to the amount on separated fissile waiting to
-be blend with natural uranium in order to produce the \glspl{FBR} MOX fuel.
-
-As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow on
-year 40, with the deployment of the first reprocessing facility.  It grows
-during the first period of the \glspl{LWR} to \glspl{FBR}-A transition until
-year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
-When he steady state is reached (full \glspl{FBR} fleet), the plutonium
-inventory starts to increase, as the breading ratio of the \glspl{FBR} is higher
-than the deployment needs.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.35]{pu_full}
-    \caption{Fissile (plutonium) inventory as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:pu_full}
-\end{figure}
-
-\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.35]{pu_uncer}
-    \caption{Fissile (plutonium) inventory relative uncertainty, with
-    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
-    contribution of each parameter: cooling time (blue), fuel enrichment (red),
-    cycle time (green), thermal power(brown), separation efficiency (light
-    blue).}\label{fig:pu_uncer}
-\end{figure}
-
-Regarding the uncertainty, beside the low inventory artefact observable around
-year 40, the relative uncertainty starts at about $5\%$, and grows until year
-125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
-it would have reached an equilibrium between $5$ and $10\%$ with longer
-simulations...
-Between year 40 and 70, the main contributor to the fissile inventory
-uncertainty is the cycle length, as for the uranium needs, lower cycle length
-implies more fuel loads.  Never the less, around year 65 (see Figure
-\ref{fig:used_fuel}), the stock of used fuel available for reprocessing starts
-to lack, and the availability of the used fuel starts to dictate the evolution
-of fissile in storage.  The uncertainty weight is then slowly transferred from
-the cycle length to the fuel cooling time.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.18]{used_fuel}
-    \caption{Used fuel inventory.}\label{fig:used_fuel}
-\end{figure}
-Between year 90 and 120, the \glspl{FBR} deployment speed increases, it has to
-compensate the non replacement of the decommissioned \glspl{LWR} as well as
-follow the power demand.  During this period the needs in plutonium are higher
-than its productions, explaining the observed decrease of the total amount, and
-the increase associated relative uncertainty.
-
-As the transition ends, the plutonium breed from the \glspl{FBR} starts to be
-sufficient to sustain the new \glspl{FBR} deployment to follow the power demand.
-
-It is also interesting to note that, the uncertainty contribution from the cycle
-length is between year 40 and 70 comes mainly from fuel batch loading
-frequencies, and after it relative contributions follows closely the thermal
-power one, suggesting a contributions through fuel discharge burnup (i.e. fuel
-discharge composition).
-
-\subsection{Discussion}
-
-Uranium consumption and separated fissile inventory are two important metrics
-regarding to non proliferation and nuclear archaeology. In this study, we have
-been able to estimate than the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
-on the enrichment implies a almost flat uncertainty of $2\%$.
-
-Regarding the reprocessed fissile inventory, this study has shown the limited
-impact of the reprocessed fuel compositions (through burnup variations) it
-limited to $5\%$, where fuel availability constrains, fuel loading frequency (cycle
-time), or fissile materials available for fuel fabrication (cooling time) can lead to higher
-uncertainties, respectively up to $10\%$ and to $30\%$. Moreover it is very
-interesting to observe the pressure transition from one to the other around
-year 70.
-
-\section{Conclusion}
-
-Two main points can be deduced from this work.  Firstly, in a transitional
-fuel cycle, the uncertainty contributions to an output metric can vary over time
-depending of various factors: deployment schedule artifact or pressure point in
-the material flows.
-
-Secondly, it is important to note the special character of the time related
-parameters uncertainty in a fuel cycle study, such as cooling time and cycle
-length. Where some of those time related parameter will on the first order only
-impact material availability (as the cooling time will do), some other, like
-cycle length, will also have a impact as physical parameters such as fuel
-enrichment or thermal power.
-
-Cycle length impacts the discharge fuel burnup, it also affects the frequency of
-the fuel loads, this, as well as the cooling may imply a uncertainty on the
-material availability, which could lead to an artificially large uncertainty.
-Those kind of time related uncertainties will require a careful analysis on further
-uncertainty analysis, in order to understand and measure accurately their
-contributions on uncertainties.
-
-This study aims to be a proof-of-principle for uncertainty propagation in
-potential commercial fuel cycle transition. While it has demonstrated the
-capability to measure the uncertainty on output fuel cycle metrics and their
-relative contributions, it has only been applied to systematic uncertainties per
-facilities (parameters randomly generated at each new facility deployment).
-This kind of study will to be extended to random uncertainty (new parameter
-values at each occurrence) and completely systematic uncertainty (shared by all
-the facilities of a kind).
-
-While the parameters contributing to natural uranium needs and fissile inventory
-uncertainties might be obvious, such study allows to estimate each parameters
-contribution, it could be less obvious for other parameters, such as
-plutonium quality, waste compositions.  Such studies could also provide research
-guidance for nuclear archaeology works, which aims to precisely estimate past
-fissile production by the different nuclear countries.
+%\input{appendix}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \appendix
-%% \section{Appendix}
-%%
-%% Numbering in the appendix is different:
-%% \begin{equation} \label{eq:appendix}
-%%   2 + 2 = 5\,.
-%% \end{equation}
-%% and another equation:
-%% \begin{equation} \label{eq:appendix2}
-%%   a + b = c\,.
-%% \end{equation}
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \section{Nomenclature}
-%%
-%% \begin{table}[H]
-%%     \centering
-%%     \begin{tabular}{l|l}
-%% %         &  \\
-%%         $N$ & Feed assay \\
-%%         $N'$ & Product assay \\
-%%         $N''$ & Tails assay \\
-%%         $\alpha$ & Feed to product enrichment factor \\
-%%         $\beta$ & Feed to tail enrichment factor \\
-%%         $\theta$ & Cut
-%%     \end{tabular}
-%% %    \caption{Caption}
-%%     \label{tab:my_label}
-%% \end{table}
-
-%% \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-%%   \centering
-%%   \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
-%%   \caption{Illustration of the material flow between the different level of
-%%       cascades without tail recycling, in this diagram, nu\_src corresponds to
-%%       an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
-%%       $\{n\}$ to the cascade and the storage getting the products of the
-%%       cascades at the level $\{n\}$.}\label{fig:flow}
-%% \end{figure}
-
-%% \begin{table}[htb]
-%% \centering
-%%   \caption{Summary of cascade properties for each level.}
-%% \begin{tabular}{cllll}
-%% \toprule
-%%
-%% Level   &           & Assay     &       & Machines  \\
-%%         & Feed      & Product   & Feed  &           \\
-%% \midrule
-%% 0       & 0.0071    & 0.0413    & 0.0029 & 167       \\
-%% 1       & 0.0413    & 0.2043    & 0.0173 & 169       \\
-%% 2       & 0.2043    & 0.5941    & 0.0971 & 168       \\
-%% 3       & 0.5941    & 0.8834    & 0.3915 & 168       \\
-%% 4       & 0.8834    & 0.9735    & 0.7746 & 169       \\
-%%
-%% \bottomrule
-%% \end{tabular}
-%%
-%%   \label{tab:cascadelvl}
-%% \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgments}
-This work was funded by the Consortium for Verification Technology under
-Department of Energy National Nuclear Security Administration award number
-DE-NA0002534
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{small}
 \bibliographystyle{ans}
-\bibliography{bibliography}
+\bibliography{refs}  % NO SPACES BETWEEN BIB FILENAMES!
+\end{small}
 \end{document}

### 2018-05-21 theory.tex
working on the flow table

\section{theory}
\subsection{Centrifuge properties}

The present work uses the analytical solution by R\"aetz \cite{raetz.phd} of the
differential equation for the gas centrifuge as described in \cite{glaser.2008}.
Centrifuge parameters, such as average gas temperature, $T$, peripheral speed,
$v$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
counter-current flow ratio, $L/P$, and efficiency, $e$ have been chosen (Table
\ref{tab:centrifuges}) to match the cascade design describe in
\cite{glaser.2008} and \cite{walker.2017}.  These parameters for a P1-type
centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.

\begin{table}[htb]
\centering
\caption{Summary of the centrifuge parameters.}
\begin{tabular}{cccccccc}
\toprule
$T$[K] & $v$[m/s]    & $h$[m] & $d$[m]   & $x$   & $F$[mg/s]  & $L/F$ & $e$  \\
\midrule
320    & $320$           & $1.8$ & $0.105$ & $1e3$  & $13$      & 2     & 1.0  \\
\bottomrule
\end{tabular}

  \label{tab:centrifuges}
\end{table}

\subsection{Cascade Design}

The cascade is built to be ideal, defined by $\alpha =\beta = const$ for all
stage of the cascade, where $\alpha$ and $\beta$ respectively represent the feed
to product and the feed to tail enrichment factors.  $\alpha$ can be expressed
as a function of the feed rate $F$, the separative performance $\delta
U(\theta)$, the cut $\theta$, and $\beta$ as a function of $alpha$ and $\theta$:

\begin{subequations} \label{eqs:alphabeta}
    \begin{equation} \label{eq:alpha}
    \alpha = \sqrt{\frac{2\delta U}{F} \frac{1-\theta}{\theta}}+1
\end{equation}
\\
\begin{equation}\label{eq:beta}
    \beta =   \left(1 - \dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 -
              \theta}\right)
              \left(\dfrac{R}{\dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1
              - \theta}}\right)
\end{equation}
\end{subequations}

From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
the cut, or the ratio of product flow to feed flow
%(all other centrifuge parameters been fixed) allowing the have $\alpha=\beta$
required to build an ideal cascade.

Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
$\theta_{i}$, changes in each stage $i$ of a cascade.

It can be shown that $\theta_{i}$ can be computed from $\alpha$,
$\beta$ values and the feed assay, $N_{i}$:
\begin{eqnarray}
    \theta_{i} = \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
           \dfrac{1}{1 + \beta/R_{i}}}
%%    \theta_{i} &=& \dfrac{N_{i} - N''_{i}}{N'_{i}-N''_{i}}\nonumber\\
%%           &=& \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
%%           \dfrac{1}{1 + \beta/R_{i}}}
\end{eqnarray}

This algorithm assumes that the corresponding separative power $\delta U$ (not
re-computed) can be achieved with the chosen centrifuge design. Once
$\theta_{i}$ is determined, it is possible to compute the product and the tail
assay.

The design of the cascade is performed through 2 steps. First one determines the
configuration and number of stages, adding stages until the product assay of the final stage is greater than or equal to than the desired assay, and the tails assay is similarly less than or equal to the desired tails assay. This determines the number of enriching and stripping stages as
well as their enrichment properties ($N_{i}$, $N'_{i}$,
$N''_{i}$,$\theta_{i}$i).

The second step determines how to populate the cascade with the user-defined
maximum number of centrifuges. One then solves the linear flow equation to
determine the theoretical flow in the cascade.

 \begin{equation}
 \setcounter{MaxMatrixCols}{20}
 \begin{bmatrix}
     -1        & 1-\theta_{_{S+1}} & 0 & ... & 0              & 0              & 0                 & 0                 & 0                 & ... & 0               & 0 \\
 \theta_{_{S}} & -1                & 0 & ... & 0              & 0              & 0                 & 0                 & 0                 & ... & 0               & 0 \\
               &                   &   &     &                &                & ...               &                   &                   &     &                 &   \\
 0             & 0                 & 0 & ... & \theta_{_{-2}} & -1             & 1 - \theta_{_{0}} & 0                 & 0                 & ... & 0               & 0 \\
 0             & 0                 & 0 & ... & 0              & \theta_{_{-1}} & -1                & 1 - \theta_{_{1}} & 0                 & ... & 0               & 0 \\
 0             & 0                 & 0 & ... & 0              & 0              & \theta_{_{0}}     & -1                & 1 - \theta_{_{2}} & 0   & ...             & 0 \\
               &                   &   &     &                &                & ...               &                   &                   &     &                 &   \\
 0             & 0                 & 0 & ... & 0              & 0              & 0                 & 0                 & 0                 & ... & -1              & 1-\theta_{_{E}} \\
 0             & 0                 & 0 & ... & 0              & 0              & 0                 & 0                 & 0                 & ... & \theta_{_{E-1}} & -1
 \end{bmatrix}
 \times
 \begin{bmatrix}
     F_{_{S}}   \\
     F_{_{S+1}} \\
     \cdots     \\
     F_{_{-1}}  \\
     F_{_{0} }  \\
     F_{_{1} }  \\
     \cdots     \\
     F_{_{E-1}} \\
     F_{_{E}}
 \end{bmatrix}
 =
 \begin{bmatrix}
     0      \\
     0      \\
     \cdots \\
     0      \\
     F      \\
     0      \\
     \cdots \\
     0      \\
     0
 \end{bmatrix}
 %\caption{caption needed!}
 \label{eq:flow}
 \end{equation}
Once the relative flow of each stage has been determined, the
cascade can be populated with actual machines up the stages
until either the maximum number available of machines or the maximum feed
flow is reached.

### 2018-05-21 theory.tex
cleaning + part of the theory

@@
 
-The cascade is built to be ideal, defined by $\alpha =\beta = const$ for all
+The cascade is built as an ideal cascade, with no losses in the separative
+work, which corresponds to $\alpha =\beta = const$ for all
 stage of the cascade, where $\alpha$ and $\beta$ respectively represent the feed
-to product and the feed to tail enrichment factors.  $\alpha$ can be expressed
-as a function of the feed rate $F$, the separative performance $\delta
-U(\theta)$, the cut $\theta$, and $\beta$ as a function of $alpha$ and $\theta$:
+to product and the feed to tail enrichment factors.  $\alpha$ and $\beta$ can be
+expressed as function of the abondance ($R$) or the enrichment ($N$) of respectively the
+product ($R'$,$N'$) and the feed,($R$,$N$) and the feed and the tails ($R''$,$N''$) such as:
+\begin{subequations} \label{eqs:alphabeta}
+    \begin{equation} \label{eq:alpha_def}
+        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
+\end{equation}
+\\
+\begin{equation}\label{eq:beta-def}
+        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
+\end{equation}
+\end{subequations}
 
-\begin{subequations} \label{eqs:alphabeta}
+As detailled in \cite{avery} it is also possible to derive $\alpha$ from the
+first principle, and express it as a function of the feed rate $F$ the separative performance $\delta
+U(\theta)$, the cut $\theta$:
+
     \begin{equation} \label{eq:alpha}
@@
 \end{equation}
-\\
+
+From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations \eqref{eqs:alphabeta} it is
+possible to express $\beta$ as a function of the feed abondance, $R$, the cut
+$\theta$ and $\alpha$:
+
 \begin{equation}\label{eq:beta}
-    \beta =   \left(1 - \dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1 -
-              \theta}\right)
-              \left(\dfrac{R}{\dfrac{N - \theta \dfrac{\alpha R}{1+\alpha R}}{1
-              - \theta}}\right)
+    \beta =   R \left(\dfrac{1-\theta}
+                     {\dfrac{R}{R+1}- \theta \dfrac{\alpha R}{1+\alpha R}} -1\right)
 \end{equation}
-\end{subequations}
 
 From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
-the cut, or the ratio of product flow to feed flow
-%(all other centrifuge parameters been fixed) allowing the have $\alpha=\beta$
-required to build an ideal cascade.
-
-Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
-$\theta_{i}$, changes in each stage $i$ of a cascade.
-
-It can be shown that $\theta_{i}$ can be computed from $\alpha$,
+the cut, $\theta$, or the ratio of product flow to feed flow required to build an ideal
+cascade:
 $\beta$ values and the feed assay, $N_{i}$:
@@
            \dfrac{1}{1 + \beta/R_{i}}}
-%%    \theta_{i} &=& \dfrac{N_{i} - N''_{i}}{N'_{i}-N''_{i}}\nonumber\\
-%%           &=& \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
-%%           \dfrac{1}{1 + \beta/R_{i}}}
 \end{eqnarray}
 
-This algorithm assumes that the corresponding separative power $\delta U$ (not
-re-computed) can be achieved with the chosen centrifuge design. Once
-$\theta_{i}$ is determined, it is possible to compute the product and the tail
-assay.
+Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
+$\theta_{i}$, changes in each stage $i$ of a cascade.  This algorithm assumes
+that the corresponding separative power $\delta U$ (not re-computed) can be
+achieved with the chosen centrifuge design, tuning other operationnal paramter
+such as the rotation speed, the counter-current flow ratio...  Once $\theta_{i}$
+is determined, it is possible to compute the product and the tail assay.
 
 The design of the cascade is performed through 2 steps.  First one determines the
-configuration and number of stages, adding stages until the product assay of the final stage is greater than or equal to than the desired assay, and the tails assay is similarly less than or equal to the desired tails assay.
-This determines the number of enriching and stripping stages as
-well as their enrichment properties ($N_{i}$, $N'_{i}$,
-$N''_{i}$,$\theta_{i}$i).
+configuration and number of stages, adding stages until the product assay of the
+final stage is greater than or equal to than the desired assay, and the tails
+assay is similarly less than or equal to the desired tails assay.  This
+determines the number of enriching and stripping stages as well as their
+enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).
 
 The second step determines how to populate the cascade with the user-defined
-maximum number of centrifuges. One then solves the linear flow equation to
-determine the theoretical flow in the cascade.
+maximum number of centrifuges.
+
+One solves the linear flow equation, \eqref{eq:flow}, to determine the
+theoretical flow in the cascade.
 
@@
 \end{equation}
-Once the relative flow of each stage has been determined, the
-cascade can be populated with actual machines up the stages
-until either the maximum number available of machines or the maximum feed
-flow is reached.
+
+Once the relative flow of each stage has been determined, the cascade can be
+populated with actual machines up the stages until the maximum number available
+of machines is reached.
+
+\subsection{Miss-use models}
+Little information is available about optimising an existing enrichment cascade
+that is being fed with a feed enrichment that does not match the design one. So
+far 3 different methods have been investigated, the first one assumes that no
+change are been made on the cascade, the second one, assumes that the cut value
+at each stage is retuned to maintain the ideal state of the cascade, the last
+one, described in \cite{walker.2017} assumes the tails to product enriching
+factor remains constants ($\gamma = \alpha\times\beta$). Models behavior, and
+assumptions are summarized in Tab. \ref{tab:models}.

### 2018-05-21 theory.tex
starting case B description

@@
 assumptions are summarized in Tab. \ref{tab:models}.
+
+\begin{table}[htb]
+\centering
+  \caption{Summary of miss-use model properties.}
+\begin{tabular}{l|ccc}
+\toprule
+
+Model                &    A                 & B                  & C  \\
+\midrule
+Constant parameters  & $\alpha_i, \theta_i$ & $\alpha_i=\beta_i$ & $\gamma_i=\alpha_i*\beta_i, \theta_i$       \\
+Optimised parameters & $\beta_i$            & $\theta_i$         & $\alpha_i, \beta_i$                     \\
+Assays determination & blended              & ideal              & blended                  \\
+Flow                 & unchanged            & scaled             & unchanged       \\
+
+\bottomrule
+\end{tabular}
+  \label{tab:models}
+\end{table}
+
+\subsubsection{Case A}
+The tuning method A does not re-optimize $\theta_i$ based on the true flow
+enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed assay
+($N'$), they do not change from stage to stage. According to equation
+\eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, when the feed assay ($N$)
+changes, then $\beta$ will change accordingly.  This breaks the ideal status of
+the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.
+
+In order to compute the proper product and tails assay at each stage, the
+tails and the product from respectively the next and the previous stage must be
+blended in order to determine the correct stage feed assay. As this is a obvious
+cycling problem, an iterative solution has been chosen: all feed assays are
+iteratively updated, blending the proper product and tails, then using the
+updated feed assay, the new product and tail assays are recomputed. This process
+is repeated until the change in assays is smaller than the set precision (1e-8
+by default).
+As the cut remain fixed at each stage the different flow do not need to be
+recomputed.
+
+\subsubsection{Case B}
+
+The second method the cut value at each stage $\theta_i$, is retuned in order to
+maintain the $\alpha_i$ and $\beta_i$ at their original values. As the cascade
+remains ideal, the product and tail assay at each stages (and for the overall
+cascade) is easily determined using equations \eqref{eqs:alphabeta}.
+
+As the cuts values change, the flow rate between the different stage has to be
+recomputed. Because the cascade is not reorganised (the number of cascade per
+stage remain the same as the original design). The new flow rate are computed as the flow rate of cascade

### 2018-05-22 theory.tex
adding case C equation

@@
 recomputed. Because the cascade is not reorganised (the number of cascade per
-stage remain the same as the original design). The new flow rate are computed as the flow rate of cascade
+stage remain the same as the original design). The new flow rate are computed as
+the flow rates of the reconfigured cascade scaled down by the possible
+flows of the original one: the flow rates of a reconfigured cascade are
+computed, the ratios of the flow stage by stage with the original are determined,
+the smaller ratio is used to scale down all the flow rates.
+
+\subsubsection{Case C}
+The last model assumes that the tail to product enrichment factor remains
+constant regardless to the feed assays. To compute the response of the cascade
+one need to determine $\alpha$ and $\beta$ such as their product and
+$\theta$ remain fixed. 
+From equations \eqref{eqs:alphabeta} and the assay conservation equation $N =
+\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
+the feed assay $N$, $gamma$ and the cut $theta$ as one solution of the second
+order equation \eqref{eq:gamma_p}:
+
+\begin{equation}\label{eq:gamma_p}
+\gamma(1-N')(P\theta-N) - N'(1-(N'\theta-N)/(-1+\theta))(-1+\theta) = 0
+\end{equation}
+
+The only solution allowing product assay values ranging between 0 and 1 is the
+following :
+\begin{equation}\label{eq:model_b_sol}
+    \frac{\gamma(N + \theta) - N 
+            - \sqrt{\gamma^2(N^2 
+                            - 2N\theta 
+                            + \theta^2) 
+                    - \gamma(2N^2 - 2\theta^2 
+                            + 2N + 2\theta) 
+                    + N^2 + 2N\theta + \theta^2 - 2N - 2\theta + 1} 
+            - \theta + 1}
+        {2\theta(\gamma - 1)}
+\end{equation}
+
+The last model is very similar to the model A.

### 2018-05-22 paper.tex
working on the flow table
first set of review comments

--- 2018-05-16 paper.tex
@@
 \newacronym{LWR}{LWR}{light water reactor}
-\newacronym{FBR}{FBR}{fast breeder reactor}
+\newacronym{SFR}{SFR}{fast breeder reactor}
 
@@
 without errors.  Those errors have different sources: data uncertainties (from
-the simulator's reliance on previously estimated/measured metrics), modeling
+%% I'm not a fan of the use of the word ``errors'' here.  We should be careful
+%% since (in English) this can meam ``mistakes''.  Uncertainty is a better
+%% word, and then we'll have to distinguish between input uncertainties and
+%% output uncertainties.
+the simulator's reliance on previously estimated/measured data), modeling
 uncertainties (from simplifications made by the simulator) and the
-``operational`` uncertainty (from the operation parameter uncertainties of
-different facilities).
+``operational'' uncertainty (from the expected behavior of the facilities
+being simulated).
+%% is this operational uncertainty really just a different kind of data?
 
-Simulation errors are important in the context of treaty verification. 
+Simulation errors could be important in the context of treaty verification. 
 Some scenarios require estimating historical fissile
@@
 subject to uncertainty, the total production quantities will then also be
-uncertain, creating an opportunity for undetected diversion.  This study seeks
+uncertain.  Any uncertainty in fissile production quantities poses a material
+accounting challenge, possibly
+creating an opportunity for undetected diversion.  This study seeks
 to understand which measures of facility operation have the most impact on the
@@
 fuel cycle simulator \cite{cyclus} to estimate the effect of individual facility uncertainties on the output metrics.
+%% should there be a reference for Total Monte Carlo?
 
@@
 To estimate the uncertainty of fuel cycle output metrics, a Total Monte
-Carlo approach has been applied.  In the following, output metric uncertainty
-corresponds to the standard deviation of the output metrics from 199
-different simulations.  For each deployed facility, the
-parameters are normally distributed with an artificially large standard
-deviation of $10\%$.
+Carlo approach has been applied.  In each of 199 independent simulations,
+some of the parameters that define facility behavior are randomly selected
+from Normal distributions with standard deviations that are $10\%$ of the mean
+value.  This artificially large standard deviation is selected for the purpose
+of demonstrating the methodology.  The mean and standard deviation of some
+output metrics are calculated from the simulation output, as a function of time.
 
-To pursue this work, both the Cycamore\cite{cycamore} package\footnote{Low
-fidelity facilities package for Cyclus} and the
-CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models} were
-updated\cite{mouginot_2018, cyclass} to evaluate the uncertainty of several
+To pursue this work, both the Cycamore\footnote{Low
+fidelity facilities package for Cyclus}\cite{cycamore} and the
+CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models}\cite{mouginot_2018, cyclass} packages were
+updated to evaluate the uncertainty of several
 operational parameters in their associated facilities.  Table
@@
 \centering
-  \caption{Summary of facility modifications according to their source package.}
+  \caption{Summary of facility modifications according to their Cyclus archetype package.}
 \begin{tabular}{cll}
@@
 \midrule
-Cycamore & Separation & Separation efficiency     \\
+Cycamore & Separation & Separation efficiency     \\ %% add hline in 2nd two columns
          & Storage    & Residence Time            \\
@@
 deployed (such as a reactor or a fuel fabrication facility) a new set of
-parameters are computed.
+parameters are sampled, and those parameters are used throughout the life
+of that facility.
 
 \subsection{The Fuel Cycle Scenario}
-This work aims to assess the impact of the operational uncertainties of a simple
-transition, inspired from the EG23 fuel cycle
-of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. Pictured in Figure \ref{fig:cycle}, this is a
-transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
-sodium fast reactor fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
-of the generated power (Figure \ref{fig:power}).
+For demonstration purposes, a simple commercial fuel cycle transition is used,
+inspired from the EG23 fuel cycle
+of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}.
+Pictured in Figure \ref{fig:cycle}, this is a
+transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a
+\gls{SFR} fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
+of the nuclear generated power (Figure \ref{fig:power}).
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
@@
   \includegraphics[scale=0.31]{cycle.png}
-  \caption{Illustration of the material flow between the different facilities,
+  \caption{Simplified representation of the material flow between the different facilities,
   with each operational parameter associated with an
@@
 \end{figure}
+%% Update this to match the one in the CVT poster?
 
@@
 composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
-transition starts around year 35, with the deployment of \glspl{FBR}. The \glspl{FBR} are loaded
+transition starts around year 35, with the deployment of \glspl{SFR}. The \glspl{SFR} are loaded
 with \gls{MOX}, which consists of plutonium blended with natural
@@
     \caption{Electric power generated over time, with the full production,
-        the \gls{LWR} contribution, and the \gls{FBR} contribution labeled in blue, orange, and green, respectively.}
+        the \gls{LWR} contribution, and the \gls{SFR} contribution labeled in blue, orange, and green, respectively.}
     \label{fig:power}
@@
 by the feed material availability).  The enrichment of the \gls{UOX} is processed
-on demand.  Buffer storages (not shown in Figure \ref{fig:cycle}) are present
+%% is it really a constant rate then?  Maybe we need a better word to describe this
+on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
+%% You can't pluralize ``storage'' in English - it's considered uncountable
 between all facilities with constant processing rates.
@@
 In this work, a time step of 1 month has been considered, i.e., each output
-metric is reported once per month. Additionally, decay processes have not be taken into
-account.
+metric is reported once per month. Additionally, decay processes have not be
+taken into account.
 
@@
 fuel fabrication model\cite{Leniau2015125} which
-calculates the fissile fraction required in the fuel to reach a target
+calculates the fissile fraction required in the fuel to reach a given target
 burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
@@
 $10\%$.
+%% Did you have to experiment to find the burnup uncertainty that results in a 10% enrichment uncertainty?
+
+For each of the parameters in Table \ref{tab:package_uncertainty}, a set of
+199 simulations was performed with only that parameter being randomly varied.
+An additional set of 199 simulations was performed in which all five
+parameters are randomly varied.  A reference simulation was performed
+with all five parameters fixed at the mean value.
 
@@
 
-The main interests of nuclear archaeology involve highly enriched uranium production and
-fissile inventories, so this study mainly focuses on the uncertainties of
+Because the main interests of nuclear archaeology involve highly enriched uranium production and
+fissile inventories, this study mainly focuses on the uncertainties of
 the total quantity of natural uranium used and the total unused fissile
 inventory (unused reprocessed plutonium).
-Generated power is also briefly being investigated to ensure the overall
+%% unused implies it's never used, but I don't think that's right.  You just mean the amount
+%% that is being stored in a separated state any point in time, right?
+Generated power is also briefly investigated to ensure the overall
 uncertainty is not contaminated with a missed fuel loading, which could
 be interesting but is not the focus of this work.
+%% what do you mean by contaminated???  This probably deserves more explanation
 
-For this study, the 199 simulations were performed six times, and a reference calculation was also
-computed. With the five parameters in Table
-\ref{tab:package_uncertainty} (separation efficiency, residence time, \gls{UOX} fuel
-enrichment, reactor cycle length, reactor thermal power) being tracked, the six sets are divided as follows: five sets where a single parameter is varied and 
-the four others remain fixed, and one with all five parameters being varied. 
-The reference calculation is a single
-simulation with all five parameters fixed at the mean value.
-
-In the following, each total uncertainty is reported at $\pm1\sigma$ around the
-mean values of the corresponding uncertainty set at each time step.  The 
-time-dependant relative uncertainties are computed as the standard deviation of a
-single set over its mean value at the corresponding time.
+At each time step, the $\pm1\sigma$ uncertainty due to the full set of varied
+parameters is reported.  In addition, the relative contribution to the total
+uncertainty from each of the parameters is calculated as the ratio of the
+$1\sigma$ uncertainty due to that parameter over the total uncertainty.
 
@@
 
-By construction, the very low uncertainty (Figure \ref{fig:power_full}) on the
-generated power is expected.
-
-\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
     \centering
@@
 
+By design, the very low uncertainty (Figure \ref{fig:power_full}) on the
+generated power is expected.
 Indeed the transition scenario has been designed to allow all the reactors to
 receive the fuel as needed allowing them to be producing power all the time.
-This ensures that the uncertainty measured any other parameters is not
-influenced by the reactors miss-loadings.  As \glspl{FBR} fuel is built from
-reprocessed used fuels, the availability of those used fuels may impact the
-capability to build the required MOX-FBR fuel.  Having reactor miss-loads, may
-impact more miss-loading later during a simulation and lead to a snow-ball
-effect.  Having a small uncertainty on the power generation ensures large miss
-load effects are not to be considered here.
+This ensures that the measured uncertainty is not affected by a facility
+disruption that has an outsized impact on material flows.
+As \gls{SFR} fuel is built from
+reprocessed used fuel, the availability of that used fuel may impact the
+capability to build the required MOX-SFR fuel.  Facility disruptions may
+cause material shortages that can lead to snow-ball effect of more disruptions
+later in the simulation.  While such disruptions are interesting in some analyses,
+they are outside the scope of this study.
 
@@
 
-As expected, cooling time, separation efficiency and thermal power don't
+As expected, cooling time, separation efficiency and thermal power do not
 affect the natural uranium consumption.  The uncertainty on the natural uranium
-consumption is dominated by the \glspl{LWR} cycle length: shorter the cycle
+consumption is dominated by the \gls{LWR} cycle length: shorter the cycle
 length is, the more fuel will be loaded.
@@
 The decrease of the cycle time uncertainty contribution, from year 30 to year
-90, can be understand as an averaging effect.  As the uncertainty are considered
-as systematic per deployed facility, each reactor will have a different cycle
-length value, so a different number of loaded batches per year.With the increase
-of deployed reactors, the number of batches of \glspl{LWR} fuel loaded converges
+90, can be understood as an averaging effect.  As the uncertainty are defined once
+per deployed facility, each reactor will have a different cycle
+length value, so a different number of batches loaded per year.  With the increase
+of deployed reactors, the number of batches of \gls{LWR} fuel loaded converges
 to the references one, reducing its impact on the uncertainty on the total
 uranium consumption.
+%% Why does the relative uncertainty due to cyle time not approach 0?
 
 The fuel enrichment contribution follow a close to constant uncertainty
-contribution of $2\%$, so as the total relative uncertainty decrease, its
-relative contribution increases over time.
+contribution of $2\%$, so as the total relative uncertainty decrease, it
+has a growing shared of the total uncertainty over time.
 
 \subsection{Fissile Inventory}
-The fissile inventory corresponds to the amount on separated fissile waiting to
-be blend with natural uranium in order to produce the \glspl{FBR} MOX fuel.
+The fissile inventory corresponds to the amount of separated fissile material waiting to
+be blended with natural uranium in order to produce the \gls{SFR} MOX fuel.
 
-As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow on
+As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow in
 year 40, with the deployment of the first reprocessing facility.  It grows
-during the first period of the \glspl{LWR} to \glspl{FBR}-A transition until
+during the first period of the \glspl{LWR} to \gls{SFR}-A transition until
 year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
-When he steady state is reached (full \glspl{FBR} fleet), the plutonium
-inventory starts to increase, as the breading ratio of the \glspl{FBR} is higher
+When he steady state is reached (full \gls{SFR} fleet), the plutonium
+inventory starts to increase, as the breading ratio of the \glspl{SFR} is higher
 than the deployment needs.
@@
 
-Regarding the uncertainty, beside the low inventory artefact observable around
-year 40, the relative uncertainty starts at about $5\%$, and grows until year
+Regarding the uncertainty, disregarding the artefact of a very low mean inventory
+observed at the onset of fissile material production, the relative uncertainty
+starts at about $5\%$, and grows until year
 125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
+%% I don't see what you mean by decrease up to 10%?
 it would have reached an equilibrium between $5$ and $10\%$ with longer
@@
 Between year 40 and 70, the main contributor to the fissile inventory
-uncertainty is the cycle length, as for the uranium needs, lower cycle length
+uncertainty is the cycle length.  As with the uranium needs, lower cycle length
 implies more fuel loads.  Never the less, around year 65 (see Figure
-\ref{fig:used_fuel}), the stock of used fuel available for reprocessing starts
-to lack, and the availability of the used fuel starts to dictate the evolution
-of fissile in storage.  The uncertainty weight is then slowly transferred from
+%% Aren't you varying the cycle length equally to be smaller and larger, so why
+%% focus on ``lower cycle lengths''?
+\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
+small enough to start limiting producton of fissile material.
+The uncertainty weight is then slowly transferred from
 the cycle length to the fuel cooling time.
@@
     \caption{Used fuel inventory, corresponding to the amount of used
-    \glspl{LWR} and \glspl{FBR} fuel, cooled and waiting to be reprocessed.}
+    \glspl{LWR} and \glspl{SFR} fuel, cooled and waiting to be reprocessed.}
     \label{fig:used_fuel}
 \end{figure}
-Between year 90 and 120, the \glspl{FBR} deployment speed increases, it has to
+Between year 90 and 120, the \gls{SFR} deployment speed increases, it has to
 compensate the non replacement of the decommissioned \glspl{LWR} as well as
@@
 
-As the transition ends, the plutonium breed from the \glspl{FBR} starts to be
-sufficient to sustain the new \glspl{FBR} deployment to follow the power demand.
+As the transition ends, the plutonium breed from the \glspl{SFR} starts to be
+sufficient to sustain the new \glspl{SFR} deployment to follow the power demand.
 

### 2018-05-22 theory.tex
first draft of theory

@@
 
-The cascade is built as an ideal cascade, with no losses in the separative
-work, which corresponds to $\alpha =\beta = const$ for all
-stage of the cascade, where $\alpha$ and $\beta$ respectively represent the feed
-to product and the feed to tail enrichment factors.  $\alpha$ and $\beta$ can be
-expressed as function of the abondance ($R$) or the enrichment ($N$) of respectively the
-product ($R'$,$N'$) and the feed,($R$,$N$) and the feed and the tails ($R''$,$N''$) such as:
+The cascade is built as an ideal cascade, with no losses in the separative work,
+which corresponds to $\alpha =\beta = const$ for all stage of the cascade, where
+$\alpha$ and $\beta$ respectively represent the feed to product and the feed to
+tail enrichment factors.  $\alpha$ and $\beta$ can be expressed as function of
+the abundance ($R$) or the enrichment ($N$) of respectively the product
+($R'$,$N'$) and the feed,($R$,$N$) and the feed and the tails ($R''$,$N''$) such
+as:
 \begin{subequations} \label{eqs:alphabeta}
@@
 
-As detailled in \cite{avery} it is also possible to derive $\alpha$ from the
-first principle, and express it as a function of the feed rate $F$ the separative performance $\delta
-U(\theta)$, the cut $\theta$:
+As detailed in \cite{avery} it is also possible to derive $\alpha$ from the
+first principle, and express it as a function of the feed rate $F$ the
+separative performance $\delta U(\theta)$, the cut $\theta$:
 
@@
 
-From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations \eqref{eqs:alphabeta} it is
-possible to express $\beta$ as a function of the feed abondance, $R$, the cut
-$\theta$ and $\alpha$:
+From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
+\eqref{eqs:alphabeta} it is possible to express $\beta$ as a function of the
+feed abundance, $R$, the cut $\theta$ and $\alpha$:
 
@@
 that the corresponding separative power $\delta U$ (not re-computed) can be
-achieved with the chosen centrifuge design, tuning other operationnal paramter
+achieved with the chosen centrifuge design, tuning other operational parameter
 such as the rotation speed, the counter-current flow ratio...  Once $\theta_{i}$
@@
 \theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
-the feed assay $N$, $gamma$ and the cut $theta$ as one solution of the second
+the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
 order equation \eqref{eq:gamma_p}:
@@
 \end{equation}
+Once the product assay is known, one can trivially determine the tail assay,
+$\alpha$ and $\beta$ using equations \eqref{eqs:alphabeta} and mass
+conservation.
 
-The last model is very similar to the model A.
+Similarly as model A, because the cut values remain constant, the flows don't
+need to be recomputed, and the correct assays, $\alpha$ and $\beta$ are
+determined through iterative blending of the product assays of the previous
+stage and the tails assay of the next stage using equation
+\eqref{eq:model_b_sol}.

### 2018-05-22 theory.tex
change case for model

@@
 
-\subsubsection{Case A}
+\subsubsection{Model A}
 The tuning method A does not re-optimize $\theta_i$ based on the true flow
@@
 
-\subsubsection{Case B}
+\subsubsection{Model B}
 
@@
 
-\subsubsection{Case C}
+\subsubsection{Model C}
 The last model assumes that the tail to product enrichment factor remains

### 2018-05-23 experiement.tex
almost finished experiment description

\section{the experiment}
This works focuses on comparing the different miss use models to a reference
calculation in which a single large cascade is build and designed to directly
produce \gls{HEU} from natural uranium.
This works uses the Cyclus fuel cycle simulator to allow material exchange
between facilities.

\subsection{The cascade configuration}
\subsubsection{reference}
As mentioned previously, all the further calculations will be compared to the
most favorable configuration to produce \gls{HEU}, where all the available
centrifuges are used in a single large cascade designed to directly produce \gls{HEU}
from natural uranium, with a tail assay close to $0.3w\%$ uranium. The design
characteristic of the reference cascade are summarized in Table
\ref{tab:cascade_config}.

\subsubsection{default cascade}
The default cascade is the cascade design for normal civilian enrichment
operation, enriching natural uranium to about $3.5w\%$. This cascade will be
layered and fed with uranium at higher enrichment to evaluate the possibility
to used them, with few or no tuning, to produce \gls{HEU}. The characteristics of
the default cascade are summarized in Table \ref{tab:cascade_config}.

\begin{table}[htb]
\centering
  \caption{Summary of cascade design.}
\begin{tabular}{cccc}
\toprule

Cascade Design &       & Reference  & Default    \\
\midrule
Targeted  & Feed       & $0.71w\%$  & $0.71w\%$  \\
Assays    & Product    & $90w\%$    & $4.0w\%$   \\
          & Tail       & $0.3w\%$   & $0.3w\%$   \\
\midrule
Effective & Product    & $90.35w\%$ & $4.13w\%$  \\
Assays    & Tail       & $0.28w\%$  & $0.28w\%$  \\ 
\midrule
Stages    & Enriching  & 4          & 4          \\
Number    & Stripping  & 39         & 10         \\
\bottomrule
\end{tabular}
  \label{tab:cascade_config}
\end{table}

\subsection{scenarios}
Seven different scenarios have been simulated:
\begin{itemize}
\item one as the reference calculation, with a single centrifuges designed to
    produce directly \gls{HEU} from natural uranium,
\item three calculations (one per miss-use model) were default cascade are
    chained to produce \gls{HEU}, without recycling the tails of each cascade,
    the cascade tails are directly sent to the waste,
\item three calculations (one per miss-use model) were default cascade are
    chained to produce \gls{HEU}, the tails of each cascade are recycled, blending
    the tail of one level in the feed of the previous level of
    cascades (see Figure \ref{fig:cascade_level}.
\end{itemize}
In the following, cascades can be connected in tandem, where each set of cascade
in parallel is called a ``level``, as illustrated on Figure
\ref{fig:cascade_level}.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.45]{flow}
    \caption{Schematic representation of the chained cascade on three level,
    with the feed, product and the tail flows, respectively in blue, green and
    red. The dashed orange line represent the alternative tail flow with
    recycling them.}
    \label{fig:cascade_level}
\end{figure}

\subsection{Level population}
In order to assign the optimum number of cascade to each level a virtual cut as
been computed as:
\begin{equation}
    \theta^{v}_{i} = \frac{F_{i}-T_{i}}{P_{i}-T_{i}},
\end{equation}
where, i represents a level of cascade and $F_{i}$, $P_{i}$ and $T_{i}$
respectively the feed, product and tail assay of the cascades at this level.

A flow equation similar to \eqref{eq:flow} is then solve to get the optimum
number of cascade per level. When the tail recycling is not enable the
$(1-\theta)$ terms are removed from the flow equation.
The results of the level population are summarized in Table \ref{tab:level}.

\begin{table}[htb]
\centering
  \caption{Summary of cascades level population.}
\begin{tabular}{ccccccccc}
\toprule

Model       &        &           & A         & A         & B         & B       & C         & C          \\
Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
        &            & Tail      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
\midrule                                                                                                 
        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $20.6w\%$ & $69.8w\%$ \\
        &            & Tail      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.72w\%$ & $9.43w\%$  \\
        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
\midrule                                                                                                 
        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $20.6w\%$ & $72.6w\%$ \\
Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $61.0w\%$ & $98.4w\%$ \\
        &            & Tail      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $9.56w\%$ & $69.4w\%$ \\
        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.31      & 0.35      \\
\midrule                                                                                                 
        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $61.0w\%$ & N.A.      \\
Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $90.4w\%$ & N.A.      \\
        &            & Tail      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $38.9w\%$ & N.A.      \\
        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:cascade_config}
\end{table}

### 2018-05-24 experiement.tex
add one figs

@@
     \includegraphics[scale=0.45]{flow}
-    \caption{Schematic representation of the chained cascade on three level,
+    \caption{Schematic representation of the chained cascades with three levels,
     with the feed, product and the tail flows, respectively in blue, green and
@@
 A flow equation similar to \eqref{eq:flow} is then solve to get the optimum
-number of cascade per level. When the tail recycling is not enable the
-$(1-\theta)$ terms are removed from the flow equation.
-The results of the level population are summarized in Table \ref{tab:level}.
+number of cascade per level. When the tail are not recycled, the $(1-\theta)$
+terms are removed from the flow equation.  The results of the level population
+are summarized in Table \ref{tab:level}.
 

### 2018-05-24 results.tex
add one figs

--- 2018-05-24 experiement.tex
@@
-\section{the experiment}
-This works focuses on comparing the different miss use models to a reference
-calculation in which a single large cascade is build and designed to directly
-produce \gls{HEU} from natural uranium.
-This works uses the Cyclus fuel cycle simulator to allow material exchange
-between facilities.
-
-\subsection{The cascade configuration}
-\subsubsection{reference}
-As mentioned previously, all the further calculations will be compared to the
-most favorable configuration to produce \gls{HEU}, where all the available
-centrifuges are used in a single large cascade designed to directly produce \gls{HEU}
-from natural uranium, with a tail assay close to $0.3w\%$ uranium. The design
-characteristic of the reference cascade are summarized in Table
-\ref{tab:cascade_config}.
-
-\subsubsection{default cascade}
-The default cascade is the cascade design for normal civilian enrichment
-operation, enriching natural uranium to about $3.5w\%$. This cascade will be
-layered and fed with uranium at higher enrichment to evaluate the possibility
-to used them, with few or no tuning, to produce \gls{HEU}. The characteristics of
-the default cascade are summarized in Table \ref{tab:cascade_config}.
-
-\begin{table}[htb]
-\centering
-  \caption{Summary of cascade design.}
-\begin{tabular}{cccc}
-\toprule
-
-Cascade Design &       & Reference  & Default    \\
-\midrule
-Targeted  & Feed       & $0.71w\%$  & $0.71w\%$  \\
-Assays    & Product    & $90w\%$    & $4.0w\%$   \\
-          & Tail       & $0.3w\%$   & $0.3w\%$   \\
-\midrule
-Effective & Product    & $90.35w\%$ & $4.13w\%$  \\
-Assays    & Tail       & $0.28w\%$  & $0.28w\%$  \\ 
-\midrule
-Stages    & Enriching  & 4          & 4          \\
-Number    & Stripping  & 39         & 10         \\
-\bottomrule
-\end{tabular}
-  \label{tab:cascade_config}
-\end{table}
-
-\subsection{scenarios}
-Seven different scenarios have been simulated:
-\begin{itemize}
-\item one as the reference calculation, with a single centrifuges designed to
-    produce directly \gls{HEU} from natural uranium,
-\item three calculations (one per miss-use model) were default cascade are
-    chained to produce \gls{HEU}, without recycling the tails of each cascade,
-    the cascade tails are directly sent to the waste,
-\item three calculations (one per miss-use model) were default cascade are
-    chained to produce \gls{HEU}, the tails of each cascade are recycled, blending
-    the tail of one level in the feed of the previous level of
-    cascades (see Figure \ref{fig:cascade_level}.
-\end{itemize}
-In the following, cascades can be connected in tandem, where each set of cascade
-in parallel is called a ``level``, as illustrated on Figure
-\ref{fig:cascade_level}.
-
+\section{Results}
+\subsection{timestep effect}
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
     \centering
-    \includegraphics[scale=0.45]{flow}
-    \caption{Schematic representation of the chained cascades with three levels,
-    with the feed, product and the tail flows, respectively in blue, green and
-    red. The dashed orange line represent the alternative tail flow with
-    recycling them.}
-    \label{fig:cascade_level}
+    \includegraphics[scale=0.18]{HEU_prod_timestep}
+    \caption{}
+    \label{fig:HEU_timestep}
 \end{figure}
-
-\subsection{Level population}
-In order to assign the optimum number of cascade to each level a virtual cut as
-been computed as:
-\begin{equation}
-    \theta^{v}_{i} = \frac{F_{i}-T_{i}}{P_{i}-T_{i}},
-\end{equation}
-where, i represents a level of cascade and $F_{i}$, $P_{i}$ and $T_{i}$
-respectively the feed, product and tail assay of the cascades at this level.
-
-A flow equation similar to \eqref{eq:flow} is then solve to get the optimum
-number of cascade per level. When the tail are not recycled, the $(1-\theta)$
-terms are removed from the flow equation.  The results of the level population
-are summarized in Table \ref{tab:level}.
-
-\begin{table}[htb]
-\centering
-  \caption{Summary of cascades level population.}
-\begin{tabular}{ccccccccc}
-\toprule
-
-Model       &        &           & A         & A         & B         & B       & C         & C          \\
-Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
-\midrule                                                                                                 
-        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
-Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
-        &            & Tail      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
-        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
-\midrule                                                                                                 
-        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
-Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $20.6w\%$ & $69.8w\%$ \\
-        &            & Tail      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.72w\%$ & $9.43w\%$  \\
-        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
-\midrule                                                                                                 
-        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $20.6w\%$ & $72.6w\%$ \\
-Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $61.0w\%$ & $98.4w\%$ \\
-        &            & Tail      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $9.56w\%$ & $69.4w\%$ \\
-        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.31      & 0.35      \\
-\midrule                                                                                                 
-        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $61.0w\%$ & N.A.      \\
-Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $90.4w\%$ & N.A.      \\
-        &            & Tail      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $38.9w\%$ & N.A.      \\
-        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
-\bottomrule
-\end{tabular}
-  \label{tab:cascade_config}
-\end{table}

### 2018-05-24 results.tex
add figures

@@
 \subsection{timestep effect}
+%% \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+%%     \centering
+%%     \includegraphics[scale=0.18]{HEU_prod_timestep}
+%%     \caption{}
+%%     \label{fig:HEU_timestep}
+%% \end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[scale=0.18]{NR_case1}
+        \caption{No tail recycling}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[scale=0.18]{R_case1}
+        \caption{Tail recycling}
+    \end{subfigure}
+    \caption{Evolution of the product assays at each level with considering
+    miss-use model A, with (right) and without recycling (left).}
+\end{figure}
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[scale=0.18]{NR_case2}
+        \caption{No tail recycling}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[scale=0.18]{R_case2}
+        \caption{Tail recycling}
+    \end{subfigure}
+    \caption{Evolution of the product assays at each level with considering
+    miss-use model B, with (right) and without recycling (left).}
+\end{figure}
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[scale=0.18]{NR_case3}
+        \caption{No tail recycling}
+    \end{subfigure}%
+    \begin{subfigure}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[scale=0.18]{R_case3}
+        \caption{Tail recycling}
+    \end{subfigure}
+    \caption{Evolution of the product assays at each level with considering
+    miss-use model C, with (right) and without recycling (left).}
+\end{figure}
+
 \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
     \centering
-    \includegraphics[scale=0.18]{HEU_prod_timestep}
-    \caption{}
-    \label{fig:HEU_timestep}
+    \includegraphics[scale=0.25]{HEU_prod_rate}
+    \caption{Production rate for the different model configuration, with in blue
+    the case without tail recycling, in orange with tail recycling, and in green
+    the reference one.}
+    \label{fig:HEU_rate}
 \end{figure}

### 2018-05-24 paper.tex
almost finished experiment description
tackling PPHW comments

@@
 Fuel cycle simulations, as with any simulation process, do not produce results
-without errors.  Those errors have different sources: data uncertainties (from
-%% I'm not a fan of the use of the word ``errors'' here.  We should be careful
-%% since (in English) this can meam ``mistakes''.  Uncertainty is a better
-%% word, and then we'll have to distinguish between input uncertainties and
-%% output uncertainties.
+without uncertainties.  Those uncertainties have different sources: data uncertainties (from
 the simulator's reliance on previously estimated/measured data), modeling
-uncertainties (from simplifications made by the simulator) and the
-``operational'' uncertainty (from the expected behavior of the facilities
-being simulated).
-%% is this operational uncertainty really just a different kind of data?
+uncertainties (from simplifications made by the simulator). This work we will be
+focused a part of the data uncertainty related to the expected behavior of the
+facilities being simulated.
 
 Simulation errors could be important in the context of treaty verification.
-Some scenarios require estimating historical fissile
-material production based on records of facility operation and material
-transfer.  If the measurements of facility operation and material transfer are
-subject to uncertainty, the total production quantities will then also be
-uncertain.  Any uncertainty in fissile production quantities poses a material
-accounting challenge, possibly
-creating an opportunity for undetected diversion.  This study seeks
-to understand which measures of facility operation have the most impact on the
-uncertainty of fissile material production across a complete fuel cycle.
-To accomplish this, a Total Monte Carlo methodology will be applied to the Cyclus
-fuel cycle simulator \cite{cyclus} to estimate the effect of individual facility uncertainties on the output metrics.
-%% should there be a reference for Total Monte Carlo?
+Some scenarios require estimating historical fissile material production based
+on records of facility operation and material transfer.  If the measurements of
+facility operation and material transfer are subject to uncertainty, the total
+production quantities will then also be uncertain.  Any uncertainty in fissile
+production quantities poses a material accounting challenge, possibly creating
+an opportunity for undetected diversion.
 
-% I don't think Total Monte Carlo should be in quotes
+This study seeks to understand which measures of facility operation have the
+most impact on the uncertainty of fissile material production across a complete
+fuel cycle.  Uncertainty propagation using a Monte Carlo method will be applied
+to the Cyclus fuel cycle simulator \cite{cyclus} to estimate the effect of
+individual facility uncertainties on the output metrics. The same simulation
+will be simulated $N$ times, for each simulation parameters affected with an
+uncertainty will be randomly determined, the distribution of each output metrics
+over the N iterations of the simulation, will be used to estimate their
+respective uncertainty.
+
 \section{The Experiment}
@@
   \caption{Summary of facility modifications according to their Cyclus archetype package.}
-\begin{tabular}{cll}
+\begin{tabular}{cl|l}
 \toprule
@@
 \midrule
-Cycamore & Separation & Separation efficiency     \\ %% add hline in 2nd two columns
+Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
          & Storage    & Residence Time            \\
@@
 \end{figure}
-%% Update this to match the one in the CVT poster?
 
@@
 
-Both fuel reprocessing and fabrication are done at a constant rate (constrained
-by the feed material availability).  The enrichment of the \gls{UOX} is processed
-%% is it really a constant rate then?  Maybe we need a better word to describe this
+Both fuel reprocessing and fabrication rate are both limited by the facilities
+throughput and the ressource available.  The enrichment of the \gls{UOX} is processed
 on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
-%% You can't pluralize ``storage'' in English - it's considered uncountable
 between all facilities with constant processing rates.
@@
 enrichment is not applied directly to the effective enrichment. It is instead applied to the
-burnup, which leads to a fuel enrichment uncertainty close to
+burnup, which appears to lead to a fuel enrichment uncertainty close to
 $10\%$.
-%% Did you have to experiment to find the burnup uncertainty that results in a 10% enrichment uncertainty?
 
@@
 the total quantity of natural uranium used and the total unused fissile
-inventory (unused reprocessed plutonium).
-%% unused implies it's never used, but I don't think that's right.  You just mean the amount
-%% that is being stored in a separated state any point in time, right?
+inventory (separated plutonium).
 Generated power is also briefly investigated to ensure the overall
 uncertainty is not contaminated with a missed fuel loading, which could
-be interesting but is not the focus of this work.
-%% what do you mean by contaminated???  This probably deserves more explanation
+be interesting but is not the focus of this work. It is assumed that no reactor
+are unexpectedly shutdown because of fuel shortage, as such events should be well
+documented...
 
@@
 to the references one, reducing its impact on the uncertainty on the total
-uranium consumption.
-%% Why does the relative uncertainty due to cyle time not approach 0?
+uranium consumption. This uncertainty contribution to the overall uncertainty
+decrease is proportional to the number of \gls{LWR} reactors and stops with the
+decommission of the last one.
 
@@
 starts at about $5\%$, and grows until year
-125 to decrease up to $10\%$ at the end of the simulation time (180y), it seems
+125 to decrease to $10\%$ at the end of the simulation time (180y), it seems
 %% I don't see what you mean by decrease up to 10%?
@@
 Between year 40 and 70, the main contributor to the fissile inventory
-uncertainty is the cycle length.  As with the uranium needs, lower cycle length
-implies more fuel loads.  Never the less, around year 65 (see Figure
-%% Aren't you varying the cycle length equally to be smaller and larger, so why
-%% focus on ``lower cycle lengths''?
+uncertainty is the cycle length.  As with the uranium needs, different cycle length
+implies different number of fuel loads, so different amount of resources used.  Never the less, around year 65 (see Figure
 \ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
-small enough to start limiting producton of fissile material.
+small enough to start limiting production of fissile material.
 The uncertainty weight is then slowly transferred from

### 2018-05-24 paper.tex
adding ackknowledgments
typo
removing a dealt comment

@@
 125 to decrease to $10\%$ at the end of the simulation time (180y), it seems
-%% I don't see what you mean by decrease up to 10%?
 it would have reached an equilibrium between $5$ and $10\%$ with longer
@@
 \ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
-small enough to start limiting production of fissile material.
+small enough to start limiting the production of fissile material.
 The uncertainty weight is then slowly transferred from

### 2018-05-24 paper.tex
removin approx

@@
 been able to estimate than the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where $\approx10\%$
-on the enrichment implies a almost flat uncertainty of $2\%$.
+variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where about
+$10\%$ on the enrichment implies a almost flat uncertainty of $2\%$.
 

### 2018-05-24 experiement.tex
fix tab refs
fix table add some text

@@
 \subsection{scenarios}
-Seven different scenarios have been simulated:
+Seven different simulations have been simulated:
 \begin{itemize}
@@
 are summarized in Table \ref{tab:level}.
-
-\begin{table}[htb]
-\centering
-  \caption{Summary of cascades level population.}
-\begin{tabular}{ccccccccc}
-\toprule
-
-Model       &        &           & A         & A         & B         & B       & C         & C          \\
-Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
-\midrule                                                                                                 
-        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
-Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
-        &            & Tail      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
-        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
-\midrule                                                                                                 
-        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
-Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $20.6w\%$ & $69.8w\%$ \\
-        &            & Tail      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.72w\%$ & $9.43w\%$  \\
-        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
-\midrule                                                                                                 
-        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $20.6w\%$ & $72.6w\%$ \\
-Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $61.0w\%$ & $98.4w\%$ \\
-        &            & Tail      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $9.56w\%$ & $69.4w\%$ \\
-        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.31      & 0.35      \\
-\midrule                                                                                                 
-        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $61.0w\%$ & N.A.      \\
-Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $90.4w\%$ & N.A.      \\
-        &            & Tail      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $38.9w\%$ & N.A.      \\
-        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
-\bottomrule
-\end{tabular}
-  \label{tab:cascade_config}
-\end{table}

### 2018-05-24 results.tex
chaneg plot form year to timestep
fix table add some text

@@
 \section{Results}
-\subsection{timestep effect}
-%% \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-%%     \centering
-%%     \includegraphics[scale=0.18]{HEU_prod_timestep}
-%%     \caption{}
-%%     \label{fig:HEU_timestep}
-%% \end{figure}
+As it can be observed on Figures \ref{fig:case1}, \ref{fig:case2} and
+\ref{fig:case3}, the different cascade levels required up to $2n+1$, with $n$ the
+level number to start enriching uranium. This corresponds to the time required
+for the material to propagate from the natural uranium source to the level,
+regardless of the duration of the timestep (hour, day, month,...). This is also
+true for the number of timestep required to reach the equilibrium assays value in
+the tail reprocessing cases. This is why one will only consider equilibrium
+values.
 
-\begin{figure}[t!]
+\begin{table}[h!]
+\centering
+  \caption{Summary of cascades level population.}
+\begin{tabular}{ccccccccc}
+\toprule
+
+Model       &        &           & A         & A         & B         & B       & C         & C          \\
+Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
+\midrule                                                                                                 
+        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
+Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
+        &            & Tail      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
+        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
+\midrule                                                                                                 
+        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
+Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $69.8w\%$ \\
+        &            & Tail      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$  \\
+        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
+\midrule                                                                                                 
+        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $72.6w\%$ \\
+Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $98.4w\%$ \\
+        &            & Tail      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
+        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.32      & 0.35      \\
+\midrule                                                                                                 
+        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
+Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
+        &            & Tail      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
+        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
+\bottomrule
+\end{tabular}
+  \label{tab:level}
+\end{table}
+
+\begin{figure}[h!]
     \centering
@@
         \caption{No tail recycling}
+        \label{sfig:case1_NR}
     \end{subfigure}%
@@
         \caption{Tail recycling}
+        \label{sfig:case1_R}
     \end{subfigure}
@@
     miss-use model A, with (right) and without recycling (left).}
+    \label{fig:case1}
 \end{figure}
-\begin{figure}[t!]
+
+\subsection{Miss-use modeling}
+As illustrated on Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
+\ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
+don't have the same effect on the cascade behavior. While the models A and C,
+allow a quick enrichment gain, when the chaining the enrichment cascades, respectively
+4/23/78/98 and 4/23/82/99, with model B, the enrichment gain is slower only
+4/21/61/90...
+The same effect is observed when recycling the tails\ldots
+
+\begin{figure}[h!]
     \centering
@@
         \caption{No tail recycling}
+        \label{sfig:case2_NR}
     \end{subfigure}%
@@
         \caption{Tail recycling}
+        \label{sfig:case2_R}
     \end{subfigure}
@@
     miss-use model B, with (right) and without recycling (left).}
+    \label{fig:case2}
 \end{figure}
-\begin{figure}[t!]
+
+\subsection{Tails recycling}
+As demonstrated on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
+\ref{sfig:case3_R}, recycling the tails increases the overall product assay at all
+the different levels. As shown on Table \ref{tab:level}, the tail assay of level
+$n$ is always higher than the product assay of level $n-2$, recycling the tails
+of level $n$ will consequently increase the feed assay of level $n-1$. Moreover,
+as the feed assay of level $n-1$ increases, its tail and product assays increase as well,
+increasing de facto the feed assays of respectively cascade levels $n-2$ and $n$...
+This effect allow to reduce the number of cascade levels required to reach
+\gls{HEU} in case A and C.
+
+\begin{figure}[h!]
     \centering
@@
         \caption{No tail recycling}
+        \label{sfig:case3_NR}
     \end{subfigure}%
@@
         \caption{Tail recycling}
+        \label{sfig:case3_R}
     \end{subfigure}
@@
     miss-use model C, with (right) and without recycling (left).}
+    \label{fig:case3}
 \end{figure}
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\subsection{Production}
+
+\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
     \centering
@@
     the case without tail recycling, in orange with tail recycling, and in green
-    the reference one.}
+    the reference one. Where A-B-C represent the model used, and NR-R
+    respectively the case without tail recycling and the case with tail recycling}
     \label{fig:HEU_rate}

### 2018-05-25 paper.tex
almost done commenting results

@@
-\documentclass{anstrans}
+\documentclass[12pt]{article}
+\usepackage{mathptmx} % Nearly Times New Roman
+\usepackage[affil-it]{authblk}
+
+%\makeglossaries
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{}
-\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H.  Wilson$^{*}$}
 
-\institute{
-$^{*}$University of Wisconsin-Madison, WI
+\usepackage{color}
+\usepackage{subcaption}
+\usepackage{graphicx}
+\usepackage{booktabs} % nice rules for tables
+\usepackage{microtype} % if using PDF
+\usepackage{xspace}
+\usepackage{listings}
+\usepackage{textcomp}
+\usepackage{multicol,tabularx,capt-of}
+\usepackage{multirow}
+
+\usepackage{fancyhdr} % allows headers and footers
+%\usepackage{ulem}
+\usepackage{pdflscape}
+% Page length commands go here in the preamble
+\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
+\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
+\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
+\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in
+
+\definecolor{listinggray}{gray}{0.9}
+\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
+\definecolor{burgundy}{rgb}{0.5, 0.0, 0.13}
+\definecolor{burntorange}{rgb}{0.8, 0.33, 0.0}
+\definecolor{chromeyellow}{rgb}{1.0, 0.65, 0.0}
+\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
+
+\lstset{
+    %backgroundcolor=\color{lbcolor},
+    language={C++},
+    tabsize=4,
+    rulecolor=\color{black},
+    upquote=true,
+    aboveskip={1.5\baselineskip},
+    belowskip={1.5\baselineskip},
+    columns=fixed,
+    extendedchars=true,
+    breaklines=true,
+    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
+    frame=single,
+    showtabs=false,
+    showspaces=false,
+    showstringspaces=false,
+    basicstyle=\scriptsize\ttfamily\color{green!40!black},
+    keywordstyle=\color[rgb]{0,0,1.0},
+    commentstyle=\color[rgb]{0.133,0.545,0.133},
+    stringstyle=\color[rgb]{0.627,0.126,0.941},
+    numberstyle=\color[rgb]{0,1,0},
+    identifierstyle=\color{black},
+    captionpos=t,
 }
 
-\email{mouginot@wisc.edu \and mummah@wisc.edu \and paul.wilson@wisc.edu}
+\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily\color{green!40!black}]|#1|}
+\newcommand{\units}[1] {\:\text{#1}}%
+\newcommand{\SN}{S$_N$}
+\newcommand{\cyclus}{\textsc{Cyclus}\xspace}
+\newcommand{\Cyclus}{\cyclus}
+\newcommand{\citeme}{\textcolor{red}{CITE}\xspace}
+\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%
 
-% Optional disclaimer: remove this command to hide
-% \disclaimer{Notice: this manuscript is a work of fiction.  Any resemblance to
-% actual articles, living or dead, is purely coincidental.}
-
-%%%% packages and definitions (optional)
-\usepackage{graphicx} % allows inclusion of graphics
-\usepackage{booktabs} % nice rules (thick lines) for tables
-\usepackage{microtype} % improves typography for PDF
-\usepackage{float}
-
-\newcommand{\SN}{S$_N$}
-\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
-\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
-\newcommand{\grad}{\vec{\nabla}} % gradient
-\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
+\newcommand{\comment}[1]{{\color{green}\textbf{#1}}}
 
 \usepackage[acronym]{glossaries}
-\newacronym{UOX}{UOX}{uranium oxide fuel}
-\newacronym{MOX}{MOX}{mixed oxide fuel}
-\newacronym{LWR}{LWR}{light water reactor}
-\newacronym{SFR}{SFR}{fast breeder reactor}
 
+\input{glossary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{frontmatter}
+\title{Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades}
+% Authors. Separated by commas
+\input{authors}
+\date{}
+% Institutes of the authors
+\input{institutions}
+\pagestyle{fancy}
 \begin{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
 
-Fuel cycle simulations, as with any simulation process, do not produce results
-without uncertainties.  Those uncertainties have different sources: data uncertainties (from
-the simulator's reliance on previously estimated/measured data), modeling
-uncertainties (from simplifications made by the simulator). This work we will be
-focused a part of the data uncertainty related to the expected behavior of the
-facilities being simulated.
+\maketitle
 
-Simulation errors could be important in the context of treaty verification.
-Some scenarios require estimating historical fissile material production based
-on records of facility operation and material transfer.  If the measurements of
-facility operation and material transfer are subject to uncertainty, the total
-production quantities will then also be uncertain.  Any uncertainty in fissile
-production quantities poses a material accounting challenge, possibly creating
-an opportunity for undetected diversion.
+% 0.Abstract
+\input{abstract}
+\nopagebreak[4]
+% I.   Motivation
+\include{motivation}
+\nopagebreak[4]
 
-This study seeks to understand which measures of facility operation have the
-most impact on the uncertainty of fissile material production across a complete
-fuel cycle.  Uncertainty propagation using a Monte Carlo method will be applied
-to the Cyclus fuel cycle simulator \cite{cyclus} to estimate the effect of
-individual facility uncertainties on the output metrics. The same simulation
-will be simulated $N$ times, for each simulation parameters affected with an
-uncertainty will be randomly determined, the distribution of each output metrics
-over the N iterations of the simulation, will be used to estimate their
-respective uncertainty.
+% II.  Theory
+%   a. cascade design
+%   b. miss-use model
+%       i.   case A
+%       ii.  case B
+%       iii. case C
+\include{theory}
+\nopagebreak[4]
 
-\section{The Experiment}
+% III. Experiement
+%   a.  cycle 
+%   b.  cascade per level optimisation
+\include{experiement}
+\nopagebreak[4]
 
-\subsection{Method}
+% IV.  results
+%   a. time step effects
+%   b. no tail recycling
+%   c. tail recycling
+\include{results}
+\nopagebreak[4]
 
-To estimate the uncertainty of fuel cycle output metrics, a Total Monte
-Carlo approach has been applied.  In each of 199 independent simulations,
-some of the parameters that define facility behavior are randomly selected
-from Normal distributions with standard deviations that are $10\%$ of the mean
-value.  This artificially large standard deviation is selected for the purpose
-of demonstrating the methodology.  The mean and standard deviation of some
-output metrics are calculated from the simulation output, as a function of time.
+% V.  Discussion
+% VI. Conclusions and future plan
+\include{dis_clusion}
+\nopagebreak[4]
 
-To pursue this work, both the Cycamore\footnote{Low
-fidelity facilities package for Cyclus}\cite{cycamore} and the
-CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models}\cite{mouginot_2018, cyclass} packages were
-updated to evaluate the uncertainty of several
-operational parameters in their associated facilities.  Table
-\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
-facilities of Cycamore and CyCLASS.
-
-\begin{table}[htb]
-\centering
-  \caption{Summary of facility modifications according to their Cyclus archetype package.}
-\begin{tabular}{cl|l}
-\toprule
-
-Package   & Facility   & Parameters                \\
-\midrule
-Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
-         & Storage    & Residence Time            \\
-\midrule
-CyCLASS  & Reactor    & Cycle Length              \\
-         &            & Power                     \\
-         &            & Fuel Enrichment (PWR-UOX) \\
-
-\bottomrule
-\end{tabular}
-
-  \label{tab:package_uncertainty}
-\end{table}
-
-The uncertainty of the different parameters in this study
-are systematic for each new deployed facility: each time a new facility is
-deployed (such as a reactor or a fuel fabrication facility) a new set of
-parameters are sampled, and those parameters are used throughout the life
-of that facility.
-
-\subsection{The Fuel Cycle Scenario}
-For demonstration purposes, a simple commercial fuel cycle transition is used,
-inspired from the EG23 fuel cycle
-of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}.
-Pictured in Figure \ref{fig:cycle}, this is a
-transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a
-\gls{SFR} fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
-of the nuclear generated power (Figure \ref{fig:power}).
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[scale=0.31]{cycle.png}
-  \caption{Simplified representation of the material flow between the different facilities,
-  with each operational parameter associated with an
-  uncertainty labeled in green.}\label{fig:cycle}
-\end{figure}
-
-As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
-composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
-transition starts around year 35, with the deployment of \glspl{SFR}. The \glspl{SFR} are loaded
-with \gls{MOX}, which consists of plutonium blended with natural
-uranium.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.18]{power.png}
-    \caption{Electric power generated over time, with the full production,
-        the \gls{LWR} contribution, and the \gls{SFR} contribution labeled in blue, orange, and green, respectively.}
-    \label{fig:power}
-\end{figure}
-
-The plutonium, required for \gls{MOX} fabrication, is reprocessed from all
-used fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel
-as it becomes available for reprocessing.
-
-Both fuel reprocessing and fabrication rate are both limited by the facilities
-throughput and the ressource available.  The enrichment of the \gls{UOX} is processed
-on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
-between all facilities with constant processing rates.
-
-In this work, a time step of 1 month has been considered, i.e., each output
-metric is reported once per month. Additionally, decay processes have not be
-taken into account.
-
-It must be noted that for this work, the fuel enrichment was determined by a
-fuel fabrication model\cite{Leniau2015125} which
-calculates the fissile fraction required in the fuel to reach a given target
-burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
-enrichment is not applied directly to the effective enrichment. It is instead applied to the
-burnup, which appears to lead to a fuel enrichment uncertainty close to
-$10\%$.
-
-For each of the parameters in Table \ref{tab:package_uncertainty}, a set of
-199 simulations was performed with only that parameter being randomly varied.
-An additional set of 199 simulations was performed in which all five
-parameters are randomly varied.  A reference simulation was performed
-with all five parameters fixed at the mean value.
-
-\section{Results}
-
-Because the main interests of nuclear archaeology involve highly enriched uranium production and
-fissile inventories, this study mainly focuses on the uncertainties of
-the total quantity of natural uranium used and the total unused fissile
-inventory (separated plutonium).
-Generated power is also briefly investigated to ensure the overall
-uncertainty is not contaminated with a missed fuel loading, which could
-be interesting but is not the focus of this work. It is assumed that no reactor
-are unexpectedly shutdown because of fuel shortage, as such events should be well
-documented...
-
-At each time step, the $\pm1\sigma$ uncertainty due to the full set of varied
-parameters is reported.  In addition, the relative contribution to the total
-uncertainty from each of the parameters is calculated as the ratio of the
-$1\sigma$ uncertainty due to that parameter over the total uncertainty.
-
-\subsection{Generated Power}
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.36]{power_full}
-    \caption{Electric power generated as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
-\end{figure}
-
-By design, the very low uncertainty (Figure \ref{fig:power_full}) on the
-generated power is expected.
-Indeed the transition scenario has been designed to allow all the reactors to
-receive the fuel as needed allowing them to be producing power all the time.
-This ensures that the measured uncertainty is not affected by a facility
-disruption that has an outsized impact on material flows.
-As \gls{SFR} fuel is built from
-reprocessed used fuel, the availability of that used fuel may impact the
-capability to build the required MOX-SFR fuel.  Facility disruptions may
-cause material shortages that can lead to snow-ball effect of more disruptions
-later in the simulation.  While such disruptions are interesting in some analyses,
-they are outside the scope of this study.
-
-\subsection{Natural Uranium Consumption dedicated to PWR-UOX fabrication}
-
-Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
-dedicated to PWR-UOX fuel fabrication as a function of time.  The uncertainty on
-the cumulative uranium consumption grows as expected with the time and the
-loading of the \glspl{LWR}.  The increase stops around year 125y with the
-decommissioning of the last \glspl{LWR}.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.35]{unat_full}
-    \caption{Cumulative consumption of natural uranium as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:unat_full}
-\end{figure}
-
-As expected, cooling time, separation efficiency and thermal power do not
-affect the natural uranium consumption.  The uncertainty on the natural uranium
-consumption is dominated by the \gls{LWR} cycle length: shorter the cycle
-length is, the more fuel will be loaded.
-
-\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.35]{unat_uncer}
-    \caption{Cumulative natural uranium consumption relative uncertainty, with
-    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
-    contribution of each parameter: cooling time (blue), fuel enrichment (red),
-    cycle time (green), thermal power(brown), separation efficiency (light
-    blue).}\label{fig:unatr_uncer}
-\end{figure}
-The relative uncertainty of the total uranium consumption starts at about
-$5.5\%$ a slowly drops and stabilise around $3\%$.
-
-Uncertainty fluctuation of the full relative uncertainty can be observed before
-year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
-beginning of the simulation have synchronised cycle, this phenomenon disappears
-with the gradual decommissioning of the initial reactors, spread on 50 years.
-
-The decrease of the cycle time uncertainty contribution, from year 30 to year
-90, can be understood as an averaging effect.  As the uncertainty are defined once
-per deployed facility, each reactor will have a different cycle
-length value, so a different number of batches loaded per year.  With the increase
-of deployed reactors, the number of batches of \gls{LWR} fuel loaded converges
-to the references one, reducing its impact on the uncertainty on the total
-uranium consumption. This uncertainty contribution to the overall uncertainty
-decrease is proportional to the number of \gls{LWR} reactors and stops with the
-decommission of the last one.
-
-The fuel enrichment contribution follow a close to constant uncertainty
-contribution of $2\%$, so as the total relative uncertainty decrease, it
-has a growing shared of the total uncertainty over time.
-
-\subsection{Fissile Inventory}
-The fissile inventory corresponds to the amount of separated fissile material waiting to
-be blended with natural uranium in order to produce the \gls{SFR} MOX fuel.
-
-As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow in
-year 40, with the deployment of the first reprocessing facility.  It grows
-during the first period of the \glspl{LWR} to \gls{SFR}-A transition until
-year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
-When he steady state is reached (full \gls{SFR} fleet), the plutonium
-inventory starts to increase, as the breading ratio of the \glspl{SFR} is higher
-than the deployment needs.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.35]{pu_full}
-    \caption{Fissile (plutonium) inventory as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:pu_full}
-\end{figure}
-
-\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.35]{pu_uncer}
-    \caption{Fissile (plutonium) inventory relative uncertainty, with
-    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
-    contribution of each parameter: cooling time (blue), fuel enrichment (red),
-    cycle time (green), thermal power(brown), separation efficiency (light
-    blue).}\label{fig:pu_uncer}
-\end{figure}
-
-Regarding the uncertainty, disregarding the artefact of a very low mean inventory
-observed at the onset of fissile material production, the relative uncertainty
-starts at about $5\%$, and grows until year
-125 to decrease to $10\%$ at the end of the simulation time (180y), it seems
-it would have reached an equilibrium between $5$ and $10\%$ with longer
-simulations...
-Between year 40 and 70, the main contributor to the fissile inventory
-uncertainty is the cycle length.  As with the uranium needs, different cycle length
-implies different number of fuel loads, so different amount of resources used.  Never the less, around year 65 (see Figure
-\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
-small enough to start limiting the production of fissile material.
-The uncertainty weight is then slowly transferred from
-the cycle length to the fuel cooling time.
-
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.18]{used_fuel}
-    \caption{Used fuel inventory, corresponding to the amount of used
-    \glspl{LWR} and \glspl{SFR} fuel, cooled and waiting to be reprocessed.}
-    \label{fig:used_fuel}
-\end{figure}
-Between year 90 and 120, the \gls{SFR} deployment speed increases, it has to
-compensate the non replacement of the decommissioned \glspl{LWR} as well as
-follow the power demand.  During this period the needs in plutonium are higher
-than its productions, explaining the observed decrease of the total amount, and
-the increase associated relative uncertainty.
-
-As the transition ends, the plutonium breed from the \glspl{SFR} starts to be
-sufficient to sustain the new \glspl{SFR} deployment to follow the power demand.
-
-It is also interesting to note that, the uncertainty contribution from the cycle
-length is between year 40 and 70 comes mainly from fuel batch loading
-frequencies, and after it relative contributions follows closely the thermal
-power one, suggesting a contributions through fuel discharge burnup (i.e.  fuel
-discharge composition).
-
-\subsection{Discussion}
-
-Uranium consumption and separated fissile inventory are two important metrics
-regarding to non proliferation and nuclear archaeology.  In this study, we have
-been able to estimate than the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where about
-$10\%$ on the enrichment implies a almost flat uncertainty of $2\%$.
-
-Regarding the reprocessed fissile inventory, this study has shown the limited
-impact of the reprocessed fuel compositions (through burnup variations) it
-limited to $5\%$, where fuel availability constrains, fuel loading frequency (cycle
-time), or fissile materials available for fuel fabrication (cooling time) can lead to higher
-uncertainties, respectively up to $10\%$ and to $30\%$.  Moreover it is very
-interesting to observe the pressure transition from one to the other around
-year 70.
-
-This preliminary study may suggest that the most important contribution to
-natural uranium consumption and fissile inventory is coming from the time when
-occurs the different material exchange between facilities, and not necessary
-from the physical parameters such as thermal power or fuel enrichment. Further
-analysis should allow us to confirm or denies it.
-
-\section{Conclusion}
-
-Two main points can be deduced from this work.  Firstly, in a transitional
-fuel cycle, the uncertainty contributions to an output metric can vary over time
-depending of various factors: deployment schedule artifact or pressure point in
-the material flows.
-
-Secondly, it is important to note the special character of the time related
-parameters uncertainty in a fuel cycle study, such as cooling time and cycle
-length.  Where some of those time related parameter will on the first order only
-impact material availability (as the cooling time will do), some other, like
-cycle length, will also have a impact as physical parameters such as fuel
-enrichment or thermal power.
-
-Cycle length impacts the discharge fuel burnup, it also affects the frequency of
-the fuel loads, this, as well as the cooling may imply a uncertainty on the
-material availability, which could lead to an artificially large uncertainty.
-Those kind of time related uncertainties will require a careful analysis on further
-uncertainty analysis, in order to understand and measure accurately their
-contributions on uncertainties.
-
-This study aims to be a proof-of-principle for uncertainty propagation in
-potential commercial fuel cycle transition.  While it has demonstrated the
-capability to measure the uncertainty on output fuel cycle metrics and their
-relative contributions, it has only been applied to systematic uncertainties per
-facilities (parameters randomly generated at each new facility deployment).
-This kind of study will to be extended to random uncertainty (new parameter
-values at each occurrence) and completely systematic uncertainty (shared by all
-the facilities of a kind).
-
-While the parameters contributing to natural uranium needs and fissile inventory
-uncertainties might be obvious, such study allows to estimate each parameters
-contribution, it could be less obvious for other parameters, such as
-plutonium quality, waste compositions.  Such studies could also provide research
-guidance for nuclear archaeology works, which aims to precisely estimate past
-fissile production by the different nuclear countries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \appendix
-%% \section{Appendix}
-%%
-%% Numbering in the appendix is different:
-%% \begin{equation} \label{eq:appendix}
-%%   2 + 2 = 5\,.
-%% \end{equation}
-%% and another equation:
-%% \begin{equation} \label{eq:appendix2}
-%%   a + b = c\,.
-%% \end{equation}
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \section{Nomenclature}
-%%
-%% \begin{table}[H]
-%%     \centering
-%%     \begin{tabular}{l|l}
-%% %         &  \\
-%%         $N$ & Feed assay \\
-%%         $N'$ & Product assay \\
-%%         $N''$ & Tails assay \\
-%%         $\alpha$ & Feed to product enrichment factor \\
-%%         $\beta$ & Feed to tail enrichment factor \\
-%%         $\theta$ & Cut
-%%     \end{tabular}
-%% %    \caption{Caption}
-%%     \label{tab:my_label}
-%% \end{table}
-
-%% \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-%%   \centering
-%%   \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
-%%   \caption{Illustration of the material flow between the different level of
-%%       cascades without tail recycling, in this diagram, nu\_src corresponds to
-%%       an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
-%%       $\{n\}$ to the cascade and the storage getting the products of the
-%%       cascades at the level $\{n\}$.}\label{fig:flow}
-%% \end{figure}
-
-%% \begin{table}[htb]
-%% \centering
-%%   \caption{Summary of cascade properties for each level.}
-%% \begin{tabular}{cllll}
-%% \toprule
-%%
-%% Level   &           & Assay     &       & Machines  \\
-%%         & Feed      & Product   & Feed  &           \\
-%% \midrule
-%% 0       & 0.0071    & 0.0413    & 0.0029 & 167       \\
-%% 1       & 0.0413    & 0.2043    & 0.0173 & 169       \\
-%% 2       & 0.2043    & 0.5941    & 0.0971 & 168       \\
-%% 3       & 0.5941    & 0.8834    & 0.3915 & 168       \\
-%% 4       & 0.8834    & 0.9735    & 0.7746 & 169       \\
-%%
-%% \bottomrule
-%% \end{tabular}
-%%
-%%   \label{tab:cascadelvl}
-%% \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Acknowledgments}
@@
 
+%\end{frontmatter}
+
+%\input{appendix}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{small}
 \bibliographystyle{ans}
-\bibliography{bibliography}
+\bibliography{refs}  % NO SPACES BETWEEN BIB FILENAMES!
+\end{small}
 \end{document}

### 2018-05-25 results.tex
almost done commenting results

@@
 
-\subsection{Production}
+\subsection{\gls{HEU} Production}
+As shown Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
+production rate, from $2$ to almost $20$ kg/y when using model A and C, and from
+$17$ to $38$ kg/y with the model B. For the reference calculation where all the
+available cascades are used within a single large cascade design for direct
+\gls{HEU} production, the \gls{HEU} production rate is slightly over $50$ kg/y.
+
+As Model A and C, relies on maintaining the cut values at each stages of the
+cascade and share the same number of levels, both the  same repartition of
+cascades across the different levels and then the same \gls{HEU} production
+rate.
 

### 2018-05-25 dis_clusion.tex
discussion and conclusion

\section{Discussion}

It is really interesting to observe that when the cascade is left completely
untouched (Model A) or when it is slightly retuned to maintain the tail to
product enrichment factor as well as the cut of each centrifuges, chaining the
cascade we can observe high increase of the enrichment at each level.  On the
contrary, when retuning the cut of each centrifuges to maintain the ideal state
of the cascades while chaining them, the \gls{HEU} production rate is favored
over the enrichment gain.

The tail recycling allows for each model a hudge gain in productivity, even for
then model B for which it does not change the number of levels required to reach
$90w\%$ of $^{235}$U in the uranium. Even if no cascades chaining also to
retrieve the same production rate as a direct enrichment, the model B with
reprocessing reach about $80\%$ of an optimum production, which is far from
being negligible\ldots

\section{Conclusion}

This works has investigated and quantify the difference between potential
retuning of a gaseous enrichment cascade in order to chain them to produce
\gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
One of this tuning method allows up to $80\%$ of the production rate of a single
large enrichment cascade designed specifically for \gls{HEU} production using
the same number of centrifuges.

This works will be extended to the near future with additional miss-use method,
allowing for example the reconfiguration of the centrifuges in the cascades.

For this study, the usage of the Cyclus fuel cycle simulator was not really
required, it only allows a quick determination of the blending equilibrium. It
is planned to make use of the Cyclus Dynamical Resource Exchange full capability
in order to automatically assign the different cascades to the different level
as function of the resources availability, optimising the productions rates in
each cases.

While mathematically correct, the authors do not guaranty the feasibility
different miss-use tuning methods implemented and are welcoming any insight on
the matter.

### 2018-05-25 experiement.tex
discussion and conclusion

@@
-\section{the experiment}
+\section{The experiment}
 This works focuses on comparing the different miss use models to a reference
@@
 are summarized in Table \ref{tab:level}.
+
+\subsection{Timestep effect}
+
+As it can be observed on Figures \ref{fig:case1}, \ref{fig:case2} and
+\ref{fig:case3}, the different cascade levels required up to $2n+1$, with $n$ the
+level number to start enriching uranium. This corresponds to the time required
+for the material to propagate from the natural uranium source to the level,
+regardless of the duration of the timestep (hour, day, month,...). This is also
+true for the number of timestep required to reach the equilibrium assays value in
+the tail reprocessing cases. This is why one will only consider equilibrium
+values.

### 2018-05-25 results.tex
discussion and conclusion

@@
 \section{Results}
-As it can be observed on Figures \ref{fig:case1}, \ref{fig:case2} and
-\ref{fig:case3}, the different cascade levels required up to $2n+1$, with $n$ the
-level number to start enriching uranium. This corresponds to the time required
-for the material to propagate from the natural uranium source to the level,
-regardless of the duration of the timestep (hour, day, month,...). This is also
-true for the number of timestep required to reach the equilibrium assays value in
-the tail reprocessing cases. This is why one will only consider equilibrium
-values.
+
+\subsection{Miss-use modeling}
 
@@
 
-Model       &        &           & A         & A         & B         & B       & C         & C          \\
-Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
+Model       &        &           & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R          \\
+%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
 \midrule                                                                                                 
@@
 
+As illustrated on Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
+\ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
+don't have the same effect on the cascade behavior. While the models A and C,
+allow a quick enrichment gain, with the cascades chaining, respectively
+4/23/78/98 and 4/23/82/99, the model B, the enrichment gain is only
+4/21/61/90...  The same effect is observed when recycling the tails\ldots
+
 \begin{figure}[h!]
@@
         \centering
-        \includegraphics[scale=0.18]{NR_case1}
+        \includegraphics[scale=0.17]{NR_case1}
         \caption{No tail recycling}
@@
         \centering
-        \includegraphics[scale=0.18]{R_case1}
+        \includegraphics[scale=0.17]{R_case1}
         \caption{Tail recycling}
@@
 
-\subsection{Miss-use modeling}
-As illustrated on Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
-\ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
-don't have the same effect on the cascade behavior. While the models A and C,
-allow a quick enrichment gain, when the chaining the enrichment cascades, respectively
-4/23/78/98 and 4/23/82/99, with model B, the enrichment gain is slower only
-4/21/61/90...
-The same effect is observed when recycling the tails\ldots
-
 \begin{figure}[h!]
@@
         \centering
-        \includegraphics[scale=0.18]{NR_case2}
+        \includegraphics[scale=0.17]{NR_case2}
         \caption{No tail recycling}
@@
         \centering
-        \includegraphics[scale=0.18]{R_case2}
+        \includegraphics[scale=0.17]{R_case2}
         \caption{Tail recycling}
@@
 \subsection{Tails recycling}
+
 As demonstrated on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
-\ref{sfig:case3_R}, recycling the tails increases the overall product assay at all
-the different levels. As shown on Table \ref{tab:level}, the tail assay of level
-$n$ is always higher than the product assay of level $n-2$, recycling the tails
-of level $n$ will consequently increase the feed assay of level $n-1$. Moreover,
-as the feed assay of level $n-1$ increases, its tail and product assays increase as well,
-increasing de facto the feed assays of respectively cascade levels $n-2$ and $n$...
-This effect allow to reduce the number of cascade levels required to reach
-\gls{HEU} in case A and C.
+\ref{sfig:case3_R}, recycling the tails increases the overall product assay at
+all the different levels. As shown on Table \ref{tab:level}, the tail assay of
+level $n$ is always higher than the product assay of level $n-2$, recycling the
+tails of level $n$ will consequently increase the feed assay of level $n-1$.
+Moreover, as the feed assay of level $n-1$ increases, its tail and product
+assays increase as well, increasing de facto the feed assays of respectively
+cascade levels $n-2$ and $n$...  This effect allow to reduce the number of
+cascade levels required to reach \gls{HEU} in case A and C.
 
@@
         \centering
-        \includegraphics[scale=0.18]{NR_case3}
+        \includegraphics[scale=0.17]{NR_case3}
         \caption{No tail recycling}
@@
         \centering
-        \includegraphics[scale=0.18]{R_case3}
+        \includegraphics[scale=0.17]{R_case3}
         \caption{Tail recycling}
@@
 \subsection{\gls{HEU} Production}
+
 As shown Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}

### 2018-05-25 dis_clusion.tex
with motivationmake bib gp

@@
 
-The tail recycling allows for each model a hudge gain in productivity, even for
+The tail recycling allows for each model a huge gain in productivity, even for
 then model B for which it does not change the number of levels required to reach
@@
 
-\section{Conclusion}
+\section{Conclusion and future works}
 

### 2018-05-25 motivation.tex
with motivationmake bib gp

\section{Motivation}

Gas centrifuge cascades are usually designed to operate in ideal manner, with no
losses in separative work, the most effective way. To achieve such ideal
configuration, the cascade is designed to be fed with a specific feed assay and
produce the target  enrichment while rejecting tails at a fix assay.

With the current international tensions regarding enrichment capabilities, this
work aims to measure the effectiveness of an enrichment cascade when used outside of
its designed scope and quantify the attractiveness of such way to build up
significant amount of \gls{HEU}.

The present work investigates the performance of a enrichment cycle when chaining
gas enrichment cascade tuned for low enrich uranium production from natural
uranium. As literature on the mater is for obvious reason limited, three
behavior models have been implemented and used to evaluate the response of an
enrich cascade when fed with different assays than the design one. This work
takes also advantage of the Cyclus\cite{cyclus} fuel cycle capabilities to
evaluate the assay blending equilibrium.

### 2018-05-25 dis_clusion.tex
add ref +add SQ mention

@@
 reprocessing reach about $80\%$ of an optimum production, which is far from
-being negligible\ldots
+being negligible, allowing to build up a Significant Quantity of \gls{HEU} in
+less than 8 months\ldots
 

### 2018-05-25 paper.tex
discussion and conclusion
Final review - formatting needed

--- 2018-05-24 paper.tex
@@
 \title{}
-\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H.  Wilson$^{*}$}
+\author{Baptiste Mouginot, Kathryn Mummah, Paul P.H.  Wilson}
 
 \institute{
-$^{*}$University of Wisconsin-Madison, WI
+University of Wisconsin-Madison, Madison, WI
 }
@@
 Fuel cycle simulations, as with any simulation process, do not produce results
-without uncertainties.  Those uncertainties have different sources: data uncertainties (from
-the simulator's reliance on previously estimated/measured data), modeling
-uncertainties (from simplifications made by the simulator). This work we will be
-focused a part of the data uncertainty related to the expected behavior of the
-facilities being simulated.
+without uncertainties.  Those uncertainties have two main sources: modeling
+uncertainty due to the simplifications and approximations built in to the
+simulator itself, and data uncertainty from the quantities provided by the
+user. This work we will be focused a subset the data uncertainty related to
+the user input that defines the performance of the facilities being simulated.
 
-Simulation errors could be important in the context of treaty verification.
-Some scenarios require estimating historical fissile material production based
-on records of facility operation and material transfer.  If the measurements of
-facility operation and material transfer are subject to uncertainty, the total
-production quantities will then also be uncertain.  Any uncertainty in fissile
-production quantities poses a material accounting challenge, possibly creating
-an opportunity for undetected diversion.
+Such simulation uncertainties could be important in the context of treaty
+verification.  Some scenarios require estimating historical fissile material
+production based on records of facility operation and material transfer.  If
+the measurements of facility operation and material transfer are subject to
+uncertainty, the total production quantities will then also be uncertain.  Any
+uncertainty in fissile production quantities poses a material accounting
+challenge, possibly creating an opportunity for undetected diversion.
 
@@
 
-To estimate the uncertainty of fuel cycle output metrics, a Total Monte
+To estimate the uncertainty of fuel cycle output metrics, a Monte
 Carlo approach has been applied.  In each of 199 independent simulations,
 some of the parameters that define facility behavior are randomly selected
-from Normal distributions with standard deviations that are $10\%$ of the mean
+from Normal distributions with standard deviations that are $10\%$ of the mean/nominal
 value.  This artificially large standard deviation is selected for the purpose
@@
 Package   & Facility   & Parameters                \\
-\midrule
+\toprule
+
 Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
          & Storage    & Residence Time            \\
-\midrule
-CyCLASS  & Reactor    & Cycle Length              \\
-         &            & Power                     \\
+\toprule
+CyCLASS  & Reactor    & Cycle Length              \\\cmidrule{3-3}
+         &            & Power                     \\\cmidrule{3-3}
          &            & Fuel Enrichment (PWR-UOX) \\
@@
 of the nuclear generated power (Figure \ref{fig:power}).
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
   \centering
@@
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
     \centering
@@
 
-Both fuel reprocessing and fabrication rate are both limited by the facilities
-throughput and the ressource available.  The enrichment of the \gls{UOX} is processed
+Both fuel reprocessing and fabrication have a constant maximum throughput, but may also be limited by the 
+availability input material.  The enrichment of the \gls{UOX} is processed
 on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
-between all facilities with constant processing rates.
+between all facilities with constant throughput.
 
@@
 enrichment is not applied directly to the effective enrichment. It is instead applied to the
-burnup, which appears to lead to a fuel enrichment uncertainty close to
+burnup, resulting in a fuel enrichment uncertainty that is also close to
 $10\%$.
@@
 inventory (separated plutonium).
-Generated power is also briefly investigated to ensure the overall
-uncertainty is not contaminated with a missed fuel loading, which could
-be interesting but is not the focus of this work. It is assumed that no reactor
-are unexpectedly shutdown because of fuel shortage, as such events should be well
-documented...
+
+The total power generated in the simulation is reviewed to ensure that none of
+the compounded uncertainties result in material shorates substantial enough to
+cause long term reactor shutdowns.  For example, since \gls{SFR} fuel is built
+from reprocessed used fuel, the availability of that used fuel may impact the
+capability to build the required \gls{SFR}-\gls{MOX} fuel.  While there may be studies in
+which this would be an interesting result, in the context of this work, such
+shutdowns would be well-documented in the operational histories of the
+facilities and should not be characterized as an uncertainty.  Figure
+\ref{fig:power_full} shows that uncertainties in generated power are indeed
+very low.
+
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.3]{power_full}
+    \caption{Electric power generated as a function of time.  The black line
+        represents the reference calculation and the blue zone
+        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
+\end{figure}
 
@@
 $1\sigma$ uncertainty due to that parameter over the total uncertainty.
-
-\subsection{Generated Power}
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.36]{power_full}
-    \caption{Electric power generated as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
-\end{figure}
-
-By design, the very low uncertainty (Figure \ref{fig:power_full}) on the
-generated power is expected.
-Indeed the transition scenario has been designed to allow all the reactors to
-receive the fuel as needed allowing them to be producing power all the time.
-This ensures that the measured uncertainty is not affected by a facility
-disruption that has an outsized impact on material flows.
-As \gls{SFR} fuel is built from
-reprocessed used fuel, the availability of that used fuel may impact the
-capability to build the required MOX-SFR fuel.  Facility disruptions may
-cause material shortages that can lead to snow-ball effect of more disruptions
-later in the simulation.  While such disruptions are interesting in some analyses,
-they are outside the scope of this study.
 
@@
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
     \centering
-    \includegraphics[scale=0.35]{unat_full}
+    \includegraphics[scale=0.3]{unat_full}
     \caption{Cumulative consumption of natural uranium as a function of time.  The black line
@@
 As expected, cooling time, separation efficiency and thermal power do not
-affect the natural uranium consumption.  The uncertainty on the natural uranium
+affect the natural uranium consumption for LWR-UOX fuel production.  The uncertainty on the natural uranium
 consumption is dominated by the \gls{LWR} cycle length: shorter the cycle
-length is, the more fuel will be loaded.
+length is, the more fuel will be loaded, and \emph{vice versa}.
 
-\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
     \centering
-    \includegraphics[scale=0.35]{unat_uncer}
+    \includegraphics[scale=0.3]{unat_uncer}
     \caption{Cumulative natural uranium consumption relative uncertainty, with
-    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
-    contribution of each parameter: cooling time (blue), fuel enrichment (red),
-    cycle time (green), thermal power(brown), separation efficiency (light
-    blue).}\label{fig:unatr_uncer}
+    the total uncertainty at 1$\sigma$ in black, and the uncertainty
+    contribution of each parameter in other colors.}\label{fig:unatr_uncer}
 \end{figure}
@@
 year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
-beginning of the simulation have synchronised cycle, this phenomenon disappears
-with the gradual decommissioning of the initial reactors, spread on 50 years.
+beginning of the simulation have synchronised fuel cycles, reloading in the same time step.
+This phenomenon disappears
+with the gradual decommissioning of the initial reactors, spread over 50 years.
 
@@
 contribution of $2\%$, so as the total relative uncertainty decrease, it
-has a growing shared of the total uncertainty over time.
+has a growing shared of the total absolute uncertainty over time.
 
@@
 The fissile inventory corresponds to the amount of separated fissile material waiting to
-be blended with natural uranium in order to produce the \gls{SFR} MOX fuel.
+be blended with natural uranium in order to produce the \gls{SFR}-\gls{MOX} fuel.
 
@@
 year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
-When he steady state is reached (full \gls{SFR} fleet), the plutonium
+When the steady state is reached (full \gls{SFR} fleet), the plutonium
 inventory starts to increase, as the breading ratio of the \glspl{SFR} is higher
@@
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
     \centering
-    \includegraphics[scale=0.35]{pu_full}
+    \includegraphics[scale=0.3]{pu_full}
     \caption{Fissile (plutonium) inventory as a function of time.  The black line
@@
 
-\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
     \centering
-    \includegraphics[scale=0.35]{pu_uncer}
+    \includegraphics[scale=0.3]{pu_uncer}
     \caption{Fissile (plutonium) inventory relative uncertainty, with
-    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
-    contribution of each parameter: cooling time (blue), fuel enrichment (red),
-    cycle time (green), thermal power(brown), separation efficiency (light
-    blue).}\label{fig:pu_uncer}
+    the total uncertainty at 1$\sigma$ in black, and the uncertainty
+    contribution of each parameter in other colors.}\label{fig:pu_uncer}
 \end{figure}
 
-Regarding the uncertainty, disregarding the artefact of a very low mean inventory
-observed at the onset of fissile material production, the relative uncertainty
-starts at about $5\%$, and grows until year
-125 to decrease to $10\%$ at the end of the simulation time (180y), it seems
-it would have reached an equilibrium between $5$ and $10\%$ with longer
-simulations...
+At the onset of fissile material production, very low mean inventories lead to
+unreliable artefacts in the relative uncertainty.
+After that, the relative uncertainty
+starts at about $5\%$ and grows until year
+125, then decreases to $10\%$ at the end of the simulation time (180y).  
 Between year 40 and 70, the main contributor to the fissile inventory
 uncertainty is the cycle length.  As with the uranium needs, different cycle length
-implies different number of fuel loads, so different amount of resources used.  Never the less, around year 65 (see Figure
+implies different number of fuel loads, so different amount of resources used.  Nevertheless, around year 65 (see Figure
 \ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
 small enough to start limiting the production of fissile material.
-The uncertainty weight is then slowly transferred from
+The dominant contribution to the uncertainty then slowly transitions from
 the cycle length to the fuel cooling time.
 
-\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
     \centering
-    \includegraphics[scale=0.18]{used_fuel}
+    \includegraphics[scale=0.16]{used_fuel}
     \caption{Used fuel inventory, corresponding to the amount of used
@@
 \end{figure}
-Between year 90 and 120, the \gls{SFR} deployment speed increases, it has to
-compensate the non replacement of the decommissioned \glspl{LWR} as well as
-follow the power demand.  During this period the needs in plutonium are higher
-than its productions, explaining the observed decrease of the total amount, and
+Between year 90 and 120, the \gls{SFR} deployment speed increases; it has to
+compensate the non-replacement of the decommissioned \glspl{LWR} as well as
+follow the growing power demand.  During this period the needs in plutonium are higher
+than its production, explaining the observed decrease of the total amount, and
 the increase associated relative uncertainty.
 
-As the transition ends, the plutonium breed from the \glspl{SFR} starts to be
-sufficient to sustain the new \glspl{SFR} deployment to follow the power demand.
+As the transition ends, the plutonium bred from the \glspl{SFR} starts to be
+sufficient to sustain the new \gls{SFR} deployment to follow the power demand.
 
 It is also interesting to note that, the uncertainty contribution from the cycle
-length is between year 40 and 70 comes mainly from fuel batch loading
-frequencies, and after it relative contributions follows closely the thermal
-power one, suggesting a contributions through fuel discharge burnup (i.e.  fuel
-discharge composition).
+length between year 40 and 70 comes mainly from fuel batch loading
+frequencies.  After 70 years this contribution follows the thermal
+power contribution closely, suggesting that fuel discharge burnup (i.e.  fuel
+discharge composition) is the mechanism of this contribution.
 
@@
 Uranium consumption and separated fissile inventory are two important metrics
-regarding to non proliferation and nuclear archaeology.  In this study, we have
-been able to estimate than the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, where about
-$10\%$ on the enrichment implies a almost flat uncertainty of $2\%$.
+related to non-proliferation and nuclear archaeology.  In this study, we have
+been able to estimate that the cycle length uncertainty of $10\%$ implies a
+variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas about
+$10\%$ uncertainty on the enrichment implies an almost constant uncertainty of $2\%$.
 
-Regarding the reprocessed fissile inventory, this study has shown the limited
-impact of the reprocessed fuel compositions (through burnup variations) it
-limited to $5\%$, where fuel availability constrains, fuel loading frequency (cycle
-time), or fissile materials available for fuel fabrication (cooling time) can lead to higher
-uncertainties, respectively up to $10\%$ and to $30\%$.  Moreover it is very
-interesting to observe the pressure transition from one to the other around
+Regarding the reprocessed fissile inventory, this study has shown the 
+impact of the reprocessed fuel compositions (through burnup variations) is
+limited to $\approx5\%$, while fuel availability constraints, such as fuel loading frequency (cycle
+time) or fissile materials available for fuel fabrication (cooling time) can lead to higher
+uncertainties, up to $10\%$ and to $30\%$, respectively.  Moreover, it is very
+interesting to observe the transition from one to the other around
 year 70.
 
-This preliminary study may suggest that the most important contribution to
-natural uranium consumption and fissile inventory is coming from the time when
-occurs the different material exchange between facilities, and not necessary
-from the physical parameters such as thermal power or fuel enrichment. Further
-analysis should allow us to confirm or denies it.
+This preliminary study may suggest that the most important contributions to
+natural uranium consumption and fissile inventory come from the parameters that
+govern the exchange of material beteren facilities, and not
+from the physical parameters that describe those facilities, such as thermal power or fuel enrichment. Further
+analysis should allow us to understand this further.
 
@@
 
-Two main points can be deduced from this work.  Firstly, in a transitional
+Two main points can be deduced from this work.  First, in a transitional
 fuel cycle, the uncertainty contributions to an output metric can vary over time
-depending of various factors: deployment schedule artifact or pressure point in
+depending of various factors: deployment schedule artefacts or constrictions in
 the material flows.
 
-Secondly, it is important to note the special character of the time related
+Second, it is important to note the special character of the time related
 parameters uncertainty in a fuel cycle study, such as cooling time and cycle
-length.  Where some of those time related parameter will on the first order only
-impact material availability (as the cooling time will do), some other, like
+length.  While some of those time related parameters will, to first order, only
+impact material availability (as the cooling time will do), others, like
 cycle length, will also have a impact as physical parameters such as fuel
@@
 
-Cycle length impacts the discharge fuel burnup, it also affects the frequency of
-the fuel loads, this, as well as the cooling may imply a uncertainty on the
-material availability, which could lead to an artificially large uncertainty.
-Those kind of time related uncertainties will require a careful analysis on further
-uncertainty analysis, in order to understand and measure accurately their
-contributions on uncertainties.
+Cycle length impacts the discharge fuel burnup and  the frequency of
+the fuel loads.  When they combine to produce in uncertainty of the
+material availability, this could result in variations related to time delays that may
+contribute to the final uncertainty in ways that are not relevant to soem analyses.
+That is, a simple time lag in a particular output that otherwise follows an identical history
+could manifest itself as a large variation at any particular time.
+Those kind of time related uncertainties will require a further analysis
+to understand and measure accurately their
+contributions to the total uncertainty.
 
@@
 This kind of study will to be extended to random uncertainty (new parameter
-values at each occurrence) and completely systematic uncertainty (shared by all
+values as a function of time) and completely systematic uncertainty (shared by all
 the facilities of a kind).
@@
 uncertainties might be obvious, such study allows to estimate each parameters
-contribution, it could be less obvious for other parameters, such as
+contribution, and it could be less obvious for other parameters, such as
 plutonium quality, waste compositions.  Such studies could also provide research
-guidance for nuclear archaeology works, which aims to precisely estimate past
+guidance for nuclear archaeology work, which aims to precisely estimate past
 fissile production by the different nuclear countries.

### 2018-05-25 paper.tex
all fits in 4 pages

@@
 \newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
+\newcommand{\ie}{\emph{i.e.\ }}
 
@@
 simulator itself, and data uncertainty from the quantities provided by the
-user. This work we will be focused a subset the data uncertainty related to
-the user input that defines the performance of the facilities being simulated.
+user. This work focuses on a subset the data uncertainty related to
+the user input that defines the performance of the simulated facilities.
 
@@
 
-This study seeks to understand which measures of facility operation have the
+This study seeks to understand which characteristics of facility operation have the
 most impact on the uncertainty of fissile material production across a complete
@@
 individual facility uncertainties on the output metrics. The same simulation
-will be simulated $N$ times, for each simulation parameters affected with an
-uncertainty will be randomly determined, the distribution of each output metrics
-over the N iterations of the simulation, will be used to estimate their
+will be performed $N$ times, with some input parameters randomly determined in each case.
+The distribution of each output metrics over the N trials of the simulation
+will be used to estimate their
 respective uncertainty.
@@
          &            & Power                     \\\cmidrule{3-3}
-         &            & Fuel Enrichment (PWR-UOX) \\
+         &            & Fuel Enrichment (\gls{LWR}-\gls{UOX} \\
 
@@
 of the nuclear generated power (Figure \ref{fig:power}).
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
   \centering
@@
 
-\begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
     \centering
     \includegraphics[scale=0.18]{power.png}
-    \caption{Electric power generated over time, with the full production,
-        the \gls{LWR} contribution, and the \gls{SFR} contribution labeled in blue, orange, and green, respectively.}
+    \caption{Electric power generated over time, including contributions from each reactor type.}
     \label{fig:power}
@@
 
-In this work, a time step of 1 month has been considered, i.e., each output
+In this work, a time step of 1 month has been considered, \ie each output
 metric is reported once per month. Additionally, decay processes have not be
@@
 The total power generated in the simulation is reviewed to ensure that none of
-the compounded uncertainties result in material shorates substantial enough to
-cause long term reactor shutdowns.  For example, since \gls{SFR} fuel is built
-from reprocessed used fuel, the availability of that used fuel may impact the
+the compounded uncertainties result in material shortages substantial enough to
+cause long term facility shutdowns.  For example, since \gls{SFR} fuel is built
+from reprocessed used fuel, availability of that used fuel may impact the
 capability to build the required \gls{SFR}-\gls{MOX} fuel.  While there may be studies in
@@
     \includegraphics[scale=0.3]{power_full}
-    \caption{Electric power generated as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
+    \caption{Electric power generated as a function of time, wit its uncertainty.}\label{fig:power_full}
 \end{figure}
@@
 
-\subsection{Natural Uranium Consumption dedicated to PWR-UOX fabrication}
+\subsection{Natural Uranium Consumption Dedicated to \gls{LWR}-\gls{UOX} fabrication}
 
 Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
-dedicated to PWR-UOX fuel fabrication as a function of time.  The uncertainty on
+dedicated to \gls{LWR}-\gls{UOX} fuel fabrication as a function of time.  The uncertainty on
 the cumulative uranium consumption grows as expected with the time and the
@@
 
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{unat_full}
-    \caption{Cumulative consumption of natural uranium as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:unat_full}
-\end{figure}
-
 As expected, cooling time, separation efficiency and thermal power do not
-affect the natural uranium consumption for LWR-UOX fuel production.  The uncertainty on the natural uranium
+affect the natural uranium consumption for \gls{LWR}-\gls{UOX} fuel production.  The uncertainty on the natural uranium
 consumption is dominated by the \gls{LWR} cycle length: shorter the cycle
@@
     \centering
+    \includegraphics[scale=0.3]{unat_full}
+    \caption{Cumulative consumption of natural uranium as a function of time, with
+      associated uncertainty.}\label{fig:unat_full}
+\end{figure}
+
+\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
+    \centering
     \includegraphics[scale=0.3]{unat_uncer}
-    \caption{Cumulative natural uranium consumption relative uncertainty, with
-    the total uncertainty at 1$\sigma$ in black, and the uncertainty
-    contribution of each parameter in other colors.}\label{fig:unatr_uncer}
+    \caption{Relative uncertainty of the cumulative natural uranium consumption, including
+      individual contributions from each varied parameter.}\label{fig:unatr_uncer}
 \end{figure}
 The relative uncertainty of the total uranium consumption starts at about
-$5.5\%$ a slowly drops and stabilise around $3\%$.
+$5.5\%$ a slowly drops and stabilize around $3\%$.
 
@@
 year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
-beginning of the simulation have synchronised fuel cycles, reloading in the same time step.
+beginning of the simulation have synchronized fuel cycles, reloading in the same time step.
 This phenomenon disappears
@@
     \includegraphics[scale=0.3]{pu_full}
-    \caption{Fissile (plutonium) inventory as a function of time.  The black line
-        represents the reference calculation and the blue zone
-        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:pu_full}
+    \caption{Fissile (plutonium) inventory as a function of time, with
+      associated uncertainty.}\label{fig:pu_full}
 \end{figure}
@@
     \includegraphics[scale=0.3]{pu_uncer}
-    \caption{Fissile (plutonium) inventory relative uncertainty, with
-    the total uncertainty at 1$\sigma$ in black, and the uncertainty
-    contribution of each parameter in other colors.}\label{fig:pu_uncer}
+    \caption{Relative uncertainty in the fissile (plutonium) inventory, with
+      individual contributions from each varied parameter.}\label{fig:pu_uncer}
 \end{figure}
@@
 At the onset of fissile material production, very low mean inventories lead to
-unreliable artefacts in the relative uncertainty.
+unreliable artifacts in the relative uncertainty.
 After that, the relative uncertainty
@@
 frequencies.  After 70 years this contribution follows the thermal
-power contribution closely, suggesting that fuel discharge burnup (i.e.  fuel
+power contribution closely, suggesting that fuel discharge burnup (\ie fuel
 discharge composition) is the mechanism of this contribution.
@@
 natural uranium consumption and fissile inventory come from the parameters that
-govern the exchange of material beteren facilities, and not
+govern the exchange of material between facilities, and not
 from the physical parameters that describe those facilities, such as thermal power or fuel enrichment. Further
@@
 Two main points can be deduced from this work.  First, in a transitional
-fuel cycle, the uncertainty contributions to an output metric can vary over time
-depending of various factors: deployment schedule artefacts or constrictions in
-the material flows.
+fuel cycle, uncertainty contributions to output metrics can vary over time
+depending of various factors: deployment schedule artifacts or material flow constrictions.
 
@@
 material availability, this could result in variations related to time delays that may
-contribute to the final uncertainty in ways that are not relevant to soem analyses.
+contribute to the final uncertainty in ways that are not relevant to some analyses.
 That is, a simple time lag in a particular output that otherwise follows an identical history

### 2018-05-25 paper.tex
all fits in 4 pages - really this time!

@@
          &            & Power                     \\\cmidrule{3-3}
-         &            & Fuel Enrichment (\gls{LWR}-\gls{UOX} \\
+         &            & \acrshort{LWR}-\acrshort{UOX} Fuel Enrichment\\
 
@@
 relative contributions, it has only been applied to systematic uncertainties per
-facilities (parameters randomly generated at each new facility deployment).
+facilities.
 This kind of study will to be extended to random uncertainty (new parameter
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \appendix
-%% \section{Appendix}
-%%
-%% Numbering in the appendix is different:
-%% \begin{equation} \label{eq:appendix}
-%%   2 + 2 = 5\,.
-%% \end{equation}
-%% and another equation:
-%% \begin{equation} \label{eq:appendix2}
-%%   a + b = c\,.
-%% \end{equation}
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \section{Nomenclature}
-%%
-%% \begin{table}[H]
-%%     \centering
-%%     \begin{tabular}{l|l}
-%% %         &  \\
-%%         $N$ & Feed assay \\
-%%         $N'$ & Product assay \\
-%%         $N''$ & Tails assay \\
-%%         $\alpha$ & Feed to product enrichment factor \\
-%%         $\beta$ & Feed to tail enrichment factor \\
-%%         $\theta$ & Cut
-%%     \end{tabular}
-%% %    \caption{Caption}
-%%     \label{tab:my_label}
-%% \end{table}
-
-%% \begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
-%%   \centering
-%%   \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
-%%   \caption{Illustration of the material flow between the different level of
-%%       cascades without tail recycling, in this diagram, nu\_src corresponds to
-%%       an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
-%%       $\{n\}$ to the cascade and the storage getting the products of the
-%%       cascades at the level $\{n\}$.}\label{fig:flow}
-%% \end{figure}
-
-%% \begin{table}[htb]
-%% \centering
-%%   \caption{Summary of cascade properties for each level.}
-%% \begin{tabular}{cllll}
-%% \toprule
-%%
-%% Level   &           & Assay     &       & Machines  \\
-%%         & Feed      & Product   & Feed  &           \\
-%% \midrule
-%% 0       & 0.0071    & 0.0413    & 0.0029 & 167       \\
-%% 1       & 0.0413    & 0.2043    & 0.0173 & 169       \\
-%% 2       & 0.2043    & 0.5941    & 0.0971 & 168       \\
-%% 3       & 0.5941    & 0.8834    & 0.3915 & 168       \\
-%% 4       & 0.8834    & 0.9735    & 0.7746 & 169       \\
-%%
-%% \bottomrule
-%% \end{tabular}
-%%
-%%   \label{tab:cascadelvl}
-%% \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Acknowledgments}

### 2018-06-18 dis_clusion.tex
some work on the flows

--- 2018-05-25 dis_clusion.tex
@@
 untouched (Model A) or when it is slightly retuned to maintain the tail to
-product enrichment factor as well as the cut of each centrifuges, chaining the
-cascade we can observe high increase of the enrichment at each level.  On the
-contrary, when retuning the cut of each centrifuges to maintain the ideal state
-of the cascades while chaining them, the \gls{HEU} production rate is favored
-over the enrichment gain.
+product enrichment factor as well as the cut of each centrifuges (Model C),
+chaining the cascade we can observe high increase of the enrichment at each
+level.  On the contrary, when retuning the cut of each centrifuges to maintain
+the ideal state of the cascades (Model B) while chaining them, the \gls{HEU}
+production rate is favored over the enrichment gain.
 
 The tail recycling allows for each model a huge gain in productivity, even for
-then model B for which it does not change the number of levels required to reach
-$90w\%$ of $^{235}$U in the uranium. Even if no cascades chaining also to
-retrieve the same production rate as a direct enrichment, the model B with
+then model B where the number of levels required to reach $90w\%$ of $^{235}$U
+in the uranium does not change. Even if no cascades chaining allows to retrieve
+the same production rate as a direct enrichment, the model B with tail
 reprocessing reach about $80\%$ of an optimum production, which is far from
-being negligible\ldots
+being negligible, allowing to build up a Significant Quantity of \gls{HEU} in
+less than 8 months\ldots
 

### 2018-06-18 experiement.tex
add ref +add SQ mention
some work on the flows

--- 2018-05-24 experiement.tex
@@
-\section{the experiment}
-This works focuses on comparing the different miss use models to a reference
+\section{The experiment}
+This works focuses on comparing the different miss-use models to a reference
 calculation in which a single large cascade is build and designed to directly
@@
 This works uses the Cyclus fuel cycle simulator to allow material exchange
-between facilities.
+between facilities. The enrichment cascade algorithm have been implemented in
+the mbmore package \cite{mbmore.2018}.
+In each cases, 5060 centrifuges have been used and spread across up to 30
+different gas enrichment cascades.
 
 \subsection{The cascade configuration}
+
 \subsubsection{reference}
-As mentioned previously, all the further calculations will be compared to the
-most favorable configuration to produce \gls{HEU}, where all the available
-centrifuges are used in a single large cascade designed to directly produce \gls{HEU}
-from natural uranium, with a tail assay close to $0.3w\%$ uranium. The design
+
+As mentioned, all the further calculations will be compared to the most
+favorable configuration to produce \gls{HEU}, where all the available
+centrifuges are used in a single large cascade designed to directly produce
+\gls{HEU} from natural uranium, with a tail assay close to $0.3w\%$. The design
 characteristic of the reference cascade are summarized in Table
@@
 \subsubsection{default cascade}
+
 The default cascade is the cascade design for normal civilian enrichment
-operation, enriching natural uranium to about $3.5w\%$. This cascade will be
-layered and fed with uranium at higher enrichment to evaluate the possibility
-to used them, with few or no tuning, to produce \gls{HEU}. The characteristics of
-the default cascade are summarized in Table \ref{tab:cascade_config}.
+operation, enriching natural uranium to about $3.5w\%$, with a tail assay close
+to $0.3w\%$. This cascade will be layered and fed with uranium at higher
+enrichment to evaluate the possibility to used them, with few or no tuning, to
+produce \gls{HEU}. The characteristics of the default cascade are summarized in
+Table \ref{tab:cascade_config}.
 
@@
 \subsection{scenarios}
-Seven different simulations have been simulated:
+In the following, cascades can be connected in tandem, where each set of cascade
+in parallel is called a ``level``, as illustrated on Figure
+\ref{fig:cascade_level}.
+Seven different simulations have been simulated, to evaluate the effectiveness
+of an enrichment cascade when used outside of its designed scope :
 \begin{itemize}
 \item one as the reference calculation, with a single centrifuges designed to
-    produce directly \gls{HEU} from natural uranium,
+    directly produce \gls{HEU} from natural uranium,
 \item three calculations (one per miss-use model) were default cascade are
@@
 \item three calculations (one per miss-use model) were default cascade are
-    chained to produce \gls{HEU}, the tails of each cascade are recycled, blending
+    chained to produce \gls{HEU}, and the tails of each cascade are recycled, blending
     the tail of one level in the feed of the previous level of
-    cascades (see Figure \ref{fig:cascade_level}.
+    cascades (see Figure \ref{fig:cascade_level}).
 \end{itemize}
-In the following, cascades can be connected in tandem, where each set of cascade
-in parallel is called a ``level``, as illustrated on Figure
-\ref{fig:cascade_level}.
 
@@
     with the feed, product and the tail flows, respectively in blue, green and
-    red. The dashed orange line represent the alternative tail flow with
-    recycling them.}
+    red. The dashed orange line represent the alternative tail flow when
+    tail recycling is considered.}
     \label{fig:cascade_level}
@@
 \subsection{Level population}
-In order to assign the optimum number of cascade to each level a virtual cut as
+In order to assign the optimum number of cascades to each level, a virtual cut as
 been computed as:
 \begin{equation}
-    \theta^{v}_{i} = \frac{F_{i}-T_{i}}{P_{i}-T_{i}},
+    \theta^{v}_{j} = \frac{F_{j}-N''_{j}}{N'_{j}-N''_{j}},
 \end{equation}
-where, i represents a level of cascade and $F_{i}$, $P_{i}$ and $T_{i}$
+where, $j$ represents a level of cascade and $N_{j}$, $N'_{j}$ and $N''_{j}$
 respectively the feed, product and tail assay of the cascades at this level.
@@
 are summarized in Table \ref{tab:level}.
+
+As it is not possible to assign a fraction of an enrichment cascade, cascade per
+level are rounded up, to the first level is attibuted the remaining available
+cascades.
+
+\subsection{Timestep effect}
+
+As it can be observed on Figures \ref{fig:case1}, \ref{fig:case2} and
+\ref{fig:case3}, the different cascade levels required up to $2n+1$ timesteps
+before it starts to enrich uranium, where $n$ corresponds to the level number.
+This corresponds to the time required for the material to propagate from the
+natural uranium source to the n-th level, regardless of the duration of the
+timestep (hour, day, month,...). This is also true for the number of timesteps
+required to reach the equilibrium assays value in the tail reprocessing cases.
+As timestep can be artificially small or large, one will only be considering
+equilibrium values flow rates and assays in the following analysis.

### 2018-06-18 motivation.tex
some work on the flows

@@
 
-The present work investigates the performance of a enrichment cycle when chaining
-gas enrichment cascade tuned for low enrich uranium production from natural
+The present work investigates the performance of an enrichment cycle when chaining
+gas enrichment cascades tuned for low enrich uranium production from natural
 uranium. As literature on the mater is for obvious reason limited, three

### 2018-06-18 results.tex
some work on the flows

@@
 4/23/78/98 and 4/23/82/99, the model B, the enrichment gain is only
-4/21/61/90...  The same effect is observed when recycling the tails\ldots
+4/21/61/90.  Similar effects can be observed when recycling the tails\ldots
 
@@
 
-As demonstrated on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
+As shown on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
 \ref{sfig:case3_R}, recycling the tails increases the overall product assay at
-all the different levels. As shown on Table \ref{tab:level}, the tail assay of
-level $n$ is always higher than the product assay of level $n-2$, recycling the
-tails of level $n$ will consequently increase the feed assay of level $n-1$.
-Moreover, as the feed assay of level $n-1$ increases, its tail and product
-assays increase as well, increasing de facto the feed assays of respectively
-cascade levels $n-2$ and $n$...  This effect allow to reduce the number of
-cascade levels required to reach \gls{HEU} in case A and C.
+all the different levels. As the tail assay of a level $n$ is always higher than
+the product assay of the level $n-2$, recycling the tails of level $n$ will
+consequently increase the feed assay of level $n-1$ (see Table \ref{tab:level}).
+Moreover, with an increased feed assay, tail and product assays increase as
+well, increasing de facto the feed assays of respectively cascade levels $n-2$
+and $n$...  This effect reduces the number of cascade levels required to reach
+\gls{HEU} in case A and C.
 
@@
 As Model A and C, relies on maintaining the cut values at each stages of the
-cascade and share the same number of levels, both the  same repartition of
-cascades across the different levels and then the same \gls{HEU} production
-rate.
+cascade and share the same number of levels, have the exact same cascade
+repartition across the different levels and the same \gls{HEU} production rate.
 

### 2018-06-18 theory.tex
discussion and conclusion
some work on the flows

@@
-\section{theory}
+\section{Theory}
 \subsection{Centrifuge properties}
@@
 \ref{tab:centrifuges}) to match the cascade design describe in
-\cite{glaser.2008} and \cite{walker.2017}.  These parameters for a P1-type
-centrifuge are used to estimate the JCPOA-compliant IR-1 centrifuge.
+\cite{glaser.2008} and \cite{walker.2017} using P1-type centrifuges.
 
@@
 The cascade is built as an ideal cascade, with no losses in the separative work,
-which corresponds to $\alpha =\beta = const$ for all stage of the cascade, where
+which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
 $\alpha$ and $\beta$ respectively represent the feed to product and the feed to
@@
 the abundance ($R$) or the enrichment ($N$) of respectively the product
-($R'$,$N'$) and the feed,($R$,$N$) and the feed and the tails ($R''$,$N''$) such
+($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
 as:
@@
 As detailed in \cite{avery} it is also possible to derive $\alpha$ from the
-first principle, and express it as a function of the feed rate $F$ the
-separative performance $\delta U(\theta)$, the cut $\theta$:
+first principle, and express it as a function of the feed rate $F$, the
+separative performance $\delta U(\theta)$ and the cut $\theta$:
 
@@
 
-Since $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
-$\theta_{i}$, changes in each stage $i$ of a cascade.  This algorithm assumes
-that the corresponding separative power $\delta U$ (not re-computed) can be
-achieved with the chosen centrifuge design, tuning other operational parameter
-such as the rotation speed, the counter-current flow ratio...  Once $\theta_{i}$
-is determined, it is possible to compute the product and the tail assay.
+As $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
+$\theta_{i}$, changes across the different stages of a cascade.  This algorithm
+assumes that the corresponding separative power $\delta U$ (not re-computed) can
+be achieved with the chosen centrifuge design, tuning other operational
+parameter such as the rotation speed, the counter-current flow ratio...  Once
+$\theta_{i}$ is determined, it is possible to compute the product and the tail
+assay.
 
-The design of the cascade is performed through 2 steps.  First one determines the
-configuration and number of stages, adding stages until the product assay of the
-final stage is greater than or equal to than the desired assay, and the tails
-assay is similarly less than or equal to the desired tails assay.  This
-determines the number of enriching and stripping stages as well as their
-enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).
+The design of the cascade is performed through 2 steps.  First one determines
+the configuration and number of stages, adding stages until the product assay of
+the final stage is greater or equal the product targeted assay, and similarly
+the tails assay is less or equal the tails desired assay.  This determines the
+number of enriching and stripping stages as well as their enrichment properties
+($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).
 
-The second step determines how to populate the cascade with the user-defined
-maximum number of centrifuges.
-
-One solves the linear flow equation, \eqref{eq:flow}, to determine the
-theoretical flow in the cascade.
+The second step determines the relative flows at each stages, solving the linear
+flow equation, \eqref{eq:flow}.
+The cascade can then be populated with actual machines until the maximum number
+available of machines is reached.
 
@@
 
-Once the relative flow of each stage has been determined, the cascade can be
-populated with actual machines up the stages until the maximum number available
-of machines is reached.
+\subsection{Miss-use models}
 
-\subsection{Miss-use models}
 Little information is available about optimising an existing enrichment cascade
 that is being fed with a feed enrichment that does not match the design one. So
-far 3 different methods have been investigated, the first one assumes that no
-change are been made on the cascade, the second one, assumes that the cut value
-at each stage is retuned to maintain the ideal state of the cascade, the last
-one, described in \cite{walker.2017} assumes the tails to product enriching
-factor remains constants ($\gamma = \alpha\times\beta$). Models behavior, and
-assumptions are summarized in Tab. \ref{tab:models}.
+far 3 different methods have been investigated.
+
+The first one assumes that no change are been made on the cascade, i.e $\delta
+U$, $F$ and $\theta$ are fixed across all stages. The second one assumes the cut
+value at each stage is retuned to maintain the ideal state of the cascade,
+$\alpha$ and $\beta$ remain fixed. The last one, described in \cite{walker.2017}
+assumes the tails to product enriching factor and the cut remain constants ($\gamma =
+\alpha\times\beta$). Models behaviors and assumptions are summarized in Tab.
+\ref{tab:models}.
 
@@
 \subsubsection{Model A}
-The tuning method A does not re-optimize $\theta_i$ based on the true flow
-enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed assay
-($N'$), they do not change from stage to stage. According to equation
-\eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, when the feed assay ($N$)
-changes, then $\beta$ will change accordingly.  This breaks the ideal status of
-the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.
 
-In order to compute the proper product and tails assay at each stage, the
-tails and the product from respectively the next and the previous stage must be
+The tuning method A does not re-optimize $\theta_i$ keeping the same flow as the
+ideal configuration. From equation \eqref{eq:alpha}, maintaining $\delta U$, $F$
+and $\theta$ unchanged implies $\alpha$ remains unchanged as well. According to
+equation \eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, if the feed
+assay ($N$) changes, $\beta$ will change accordingly.  This breaks the
+ideal status of the cascade, i.e. $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.
+
+In order to compute the proper product and tails assay at each stage, the tails
+and the product from respectively the next and the previous stage must be
 blended in order to determine the correct stage feed assay. As this is a obvious
@@
 updated feed assay, the new product and tail assays are recomputed. This process
-is repeated until the change in assays is smaller than the set precision (1e-8
-by default).
-As the cut remain fixed at each stage the different flow do not need to be
-recomputed.
+is repeated until the sum of the square difference in assays is smaller than the
+precision (1e-8).  As the cut remain fixed at each stage the different flow do
+not need to be recomputed.
 
@@
 stage remain the same as the original design). The new flow rate are computed as
-the flow rates of the reconfigured cascade scaled down by the possible
-flows of the original one: the flow rates of a reconfigured cascade are
-computed, the ratios of the flow stage by stage with the original are determined,
-the smaller ratio is used to scale down all the flow rates.
+the flow rates of the reconfigured cascade scaled down to match the allowed
+flows of the original one: the flow rates at each stage of a miss-used cascade
+have to be inferior or equal to the initial cascade design.
 
@@
 
-The only solution allowing product assay values ranging between 0 and 1 is the
+The only solution allowing product assay to range between 0 and 1 is the
 following :

### 2018-06-27 abstract.tex
intagrating some gonuke comments

@@
 The goal of this work focuses on developing the necessary understanding of
-potential misuse of enrichment cascades to design more effective and efficient
-international safeguards approaches.  While it is straightforward to design an
-enrichment cascade under ideal conditions as a function of the theoretical feed,
-product and tails assays, it is very difficult to find reliable information
-about the behavior of a given cascade when the feed assay does not match the
-design value. Several methods have been developed to assess the behavior of an
-enrichment cascade in such circumstances, those methods evaluate the cut, the
-feed to product, feed to tail and the product to tail enrichment ratio,
-respectively, alpha, beta and gamma, as a function of the cascade feed assay. As
-those four parameters depends on each other, determining two of them allows to
-compute the other.  The first approach consists of fixing the cut and alpha
-recomputing the corresponding assays at each stages of the cascade. The second
-one maintains the ideal condition of the cascade (alpha and beta fixed across
-the whole cascade), modifying the cut value at each stage accordingly. Both
-approaches have been implemented into the Cyclus fuel cycle
-simulator\cite{cyclus, mbmore.2018}. The
-third fixes the cut and gamma, using both alpha and beta at each stage as free
-parameters. The third method has been investigated in \cite{walker.2017}.
+potential misuse of enrichment cascades. The latter would allow more effective
+international safeguards designs and approaches.  While it is straightforward to
+design an enrichment cascade under ideal conditions as a function of the
+theoretical feed, product and tails assays, it is very difficult to find
+reliable information about the behavior of a given cascade when the feed assay
+does not match the design value. Several methods have been developed to assess
+the behavior of an enrichment cascade in such circumstances. In addition of the
+cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
+product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
+as a function of the cascade feed assay. As those four parameters depend on each
+other, determining two of them allows to fully define the other.  The first
+approach consists of fixing $\theta$ and $\alpha$ recomputing the corresponding
+assays at each stages of the cascade. The second one maintains the ideal
+condition of the cascade ($\alpha$ and $\beta$ fixed across the whole cascade),
+modifying $\theta$ value at each stage accordingly. Both approaches have been
+implemented into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The
+third fixes $\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage
+as free parameters. The third method has been investigated in
+\cite{walker.2017}.
 

### 2018-06-27 dis_clusion.tex
intagrating some gonuke comments

@@
 It is really interesting to observe that when the cascade is left completely
-untouched (Model A) or when it is slightly retuned to maintain the tail to
+untouched (Model A) or when it is slightly retuned to maintain the tails to
 product enrichment factor as well as the cut of each centrifuges (Model C),
@@
 
-The tail recycling allows for each model a huge gain in productivity, even for
+The tails recycling allows for each model a huge gain in productivity, even for
 then model B where the number of levels required to reach $90w\%$ of $^{235}$U
@@
 
-This works will be extended to the near future with additional miss-use method,
+This works will be extended to the near future with additional misuse method,
 allowing for example the reconfiguration of the centrifuges in the cascades.
@@
 While mathematically correct, the authors do not guaranty the feasibility
-different miss-use tuning methods implemented and are welcoming any insight on
+different misuse tuning methods implemented and are welcoming any insight on
 the matter.

### 2018-06-27 experiement.tex
intagrating some gonuke comments

@@
 \section{The experiment}
-This works focuses on comparing the different miss-use models to a reference
+This works focuses on comparing the different misuse models to a reference
 calculation in which a single large cascade is build and designed to directly
@@
 between facilities. The enrichment cascade algorithm have been implemented in
-the mbmore package \cite{mbmore.2018}.
+the $mbmore$ package \cite{mbmore.2018}.
 In each cases, 5060 centrifuges have been used and spread across up to 30
@@
 centrifuges are used in a single large cascade designed to directly produce
-\gls{HEU} from natural uranium, with a tail assay close to $0.3w\%$. The design
+\gls{HEU} from natural uranium, with a tails assay close to $0.3w\%$. The design
 characteristic of the reference cascade are summarized in Table
@@
 The default cascade is the cascade design for normal civilian enrichment
-operation, enriching natural uranium to about $3.5w\%$, with a tail assay close
+operation, enriching natural uranium to about $3.5w\%$, with a tails assay close
 to $0.3w\%$. This cascade will be layered and fed with uranium at higher
@@
 Targeted  & Feed       & $0.71w\%$   & $0.71w\%$  \\
-Assays    & Product    & $90w\%$    & $4.0w\%$   \\
-          & Tail       & $0.3w\%$   & $0.3w\%$   \\
+Assays    & Product    & $90w\%$     & $3.5w\%$   \\
+          & Tails      & $0.3w\%$   & $0.3w\%$   \\
 \midrule
 Effective & Product    & $90.35w\%$  & $4.13w\%$  \\
-Assays    & Tail       & $0.28w\%$  & $0.28w\%$  \\ 
+Assays    & Tails      & $0.29w\%$   & $0.29w\%$  \\ 
 \midrule
@@
     directly produce \gls{HEU} from natural uranium,
-\item three calculations (one per miss-use model) were default cascade are
+\item three calculations (one per misuse model) were default cascade are
     chained to produce \gls{HEU}, without recycling the tails of each cascade,
     the cascade tails are directly sent to the waste,
-\item three calculations (one per miss-use model) were default cascade are
+\item three calculations (one per misuse model) were default cascade are
     chained to produce \gls{HEU}, and the tails of each cascade are recycled, blending
-    the tail of one level in the feed of the previous level of
+    the tails of one level in the feed of the previous level of
     cascades (see Figure \ref{fig:cascade_level}).
@@
     \caption{Schematic representation of the chained cascades with three levels,
-    with the feed, product and the tail flows, respectively in blue, green and
-    red. The dashed orange line represent the alternative tail flow when
-    tail recycling is considered.}
+    with the feed, product and the tails flows, respectively in blue, green and
+    red. The dashed orange line represent the alternative tails flow when
+    tails recycling is considered.}
     \label{fig:cascade_level}
@@
 where, $j$ represents a level of cascade and $N_{j}$, $N'_{j}$ and $N''_{j}$
-respectively the feed, product and tail assay of the cascades at this level.
+respectively the feed, product and tails assay of the cascades at this level.
 
 A flow equation similar to \eqref{eq:flow} is then solve to get the optimum
-number of cascade per level. When the tail are not recycled, the $(1-\theta)$
+number of cascade per level. When the tails are not recycled, the $(1-\theta)$
 terms are removed from the flow equation.  The results of the level population
@@
 As it is not possible to assign a fraction of an enrichment cascade, cascade per
-level are rounded up, to the first level is attibuted the remaining available
-cascades.
+level are rounded up for each level but the first one. To the first level is
+attributed the remaining available cascades.
 
@@
 timestep (hour, day, month,...). This is also true for the number of timesteps
-required to reach the equilibrium assays value in the tail reprocessing cases.
+required to reach the equilibrium assays value in the tails reprocessing cases.
 As timestep can be artificially small or large, one will only be considering

### 2018-06-27 motivation.tex
intagrating some gonuke comments

@@
 
-Gas centrifuge cascades are usually designed to operate in ideal manner, with no
-losses in separative work, the most effective way. To achieve such ideal
-configuration, the cascade is designed to be fed with a specific feed assay and
-produce the target  enrichment while rejecting tails at a fix assay.
+Gas centrifuge cascades are usually designed to operate in an ideal manner, with
+no losses in separative work. To achieve such ideal configuration, the cascade
+is designed to be fed with a specific feed assay and produce the target
+enrichment while rejecting tails at a fixed assay.
 
@@
 its designed scope and quantify the attractiveness of such way to build up
-significant amount of \gls{HEU}.
+significant quantity of \gls{HEU}.
 
@@
 enrich cascade when fed with different assays than the design one. This work
-takes also advantage of the Cyclus\cite{cyclus} fuel cycle capabilities to
-evaluate the assay blending equilibrium.
+also takes advantage of the Cyclus\cite{cyclus} fuel cycle capabilities to
+evaluate the assay values at equilibrium.

### 2018-06-27 paper.tex
Add title
intagrating some gonuke comments

@@
-\documentclass{anstrans}
+\documentclass[12pt]{article}
+\usepackage{mathptmx} % Nearly Times New Roman
+\usepackage[affil-it]{authblk}
+
+%\makeglossaries
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{}
-\author{Baptiste Mouginot, Kathryn Mummah, Paul P.H.  Wilson}
 
-\institute{
-University of Wisconsin-Madison, Madison, WI
+\usepackage{color}
+\usepackage{subcaption}
+\usepackage{graphicx}
+\usepackage{booktabs} % nice rules for tables
+\usepackage{microtype} % if using PDF
+\usepackage{xspace}
+\usepackage{listings}
+\usepackage{textcomp}
+\usepackage{multicol,tabularx,capt-of}
+\usepackage{multirow}
+
+\usepackage{fancyhdr} % allows headers and footers
+%\usepackage{ulem}
+\usepackage{pdflscape}
+% Page length commands go here in the preamble
+\setlength{\oddsidemargin}{-0.25in} % Left margin of 1 in + 0 in = 1 in
+\setlength{\textwidth}{7in}   % Right margin of 8.5 in - 1 in - 6.5 in = 1 in
+\setlength{\topmargin}{-.75in}  % Top margin of 2 in -0.75 in = 1 in
+\setlength{\textheight}{9.2in}  % Lower margin of 11 in - 9 in - 1 in = 1 in
+
+\definecolor{listinggray}{gray}{0.9}
+\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
+\definecolor{burgundy}{rgb}{0.5, 0.0, 0.13}
+\definecolor{burntorange}{rgb}{0.8, 0.33, 0.0}
+\definecolor{chromeyellow}{rgb}{1.0, 0.65, 0.0}
+\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
+
+\lstset{
+    %backgroundcolor=\color{lbcolor},
+    language={C++},
+    tabsize=4,
+    rulecolor=\color{black},
+    upquote=true,
+    aboveskip={1.5\baselineskip},
+    belowskip={1.5\baselineskip},
+    columns=fixed,
+    extendedchars=true,
+    breaklines=true,
+    prebreak=\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
+    frame=single,
+    showtabs=false,
+    showspaces=false,
+    showstringspaces=false,
+    basicstyle=\scriptsize\ttfamily\color{green!40!black},
+    keywordstyle=\color[rgb]{0,0,1.0},
+    commentstyle=\color[rgb]{0.133,0.545,0.133},
+    stringstyle=\color[rgb]{0.627,0.126,0.941},
+    numberstyle=\color[rgb]{0,1,0},
+    identifierstyle=\color{black},
+    captionpos=t,
 }
 
-\email{mouginot@wisc.edu \and mummah@wisc.edu \and paul.wilson@wisc.edu}
+\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily\color{green!40!black}]|#1|}
+\newcommand{\units}[1] {\:\text{#1}}%
+\newcommand{\SN}{S$_N$}
+\newcommand{\cyclus}{\textsc{Cyclus}\xspace}
+\newcommand{\Cyclus}{\cyclus}
+\newcommand{\citeme}{\textcolor{red}{CITE}\xspace}
+\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%
 
-% Optional disclaimer: remove this command to hide
-% \disclaimer{Notice: this manuscript is a work of fiction.  Any resemblance to
-% actual articles, living or dead, is purely coincidental.}
-
-%%%% packages and definitions (optional)
-\usepackage{graphicx} % allows inclusion of graphics
-\usepackage{booktabs} % nice rules (thick lines) for tables
-\usepackage{microtype} % improves typography for PDF
-\usepackage{float}
-
-\newcommand{\SN}{S$_N$}
-\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
-\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
-\newcommand{\grad}{\vec{\nabla}} % gradient
-\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
-\newcommand{\ie}{\emph{i.e.\ }}
+\newcommand{\comment}[1]{{\color{green}\textbf{#1}}}
 
 \usepackage[acronym]{glossaries}
-\newacronym{UOX}{UOX}{uranium oxide fuel}
-\newacronym{MOX}{MOX}{mixed oxide fuel}
-\newacronym{LWR}{LWR}{light water reactor}
-\newacronym{SFR}{SFR}{fast breeder reactor}
 
+\input{glossary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{frontmatter}
+\title{Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades}
+% Authors. Separated by commas
+\input{authors}
+\date{}
+% Institutes of the authors
+\input{institutions}
+\pagestyle{fancy}
 \begin{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
 
-Fuel cycle simulations, as with any simulation process, do not produce results
-without uncertainties.  Those uncertainties have two main sources: modeling
-uncertainty due to the simplifications and approximations built in to the
-simulator itself, and data uncertainty from the quantities provided by the
-user. This work focuses on a subset the data uncertainty related to
-the user input that defines the performance of the simulated facilities.
+\maketitle
 
-Such simulation uncertainties could be important in the context of treaty
-verification.  Some scenarios require estimating historical fissile material
-production based on records of facility operation and material transfer.  If
-the measurements of facility operation and material transfer are subject to
-uncertainty, the total production quantities will then also be uncertain.  Any
-uncertainty in fissile production quantities poses a material accounting
-challenge, possibly creating an opportunity for undetected diversion.
+% 0.Abstract
+\input{abstract}
+% I.   Motivation
+\input{motivation}
 
-This study seeks to understand which characteristics of facility operation have the
-most impact on the uncertainty of fissile material production across a complete
-fuel cycle.  Uncertainty propagation using a Monte Carlo method will be applied
-to the Cyclus fuel cycle simulator \cite{cyclus} to estimate the effect of
-individual facility uncertainties on the output metrics. The same simulation
-will be performed $N$ times, with some input parameters randomly determined in each case.
-The distribution of each output metrics over the N trials of the simulation
-will be used to estimate their
-respective uncertainty.
+% II.  Theory
+%   a. cascade design
+%   b. misuse model
+%       i.   case A
+%       ii.  case B
+%       iii. case C
+\input{theory}
 
-\section{The Experiment}
+% III. Experiement
+%   a.  cycle 
+%   b.  cascade per level optimisation
+\input{experiement}
 
-\subsection{Method}
+% IV.  results
+%   a. time step effects
+%   b. no tails recycling
+%   c. tails recycling
+\input{results}
 
-To estimate the uncertainty of fuel cycle output metrics, a Monte
-Carlo approach has been applied.  In each of 199 independent simulations,
-some of the parameters that define facility behavior are randomly selected
-from Normal distributions with standard deviations that are $10\%$ of the mean/nominal
-value.  This artificially large standard deviation is selected for the purpose
-of demonstrating the methodology.  The mean and standard deviation of some
-output metrics are calculated from the simulation output, as a function of time.
+% V.  Discussion
+% VI. Conclusions and future plan
+\input{dis_clusion}
 
-To pursue this work, both the Cycamore\footnote{Low
-fidelity facilities package for Cyclus}\cite{cycamore} and the
-CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models}\cite{mouginot_2018, cyclass} packages were
-updated to evaluate the uncertainty of several
-operational parameters in their associated facilities.  Table
-\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
-facilities of Cycamore and CyCLASS.
-
-\begin{table}[htb]
-\centering
-  \caption{Summary of facility modifications according to their Cyclus archetype package.}
-\begin{tabular}{cl|l}
-\toprule
-
-Package   & Facility   & Parameters                \\
-\toprule
-
-Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
-         & Storage    & Residence Time            \\
-\toprule
-CyCLASS  & Reactor    & Cycle Length              \\\cmidrule{3-3}
-         &            & Power                     \\\cmidrule{3-3}
-         &            & \acrshort{LWR}-\acrshort{UOX} Fuel Enrichment\\
-
-\bottomrule
-\end{tabular}
-
-  \label{tab:package_uncertainty}
-\end{table}
-
-The uncertainty of the different parameters in this study
-are systematic for each new deployed facility: each time a new facility is
-deployed (such as a reactor or a fuel fabrication facility) a new set of
-parameters are sampled, and those parameters are used throughout the life
-of that facility.
-
-\subsection{The Fuel Cycle Scenario}
-For demonstration purposes, a simple commercial fuel cycle transition is used,
-inspired from the EG23 fuel cycle
-of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}.
-Pictured in Figure \ref{fig:cycle}, this is a
-transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a
-\gls{SFR} fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
-of the nuclear generated power (Figure \ref{fig:power}).
-\begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[scale=0.31]{cycle.png}
-  \caption{Simplified representation of the material flow between the different facilities,
-  with each operational parameter associated with an
-  uncertainty labeled in green.}\label{fig:cycle}
-\end{figure}
-
-As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
-composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
-transition starts around year 35, with the deployment of \glspl{SFR}. The \glspl{SFR} are loaded
-with \gls{MOX}, which consists of plutonium blended with natural
-uranium.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.18]{power.png}
-    \caption{Electric power generated over time, including contributions from each reactor type.}
-    \label{fig:power}
-\end{figure}
-
-The plutonium, required for \gls{MOX} fabrication, is reprocessed from all
-used fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel
-as it becomes available for reprocessing.
-
-Both fuel reprocessing and fabrication have a constant maximum throughput, but may also be limited by the 
-availability input material.  The enrichment of the \gls{UOX} is processed
-on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
-between all facilities with constant throughput.
-
-In this work, a time step of 1 month has been considered, \ie each output
-metric is reported once per month. Additionally, decay processes have not be
-taken into account.
-
-It must be noted that for this work, the fuel enrichment was determined by a
-fuel fabrication model\cite{Leniau2015125} which
-calculates the fissile fraction required in the fuel to reach a given target
-burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
-enrichment is not applied directly to the effective enrichment. It is instead applied to the
-burnup, resulting in a fuel enrichment uncertainty that is also close to
-$10\%$.
-
-For each of the parameters in Table \ref{tab:package_uncertainty}, a set of
-199 simulations was performed with only that parameter being randomly varied.
-An additional set of 199 simulations was performed in which all five
-parameters are randomly varied.  A reference simulation was performed
-with all five parameters fixed at the mean value.
-
-\section{Results}
-
-Because the main interests of nuclear archaeology involve highly enriched uranium production and
-fissile inventories, this study mainly focuses on the uncertainties of
-the total quantity of natural uranium used and the total unused fissile
-inventory (separated plutonium).
-
-The total power generated in the simulation is reviewed to ensure that none of
-the compounded uncertainties result in material shortages substantial enough to
-cause long term facility shutdowns.  For example, since \gls{SFR} fuel is built
-from reprocessed used fuel, availability of that used fuel may impact the
-capability to build the required \gls{SFR}-\gls{MOX} fuel.  While there may be studies in
-which this would be an interesting result, in the context of this work, such
-shutdowns would be well-documented in the operational histories of the
-facilities and should not be characterized as an uncertainty.  Figure
-\ref{fig:power_full} shows that uncertainties in generated power are indeed
-very low.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{power_full}
-    \caption{Electric power generated as a function of time, wit its uncertainty.}\label{fig:power_full}
-\end{figure}
-
-At each time step, the $\pm1\sigma$ uncertainty due to the full set of varied
-parameters is reported.  In addition, the relative contribution to the total
-uncertainty from each of the parameters is calculated as the ratio of the
-$1\sigma$ uncertainty due to that parameter over the total uncertainty.
-
-\subsection{Natural Uranium Consumption Dedicated to \gls{LWR}-\gls{UOX} fabrication}
-
-Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
-dedicated to \gls{LWR}-\gls{UOX} fuel fabrication as a function of time.  The uncertainty on
-the cumulative uranium consumption grows as expected with the time and the
-loading of the \glspl{LWR}.  The increase stops around year 125y with the
-decommissioning of the last \glspl{LWR}.
-
-As expected, cooling time, separation efficiency and thermal power do not
-affect the natural uranium consumption for \gls{LWR}-\gls{UOX} fuel production.  The uncertainty on the natural uranium
-consumption is dominated by the \gls{LWR} cycle length: shorter the cycle
-length is, the more fuel will be loaded, and \emph{vice versa}.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{unat_full}
-    \caption{Cumulative consumption of natural uranium as a function of time, with
-      associated uncertainty.}\label{fig:unat_full}
-\end{figure}
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{unat_uncer}
-    \caption{Relative uncertainty of the cumulative natural uranium consumption, including
-      individual contributions from each varied parameter.}\label{fig:unatr_uncer}
-\end{figure}
-The relative uncertainty of the total uranium consumption starts at about
-$5.5\%$ a slowly drops and stabilize around $3\%$.
-
-Uncertainty fluctuation of the full relative uncertainty can be observed before
-year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
-beginning of the simulation have synchronized fuel cycles, reloading in the same time step.
-This phenomenon disappears
-with the gradual decommissioning of the initial reactors, spread over 50 years.
-
-The decrease of the cycle time uncertainty contribution, from year 30 to year
-90, can be understood as an averaging effect.  As the uncertainty are defined once
-per deployed facility, each reactor will have a different cycle
-length value, so a different number of batches loaded per year.  With the increase
-of deployed reactors, the number of batches of \gls{LWR} fuel loaded converges
-to the references one, reducing its impact on the uncertainty on the total
-uranium consumption. This uncertainty contribution to the overall uncertainty
-decrease is proportional to the number of \gls{LWR} reactors and stops with the
-decommission of the last one.
-
-The fuel enrichment contribution follow a close to constant uncertainty
-contribution of $2\%$, so as the total relative uncertainty decrease, it
-has a growing shared of the total absolute uncertainty over time.
-
-\subsection{Fissile Inventory}
-The fissile inventory corresponds to the amount of separated fissile material waiting to
-be blended with natural uranium in order to produce the \gls{SFR}-\gls{MOX} fuel.
-
-As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow in
-year 40, with the deployment of the first reprocessing facility.  It grows
-during the first period of the \glspl{LWR} to \gls{SFR}-A transition until
-year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
-When the steady state is reached (full \gls{SFR} fleet), the plutonium
-inventory starts to increase, as the breading ratio of the \glspl{SFR} is higher
-than the deployment needs.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{pu_full}
-    \caption{Fissile (plutonium) inventory as a function of time, with
-      associated uncertainty.}\label{fig:pu_full}
-\end{figure}
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{pu_uncer}
-    \caption{Relative uncertainty in the fissile (plutonium) inventory, with
-      individual contributions from each varied parameter.}\label{fig:pu_uncer}
-\end{figure}
-
-At the onset of fissile material production, very low mean inventories lead to
-unreliable artifacts in the relative uncertainty.
-After that, the relative uncertainty
-starts at about $5\%$ and grows until year
-125, then decreases to $10\%$ at the end of the simulation time (180y).  
-Between year 40 and 70, the main contributor to the fissile inventory
-uncertainty is the cycle length.  As with the uranium needs, different cycle length
-implies different number of fuel loads, so different amount of resources used.  Nevertheless, around year 65 (see Figure
-\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
-small enough to start limiting the production of fissile material.
-The dominant contribution to the uncertainty then slowly transitions from
-the cycle length to the fuel cooling time.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.16]{used_fuel}
-    \caption{Used fuel inventory, corresponding to the amount of used
-    \glspl{LWR} and \glspl{SFR} fuel, cooled and waiting to be reprocessed.}
-    \label{fig:used_fuel}
-\end{figure}
-Between year 90 and 120, the \gls{SFR} deployment speed increases; it has to
-compensate the non-replacement of the decommissioned \glspl{LWR} as well as
-follow the growing power demand.  During this period the needs in plutonium are higher
-than its production, explaining the observed decrease of the total amount, and
-the increase associated relative uncertainty.
-
-As the transition ends, the plutonium bred from the \glspl{SFR} starts to be
-sufficient to sustain the new \gls{SFR} deployment to follow the power demand.
-
-It is also interesting to note that, the uncertainty contribution from the cycle
-length between year 40 and 70 comes mainly from fuel batch loading
-frequencies.  After 70 years this contribution follows the thermal
-power contribution closely, suggesting that fuel discharge burnup (\ie fuel
-discharge composition) is the mechanism of this contribution.
-
-\subsection{Discussion}
-
-Uranium consumption and separated fissile inventory are two important metrics
-related to non-proliferation and nuclear archaeology.  In this study, we have
-been able to estimate that the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas about
-$10\%$ uncertainty on the enrichment implies an almost constant uncertainty of $2\%$.
-
-Regarding the reprocessed fissile inventory, this study has shown the 
-impact of the reprocessed fuel compositions (through burnup variations) is
-limited to $\approx5\%$, while fuel availability constraints, such as fuel loading frequency (cycle
-time) or fissile materials available for fuel fabrication (cooling time) can lead to higher
-uncertainties, up to $10\%$ and to $30\%$, respectively.  Moreover, it is very
-interesting to observe the transition from one to the other around
-year 70.
-
-This preliminary study may suggest that the most important contributions to
-natural uranium consumption and fissile inventory come from the parameters that
-govern the exchange of material between facilities, and not
-from the physical parameters that describe those facilities, such as thermal power or fuel enrichment. Further
-analysis should allow us to understand this further.
-
-\section{Conclusion}
-
-Two main points can be deduced from this work.  First, in a transitional
-fuel cycle, uncertainty contributions to output metrics can vary over time
-depending of various factors: deployment schedule artifacts or material flow constrictions.
-
-Second, it is important to note the special character of the time related
-parameters uncertainty in a fuel cycle study, such as cooling time and cycle
-length.  While some of those time related parameters will, to first order, only
-impact material availability (as the cooling time will do), others, like
-cycle length, will also have a impact as physical parameters such as fuel
-enrichment or thermal power.
-
-Cycle length impacts the discharge fuel burnup and  the frequency of
-the fuel loads.  When they combine to produce in uncertainty of the
-material availability, this could result in variations related to time delays that may
-contribute to the final uncertainty in ways that are not relevant to some analyses.
-That is, a simple time lag in a particular output that otherwise follows an identical history
-could manifest itself as a large variation at any particular time.
-Those kind of time related uncertainties will require a further analysis
-to understand and measure accurately their
-contributions to the total uncertainty.
-
-This study aims to be a proof-of-principle for uncertainty propagation in
-potential commercial fuel cycle transition.  While it has demonstrated the
-capability to measure the uncertainty on output fuel cycle metrics and their
-relative contributions, it has only been applied to systematic uncertainties per
-facilities.
-This kind of study will to be extended to random uncertainty (new parameter
-values as a function of time) and completely systematic uncertainty (shared by all
-the facilities of a kind).
-
-While the parameters contributing to natural uranium needs and fissile inventory
-uncertainties might be obvious, such study allows to estimate each parameters
-contribution, and it could be less obvious for other parameters, such as
-plutonium quality, waste compositions.  Such studies could also provide research
-guidance for nuclear archaeology work, which aims to precisely estimate past
-fissile production by the different nuclear countries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Acknowledgments}

### 2018-06-27 results.tex
intagrating some gonuke comments

@@
 Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
-        &            & Tail      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
+        &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
         & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
@@
 Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $69.8w\%$ \\
-        &            & Tail      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$  \\
+        &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$  \\
         & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
@@
 Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $98.4w\%$ \\
-        &            & Tail      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
+        &            & Tails      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
         & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.32      & 0.35      \\
@@
 Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
-        &            & Tail      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
+        &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
         & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
@@
         \includegraphics[scale=0.17]{NR_case1}
-        \caption{No tail recycling}
+        \caption{No tails recycling}
         \label{sfig:case1_NR}
@@
         \includegraphics[scale=0.17]{R_case1}
-        \caption{Tail recycling}
+        \caption{Tails recycling}
         \label{sfig:case1_R}
@@
     \caption{Evolution of the product assays at each level with considering
-    miss-use model A, with (right) and without recycling (left).}
+    misuse model A, with (right) and without recycling (left).}
     \label{fig:case1}
@@
         \includegraphics[scale=0.17]{NR_case2}
-        \caption{No tail recycling}
+        \caption{No tails recycling}
         \label{sfig:case2_NR}
@@
         \includegraphics[scale=0.17]{R_case2}
-        \caption{Tail recycling}
+        \caption{Tails recycling}
         \label{sfig:case2_R}
@@
     \caption{Evolution of the product assays at each level with considering
-    miss-use model B, with (right) and without recycling (left).}
+    misuse model B, with (right) and without recycling (left).}
     \label{fig:case2}
@@
 \ref{sfig:case3_R}, recycling the tails increases the overall product assay at
-all the different levels. As the tail assay of a level $n$ is always higher than
+all the different levels. As the tails assay of a level $n$ is always higher than
 the product assay of the level $n-2$, recycling the tails of level $n$ will
 consequently increase the feed assay of level $n-1$ (see Table \ref{tab:level}).
-Moreover, with an increased feed assay, tail and product assays increase as
+Moreover, with an increased feed assay, tails and product assays increase as
 well, increasing de facto the feed assays of respectively cascade levels $n-2$
@@
         \includegraphics[scale=0.17]{NR_case3}
-        \caption{No tail recycling}
+        \caption{No tails recycling}
         \label{sfig:case3_NR}
@@
         \includegraphics[scale=0.17]{R_case3}
-        \caption{Tail recycling}
+        \caption{Tails recycling}
         \label{sfig:case3_R}
@@
     \caption{Evolution of the product assays at each level with considering
-    miss-use model C, with (right) and without recycling (left).}
+    misuse model C, with (right) and without recycling (left).}
     \label{fig:case3}
@@
     \caption{Production rate for the different model configuration, with in blue
-    the case without tail recycling, in orange with tail recycling, and in green
+    the case without tails recycling, in orange with tails recycling, and in green
     the reference one. Where A-B-C represent the model used, and NR-R
-    respectively the case without tail recycling and the case with tail recycling}
+    respectively the case without tails recycling and the case with tails recycling}
     \label{fig:HEU_rate}

### 2018-06-27 theory.tex
intagrating some gonuke comments

@@
 \midrule
-320    & $320$           & $1.8$ & $0.105$ & $1e3$  & $13$      & 2     & 1.0  \\
+320    & $320$       & $1.8$  & $0.105$  & $1^{3}$ & $13$       & 2     & 1.0  \\
 \bottomrule
@@
 $\alpha$ and $\beta$ respectively represent the feed to product and the feed to
-tail enrichment factors.  $\alpha$ and $\beta$ can be expressed as function of
+tails enrichment factors.  $\alpha$ and $\beta$ can be expressed as function of
 the abundance ($R$) or the enrichment ($N$) of respectively the product
@@
 as:
-\begin{subequations} \label{eqs:alphabeta}
+\begin{subequations} \label{eq:alphabeta}
     \begin{equation} \label{eq:alpha_def}
@@
 From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
-\eqref{eqs:alphabeta} it is possible to express $\beta$ as a function of the
+\eqref{eq:alphabeta} it is possible to express $\beta$ as a function of the
 feed abundance, $R$, the cut $\theta$ and $\alpha$:
@@
 From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
-the cut, $\theta$, or the ratio of product flow to feed flow required to build an ideal
-cascade:
-$\beta$ values and the feed assay, $N_{i}$:
+the cut, $\theta$ required to build an ideal cascade:
 \begin{eqnarray}
@@
            \dfrac{1}{1 + \beta/R_{i}}}
+           \label{eq:theta}
 \end{eqnarray}
@@
 be achieved with the chosen centrifuge design, tuning other operational
-parameter such as the rotation speed, the counter-current flow ratio...  Once
+parameter such as the rotation speed, the counter-current flow ratio, etc.  Once
 $\theta_{i}$ is determined, it is possible to compute the product and the tail
@@
 
-\subsection{Miss-use models}
+\subsection{Misuse models}
 
@@
 \centering
-  \caption{Summary of miss-use model properties.}
+  \caption{Summary of misuse model properties.}
 \begin{tabular}{l|ccc}
@@
 \midrule
-Constant parameters  & $\alpha_i, \theta_i$ & $\alpha_i=\beta_i$ & $\gamma_i=\alpha_i*\beta_i, \theta_i$       \\
-Optimised parameters & $\beta_i$            & $\theta_i$         & $\alpha_i, \beta_i$                     \\
+Constant parameters  & $\alpha_i, \theta_i$ & $\alpha_i=\beta_i$ & $\gamma_i=\alpha_i .\beta_i, \theta_i$       \\
+Varying parameters   & $\beta_i$            & $\theta_i$         & $\alpha_i, \beta_i$                     \\
 Assays determination & blended              & ideal              & blended                  \\
-Flow                 & unchanged            & scaled             & unchanged       \\
+Flow                 & unchanged            & reduced            & unchanged       \\
 
@@
 In order to compute the proper product and tails assay at each stage, the tails
-and the product from respectively the next and the previous stage must be
-blended in order to determine the correct stage feed assay. As this is a obvious
-cycling problem, an iterative solution has been chosen: all feed assays are
+and the product from the next and the previous stage respectively must be
+blended in order to determine the correct stage feed assay. All feed assays are
 iteratively updated, blending the proper product and tails, then using the
-updated feed assay, the new product and tail assays are recomputed. This process
-is repeated until the sum of the square difference in assays is smaller than the
-precision (1e-8).  As the cut remain fixed at each stage the different flow do
-not need to be recomputed.
+updated feed assay, the new product and tails assays are recomputed. This
+process is repeated until the sum of the square difference in assays is smaller
+than $1^{-8}$.  As the cut remain fixed at each stage the flows do not need to
+be recomputed.
 
@@
 
-The second method the cut value at each stage $\theta_i$, is retuned in order to
-maintain the $\alpha_i$ and $\beta_i$ at their original values. As the cascade
-remains ideal, the product and tail assay at each stages (and for the overall
-cascade) is easily determined using equations \eqref{eqs:alphabeta}.
+Using the second method, the cut value at each stage $\theta_i$, is retuned in
+order to maintain the $\alpha_i$ and $\beta_i$ at their original values
+(equation \eqref{eq:theta}). As the cascade remains ideal, the product and tails
+assay at each stages are easily determined using equations \eqref{eq:alphabeta}.
 
-As the cuts values change, the flow rate between the different stage has to be
-recomputed. Because the cascade is not reorganised (the number of cascade per
-stage remain the same as the original design). The new flow rate are computed as
-the flow rates of the reconfigured cascade scaled down to match the allowed
-flows of the original one: the flow rates at each stage of a miss-used cascade
-have to be inferior or equal to the initial cascade design.
+As the cut values change, the relative flow rates between the different stage
+are recomputed using equation \eqref{eq:flow}. The new flows are also
+constrained by the fixed design of the cascade, number of centrifuges limiting
+the flow at each level.
 
 \subsubsection{Model C}
-The last model assumes that the tail to product enrichment factor remains
+The last model assumes that the tails to product enrichment factor remains
 constant regardless to the feed assays. To compute the response of the cascade
@@
 $\theta$ remain fixed. 
-From equations \eqref{eqs:alphabeta} and the assay conservation equation $N =
+From equations \eqref{eq:alphabeta} and the assay conservation equation $N =
 \theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
@@
 \end{equation}
-Once the product assay is known, one can trivially determine the tail assay,
-$\alpha$ and $\beta$ using equations \eqref{eqs:alphabeta} and mass
+Once the product assay is known, one can trivially determine the tails assay,
+$\alpha$ and $\beta$ using equations \eqref{eq:alphabeta} and mass
 conservation.

### 2018-06-28 dis_clusion.tex
finish with gonuke comments

@@
 
-It is really interesting to observe that when the cascade is left completely
-untouched (Model A) or when it is slightly retuned to maintain the tails to
-product enrichment factor as well as the cut of each centrifuges (Model C),
-chaining the cascade we can observe high increase of the enrichment at each
-level.  On the contrary, when retuning the cut of each centrifuges to maintain
-the ideal state of the cascades (Model B) while chaining them, the \gls{HEU}
-production rate is favored over the enrichment gain.
+We can observe that when the cascade is left completely untouched (Model A) or
+when it is slightly retuned to maintain the tails to product enrichment factor
+as well as the cut of each centrifuges (Model C), chaining the cascade we can
+observe high increase of the enrichment at each level.  On the contrary, when
+retuning the cut of each centrifuges to maintain the ideal state of the cascades
+(Model B) while chaining them, the \gls{HEU} production rate is favored over the
+enrichment gain.
 
-The tails recycling allows for each model a huge gain in productivity, even for
-then model B where the number of levels required to reach $90w\%$ of $^{235}$U
-in the uranium does not change. Even if no cascades chaining allows to retrieve
-the same production rate as a direct enrichment, the model B with tail
-reprocessing reach about $80\%$ of an optimum production, which is far from
-being negligible, allowing to build up a Significant Quantity of \gls{HEU} in
-less than 8 months\ldots
+The tails recycling allows each model to achieve a large gain in productivity,
+even for then model B in which the number of levels required to reach $90w\%$ of
+$^{235}$U in the uranium does not change. Even if no cascade chaining options
+achieves the same production rate as direct enrichment, the model B with tail
+recycling reached about $80\%$ of the optimum production rate. Such production
+rate would allow the build up of a Significant Quantity of \gls{HEU} in less
+than 8 months\ldots
 
@@
 While mathematically correct, the authors do not guaranty the feasibility
-different misuse tuning methods implemented and are welcoming any insight on
-the matter.
+different misuse tuning methods implemented and are welcoming any insight on the
+matter.

### 2018-06-28 experiement.tex
finish with gonuke comments

@@
 
-\subsubsection{reference}
+\subsubsection{Reference}
 
@@
 
-\subsubsection{default cascade}
+\subsubsection{Default cascade}
 
@@
 to $0.3w\%$. This cascade will be layered and fed with uranium at higher
-enrichment to evaluate the possibility to used them, with few or no tuning, to
+enrichment to evaluate the possibility to use them, with little or no tuning, to
 produce \gls{HEU}. The characteristics of the default cascade are summarized in
@@
 
-\subsection{scenarios}
+\subsection{Scenarios}
 In the following, cascades can be connected in tandem, where each set of cascade
@@
 \begin{itemize}
-\item one as the reference calculation, with a single centrifuges designed to
+\item one as the reference calculation, with a single cascade designed to
     directly produce \gls{HEU} from natural uranium,
-\item three calculations (one per misuse model) were default cascade are
-    chained to produce \gls{HEU}, without recycling the tails of each cascade,
-    the cascade tails are directly sent to the waste,
-\item three calculations (one per misuse model) were default cascade are
+\item three calculations (one per misuse model) where default cascade are
+    chained to produce \gls{HEU}, without recycling the tails of each cascade
+    sending their tails to the waste,
+\item three calculations (one per misuse model) where default cascade are
     chained to produce \gls{HEU}, and the tails of each cascade are recycled, blending
@@
     \caption{Schematic representation of the chained cascades with three levels,
-    with the feed, product and the tails flows, respectively in blue, green and
-    red. The dashed orange line represent the alternative tails flow when
+    with the feed, product and the tails flows, in blue, green and red,
+    respectively. The dashed orange line represent the alternative tails flow when
     tails recycling is considered.}
@@
 As it is not possible to assign a fraction of an enrichment cascade, cascade per
-level are rounded up for each level but the first one. To the first level is
-attributed the remaining available cascades.
+level are rounded up for each level but the first one. The remaining available
+cascades is attributed to the first level.
 
@@
 before it starts to enrich uranium, where $n$ corresponds to the level number.
-This corresponds to the time required for the material to propagate from the
-natural uranium source to the n-th level, regardless of the duration of the
-timestep (hour, day, month,...). This is also true for the number of timesteps
-required to reach the equilibrium assays value in the tails reprocessing cases.
-As timestep can be artificially small or large, one will only be considering
-equilibrium values flow rates and assays in the following analysis.
+This corresponds to the number of timesteps required for the material to
+propagate from the natural uranium source to the n-th level, regardless of the
+duration of the timestep (hour, day, month,...). This is also true for the
+number of timesteps required to reach the equilibrium assays value in the tails
+reprocessing cases.  As timestep can be artificially small or large, one will
+only be considering equilibrium values flow rates and assays in the following
+analysis.

### 2018-06-28 results.tex
finish with gonuke comments

@@
         &            & Tails     & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$ \\
-        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
+        & Cascades   &           & 25        & 25        & 25        & 24        & 25        & 25        \\
 \midrule                                                                                                 
@@
         &            & Tails     & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$ \\
-        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
+        & Cascades   &           & 3         & 4         & 3         & 4         & 3         & 4         \\
 \midrule                                                                                                 
@@
         &            & Tails     & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
-        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.32      & 0.35      \\
+        & Cascades   &           & 1         & 1         & 1         & 1         & 1         & 1         \\
 \midrule                                                                                                 
@@
         &            & Tails     & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
-        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
+        & Cascades   &           & 1         & N.A.      & 1         & 1         & 1         & N.A.      \\
 \bottomrule
@@
 4/23/78/98 and 4/23/82/99, the model B, the enrichment gain is only
-4/21/61/90.  Similar effects can be observed when recycling the tails\ldots
+4/21/61/90.
 
@@
 
-As shown on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
+As shown in Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
 \ref{sfig:case3_R}, recycling the tails increases the overall product assay at
-all the different levels. As the tails assay of a level $n$ is always higher than
-the product assay of the level $n-2$, recycling the tails of level $n$ will
-consequently increase the feed assay of level $n-1$ (see Table \ref{tab:level}).
+all the different levels. As the tails assay of a level $n+1$ is always higher than
+the product assay of the level $n-1$, recycling the tails of level $n+1$ will
+consequently increase the feed assay of level $n$ (see Table \ref{tab:level}).
 Moreover, with an increased feed assay, tails and product assays increase as
-well, increasing de facto the feed assays of respectively cascade levels $n-2$
-and $n$...  This effect reduces the number of cascade levels required to reach
+well, increasing de facto the feed assays of respectively cascade levels $n-1$
+and $n+1$, etc.  This effect reduces the number of cascade levels required to reach
 \gls{HEU} in case A and C.
@@
 
-As shown Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
+As shown in Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
 production rate, from $2$ to almost $20$ kg/y when using model A and C, and from
@@
     \includegraphics[scale=0.25]{HEU_prod_rate}
-    \caption{Production rate for the different model configuration, with in blue
-    the case without tails recycling, in orange with tails recycling, and in green
-    the reference one. Where A-B-C represent the model used, and NR-R
-    respectively the case without tails recycling and the case with tails recycling}
+    \caption{Production rate at equilibrium for the different model
+        configurations, the case without tails recycling (blue), with tails
+        recycling (orange), and the reference one (green). A-B-C represent
+        the model used, and NR-R the case without tails recycling and the case
+        with tails recycling, respectively.}
     \label{fig:HEU_rate}

### 2018-06-28 theory.tex
finish with gonuke comments

@@
 \begin{equation}\label{eq:gamma_p}
-\gamma(1-N')(P\theta-N) - N'(1-(N'\theta-N)/(-1+\theta))(-1+\theta) = 0
+    \theta(\gamma-1)N'^2+((N+\theta)(\gamma-1)+1)N'-N\gamma = 0
 \end{equation}
@@
 \begin{equation}\label{eq:model_b_sol}
-    \frac{\gamma(N + \theta) - N 
-            - \sqrt{\gamma^2(N^2 
-                            - 2N\theta 
-                            + \theta^2) 
-                    - \gamma(2N^2 - 2\theta^2 
-                            + 2N + 2\theta) 
-                    + N^2 + 2N\theta + \theta^2 - 2N - 2\theta + 1} 
-            - \theta + 1}
+    N' = \frac{N+\theta}{2\theta} +
+         \frac{1 - \sqrt{\gamma^{2}(N-\theta)^{2}
+                         + 2\gamma( N^{2} + N - \theta^{2} + \theta)
+                         + (N + \theta + 1)^{2}}}
               {2\theta(\gamma - 1)}
@@
 
-Similarly as model A, because the cut values remain constant, the flows don't
+Similar to model A, because the cut values remain constant, the flows don't
 need to be recomputed, and the correct assays, $\alpha$ and $\beta$ are

### 2018-06-28 experiement.tex
finxing typos

@@
 In the following, cascades can be connected in tandem, where each set of cascade
-in parallel is called a ``level``, as illustrated on Figure
+in parallel is called a ``level``, as illustrated in Figure
 \ref{fig:cascade_level}.
@@
 
-As it can be observed on Figures \ref{fig:case1}, \ref{fig:case2} and
+As it can be observed in Figures \ref{fig:case1}, \ref{fig:case2} and
 \ref{fig:case3}, the different cascade levels required up to $2n+1$ timesteps
@@
 This corresponds to the number of timesteps required for the material to
-propagate from the natural uranium source to the n-th level, regardless of the
-duration of the timestep (hour, day, month,...). This is also true for the
+propagate from the natural uranium source to the $n$-th level, regardless of the
+duration of the timestep (hour, day, month, etc.). This is also true for the
 number of timesteps required to reach the equilibrium assays value in the tails
 reprocessing cases.  As timestep can be artificially small or large, one will
-only be considering equilibrium values flow rates and assays in the following
+only be considering equilibrium values of flow rates and assays in the following
 analysis.

### 2018-06-28 results.tex
finxing typos

@@
 
-As illustrated on Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
+As illustrated in Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
 \ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
@@
 As shown in Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
-production rate, from $2$ to almost $20$ kg/y when using model A and C, and from
+production rate, from $2$ to almost $20$ kg/y when using models A and C, and from
 $17$ to $38$ kg/y with the model B. For the reference calculation where all the
@@
 
-As Model A and C, relies on maintaining the cut values at each stages of the
+As models A and C, rely on maintaining the cut values at each stages of the
 cascade and share the same number of levels, have the exact same cascade

### 2018-06-28 abstract.tex
additional fix

@@
 as a function of the cascade feed assay. As those four parameters depend on each
-other, determining two of them allows to fully define the other.  The first
-approach consists of fixing $\theta$ and $\alpha$ recomputing the corresponding
-assays at each stages of the cascade. The second one maintains the ideal
-condition of the cascade ($\alpha$ and $\beta$ fixed across the whole cascade),
-modifying $\theta$ value at each stage accordingly. Both approaches have been
-implemented into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The
-third fixes $\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage
-as free parameters. The third method has been investigated in
-\cite{walker.2017}.
+other, determining two of them fully defines the other.  The first approach
+consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
+each stages of the cascade. The second one maintains the ideal condition of the
+cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
+$\theta$ value at each stage accordingly. Both approaches have been implemented
+into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
+$\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
+parameters. The third method has been investigated in \cite{walker.2017}.
 

### 2018-06-28 experiement.tex
additional fix

@@
 where, $j$ represents a level of cascade and $N_{j}$, $N'_{j}$ and $N''_{j}$
-respectively the feed, product and tails assay of the cascades at this level.
+the feed, product and tails assay, respectively, of the cascades at this level.
 
-A flow equation similar to \eqref{eq:flow} is then solve to get the optimum
+A flow equation similar to \eqref{eq:flow} is then solved to obtain the optimum
 number of cascade per level. When the tails are not recycled, the $(1-\theta)$

### 2018-06-28 theory.tex
finxing typos
additional fix

@@
 \midrule
-320    & $320$       & $1.8$  & $0.105$  & $1^{3}$ & $13$       & 2     & 1.0  \\
+320    & $320$       & $1.8$  & $0.105$  & $10^{3}$ & $13$       & 2     & 1.0  \\
 \bottomrule
@@
 process is repeated until the sum of the square difference in assays is smaller
-than $1^{-8}$.  As the cut remain fixed at each stage the flows do not need to
+than $10^{-8}$.  As the cut remain fixed at each stage the flows do not need to
 be recomputed.
@@
 order to maintain the $\alpha_i$ and $\beta_i$ at their original values
-(equation \eqref{eq:theta}). As the cascade remains ideal, the product and tails
+(equation \eqref{eq:theta}). The cascade remaining ideal, the product and tails
 assay at each stages are easily determined using equations \eqref{eq:alphabeta}.
@@
 As the cut values change, the relative flow rates between the different stage
-are recomputed using equation \eqref{eq:flow}. The new flows are also
-constrained by the fixed design of the cascade, number of centrifuges limiting
-the flow at each level.
+are recomputed using equation \eqref{eq:flow}. The flow rates are determinted as
+the largest flow rates allowed by the cascade design, number of centrifuges
+limiting the flow at each stage.
 
@@
 constant regardless to the feed assays. To compute the response of the cascade
-one need to determine $\alpha$ and $\beta$ such as their product and
+one need to determine $\alpha$ and $\beta$ such that their product and
 $\theta$ remain fixed. 

### 2018-06-29 results.tex
fix inconsistancy in the assay values...

@@
 \midrule                                                                                                 
-        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
-Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
-        &            & Tails     & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$ \\
+        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.33w\%$ \\
+Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $4.82w\%$ \\
+        &            & Tails     & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
         & Cascades   &           & 25        & 25        & 25        & 24        & 25        & 25        \\
 \midrule                                                                                                 
-        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
-Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $69.8w\%$ \\
-        &            & Tails     & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$ \\
+        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $12.2w\%$ \\
+Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $58.5w\%$ \\
+        &            & Tails     & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
         & Cascades   &           & 3         & 4         & 3         & 4         & 3         & 4         \\
 \midrule                                                                                                 
-        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $72.6w\%$ \\
-Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $98.4w\%$ \\
-        &            & Tails     & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
+        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $58.5w\%$ \\
+Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $97.0w\%$ \\
+        &            & Tails     & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
         & Cascades   &           & 1         & 1         & 1         & 1         & 1         & 1         \\

### 2018-06-29 results.tex
new figures

@@
 
-As illustrated in Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
-\ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
-don't have the same effect on the cascade behavior. While the models A and C,
-allow a quick enrichment gain, with the cascades chaining, respectively
-4/23/78/98 and 4/23/82/99, the model B, the enrichment gain is only
-4/21/61/90.
+As illustrated in Figures \ref{fig:assays} and summarized on Tab
+\ref{tab:level}, the different model don't have the same effect on the cascade
+behavior. While the models A and C, allow a quick enrichment gain, with the
+cascades chaining, respectively 4/23/78/98 and 4/23/82/99, the model B, the
+enrichment gain is only 4/21/61/90.
 
@@
         \centering
-        \includegraphics[scale=0.17]{NR_case1}
-        \caption{No tails recycling}
-        \label{sfig:case1_NR}
+        \includegraphics[scale=0.2]{feed_assays}
+        \caption{Feed Assays.}
+        \label{sfig:feed_assay}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[scale=0.17]{R_case1}
-        \caption{Tails recycling}
-        \label{sfig:case1_R}
+        \includegraphics[scale=0.2]{product_assays}
+        \caption{Product Assays.}
+        \label{sfig:product_assay}
     \end{subfigure}
-    \caption{Evolution of the product assays at each level with considering
-    misuse model A, with (right) and without recycling (left).}
-    \label{fig:case1}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
     \begin{subfigure}[t]{0.45\textwidth}
         \centering
-        \includegraphics[scale=0.17]{NR_case2}
-        \caption{No tails recycling}
-        \label{sfig:case2_NR}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.45\textwidth}
-        \centering
-        \includegraphics[scale=0.17]{R_case2}
-        \caption{Tails recycling}
-        \label{sfig:case2_R}
+        \includegraphics[scale=0.2]{tails_assays}
+        \caption{Tails Assays.}
+        \label{sfig:tails_assay}
     \end{subfigure}
-    \caption{Evolution of the product assays at each level with considering
-    misuse model B, with (right) and without recycling (left).}
-    \label{fig:case2}
+    \caption{Feed (\subref{sfig:feed_assay}), product
+        (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
+        in $m\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
+        blue), per model (A/B/C) and without/with tails recycling (NR/R).}
+    \label{fig:assays}
 \end{figure}
@@
 
-As shown in Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
-\ref{sfig:case3_R}, recycling the tails increases the overall product assay at
+As shown in Figures \ref{fig:assays}, recycling the tails increases the overall product assay at
 all the different levels. As the tails assay of a level $n+1$ is always higher than
@@
 \gls{HEU} in case A and C.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}[t]{0.45\textwidth}
-        \centering
-        \includegraphics[scale=0.17]{NR_case3}
-        \caption{No tails recycling}
-        \label{sfig:case3_NR}
-    \end{subfigure}%
-    \begin{subfigure}[t]{0.45\textwidth}
-        \centering
-        \includegraphics[scale=0.17]{R_case3}
-        \caption{Tails recycling}
-        \label{sfig:case3_R}
-    \end{subfigure}
-    \caption{Evolution of the product assays at each level with considering
-    misuse model C, with (right) and without recycling (left).}
-    \label{fig:case3}
-\end{figure}
 

### 2018-06-29 experiement.tex
add model explanation

@@
 
-As it can be observed in Figures \ref{fig:case1}, \ref{fig:case2} and
-\ref{fig:case3}, the different cascade levels required up to $2n+1$ timesteps
+The different cascade levels required up to $2n+1$ timesteps
 before it starts to enrich uranium, where $n$ corresponds to the level number.

### 2018-06-29 results.tex
add model explanation

@@
         in $m\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
-        blue), per model (A/B/C) and without/with tails recycling (NR/R).}
+        blue), per model (A/B/C) and without/with tails recycling (NR/R). The
+        black dashed line represents the $90 m\%$ enrichment threshold.}
     \label{fig:assays}

### 2018-06-29 theory.tex
add model explanation

@@
 
+This model assumes that it is possible to maintain the separative power of a
+centrifuges, $\delta U$, for any feed assays $N$ while maintaining its cut
+$\theta$ and feed flow $F$.
+
 \subsubsection{Model B}
@@
 limiting the flow at each stage.
+
+This model assumes that it is possible to tune a centrifuge separative power
+$\delta U$, for any feed assay $N$, cut $\theta$ and feed flow $F$, in order to
+maintain its constant feed to product enrichment factor $\alpha$.
 
@@
 \eqref{eq:model_b_sol}.
+
+This model assumes that it is possible to tune the centrifuge separative power
+$\delta U$ in order to maintain, for any feed assay $N$, its tails to product
+enrichment factor $\gamma$, while maintaining its cut $\theta$ and feed flow
+$F$.

### 2018-07-05 abstract.tex
PPH comments 2

@@
 The goal of this work focuses on developing the necessary understanding of
-potential misuse of enrichment cascades. The latter would allow more effective
+potential misuse of enrichment cascades, contributing to more effective
 international safeguards designs and approaches.  While it is straightforward to
@@
 does not match the design value. Several methods have been developed to assess
-the behavior of an enrichment cascade in such circumstances. In addition of the
+the behavior of an enrichment cascade in such circumstances. In addition to the
 cut ($\theta$) those methods evaluate the feed to product, feed to tails and the

### 2018-07-05 dis_clusion.tex
PPH comments 2

@@
 when it is slightly retuned to maintain the tails to product enrichment factor
-as well as the cut of each centrifuges (Model C), chaining the cascade we can
-observe high increase of the enrichment at each level.  On the contrary, when
+as well as the cut of each centrifuges (Model C), chaining the cascade can
+achieve large increase of the enrichment at each level.  On the contrary, when
 retuning the cut of each centrifuges to maintain the ideal state of the cascades
@@
 recycling reached about $80\%$ of the optimum production rate. Such production
-rate would allow the build up of a Significant Quantity of \gls{HEU} in less
+rate would allow the accumulation of a Significant Quantity of \gls{HEU} in less
 than 8 months\ldots
 
-\section{Conclusion and future works}
+\section{Conclusion and futur work}
 
-This works has investigated and quantify the difference between potential
-retuning of a gaseous enrichment cascade in order to chain them to produce
+This work has investigated and quantified the difference between potential
+models for retuning of a centrifuge enrichment cascade in order to chain them to produce
 \gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
-One of this tuning method allows up to $80\%$ of the production rate of a single
+One of these tuning method achieves up to $80\%$ of the production rate of a single
 large enrichment cascade designed specifically for \gls{HEU} production using
@@
 
-This works will be extended to the near future with additional misuse method,
-allowing for example the reconfiguration of the centrifuges in the cascades.
+This work will be extended to the near future with additional misuse methods,
+allowing for example, the reconfiguration of the centrifuges in the cascades.
 
-For this study, the usage of the Cyclus fuel cycle simulator was not really
+For this study, the use of the Cyclus fuel cycle simulator was not
 required, it only allows a quick determination of the blending equilibrium. It
-is planned to make use of the Cyclus Dynamical Resource Exchange full capability
+is planned to make use of the full capability of Cyclus Dynamical Resource Exchange 
 in order to automatically assign the different cascades to the different level
@@
 
-While mathematically correct, the authors do not guaranty the feasibility
+While mathematically correct, the authors do not guaranty the feasibility of the
 different misuse tuning methods implemented and are welcoming any insight on the

### 2018-07-05 experiement.tex
PPH comments 2

@@
 \section{The experiment}
-This works focuses on comparing the different misuse models to a reference
+This work focuses on comparing the different misuse models to a reference
 calculation in which a single large cascade is build and designed to directly
@@
 In each cases, 5060 centrifuges have been used and spread across up to 30
-different gas enrichment cascades.
+different gas centrifuge enrichment cascades.
 
@@
 \midrule
-Stages    & Enriching  & 4          & 4          \\
-Number    & Stripping  & 39         & 10         \\
+Stages    & Stripping  & 4          & 4          \\
+Number    & Enriching  & 39         & 10         \\
 \bottomrule
@@
 \ref{fig:cascade_level}.
-Seven different simulations have been simulated, to evaluate the effectiveness
+The reseults from seven different simulations have been compared, to evaluate the effectiveness
 of an enrichment cascade when used outside of its designed scope :
@@
 \subsection{Level population}
-In order to assign the optimum number of cascades to each level, a virtual cut as
+In order to assign the optimum number of cascades to each level, a ``level cut'' as
 been computed as:
 \begin{equation}
-    \theta^{v}_{j} = \frac{F_{j}-N''_{j}}{N'_{j}-N''_{j}},
+    \Omega_{j} = \frac{N_{j}-N''_{j}}{N'_{j}-N''_{j}},
 \end{equation}
@@
 level are rounded up for each level but the first one. The remaining available
-cascades is attributed to the first level.
+cascades are attributed to the first level.
 
-\subsection{Timestep effect}
-
-The different cascade levels required up to $2n+1$ timesteps
-before it starts to enrich uranium, where $n$ corresponds to the level number.
-This corresponds to the number of timesteps required for the material to
-propagate from the natural uranium source to the $n$-th level, regardless of the
-duration of the timestep (hour, day, month, etc.). This is also true for the
-number of timesteps required to reach the equilibrium assays value in the tails
-reprocessing cases.  As timestep can be artificially small or large, one will
-only be considering equilibrium values of flow rates and assays in the following
-analysis.
+%% \subsection{Timestep effect}
+%% 
+%% The different cascade levels required up to $2n+1$ timesteps
+%% before it starts to enrich uranium, where $n$ corresponds to the level number.
+%% This corresponds to the number of timesteps required for the material to
+%% propagate from the natural uranium source to the $n$-th level, regardless of the
+%% duration of the timestep (hour, day, month, etc.). This is also true for the
+%% number of timesteps required to reach the equilibrium assays value in the tails
+%% reprocessing cases.  As timestep can be artificially small or large, one will
+%% only be considering equilibrium values of flow rates and assays in the following
+%% analysis.

### 2018-07-05 results.tex
PPH comments 2

--- 2018-06-29 results.tex
@@
         &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
-        & Cascades   &           & 25        & 25        & 25        & 24        & 25        & 25        \\
+        & Cascades   & Real(Ideal)& 25(26.7)  & 25(26.4)  & 25(26.6)  & 24(25.8)  & 25(26.7)  & 25(26.4)  \\
 \midrule                                                                                                 
@@
         &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
-        & Cascades   &           & 3         & 4         & 3         & 4         & 3         & 4         \\
+        & Cascades   & Real(Ideal)& 3(2.9)    & 4(3.2)    & 3(2.9)    & 4(3.4)    & 3(2.9)    & 4(3.2)    \\
 \midrule                                                                                                 
@@
         &            & Tails      & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
-        & Cascades   &           & 1         & 1         & 1         & 1         & 1         & 1         \\
+        & Cascades   & Real(Ideal)& 1(0.3)    & 1(0.3)    & 1(0.4)    & 1(0.6)    & 1(0.3)    & 1(0.35)   \\
 \midrule                                                                                                 
@@
         &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
-        & Cascades   &           & 1         & N.A.      & 1         & 1         & 1         & N.A.      \\
+        & Cascades   & Real(Ideal)& 1(0.03)   & N.A.      & 1(0.08)   & 1(0.2)    & 1(0.03)   & N.A.      \\
 \bottomrule
@@
 \ref{tab:level}, the different model don't have the same effect on the cascade
-behavior. While the models A and C, allow a quick enrichment gain, with the
-cascades chaining, respectively 4/23/78/98 and 4/23/82/99, the model B, the
-enrichment gain is only 4/21/61/90.
+behavior. While the models A and C, achieve a quick enrichment gain, with the
+cascades chaining, 4/23/78/98 and 4/23/82/99 respectively, model B, only
+achieves an enrichment gain of 4/21/61/90.
 
@@
         (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
-        in $m\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
-        blue), per model (A/B/C) and without/with tails recycling (NR/R).}
+        in $w\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
+        blue), per model (A/B/C) and without/with tails recycling (NR/R). The
+        black dashed line represents the $90 w\%$ enrichment threshold.}
     \label{fig:assays}
@@
 
-\subsection{\gls{HEU} Production}
+\subsection{\gls{HEU} Production Rate}
 

### 2018-07-05 theory.tex
PPH comments 2

@@
 which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
-$\alpha$ and $\beta$ respectively represent the feed to product and the feed to
-tails enrichment factors.  $\alpha$ and $\beta$ can be expressed as function of
+$\alpha$ and $\beta$ represent the feed to product and the feed to
+tails enrichment factors respectively.  $\alpha$ and $\beta$ can be expressed as function of
 the abundance ($R$) or the enrichment ($N$) of respectively the product
@@
 \begin{bmatrix}
-     -1        & 1-\theta_{_{S+1}} & 0 & ...  & 0              & 0              & 0                 & 0                 & 0                 & ...  & 0               & 0 \\
- \theta_{_{S}} & -1                & 0 & ...  & 0              & 0              & 0                 & 0                 & 0                 & ...  & 0               & 0 \\
-               &                   &   &     &                &                & ...               &                   &                   &     &                 &   \\
- 0             & 0                 & 0 & ...  & \theta_{_{-2}} & -1             & 1 - \theta_{_{0}} & 0                 & 0                 & ...  & 0               & 0 \\
- 0             & 0                 & 0 & ...  & 0              & \theta_{_{-1}} & -1                & 1 - \theta_{_{1}} & 0                 & ...  & 0               & 0 \\
- 0             & 0                 & 0 & ...  & 0              & 0              & \theta_{_{0}}     & -1                & 1 - \theta_{_{2}} & 0   & ...             & 0 \\
-               &                   &   &     &                &                & ...               &                   &                   &     &                 &   \\
- 0             & 0                 & 0 & ...  & 0              & 0              & 0                 & 0                 & 0                 & ...  & -1              & 1-\theta_{_{E}} \\
- 0             & 0                 & 0 & ...  & 0              & 0              & 0                 & 0                 & 0                 & ...  & \theta_{_{E-1}} & -1
+     -1      & 1-\theta_{_{S+1}} & 0                 & ...  & 0            & 0            & 0             & 0             & 0             & ... & 0               & 0  & 0 \\
+\theta_{_S}  & -1                & 1-\theta_{_{S+2}} & ...  & 0            & 0            & 0             & 0             & 0             & ... & 0               & 0  & 0 \\
+             &                   &                   &      &              &              & ...           &               &               &     &                 &    &   \\
+ 0           & 0                 & 0                 & ...  & \theta_{_-2} & -1           & 1-\theta_{_0} & 0             & 0             & ... & 0               & 0  & 0 \\
+ 0           & 0                 & 0                 & ...  & 0            & \theta_{_-1} & -1            & 1-\theta_{_1} & 0             & ... & 0               & 0  & 0 \\
+ 0           & 0                 & 0                 & ...  & 0            & 0            & \theta_{_0}   & -1            & 1-\theta_{_2} & ... & 0               & 0  & 0 \\
+             &                   &                   &      &              &              & ...           &               &               &     &                 &    &   \\
+ 0           & 0                 & 0                 & ...  & 0            & 0            & 0             & 0             & 0             & ... & \theta_{_{E-2}} & -1 & 1-\theta_{_E} \\
+ 0           & 0                 & 0                 & ...  & 0            & 0            & 0             & 0             & 0             & ... & 0               & \theta_{_{E-1}} & -1
  \end{bmatrix}
@@
 Little information is available about optimising an existing enrichment cascade
-that is being fed with a feed enrichment that does not match the design one. So
-far 3 different methods have been investigated.
+that is being fed with a feed enrichment that does not match the design
+enrichment. So far 3 different methods have been investigated.
 
-The first one assumes that no change are been made on the cascade, i.e $\delta
+The first one assumes that no change are been made to the cascade, i.e $\delta
 U$, $F$ and $\theta$ are fixed across all stages. The second one assumes the cut

### 2018-07-05 dis_clusion.tex
new proposition for Model B scaling description

@@
 
-\section{Conclusion and futur work}
+\section{Conclusion and future work}
 
-This work has investigated and quantified the difference between potential
-models for retuning of a centrifuge enrichment cascade in order to chain them to produce
-\gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
-One of these tuning method achieves up to $80\%$ of the production rate of a single
+This work has investigated the possibility to chain centrifuge enrichment
+cascades designed to enrich uranium for commercial reactors in order to
+produce \gls{HEU}. Three methods have been implemented to model enrichment
+cascade behavior when fed with different uranium enrichment than the designed
+enrichment.
+
+%% This work has investigated and quantified the difference between potential
+%% models for retuning of a centrifuge enrichment cascade in order to chain them to produce
+%% \gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
+One of these method achieves up to $80\%$ of the production rate of a single
 large enrichment cascade designed specifically for \gls{HEU} production using

### 2018-07-05 theory.tex
new proposition for Model B scaling description

@@
 As the cut values change, the relative flow rates between the different stage
-are recomputed using equation \eqref{eq:flow}. The flow rates are determinted as
-the largest flow rates allowed by the cascade design, number of centrifuges
-limiting the flow at each stage.
+are recomputed using equation \eqref{eq:flow}. 
+The new relative flow rates are compared stage by stage to the flow rates allowed by the
+cascade design, the number of centrifuges per stage limiting the flow. The new
+absolute flow rates are computed by scaling the relative flow rates using the most
+limiting stage.
+
+%% The flow rates are determinted as
+%% the largest flow rates allowed by the cascade design, number of centrifuges
+%% limiting the flow at each stage.
 

### 2018-07-17 dis_clusion.tex

@@
 This work has investigated the possibility to chain centrifuge enrichment
-cascades designed to enrich uranium for commercial reactors in order to
-produce \gls{HEU}. Three methods have been implemented to model enrichment
+cascades that are designed to enrich uranium for commercial reactors in order to
+produce \gls{HEU}, instead. Three methods have been implemented to model enrichment
 cascade behavior when fed with different uranium enrichment than the designed
@@
 
-For this study, the use of the Cyclus fuel cycle simulator was not
-required, it only allows a quick determination of the blending equilibrium. It
-is planned to make use of the full capability of Cyclus Dynamical Resource Exchange 
-in order to automatically assign the different cascades to the different level
-as function of the resources availability, optimising the productions rates in
-each cases.
+For this study, the use of the Cyclus fuel cycle simulator was not required;
+it only allows a quick determination of the blending equilibrium. Future
+studies will make use of the full capability of Cyclus Dynamic Resource
+Exchange in order to automatically assign the different cascades to the
+different level as function of the resources availability, optimising the
+productions rates in each cases.
 

### 2018-07-17 results.tex

@@
         &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
-        & Cascades   & Real(Ideal)& 25(26.7)  & 25(26.4)  & 25(26.6)  & 24(25.8)  & 25(26.7)  & 25(26.4)  \\
+        & Cascades   & Impl. (Ideal)& 25(26.7)  & 25(26.4)  & 25(26.6)  & 24(25.8)  & 25(26.7)  & 25(26.4)  \\
 \midrule                                                                                                 
@@
         &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
-        & Cascades   & Real(Ideal)& 3(2.9)    & 4(3.2)    & 3(2.9)    & 4(3.4)    & 3(2.9)    & 4(3.2)    \\
+        & Cascades   & Impl. (Ideal)& 3(2.9)    & 4(3.2)    & 3(2.9)    & 4(3.4)    & 3(2.9)    & 4(3.2)    \\
 \midrule                                                                                                 
@@
         &            & Tails      & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
-        & Cascades   & Real(Ideal)& 1(0.3)    & 1(0.3)    & 1(0.4)    & 1(0.6)    & 1(0.3)    & 1(0.35)   \\
+        & Cascades   & Impl. (Ideal)& 1(0.3)    & 1(0.3)    & 1(0.4)    & 1(0.6)    & 1(0.3)    & 1(0.35)   \\
 \midrule                                                                                                 
@@
         &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
-        & Cascades   & Real(Ideal)& 1(0.03)   & N.A.      & 1(0.08)   & 1(0.2)    & 1(0.03)   & N.A.      \\
+        & Cascades   & Impl. (Ideal)& 1(0.03)   & N.A.      & 1(0.08)   & 1(0.2)    & 1(0.03)   & N.A.      \\
 \bottomrule
@@
 
-As illustrated in Figures \ref{fig:assays} and summarized on Tab
-\ref{tab:level}, the different model don't have the same effect on the cascade
-behavior. While the models A and C, achieve a quick enrichment gain, with the
-cascades chaining, 4/23/78/98 and 4/23/82/99 respectively, model B, only
-achieves an enrichment gain of 4/21/61/90.
+As illustrated in Figures \ref{fig:assays} and summarized on Table
+\ref{tab:level}, the different models don't have the same effect on the
+cascade behavior. While models A and C, achieve a quick enrichment gain with
+the cascades chaining, 4/23/78/98 and 4/23/82/99, respectively, model B, only
+achieves an enrichment gain of 4/21/61/90.  This table also shows the integer
+number of cascades implemented (Impl.) at each level in the simulation, as well as the
+non-integer number of cascades that would achieve an ideal configuration (Ideal).
 

### 2018-07-17 theory.tex

@@
 
-As the cut values change, the relative flow rates between the different stage
-are recomputed using equation \eqref{eq:flow}. 
-The new relative flow rates are compared stage by stage to the flow rates allowed by the
-cascade design, the number of centrifuges per stage limiting the flow. The new
-absolute flow rates are computed by scaling the relative flow rates using the most
-limiting stage.
+As the cut values change, the relative flow rates between the different stages
+are recomputed using equation \eqref{eq:flow}.  Under this model, the flow at
+each stage of the original ideal cascade is assumed to be the maximum flow
+allowed at that stage.  Therefore, all of the recomputed flow rates are scaled
+together to ensure that no stage experiences a flow rate larger than that of
+the original cascade.  Some stages may now experience flow rates much lower
+than the original cascade.
 

### 2018-07-17 abstract.tex
new production figure + addition of symetric adjectif when refering to cascade design

@@
 international safeguards designs and approaches.  While it is straightforward to
-design an enrichment cascade under ideal conditions as a function of the
+design an symmetric enrichment cascade under ideal conditions as a function of the
 theoretical feed, product and tails assays, it is very difficult to find
@@
 each approach, this work compares the results produced by these methods within
-scenarios involving misuse of enrichment cascades simulated using the dynamic
+scenarios involving misuse of symmetric enrichment cascades simulated using the dynamic
 nuclear fuel cycle simulator, Cyclus.

### 2018-07-17 dis_clusion.tex
new production figure + addition of symetric adjectif when refering to cascade design

@@
 cascades that are designed to enrich uranium for commercial reactors in order to
-produce \gls{HEU}, instead. Three methods have been implemented to model enrichment
-cascade behavior when fed with different uranium enrichment than the designed
-enrichment.
+produce \gls{HEU}, instead. Three methods have been implemented to model
+symmetric enrichment cascade behavior when fed with different uranium enrichment
+than the designed enrichment.
 

### 2018-07-17 motivation.tex
new production figure + addition of symetric adjectif when refering to cascade design

@@
 With the current international tensions regarding enrichment capabilities, this
-work aims to measure the effectiveness of an enrichment cascade when used outside of
-its designed scope and quantify the attractiveness of such way to build up
-significant quantity of \gls{HEU}.
+work aims to measure the effectiveness of an symmetric enrichment cascade when
+used outside of its designed scope and quantify the attractiveness of such way
+to build up significant quantity of \gls{HEU}.
 

### 2018-07-17 theory.tex
new production figure + addition of symetric adjectif when refering to cascade design

@@
 
-The cascade is built as an ideal cascade, with no losses in the separative work,
+The cascade is built as a ideal symmetric cascade, with no losses in the separative work,
 which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
@@
 
-The design of the cascade is performed through 2 steps.  First one determines
-the configuration and number of stages, adding stages until the product assay of
-the final stage is greater or equal the product targeted assay, and similarly
-the tails assay is less or equal the tails desired assay.  This determines the
-number of enriching and stripping stages as well as their enrichment properties
-($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).
+The design of the ideal symmetric cascade is performed through 2 steps.  First
+one determines the configuration and number of stages, adding stages until the
+product assay of the final stage is greater or equal the product targeted assay,
+and similarly the tails assay is less or equal the tails desired assay.  This
+determines the number of enriching and stripping stages as well as their
+enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).
 

### 2018-07-17 motivation.tex
fix grammar

--- 2018-06-27 motivation.tex
@@
 With the current international tensions regarding enrichment capabilities, this
-work aims to measure the effectiveness of an enrichment cascade when used outside of
-its designed scope and quantify the attractiveness of such way to build up
-significant quantity of \gls{HEU}.
+work aims to measure the effectiveness of a symmetric enrichment cascade when
+used outside of its designed scope and quantify the attractiveness of such way
+to build up significant quantity of \gls{HEU}.
 

### 2018-07-17 theory.tex
fix grammar

@@
 
-The cascade is built as a ideal symmetric cascade, with no losses in the separative work,
+The cascade is built as a symmetric ideal cascade, with no losses in the separative work,
 which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where

### 2018-07-17 abstract.tex

@@
 international safeguards designs and approaches.  While it is straightforward to
-design an symmetric enrichment cascade under ideal conditions as a function of the
+design a symmetric enrichment cascade under ideal conditions as a function of the
 theoretical feed, product and tails assays, it is very difficult to find

### 2018-07-17 experiement.tex

@@
 favorable configuration to produce \gls{HEU}, where all the available
-centrifuges are used in a single large cascade designed to directly produce
-\gls{HEU} from natural uranium, with a tails assay close to $0.3w\%$. The design
-characteristic of the reference cascade are summarized in Table
-\ref{tab:cascade_config}.
+centrifuges are used in a single large ideal symmetric cascade designed to
+directly produce \gls{HEU} from natural uranium, with a tails assay close to
+$0.3w\%$. The design characteristic of the reference cascade are summarized in
+Table \ref{tab:cascade_config}.
 
@@
 
-The default cascade is the cascade design for normal civilian enrichment
-operation, enriching natural uranium to about $3.5w\%$, with a tails assay close
-to $0.3w\%$. This cascade will be layered and fed with uranium at higher
-enrichment to evaluate the possibility to use them, with little or no tuning, to
-produce \gls{HEU}. The characteristics of the default cascade are summarized in
-Table \ref{tab:cascade_config}.
+The default cascade is the ideal symmetric cascade designed for normal civilian
+enrichment operation, enriching natural uranium to about $3.5w\%$, with a tails
+assay close to $0.3w\%$. This cascade will be layered and fed with uranium at
+higher enrichment to evaluate the possibility to use them, with little or no
+tuning, to produce \gls{HEU}. The characteristics of the default cascade are
+summarized in Table \ref{tab:cascade_config}.
 

### 2018-07-20 paper.tex
new figures

--- 2018-05-25 paper.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{}
+\title{Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations}
 \author{Baptiste Mouginot, Kathryn Mummah, Paul P.H.  Wilson}
@@
 \newacronym{SFR}{SFR}{fast breeder reactor}
+\newacronym{OFAT}{OFAT}{one-factor-at-a-time}
 
@@
 uncertainty due to the simplifications and approximations built in to the
-simulator itself, and data uncertainty from the quantities provided by the
-user. This work focuses on a subset the data uncertainty related to
-the user input that defines the performance of the simulated facilities.
+simulator itself, and data uncertainty from the quantities provided by the user.
+This work focuses on a subset the data uncertainty related to the user input
+that defines the performance of the simulated facilities.
 
@@
 verification.  Some scenarios require estimating historical fissile material
-production based on records of facility operation and material transfer.  If
-the measurements of facility operation and material transfer are subject to
+production based on records of facility operation and material transfer.  If the
+measurements of facility operation and material transfer are subject to
 uncertainty, the total production quantities will then also be uncertain.  Any
@@
 
-This study seeks to understand which characteristics of facility operation have the
-most impact on the uncertainty of fissile material production across a complete
-fuel cycle.  Uncertainty propagation using a Monte Carlo method will be applied
-to the Cyclus fuel cycle simulator \cite{cyclus} to estimate the effect of
-individual facility uncertainties on the output metrics. The same simulation
-will be performed $N$ times, with some input parameters randomly determined in each case.
-The distribution of each output metrics over the N trials of the simulation
-will be used to estimate their
-respective uncertainty.
+This study seeks to understand which characteristics of facility operation have
+the most impact on the uncertainty of fissile material production across a
+complete fuel cycle.  Uncertainty propagation using a Monte Carlo method will be
+applied to the Cyclus fuel cycle simulator \cite{cyclus} to estimate the effect
+of individual facility uncertainties on the output metrics. The same simulation
+will be performed $N$ times, with some input parameters randomly determined in
+each case.  The distribution of each output metrics over the N trials of the
+simulation will be used to estimate their respective uncertainty.
 
@@
 
-To estimate the uncertainty of fuel cycle output metrics, a Monte
-Carlo approach has been applied.  In each of 199 independent simulations,
-some of the parameters that define facility behavior are randomly selected
-from Normal distributions with standard deviations that are $10\%$ of the mean/nominal
+To estimate the uncertainty of fuel cycle output metrics, a Monte Carlo approach
+has been applied.  In each of 199 independent simulations, some of the
+parameters that define facility behavior are randomly selected from Normal
+distributions with standard deviations that are $10\%$ of the mean/nominal
 value.  This artificially large standard deviation is selected for the purpose
@@
 
-To pursue this work, both the Cycamore\footnote{Low
-fidelity facilities package for Cyclus}\cite{cycamore} and the
-CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models}\cite{mouginot_2018, cyclass} packages were
-updated to evaluate the uncertainty of several
-operational parameters in their associated facilities.  Table
-\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
-facilities of Cycamore and CyCLASS.
+To pursue this work, both the Cycamore\footnote{Low fidelity facilities package
+for Cyclus}\cite{cycamore} and the CyCLASS\footnote{Reactor and fuel fabrication
+facility based on CLASS\cite{CLASS} models}\cite{mouginot_2018, cyclass}
+packages were updated to evaluate the uncertainty of several operational
+parameters in their associated facilities.  Table \ref{tab:package_uncertainty}
+summarizes all uncertainty-tracking modifications implemented in the facilities
+of Cycamore and CyCLASS.
 
@@
 
-The uncertainty of the different parameters in this study
-are systematic for each new deployed facility: each time a new facility is
-deployed (such as a reactor or a fuel fabrication facility) a new set of
-parameters are sampled, and those parameters are used throughout the life
-of that facility.
+The uncertainty of the different parameters in this study are systematic for
+each new deployed facility: each time a new facility is deployed (such as a
+reactor or a fuel fabrication facility) a new set of parameters are sampled, and
+those parameters are used throughout the life of that facility.
 
 \subsection{The Fuel Cycle Scenario}
+
 For demonstration purposes, a simple commercial fuel cycle transition is used,
-inspired from the EG23 fuel cycle
-of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}.
-Pictured in Figure \ref{fig:cycle}, this is a
-transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a
-\gls{SFR} fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
-of the nuclear generated power (Figure \ref{fig:power}).
+inspired from the EG23 fuel cycle of the Nuclear Fuel Cycle Evaluation and
+Screening Report\cite{ES}.  Pictured in Figure \ref{fig:cycle}, this is a
+transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a \gls{SFR}
+fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth of the nuclear
+generated power (Figure \ref{fig:power}).
+
 \begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
@@
 composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
-transition starts around year 35, with the deployment of \glspl{SFR}. The \glspl{SFR} are loaded
-with \gls{MOX}, which consists of plutonium blended with natural
-uranium.
+transition starts around year 35, with the deployment of \glspl{SFR}. The
+\glspl{SFR} are loaded with \gls{MOX}, which consists of plutonium blended with
+natural uranium.
 
@@
 
-The plutonium, required for \gls{MOX} fabrication, is reprocessed from all
-used fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel
-as it becomes available for reprocessing.
+The plutonium, required for \gls{MOX} fabrication, is reprocessed from all used
+fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel as
+it becomes available for reprocessing.
 
-Both fuel reprocessing and fabrication have a constant maximum throughput, but may also be limited by the 
-availability input material.  The enrichment of the \gls{UOX} is processed
-on demand.  Buffer storage facilities (not shown in Figure \ref{fig:cycle}) are present
-between all facilities with constant throughput.
+Both fuel reprocessing and fabrication have a constant maximum throughput, but
+may also be limited by the availability input material.  The enrichment of the
+\gls{UOX} is processed on demand.  Buffer storage facilities (not shown in
+Figure \ref{fig:cycle}) are present between all facilities with constant
+throughput.
 
-In this work, a time step of 1 month has been considered, \ie each output
-metric is reported once per month. Additionally, decay processes have not be
-taken into account.
+In this work, a time step of 1 month has been considered, \ie each output metric
+is reported once per month. Additionally, decay processes have not be taken into
+account.
 
 It must be noted that for this work, the fuel enrichment was determined by a
-fuel fabrication model\cite{Leniau2015125} which
-calculates the fissile fraction required in the fuel to reach a given target
-burnup at the end of irradiation.  Therefore, the uncertainty of the fuel
-enrichment is not applied directly to the effective enrichment. It is instead applied to the
-burnup, resulting in a fuel enrichment uncertainty that is also close to
-$10\%$.
+fuel fabrication model\cite{Leniau2015125} which calculates the fissile fraction
+required in the fuel to reach a given target burnup at the end of irradiation.
+Therefore, the uncertainty of the fuel enrichment is not applied directly to the
+effective enrichment. It is instead applied to the burnup, resulting in a fuel
+enrichment uncertainty that is also close to $10\%$.
 
-For each of the parameters in Table \ref{tab:package_uncertainty}, a set of
-199 simulations was performed with only that parameter being randomly varied.
-An additional set of 199 simulations was performed in which all five
-parameters are randomly varied.  A reference simulation was performed
+For each of the parameters in Table \ref{tab:package_uncertainty}, a set of 199
+simulations was performed with only that parameter being randomly varied.  An
+additional set of 199 simulations was performed in which all five parameters are
+randomly varied, using \gls{OFAT} method.  A reference simulation was performed
 with all five parameters fixed at the mean value.
@@
 
-Because the main interests of nuclear archaeology involve highly enriched uranium production and
-fissile inventories, this study mainly focuses on the uncertainties of
-the total quantity of natural uranium used and the total unused fissile
-inventory (separated plutonium).
+Because the main interests of nuclear archaeology involve highly enriched
+uranium production and fissile inventories, this study mainly focuses on the
+uncertainties of the total quantity of natural uranium used and the total unused
+fissile inventory (separated plutonium).
 
@@
 from reprocessed used fuel, availability of that used fuel may impact the
-capability to build the required \gls{SFR}-\gls{MOX} fuel.  While there may be studies in
-which this would be an interesting result, in the context of this work, such
-shutdowns would be well-documented in the operational histories of the
-facilities and should not be characterized as an uncertainty.  Figure
-\ref{fig:power_full} shows that uncertainties in generated power are indeed
-very low.
+capability to build the required \gls{SFR}-\gls{MOX} fuel.  While there may be
+studies in which this would be an interesting result, in the context of this
+work, such shutdowns would be well-documented in the operational histories of
+the facilities and should not be characterized as an uncertainty.  Figure
+\ref{fig:power_full} shows that uncertainties in generated power are indeed very
+low.
 
@@
 Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
-dedicated to \gls{LWR}-\gls{UOX} fuel fabrication as a function of time.  The uncertainty on
-the cumulative uranium consumption grows as expected with the time and the
-loading of the \glspl{LWR}.  The increase stops around year 125y with the
-decommissioning of the last \glspl{LWR}.
+dedicated to \gls{LWR}-\gls{UOX} fuel fabrication as a function of time.  The
+uncertainty on the cumulative uranium consumption grows as expected with the
+time and the loading of the \glspl{LWR}.  The increase stops around year 125y
+with the decommissioning of the last \glspl{LWR}.
 
-As expected, cooling time, separation efficiency and thermal power do not
-affect the natural uranium consumption for \gls{LWR}-\gls{UOX} fuel production.  The uncertainty on the natural uranium
-consumption is dominated by the \gls{LWR} cycle length: shorter the cycle
-length is, the more fuel will be loaded, and \emph{vice versa}.
+As expected, cooling time, separation efficiency and thermal power do not affect
+the natural uranium consumption for \gls{LWR}-\gls{UOX} fuel production.  The
+uncertainty on the natural uranium consumption is dominated by the \gls{LWR}
+cycle length: shorter the cycle length is, the more fuel will be loaded, and
+\emph{vice versa}.
 
@@
 \end{figure}
+
 The relative uncertainty of the total uranium consumption starts at about
-$5.5\%$ a slowly drops and stabilize around $3\%$.
+$7\%$ a slowly drops and stabilize around $3\%$.
 
@@
 year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
-beginning of the simulation have synchronized fuel cycles, reloading in the same time step.
-This phenomenon disappears
-with the gradual decommissioning of the initial reactors, spread over 50 years.
+beginning of the simulation have synchronized fuel cycles, reloading in the same
+time step.  This phenomenon disappears with the gradual decommissioning of the
+initial reactors, spread over 50 years.
 
 The decrease of the cycle time uncertainty contribution, from year 30 to year
-90, can be understood as an averaging effect.  As the uncertainty are defined once
-per deployed facility, each reactor will have a different cycle
-length value, so a different number of batches loaded per year.  With the increase
-of deployed reactors, the number of batches of \gls{LWR} fuel loaded converges
-to the references one, reducing its impact on the uncertainty on the total
-uranium consumption. This uncertainty contribution to the overall uncertainty
-decrease is proportional to the number of \gls{LWR} reactors and stops with the
+90, can be understood as an averaging effect.  As the uncertainty are defined
+once per deployed facility, each reactor will have a different cycle length
+value, so a different number of batches loaded per year.  With the increase of
+deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
+the references one, reducing its impact on the uncertainty on the total uranium
+consumption. This uncertainty contribution to the overall uncertainty decrease
+is proportional to the number of \gls{LWR} reactors and stops with the
 decommission of the last one.
@@
 The fuel enrichment contribution follow a close to constant uncertainty
-contribution of $2\%$, so as the total relative uncertainty decrease, it
-has a growing shared of the total absolute uncertainty over time.
+contribution of $2\%$, so as the total relative uncertainty decrease, it has a
+growing shared of the total absolute uncertainty over time.
 
 \subsection{Fissile Inventory}
-The fissile inventory corresponds to the amount of separated fissile material waiting to
-be blended with natural uranium in order to produce the \gls{SFR}-\gls{MOX} fuel.
+
+The fissile inventory corresponds to the amount of separated fissile material
+waiting to be blended with natural uranium in order to produce the
+\gls{SFR}-\gls{MOX} fuel.
 
@@
 year 40, with the deployment of the first reprocessing facility.  It grows
-during the first period of the \glspl{LWR} to \gls{SFR}-A transition until
-year 90, then decrease slightly as the last \glspl{LWR} are decommissioned.
-When the steady state is reached (full \gls{SFR} fleet), the plutonium
-inventory starts to increase, as the breading ratio of the \glspl{SFR} is higher
-than the deployment needs.
+during the first period of the \glspl{LWR} to \gls{SFR}-A transition until year
+90, then decrease slightly as the last \glspl{LWR} are decommissioned.  When the
+steady state is reached (full \gls{SFR} fleet), the plutonium inventory starts
+to increase, as the breading ratio of the \glspl{SFR} is higher than the
+deployment needs.
 
@@
 At the onset of fissile material production, very low mean inventories lead to
-unreliable artifacts in the relative uncertainty.
-After that, the relative uncertainty
-starts at about $5\%$ and grows until year
-125, then decreases to $10\%$ at the end of the simulation time (180y).  
-Between year 40 and 70, the main contributor to the fissile inventory
-uncertainty is the cycle length.  As with the uranium needs, different cycle length
-implies different number of fuel loads, so different amount of resources used.  Nevertheless, around year 65 (see Figure
-\ref{fig:used_fuel}), the stock of used fuel available for reprocessing becomes
-small enough to start limiting the production of fissile material.
-The dominant contribution to the uncertainty then slowly transitions from
-the cycle length to the fuel cooling time.
+unreliable artifacts in the relative uncertainty.  After that, the relative
+uncertainty starts at about $5\%$ and grows until year 125, then decreases to
+$10\%$ at the end of the simulation time (180y).  Between year 40 and 70, the
+main contributor to the fissile inventory uncertainty is the cycle length.  As
+with the uranium needs, different cycle length implies different number of fuel
+loads, so different amount of resources used.  Nevertheless, around year 65 (see
+Figure \ref{fig:used_fuel}), the stock of used fuel available for reprocessing
+becomes small enough to start limiting the production of fissile material.  The
+dominant contribution to the uncertainty then slowly transitions from the cycle
+length to the fuel cooling time.
 
@@
 \end{figure}
+
 Between year 90 and 120, the \gls{SFR} deployment speed increases; it has to
 compensate the non-replacement of the decommissioned \glspl{LWR} as well as
-follow the growing power demand.  During this period the needs in plutonium are higher
-than its production, explaining the observed decrease of the total amount, and
-the increase associated relative uncertainty.
+follow the growing power demand.  During this period the needs in plutonium are
+higher than its production, explaining the observed decrease of the total
+amount, and the increase associated relative uncertainty.
 
@@
 It is also interesting to note that, the uncertainty contribution from the cycle
-length between year 40 and 70 comes mainly from fuel batch loading
-frequencies.  After 70 years this contribution follows the thermal
-power contribution closely, suggesting that fuel discharge burnup (\ie fuel
-discharge composition) is the mechanism of this contribution.
+length between year 40 and 70 comes mainly from fuel batch loading frequencies.
+After 70 years this contribution follows the thermal power contribution closely,
+suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
+mechanism of this contribution.
+
+Around the year 70, it is possible to observe the relative uncertainty related
+to cycle time being larger than the overall relative uncertainty. This effect is
+directly related to the \gls{OFAT} method used to estimate the individual
+uncertainty contribution. While allowing a quick access to the individual
+contribution, the \gls{OFAT} method does not capture coupling effect between the
+different parameters.
 
@@
 been able to estimate that the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas about
-$10\%$ uncertainty on the enrichment implies an almost constant uncertainty of $2\%$.
+variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas
+about $10\%$ uncertainty on the enrichment implies an almost constant
+uncertainty of $2\%$.
 
-Regarding the reprocessed fissile inventory, this study has shown the 
-impact of the reprocessed fuel compositions (through burnup variations) is
-limited to $\approx5\%$, while fuel availability constraints, such as fuel loading frequency (cycle
-time) or fissile materials available for fuel fabrication (cooling time) can lead to higher
-uncertainties, up to $10\%$ and to $30\%$, respectively.  Moreover, it is very
-interesting to observe the transition from one to the other around
-year 70.
+Regarding the reprocessed fissile inventory, this study has shown the impact of
+the reprocessed fuel compositions (through burnup variations) is limited to
+$\approx5\%$, while fuel availability constraints, such as fuel loading
+frequency (cycle time) or fissile materials available for fuel fabrication
+(cooling time) can lead to higher uncertainties, up to $10\%$ and to $30\%$,
+respectively.  Moreover, it is very interesting to observe the transition from
+one to the other around year 70.
 
@@
 natural uranium consumption and fissile inventory come from the parameters that
-govern the exchange of material between facilities, and not
-from the physical parameters that describe those facilities, such as thermal power or fuel enrichment. Further
-analysis should allow us to understand this further.
+govern the exchange of material between facilities, and not from the physical
+parameters that describe those facilities, such as thermal power or fuel
+enrichment. Further analysis should allow us to understand this further.
 
@@
 
-Two main points can be deduced from this work.  First, in a transitional
-fuel cycle, uncertainty contributions to output metrics can vary over time
-depending of various factors: deployment schedule artifacts or material flow constrictions.
+Two main points can be deduced from this work.  First, in a transitional fuel
+cycle, uncertainty contributions to output metrics can vary over time depending
+of various factors: deployment schedule artifacts or material flow
+constrictions.
 
@@
 length.  While some of those time related parameters will, to first order, only
-impact material availability (as the cooling time will do), others, like
-cycle length, will also have a impact as physical parameters such as fuel
-enrichment or thermal power.
+impact material availability (as the cooling time will do), others, like cycle
+length, will also have a impact as physical parameters such as fuel enrichment
+or thermal power.
 
-Cycle length impacts the discharge fuel burnup and  the frequency of
-the fuel loads.  When they combine to produce in uncertainty of the
-material availability, this could result in variations related to time delays that may
-contribute to the final uncertainty in ways that are not relevant to some analyses.
-That is, a simple time lag in a particular output that otherwise follows an identical history
-could manifest itself as a large variation at any particular time.
-Those kind of time related uncertainties will require a further analysis
-to understand and measure accurately their
-contributions to the total uncertainty.
+Cycle length impacts the discharge fuel burnup and  the frequency of the fuel
+loads.  When they combine to produce in uncertainty of the material
+availability, this could result in variations related to time delays that may
+contribute to the final uncertainty in ways that are not relevant to some
+analyses.  That is, a simple time lag in a particular output that otherwise
+follows an identical history could manifest itself as a large variation at any
+particular time.  Those kind of time related uncertainties will require a
+further analysis to understand and measure accurately their contributions to the
+total uncertainty.
 
@@
 relative contributions, it has only been applied to systematic uncertainties per
-facilities.
-This kind of study will to be extended to random uncertainty (new parameter
-values as a function of time) and completely systematic uncertainty (shared by all
-the facilities of a kind).
+facilities.  This kind of study will to be extended to random uncertainty (new
+parameter values as a function of time) and completely systematic uncertainty
+(shared by all the facilities of a kind).
 

### 2018-07-20 paper.tex
review correction

@@
 required in the fuel to reach a given target burnup at the end of irradiation.
-Therefore, the uncertainty of the fuel enrichment is not applied directly to the
-effective enrichment. It is instead applied to the burnup, resulting in a fuel
-enrichment uncertainty that is also close to $10\%$.
+The targeted burnup is a operational parameter and does not necessary related to the
+actual achieved burnup (computed from the real cycle length and the thermal
+power of the reactor). Therefore, the uncertainty of the fuel enrichment is not
+applied directly to the effective enrichment. It is instead applied to the
+targeted burnup, resulting in a fuel enrichment uncertainty that is also close
+to $10\%$.
 
@@
     \includegraphics[scale=0.3]{power_full}
-    \caption{Electric power generated as a function of time, wit its uncertainty.}\label{fig:power_full}
+    \caption{Electric power generated as a function of time, with its uncertainty.}\label{fig:power_full}
 \end{figure}
@@
 The relative uncertainty of the total uranium consumption starts at about
-$7\%$ a slowly drops and stabilize around $3\%$.
+$7\%$, slowly droping and stabilizing around $3\%$.
 
-Uncertainty fluctuation of the full relative uncertainty can be observed before
-year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
-beginning of the simulation have synchronized fuel cycles, reloading in the same
-time step.  This phenomenon disappears with the gradual decommissioning of the
+Fluctuation of the full relative uncertainty can be observed before year 50.
+Those fluctuation are induced by the fuel loading: all reactors at the beginning
+of the simulation have synchronized fuel cycles, reloading in the same time
+step.  This phenomenon disappears with the gradual decommissioning of the
 initial reactors, spread over 50 years.
@@
 deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
-the references one, reducing its impact on the uncertainty on the total uranium
+the mean (reference) value, reducing its impact on the uncertainty on the total uranium
 consumption. This uncertainty contribution to the overall uncertainty decrease
@@
 
-It is also interesting to note that, the uncertainty contribution from the cycle
-length between year 40 and 70 comes mainly from fuel batch loading frequencies.
-After 70 years this contribution follows the thermal power contribution closely,
+The uncertainty contribution from the cycle length between year 40 and 70 comes
+mainly from fuel batch loading frequencies (Figure \ref{fig:pu_uncer}.  After 70
+years this contribution follows the thermal power contribution closely,
 suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
-mechanism of this contribution.
+mechanism of this contribution, the variation of cycle length being driving a
+direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
+Fuel enrichment and separation efficiency showed a relative contribution smaller
+than $0.4\%$.
 
-Around the year 70, it is possible to observe the relative uncertainty related
-to cycle time being larger than the overall relative uncertainty. This effect is
-directly related to the \gls{OFAT} method used to estimate the individual
-uncertainty contribution. While allowing a quick access to the individual
-contribution, the \gls{OFAT} method does not capture coupling effect between the
-different parameters.
+Around the year 70, the relative uncertainty related to cycle time is slightly
+bigger than the overall relative uncertainty. This effect is related to the
+\gls{OFAT} method used to estimate the individual uncertainty contribution.
+While allowing a quick access to the individual contribution, the \gls{OFAT}
+method does not capture coupling effect between the different parameters.
 
@@
 
-Two main points can be deduced from this work.  First, in a transitional fuel
+Three main points can be deduced from this work.  First, in a transitional fuel
 cycle, uncertainty contributions to output metrics can vary over time depending
@@
 or thermal power.
+
+Finally, Figure \ref{fig:pu_uncer} shows the limit of the \gls{OFAT} method to
+assess the individual contribution of each parameter, missing all the coupling
+effect between each of them...
 
@@
 parameter values as a function of time) and completely systematic uncertainty
-(shared by all the facilities of a kind).
+(shared by all the facilities of a kind). Additionally more sophisticated methods needs to
+be used to assess precisely each parameter contributions..
 

### 2018-07-20 paper.tex
tackling last comment

@@
 been able to estimate that the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas
-about $10\%$ uncertainty on the enrichment implies an almost constant
-uncertainty of $2\%$.
+variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas about
+$10\%$ uncertainty on the enrichment implies an almost constant uncertainty of $2\%$.
 
@@
 parameters that describe those facilities, such as thermal power or fuel
-enrichment. Further analysis should allow us to understand this further.
+enrichment. Moreover such conclusions might change in a different scenario with
+different hypothesis: not considering radioactive decay remove the decay of
+$^{241}$Pu during cooling and considering a transition to fast reactors reduce
+the effect of composition change induced by the cycle length variations.
 
@@
 assess the individual contribution of each parameter, missing all the coupling
-effect between each of them...
+effects between each of them...
 
@@
 further analysis to understand and measure accurately their contributions to the
-total uncertainty.
+total uncertainty. I
 
@@
 parameter values as a function of time) and completely systematic uncertainty
-(shared by all the facilities of a kind). Additionally more sophisticated methods needs to
-be used to assess precisely each parameter contributions..
+(shared by all the facilities of a kind). Additionally more sophisticated
+methods needs to be used to assess precisely each parameter contributions..
 

### 2018-07-20 paper.tex
english

@@
 parameters that describe those facilities, such as thermal power or fuel
-enrichment. Moreover such conclusions might change in a different scenario with
+enrichment. Moreover such conclusions might change for different scenarios with
 different hypothesis: not considering radioactive decay remove the decay of
@@
 relative contributions, it has only been applied to systematic uncertainties per
-facilities.  This kind of study will to be extended to random uncertainty (new
+facilities.  This kind of study will be extended to random uncertainty (new
 parameter values as a function of time) and completely systematic uncertainty

### 2018-07-23 paper.tex
some corrections

@@
 required in the fuel to reach a given target burnup at the end of irradiation.
-The targeted burnup is a operational parameter and does not necessary related to the
-actual achieved burnup (computed from the real cycle length and the thermal
-power of the reactor). Therefore, the uncertainty of the fuel enrichment is not
-applied directly to the effective enrichment. It is instead applied to the
-targeted burnup, resulting in a fuel enrichment uncertainty that is also close
-to $10\%$.
+The target burnup is an operational parameter and does not necessary relate to
+the actual achieved burnup (computed from the real cycle length and the thermal
+power of the reactor). The uncertainty of the fuel enrichment is not applied
+directly to the effective enrichment. It is instead applied to the targeted
+burnup, resulting in a fuel enrichment uncertainty that is also close to $10\%$.
 
-For each of the parameters in Table \ref{tab:package_uncertainty}, a set of 199
-simulations was performed with only that parameter being randomly varied.  An
-additional set of 199 simulations was performed in which all five parameters are
-randomly varied, using \gls{OFAT} method.  A reference simulation was performed
-with all five parameters fixed at the mean value.
+An set of 199 simulations was performed in which all five parameters are
+randomly varied. Additionnaly, for each of the parameters in Table
+\ref{tab:package_uncertainty}, a set of 199 simulations was performed with only
+that parameter being randomly varied using the \gls{OFAT} method to estimated each
+parameter contribution to the overall uncertianty.  A reference simulation was
+performed with all five parameters fixed at the mean value.
 
@@
 deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
-the mean (reference) value, reducing its impact on the uncertainty on the total uranium
-consumption. This uncertainty contribution to the overall uncertainty decrease
-is proportional to the number of \gls{LWR} reactors and stops with the
+the mean (reference) value, reducing its impact on the uncertainty on the total
+uranium consumption. This uncertainty contribution to the overall uncertainty
+decrease is proportional to the number of \gls{LWR} reactors and stops with the
 decommission of the last one.
@@
 The fuel enrichment contribution follow a close to constant uncertainty
-contribution of $2\%$, so as the total relative uncertainty decrease, it has a
-growing shared of the total absolute uncertainty over time.
+contribution of $2\%$, so as the total relative uncertainty decrease, it
+has a growing share of the total absolute uncertainty over time.
 
@@
 parameters that describe those facilities, such as thermal power or fuel
-enrichment. Moreover such conclusions might change for different scenarios with
-different hypothesis: not considering radioactive decay remove the decay of
-$^{241}$Pu during cooling and considering a transition to fast reactors reduce
-the effect of composition change induced by the cycle length variations.
+enrichment. Nevertheless such conclusions might constrained by the simulation
+different hypothesis: not considering radioactive decay removes the decay of
+$^{241}$Pu during cooling and considering a transition to fast reactors
+minimizes the impact of the discharge composition change induced by the cycle
+length variations.
 
@@
 assess the individual contribution of each parameter, missing all the coupling
-effects between each of them...
+effects between them...
 
@@
 further analysis to understand and measure accurately their contributions to the
-total uncertainty. I
+total uncertainty.
 
@@
 
-While the parameters contributing to natural uranium needs and fissile inventory
-uncertainties might be obvious, such study allows to estimate each parameters
-contribution, and it could be less obvious for other parameters, such as
-plutonium quality, waste compositions.  Such studies could also provide research
-guidance for nuclear archaeology work, which aims to precisely estimate past
-fissile production by the different nuclear countries.
+Such studies could provide research guidance for nuclear archaeology work,
+which aims to precisely estimate past fissile production by the different
+nuclear countries.
 

### 2018-07-23 paper.tex
reformating

--- 2018-07-20 paper.tex
@@
 \newacronym{SFR}{SFR}{fast breeder reactor}
-\newacronym{OFAT}{OFAT}{one-factor-at-a-time}
 
@@
 required in the fuel to reach a given target burnup at the end of irradiation.
-The targeted burnup is a operational parameter and does not necessary related to the
-actual achieved burnup (computed from the real cycle length and the thermal
-power of the reactor). Therefore, the uncertainty of the fuel enrichment is not
-applied directly to the effective enrichment. It is instead applied to the
-targeted burnup, resulting in a fuel enrichment uncertainty that is also close
-to $10\%$.
+Therefore, the uncertainty of the fuel enrichment is not applied directly to the
+effective enrichment. It is instead applied to the burnup, resulting in a fuel
+enrichment uncertainty that is also close to $10\%$.
 
@@
 additional set of 199 simulations was performed in which all five parameters are
-randomly varied, using \gls{OFAT} method.  A reference simulation was performed
-with all five parameters fixed at the mean value.
+randomly varied.  A reference simulation was performed with all five parameters
+fixed at the mean value.
 
@@
     \includegraphics[scale=0.3]{power_full}
-    \caption{Electric power generated as a function of time, with its uncertainty.}\label{fig:power_full}
+    \caption{Electric power generated as a function of time, wit its uncertainty.}\label{fig:power_full}
 \end{figure}
@@
 The relative uncertainty of the total uranium consumption starts at about
-$7\%$, slowly droping and stabilizing around $3\%$.
+$5.5\%$ a slowly drops and stabilize around $3\%$.
 
-Fluctuation of the full relative uncertainty can be observed before year 50.
-Those fluctuation are induced by the fuel loading: all reactors at the beginning
-of the simulation have synchronized fuel cycles, reloading in the same time
-step.  This phenomenon disappears with the gradual decommissioning of the
+Uncertainty fluctuation of the full relative uncertainty can be observed before
+year 50.  Those fluctuation are induced by the fuel loading: all reactors at the
+beginning of the simulation have synchronized fuel cycles, reloading in the same
+time step.  This phenomenon disappears with the gradual decommissioning of the
 initial reactors, spread over 50 years.
@@
 deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
-the mean (reference) value, reducing its impact on the uncertainty on the total uranium
+the references one, reducing its impact on the uncertainty on the total uranium
 consumption. This uncertainty contribution to the overall uncertainty decrease
@@
 
-The uncertainty contribution from the cycle length between year 40 and 70 comes
-mainly from fuel batch loading frequencies (Figure \ref{fig:pu_uncer}.  After 70
-years this contribution follows the thermal power contribution closely,
+It is also interesting to note that, the uncertainty contribution from the cycle
+length between year 40 and 70 comes mainly from fuel batch loading frequencies.
+After 70 years this contribution follows the thermal power contribution closely,
 suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
-mechanism of this contribution, the variation of cycle length being driving a
-direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
-Fuel enrichment and separation efficiency showed a relative contribution smaller
-than $0.4\%$.
-
-Around the year 70, the relative uncertainty related to cycle time is slightly
-bigger than the overall relative uncertainty. This effect is related to the
-\gls{OFAT} method used to estimate the individual uncertainty contribution.
-While allowing a quick access to the individual contribution, the \gls{OFAT}
-method does not capture coupling effect between the different parameters.
+mechanism of this contribution.
 
@@
 been able to estimate that the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas about
-$10\%$ uncertainty on the enrichment implies an almost constant uncertainty of $2\%$.
+variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas
+about $10\%$ uncertainty on the enrichment implies an almost constant
+uncertainty of $2\%$.
 
@@
 parameters that describe those facilities, such as thermal power or fuel
-enrichment. Moreover such conclusions might change in a different scenario with
-different hypothesis: not considering radioactive decay remove the decay of
-$^{241}$Pu during cooling and considering a transition to fast reactors reduce
-the effect of composition change induced by the cycle length variations.
+enrichment. Further analysis should allow us to understand this further.
 
@@
 
-Three main points can be deduced from this work.  First, in a transitional fuel
+Two main points can be deduced from this work.  First, in a transitional fuel
 cycle, uncertainty contributions to output metrics can vary over time depending
@@
 
-Finally, Figure \ref{fig:pu_uncer} shows the limit of the \gls{OFAT} method to
-assess the individual contribution of each parameter, missing all the coupling
-effects between each of them...
-
 Cycle length impacts the discharge fuel burnup and  the frequency of the fuel
@@
 parameter values as a function of time) and completely systematic uncertainty
-(shared by all the facilities of a kind). Additionally more sophisticated
-methods needs to be used to assess precisely each parameter contributions..
+(shared by all the facilities of a kind).
 

### 2018-07-23 paper.tex
corrections

--- 2018-07-23 paper.tex
@@
 
-An set of 199 simulations was performed in which all five parameters are
-randomly varied. Additionnaly, for each of the parameters in Table
-\ref{tab:package_uncertainty}, a set of 199 simulations was performed with only
-that parameter being randomly varied using the \gls{OFAT} method to estimated each
-parameter contribution to the overall uncertianty.  A reference simulation was
-performed with all five parameters fixed at the mean value.
+A set of 199 simulations was performed in which all five parameters in Table
+\ref{tab:package_uncertainty} are randomly varied. Additionnaly, for each of the
+parameters, a set of 199 simulations was performed with only that parameter
+being randomly varied using the \gls{OFAT} method to estimated each parameter
+contribution to the overall uncertianty.  A reference simulation was performed
+with all five parameters fixed at the mean value.
 
@@
 The relative uncertainty of the total uranium consumption starts at about
-$7\%$, slowly droping and stabilizing around $3\%$.
+$7\%$, slowly droping and stabilizing around $3\%$ around year 100.
 

### 2018-07-23 paper.tex
formulation

@@
 A set of 199 simulations was performed in which all five parameters in Table
-\ref{tab:package_uncertainty} are randomly varied. Additionnaly, for each of the
-parameters, a set of 199 simulations was performed with only that parameter
-being randomly varied using the \gls{OFAT} method to estimated each parameter
-contribution to the overall uncertianty.  A reference simulation was performed
-with all five parameters fixed at the mean value.
+\ref{tab:package_uncertainty} are randomly varied. Additionnaly, for each of
+those parameters, a set of 199 simulations was performed with only that
+parameter being randomly varied, using the \gls{OFAT} method to estimated each
+parameter contribution to the overall uncertianty.  A reference simulation was
+performed with all five parameters fixed at the mean value.
 
@@
 
-The relative uncertainty of the total uranium consumption starts at about
-$7\%$, slowly droping and stabilizing around $3\%$ around year 100.
+The relative uncertainty of the uranium consumption dedicated to \gls{PWR}
+\gls{UOX} fuel fabrication starts at about $7\%$, slowly dropping from year 20
+to 100 and stabilizing around $3\%$ after year 100.
 

### 2018-07-23 paper.tex
last fix

@@
 A set of 199 simulations was performed in which all five parameters in Table
-\ref{tab:package_uncertainty} are randomly varied. Additionnaly, for each of
+\ref{tab:package_uncertainty} are randomly varied. Additionally, for each of
 those parameters, a set of 199 simulations was performed with only that
 parameter being randomly varied, using the \gls{OFAT} method to estimated each
-parameter contribution to the overall uncertianty.  A reference simulation was
+parameter contribution to the overall uncertainty.  A reference simulation was
 performed with all five parameters fixed at the mean value.
@@
 deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
-the mean (reference) value, reducing its impact on the uncertainty on the total
+the mean (reference) value, reducing its impact on the uncertainty on the
 uranium consumption. This uncertainty contribution to the overall uncertainty
@@
 direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
-Fuel enrichment and separation efficiency showed a relative contribution smaller
-than $0.4\%$.
+Both the fuel enrichment and separation efficiency showed a relative
+contribution smaller than $0.4\%$.
 
@@
 parameters that describe those facilities, such as thermal power or fuel
-enrichment. Nevertheless such conclusions might constrained by the simulation
-different hypothesis: not considering radioactive decay removes the decay of
-$^{241}$Pu during cooling and considering a transition to fast reactors
-minimizes the impact of the discharge composition change induced by the cycle
-length variations.
+enrichment. Nevertheless such conclusions are constrained by the simulation
+hypothesis: not considering radioactive decay removes the decay of $^{241}$Pu
+during cooling and considering a transition to fast reactors minimizes the
+impact of the discharge composition change induced by the cycle length
+variations, when reprocessing them to build the next \gls{MOX} fuel batch.
 

### 2018-07-28 paper.tex
new pdf build, change PWR into LWR
final read

@@
 
-The relative uncertainty of the uranium consumption dedicated to \gls{PWR}
+The relative uncertainty of the uranium consumption dedicated to \gls{LWR}
 \gls{UOX} fuel fabrication starts at about $7\%$, slowly dropping from year 20
@@
 Fluctuation of the full relative uncertainty can be observed before year 50.
-Those fluctuation are induced by the fuel loading: all reactors at the beginning
+Those fluctuations are induced by the fuel loading: all reactors at the beginning
 of the simulation have synchronized fuel cycles, reloading in the same time
@@
 suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
-mechanism of this contribution, the variation of cycle length being driving a
+mechanism of this contribution, the variation of cycle length driving a
 direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
@@
 \gls{OFAT} method used to estimate the individual uncertainty contribution.
-While allowing a quick access to the individual contribution, the \gls{OFAT}
-method does not capture coupling effect between the different parameters.
+While allowing a straightforward estimate of the individual contribution, the \gls{OFAT}
+method does not capture coupling effects between the different parameters.
 
@@
 parameters that describe those facilities, such as thermal power or fuel
-enrichment. Nevertheless such conclusions are constrained by the simulation
-hypothesis: not considering radioactive decay removes the decay of $^{241}$Pu
-during cooling and considering a transition to fast reactors minimizes the
-impact of the discharge composition change induced by the cycle length
-variations, when reprocessing them to build the next \gls{MOX} fuel batch.
+enrichment. Nevertheless such conclusions are specific to this particular scenario
+definition: not considering radioactive decay removes the decay of $^{241}$Pu
+during cooling, and a transition to fast reactors minimizes the
+impact of the change in discharge composition induced by the cycle length
+variations when reprocessing spent fuel to build the next \gls{MOX} fuel batch.
 
@@
 assess the individual contribution of each parameter, missing all the coupling
-effects between them...
+effects between them.
 

### 2018-08-09 paper.tex
squeeze images to fit on 4 pages
fresh start

--- 2018-07-23 paper.tex
@@
-\documentclass{anstrans}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations}
-\author{Baptiste Mouginot, Kathryn Mummah, Paul P.H.  Wilson}
+\documentclass[review]{./elsarticle}
 
-\institute{
-University of Wisconsin-Madison, Madison, WI
-}
+\usepackage{lineno,hyperref}
+\modulolinenumbers[5]
 
-\email{mouginot@wisc.edu \and mummah@wisc.edu \and paul.wilson@wisc.edu}
+\journal{Journal of \LaTeX\ Templates}
 
-% Optional disclaimer: remove this command to hide
-% \disclaimer{Notice: this manuscript is a work of fiction.  Any resemblance to
-% actual articles, living or dead, is purely coincidental.}
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%% packages and definitions (optional)
-\usepackage{graphicx} % allows inclusion of graphics
-\usepackage{booktabs} % nice rules (thick lines) for tables
-\usepackage{microtype} % improves typography for PDF
-\usepackage{float}
+%% Numbered
+%\bibliographystyle{model1-num-names}
 
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+
+\usepackage{color}
+\usepackage{subcaption}
+\usepackage{graphicx}
+\usepackage{booktabs} % nice rules for tables
+\usepackage{microtype} % if using PDF
+\usepackage{xspace}
+\usepackage{listings}
+\usepackage{textcomp}
+\usepackage{multicol,tabularx,capt-of}
+\usepackage{multirow}
+\usepackage{pdflscape}
+
+\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily\color{green!40!black}]|#1|}
+\newcommand{\units}[1] {\:\text{#1}}%
 \newcommand{\SN}{S$_N$}
-\renewcommand{\vec}[1]{\bm{#1}} %vector is bold italic
-\newcommand{\vd}{\bm{\cdot}} % slightly bold vector dot
-\newcommand{\grad}{\vec{\nabla}} % gradient
-\newcommand{\ud}{\mathop{}\!\mathrm{d}} % upright derivative symbol
-\newcommand{\ie}{\emph{i.e.\ }}
+\newcommand{\cyclus}{\textsc{Cyclus}\xspace}
+\newcommand{\Cyclus}{\cyclus}
+\newcommand{\citeme}{\textcolor{red}{CITE}\xspace}
+\newcommand{\TODO}[1] {{\color{red}\textbf{TODO: #1}}}%
+
+\newcommand{\comment}[1]{{\color{green}\textbf{#1}}}
 
 \usepackage[acronym]{glossaries}
-\newacronym{UOX}{UOX}{uranium oxide fuel}
-\newacronym{MOX}{MOX}{mixed oxide fuel}
-\newacronym{LWR}{LWR}{light water reactor}
-\newacronym{SFR}{SFR}{fast breeder reactor}
-\newacronym{OFAT}{OFAT}{one-factor-at-a-time}
+%\makeglossaries
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\input{glossary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
 
-Fuel cycle simulations, as with any simulation process, do not produce results
-without uncertainties.  Those uncertainties have two main sources: modeling
-uncertainty due to the simplifications and approximations built in to the
-simulator itself, and data uncertainty from the quantities provided by the user.
-This work focuses on a subset the data uncertainty related to the user input
-that defines the performance of the simulated facilities.
+\begin{frontmatter}
 
-Such simulation uncertainties could be important in the context of treaty
-verification.  Some scenarios require estimating historical fissile material
-production based on records of facility operation and material transfer.  If the
-measurements of facility operation and material transfer are subject to
-uncertainty, the total production quantities will then also be uncertain.  Any
-uncertainty in fissile production quantities poses a material accounting
-challenge, possibly creating an opportunity for undetected diversion.
+\input{authors}
 
-This study seeks to understand which characteristics of facility operation have
-the most impact on the uncertainty of fissile material production across a
-complete fuel cycle.  Uncertainty propagation using a Monte Carlo method will be
-applied to the Cyclus fuel cycle simulator \cite{cyclus} to estimate the effect
-of individual facility uncertainties on the output metrics. The same simulation
-will be performed $N$ times, with some input parameters randomly determined in
-each case.  The distribution of each output metrics over the N trials of the
-simulation will be used to estimate their respective uncertainty.
+\date{}
 
-\section{The Experiment}
+\title{Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades}
+\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
 
-\subsection{Method}
+% 0.Abstract
+\input{abstract}
 
-To estimate the uncertainty of fuel cycle output metrics, a Monte Carlo approach
-has been applied.  In each of 199 independent simulations, some of the
-parameters that define facility behavior are randomly selected from Normal
-distributions with standard deviations that are $10\%$ of the mean/nominal
-value.  This artificially large standard deviation is selected for the purpose
-of demonstrating the methodology.  The mean and standard deviation of some
-output metrics are calculated from the simulation output, as a function of time.
+\begin{keyword}
+\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
+\MSC[2010] 00-01\sep  99-00
+\end{keyword}
 
-To pursue this work, both the Cycamore\footnote{Low fidelity facilities package
-for Cyclus}\cite{cycamore} and the CyCLASS\footnote{Reactor and fuel fabrication
-facility based on CLASS\cite{CLASS} models}\cite{mouginot_2018, cyclass}
-packages were updated to evaluate the uncertainty of several operational
-parameters in their associated facilities.  Table \ref{tab:package_uncertainty}
-summarizes all uncertainty-tracking modifications implemented in the facilities
-of Cycamore and CyCLASS.
+\end{frontmatter}
 
-\begin{table}[htb]
-\centering
-  \caption{Summary of facility modifications according to their Cyclus archetype package.}
-\begin{tabular}{cl|l}
-\toprule
+\linenumbers
 
-Package   & Facility   & Parameters                \\
-\toprule
+\maketitle
 
-Cycamore & Separation & Separation efficiency     \\\cmidrule{2-3} 
-         & Storage    & Residence Time            \\
-\toprule
-CyCLASS  & Reactor    & Cycle Length              \\\cmidrule{3-3}
-         &            & Power                     \\\cmidrule{3-3}
-         &            & \acrshort{LWR}-\acrshort{UOX} Fuel Enrichment\\
+% I.   Motivation
+\input{motivation}
 
-\bottomrule
-\end{tabular}
+% II.  Theory
+%   a. cascade design
+%   b. misuse model
+%       i.   case A
+%       ii.  case B
+%       iii. case C
+\input{theory}
 
-  \label{tab:package_uncertainty}
-\end{table}
+% III. Experiement
+%   a.  cycle 
+%   b.  cascade per level optimisation
+\input{experiement}
 
-The uncertainty of the different parameters in this study are systematic for
-each new deployed facility: each time a new facility is deployed (such as a
-reactor or a fuel fabrication facility) a new set of parameters are sampled, and
-those parameters are used throughout the life of that facility.
+% IV.  results
+%   a. time step effects
+%   b. no tails recycling
+%   c. tails recycling
+\input{results}
 
-\subsection{The Fuel Cycle Scenario}
+% V.  Discussion
+% VI. Conclusions and future plan
+\input{dis_clusion}
 
-For demonstration purposes, a simple commercial fuel cycle transition is used,
-inspired from the EG23 fuel cycle of the Nuclear Fuel Cycle Evaluation and
-Screening Report\cite{ES}.  Pictured in Figure \ref{fig:cycle}, this is a
-transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a \gls{SFR}
-fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth of the nuclear
-generated power (Figure \ref{fig:power}).
-
-\begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
-  \centering
-  \includegraphics[scale=0.31]{cycle.png}
-  \caption{Simplified representation of the material flow between the different facilities,
-  with each operational parameter associated with an
-  uncertainty labeled in green.}\label{fig:cycle}
-\end{figure}
-
-As illustrated in Figure \ref{fig:power}, the transition starts with a fleet
-composed of only \glspl{LWR} loaded with enriched \gls{UOX} fuel.  The actual
-transition starts around year 35, with the deployment of \glspl{SFR}. The
-\glspl{SFR} are loaded with \gls{MOX}, which consists of plutonium blended with
-natural uranium.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.18]{power.png}
-    \caption{Electric power generated over time, including contributions from each reactor type.}
-    \label{fig:power}
-\end{figure}
-
-The plutonium, required for \gls{MOX} fabrication, is reprocessed from all used
-fuel.  At first, it is sourced only from \gls{UOX}, then used \gls{MOX} fuel as
-it becomes available for reprocessing.
-
-Both fuel reprocessing and fabrication have a constant maximum throughput, but
-may also be limited by the availability input material.  The enrichment of the
-\gls{UOX} is processed on demand.  Buffer storage facilities (not shown in
-Figure \ref{fig:cycle}) are present between all facilities with constant
-throughput.
-
-In this work, a time step of 1 month has been considered, \ie each output metric
-is reported once per month. Additionally, decay processes have not be taken into
-account.
-
-It must be noted that for this work, the fuel enrichment was determined by a
-fuel fabrication model\cite{Leniau2015125} which calculates the fissile fraction
-required in the fuel to reach a given target burnup at the end of irradiation.
-The target burnup is an operational parameter and does not necessary relate to
-the actual achieved burnup (computed from the real cycle length and the thermal
-power of the reactor). The uncertainty of the fuel enrichment is not applied
-directly to the effective enrichment. It is instead applied to the targeted
-burnup, resulting in a fuel enrichment uncertainty that is also close to $10\%$.
-
-A set of 199 simulations was performed in which all five parameters in Table
-\ref{tab:package_uncertainty} are randomly varied. Additionnaly, for each of
-those parameters, a set of 199 simulations was performed with only that
-parameter being randomly varied, using the \gls{OFAT} method to estimated each
-parameter contribution to the overall uncertianty.  A reference simulation was
-performed with all five parameters fixed at the mean value.
-
-\section{Results}
-
-Because the main interests of nuclear archaeology involve highly enriched
-uranium production and fissile inventories, this study mainly focuses on the
-uncertainties of the total quantity of natural uranium used and the total unused
-fissile inventory (separated plutonium).
-
-The total power generated in the simulation is reviewed to ensure that none of
-the compounded uncertainties result in material shortages substantial enough to
-cause long term facility shutdowns.  For example, since \gls{SFR} fuel is built
-from reprocessed used fuel, availability of that used fuel may impact the
-capability to build the required \gls{SFR}-\gls{MOX} fuel.  While there may be
-studies in which this would be an interesting result, in the context of this
-work, such shutdowns would be well-documented in the operational histories of
-the facilities and should not be characterized as an uncertainty.  Figure
-\ref{fig:power_full} shows that uncertainties in generated power are indeed very
-low.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{power_full}
-    \caption{Electric power generated as a function of time, with its uncertainty.}\label{fig:power_full}
-\end{figure}
-
-At each time step, the $\pm1\sigma$ uncertainty due to the full set of varied
-parameters is reported.  In addition, the relative contribution to the total
-uncertainty from each of the parameters is calculated as the ratio of the
-$1\sigma$ uncertainty due to that parameter over the total uncertainty.
-
-\subsection{Natural Uranium Consumption Dedicated to \gls{LWR}-\gls{UOX} fabrication}
-
-Figure \ref{fig:unat_full} represents the cumulative natural uranium consumption
-dedicated to \gls{LWR}-\gls{UOX} fuel fabrication as a function of time.  The
-uncertainty on the cumulative uranium consumption grows as expected with the
-time and the loading of the \glspl{LWR}.  The increase stops around year 125y
-with the decommissioning of the last \glspl{LWR}.
-
-As expected, cooling time, separation efficiency and thermal power do not affect
-the natural uranium consumption for \gls{LWR}-\gls{UOX} fuel production.  The
-uncertainty on the natural uranium consumption is dominated by the \gls{LWR}
-cycle length: shorter the cycle length is, the more fuel will be loaded, and
-\emph{vice versa}.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{unat_full}
-    \caption{Cumulative consumption of natural uranium as a function of time, with
-      associated uncertainty.}\label{fig:unat_full}
-\end{figure}
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{unat_uncer}
-    \caption{Relative uncertainty of the cumulative natural uranium consumption, including
-      individual contributions from each varied parameter.}\label{fig:unatr_uncer}
-\end{figure}
-
-The relative uncertainty of the uranium consumption dedicated to \gls{PWR}
-\gls{UOX} fuel fabrication starts at about $7\%$, slowly dropping from year 20
-to 100 and stabilizing around $3\%$ after year 100.
-
-Fluctuation of the full relative uncertainty can be observed before year 50.
-Those fluctuation are induced by the fuel loading: all reactors at the beginning
-of the simulation have synchronized fuel cycles, reloading in the same time
-step.  This phenomenon disappears with the gradual decommissioning of the
-initial reactors, spread over 50 years.
-
-The decrease of the cycle time uncertainty contribution, from year 30 to year
-90, can be understood as an averaging effect.  As the uncertainty are defined
-once per deployed facility, each reactor will have a different cycle length
-value, so a different number of batches loaded per year.  With the increase of
-deployed reactors, the number of batches of \gls{LWR} fuel loaded converges to
-the mean (reference) value, reducing its impact on the uncertainty on the total
-uranium consumption. This uncertainty contribution to the overall uncertainty
-decrease is proportional to the number of \gls{LWR} reactors and stops with the
-decommission of the last one.
-
-The fuel enrichment contribution follow a close to constant uncertainty
-contribution of $2\%$, so as the total relative uncertainty decrease, it
-has a growing share of the total absolute uncertainty over time.
-
-\subsection{Fissile Inventory}
-
-The fissile inventory corresponds to the amount of separated fissile material
-waiting to be blended with natural uranium in order to produce the
-\gls{SFR}-\gls{MOX} fuel.
-
-As observed on Figure \ref{fig:pu_full}, the fissile inventory starts to grow in
-year 40, with the deployment of the first reprocessing facility.  It grows
-during the first period of the \glspl{LWR} to \gls{SFR}-A transition until year
-90, then decrease slightly as the last \glspl{LWR} are decommissioned.  When the
-steady state is reached (full \gls{SFR} fleet), the plutonium inventory starts
-to increase, as the breading ratio of the \glspl{SFR} is higher than the
-deployment needs.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{pu_full}
-    \caption{Fissile (plutonium) inventory as a function of time, with
-      associated uncertainty.}\label{fig:pu_full}
-\end{figure}
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.3]{pu_uncer}
-    \caption{Relative uncertainty in the fissile (plutonium) inventory, with
-      individual contributions from each varied parameter.}\label{fig:pu_uncer}
-\end{figure}
-
-At the onset of fissile material production, very low mean inventories lead to
-unreliable artifacts in the relative uncertainty.  After that, the relative
-uncertainty starts at about $5\%$ and grows until year 125, then decreases to
-$10\%$ at the end of the simulation time (180y).  Between year 40 and 70, the
-main contributor to the fissile inventory uncertainty is the cycle length.  As
-with the uranium needs, different cycle length implies different number of fuel
-loads, so different amount of resources used.  Nevertheless, around year 65 (see
-Figure \ref{fig:used_fuel}), the stock of used fuel available for reprocessing
-becomes small enough to start limiting the production of fissile material.  The
-dominant contribution to the uncertainty then slowly transitions from the cycle
-length to the fuel cooling time.
-
-\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
-    \centering
-    \includegraphics[scale=0.16]{used_fuel}
-    \caption{Used fuel inventory, corresponding to the amount of used
-    \glspl{LWR} and \glspl{SFR} fuel, cooled and waiting to be reprocessed.}
-    \label{fig:used_fuel}
-\end{figure}
-
-Between year 90 and 120, the \gls{SFR} deployment speed increases; it has to
-compensate the non-replacement of the decommissioned \glspl{LWR} as well as
-follow the growing power demand.  During this period the needs in plutonium are
-higher than its production, explaining the observed decrease of the total
-amount, and the increase associated relative uncertainty.
-
-As the transition ends, the plutonium bred from the \glspl{SFR} starts to be
-sufficient to sustain the new \gls{SFR} deployment to follow the power demand.
-
-The uncertainty contribution from the cycle length between year 40 and 70 comes
-mainly from fuel batch loading frequencies (Figure \ref{fig:pu_uncer}.  After 70
-years this contribution follows the thermal power contribution closely,
-suggesting that fuel discharge burnup (\ie fuel discharge composition) is the
-mechanism of this contribution, the variation of cycle length being driving a
-direct variation of the burnup as the thermal power is held constant.  \gls{UOX}
-Fuel enrichment and separation efficiency showed a relative contribution smaller
-than $0.4\%$.
-
-Around the year 70, the relative uncertainty related to cycle time is slightly
-bigger than the overall relative uncertainty. This effect is related to the
-\gls{OFAT} method used to estimate the individual uncertainty contribution.
-While allowing a quick access to the individual contribution, the \gls{OFAT}
-method does not capture coupling effect between the different parameters.
-
-\subsection{Discussion}
-
-Uranium consumption and separated fissile inventory are two important metrics
-related to non-proliferation and nuclear archaeology.  In this study, we have
-been able to estimate that the cycle length uncertainty of $10\%$ implies a
-variation of $3\%$ to $5\%$ on the total uranium needs uncertainty, whereas about
-$10\%$ uncertainty on the enrichment implies an almost constant uncertainty of $2\%$.
-
-Regarding the reprocessed fissile inventory, this study has shown the impact of
-the reprocessed fuel compositions (through burnup variations) is limited to
-$\approx5\%$, while fuel availability constraints, such as fuel loading
-frequency (cycle time) or fissile materials available for fuel fabrication
-(cooling time) can lead to higher uncertainties, up to $10\%$ and to $30\%$,
-respectively.  Moreover, it is very interesting to observe the transition from
-one to the other around year 70.
-
-This preliminary study may suggest that the most important contributions to
-natural uranium consumption and fissile inventory come from the parameters that
-govern the exchange of material between facilities, and not from the physical
-parameters that describe those facilities, such as thermal power or fuel
-enrichment. Nevertheless such conclusions might constrained by the simulation
-different hypothesis: not considering radioactive decay removes the decay of
-$^{241}$Pu during cooling and considering a transition to fast reactors
-minimizes the impact of the discharge composition change induced by the cycle
-length variations.
-
-\section{Conclusion}
-
-Three main points can be deduced from this work.  First, in a transitional fuel
-cycle, uncertainty contributions to output metrics can vary over time depending
-of various factors: deployment schedule artifacts or material flow
-constrictions.
-
-Second, it is important to note the special character of the time related
-parameters uncertainty in a fuel cycle study, such as cooling time and cycle
-length.  While some of those time related parameters will, to first order, only
-impact material availability (as the cooling time will do), others, like cycle
-length, will also have a impact as physical parameters such as fuel enrichment
-or thermal power.
-
-Finally, Figure \ref{fig:pu_uncer} shows the limit of the \gls{OFAT} method to
-assess the individual contribution of each parameter, missing all the coupling
-effects between them...
-
-Cycle length impacts the discharge fuel burnup and the frequency of the fuel
-loads.  When they combine to produce in uncertainty of the material
-availability, this could result in variations related to time delays that may
-contribute to the final uncertainty in ways that are not relevant to some
-analyses.  That is, a simple time lag in a particular output that otherwise
-follows an identical history could manifest itself as a large variation at any
-particular time.  Those kind of time related uncertainties will require a
-further analysis to understand and measure accurately their contributions to the
-total uncertainty.
-
-This study aims to be a proof-of-principle for uncertainty propagation in
-potential commercial fuel cycle transition.  While it has demonstrated the
-capability to measure the uncertainty on output fuel cycle metrics and their
-relative contributions, it has only been applied to systematic uncertainties per
-facilities.  This kind of study will be extended to random uncertainty (new
-parameter values as a function of time) and completely systematic uncertainty
-(shared by all the facilities of a kind). Additionally more sophisticated
-methods needs to be used to assess precisely each parameter contributions..
-
-Such studies could provide research guidance for nuclear archaeology work,
-which aims to precisely estimate past fissile production by the different
-nuclear countries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Acknowledgments}
@@
 
+%\end{frontmatter}
+
+%\input{appendix}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{ans}
-\bibliography{bibliography}
+\begin{small}
+\bibliography{refs}  % NO SPACES BETWEEN BIB FILENAMES!
+\end{small}
 \end{document}

### 2018-08-10 theory.tex
done for the night ?

@@
 \section{Theory}
+
+In the following section, one will describe the different equations and
+algorithms used to model the behavior of a symmetric ideal gas centrifuge cascade from the
+individual centrifuge property, and to model the centrifuge behavior when fed
+with a different feed enrichment than the design one.
+
 \subsection{Centrifuge properties}
 
-The present work uses the analytical solution by R\"aetz \cite{raetz.phd} of the
-differential equation for the gas centrifuge as described in \cite{glaser.2008}.
+\subsubsection{Separative power}
+
+\paragraph{R\"aetz equation}
+
+As described in \cite{glaser.2008}, the separative power of a single centrifuge
+can be express as an analytical solution R\"aetz \cite{raetz.phd} of the
+differential equation for the gas centrifuge:
+
+\begin{eqnarray}
+    \delta U(L,F,\theta,Z_{p}) &= &\frac{1}{2} 
+            F\theta(1 - \theta) 
+            \left(\frac{\Delta M}{2 RT}v_{a}^{2}\right)^{2}
+            \left(\frac{r_{2}}{a}\right)^{4}
+            \left[1 - \left(\frac{r_{1}}{r_{2}}\right)^{2}\right]^{2}
+            \label{eq_raetz}\\  
+        &&
+            \left[ 
+                \left(\frac{1+L/F}{\theta}\right)
+                (1- exp[ - A_{P}(L,F,\theta)Z_{p}])  \nonumber  \right. \\ 
+        &&~~ + \left.\left(\frac{L/F}{1 - \theta}\right)
+                (1 - exp[ -A_{W}(L,F,\theta)(Z - Z_{p}])\right]^{2}, \nonumber
+                \\ 
+    \textrm{with~ ~ ~ ~ ~} 
+        A_{P} &= &\frac{2\pi D\rho }{ ln(r_{2}/r_{1}) } 
+                 \frac{ 1 }{ F }
+                 \frac{ 1-\theta }{(1+L/F)(1-\theta+L/F) }\\
+        A_{W} &= &\frac{2\pi D\rho }{ ln(r_{2}/r_{1}) } 
+                 \frac{ 1 }{ F }
+                 \frac{ 1-\theta }{ (L/F)(1-\theta+L/F) }
+\end{eqnarray}
+
 Centrifuge parameters, such as average gas temperature, $T$, peripheral speed,
@@
     \end{tabular}
-
     \label{tab:centrifuges}
@@
 
-\subsection{Cascade Design}
+\paragraph{First principle}
 
-The cascade is built as a symmetric ideal cascade, with no losses in the separative work,
-which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
-$\alpha$ and $\beta$ represent the feed to product and the feed to
-tails enrichment factors respectively.  $\alpha$ and $\beta$ can be expressed as function of
-the abundance ($R$) or the enrichment ($N$) of respectively the product
-($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
-as:
-\begin{subequations} \label{eq:alphabeta}
-    \begin{equation} \label{eq:alpha_def}
-        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
+It can be shown \ref{avery} that the separative power of a single centrifuge can be
+derive from the first principle and expressed as a function of the feed to
+product enrichment factor, $\alpha$, the cut, $\theta$, and the feed rate, $F$:
+
+\begin{equation} \label{eq_alpha_principle}
+    \delta U = \frac{F}{2}\frac{\theta}{1-\theta}(\alpha-1)^{2}
 \end{equation}
-\\
-\begin{equation}\label{eq:beta-def}
-        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
+
+\subsection{Centrifuges basic properties and definition}
+
+In order to add clarity to the rest of this work, one will take the time to
+define properly the different notation and the basic equation related to gaseous
+centrifuge. The different enrichment factor, $\alpha$ (feed to product), $\beta$
+(feed to tail) and $\gamma$(tail to product) are defined as the ratio of the
+different abundance ($R = \frac{N}{1-N}$) where $N, N', N''$ respectively
+correspond to the enrichment relative to the feed, the product and the tails:
+
+\begin{subequations}
+    \label{eq_alphabeta}
+    \begin{equation} \label{eq_alpha_def}
+        \alpha = \frac{N}{1-N}\frac{1-N'}{N'}
+    \end{equation}
+    \begin{equation}\label{eq_beta-def}
+        \beta = \frac{N''}{1-N''}\frac{1-N}{N}
+    \end{equation}
+    \begin{equation}\label{eq_gamma-def}
+        \gamma = \alpha.\beta
     \end{equation}
@@
 
-As detailed in \cite{avery} it is also possible to derive $\alpha$ from the
-first principle, and express it as a function of the feed rate $F$, the
-separative performance $\delta U(\theta)$ and the cut $\theta$:
+\subsection{Cascade Design}
+\subsubsection{Symmetric Cascade}
 
-    \begin{equation} \label{eq:alpha}
-    \alpha = \sqrt{\frac{2\delta U}{F} \frac{1-\theta}{\theta}}+1
+A symmetric cascade is a cascade where a stage is feed, $F$, with the tail, $T$, of the next
+stage, the product, $P$, of the previous one, and for the cascade feeding stage
+an external feed, $F_{ext}$, i.e. :
+
+\begin{equation}
+    F_{i} = T_{i+1} + F_{i-1} ~(+ F_{ext})
+\end{equation}
+
+\subsubsection{Symmetric Ideal Cascade}
+The cascade is built as a symmetric ideal cascade, with no losses in the
+separative work, which means that the tail assay of the next stage ($N''_{i+1}$)
+is the as the product assay of the previous stage ($N'_{i-1}$), which can be
+expressed as:
+\begin{equation}
+    \forall i~ N_{i} = N'_{i-1} = N''_{i+1}~ ~\Leftrightarrow~ ~\forall (i,j)~
+    \alpha_{i} = \beta_{j}
+\end{equation}
+
+\subsection{Building the cascade}
+
+The method used to design a symmetric ideal cascade starts with the feeding
+stage. As all the enrichment factor are equal across all the cascade, the
+feeding stage is used to determine those.
+The feed assay of the feeding stage, $N_{0}$ is fixed by the external feed assay
+provided as an input.
+
+From equation \eqref{eq_raetz} and \eqref{eq_alpha_principle} it is possible to
+express $\alpha$ as a function of the feed rate $F$, the separative performance
+$\delta U(\theta)$ and the cut $\theta$:
+
+\begin{equation} \label{eq_alpha}
+    \alpha = \sqrt{\frac{2\delta U(\theta)}{F} \frac{1-\theta}{\theta}} + 1
 \end{equation}
@@
 From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
-\eqref{eq:alphabeta} it is possible to express $\beta$ as a function of the
+\eqref{eq_alphabeta} it is possible to express $\beta$ as a function of the
 feed abundance, $R$, the cut $\theta$ and $\alpha$:
 
-\begin{equation}\label{eq:beta}
+\begin{equation}\label{eq_beta}
     \beta =   R \left(\dfrac{1-\theta}
@@
 
-From equation \eqref{eq:alpha} and \eqref{eq:beta} it is possible to determine
+As illustrated on figure \ref{fig_a_m_b}, the $\theta$ value to ensure a ideal feeding
+stage to the cascade range 0.45 0.525 depending on the feed assay.
+
+\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
+    \centering
+    \includegraphics[scale=0.5]{alpha_minus_beta}
+    \caption{Evolution of the difference between $\alpha$ and $\beta$ as a
+    function of the cut value for different of feed assays, 0.007 (black),
+    0.035 (red), 0.2 (green), 0.7 (black). }
+    \label{fig_a_m_b}
+\end{figure}
+
+From equation \eqref{eq_alpha} and \eqref{eq_beta} it is possible to determine
 the cut, $\theta$ required to build an ideal cascade:
+
 \begin{eqnarray}
@@
            \dfrac{1}{1 + \beta/R_{i}}}
-           \label{eq:theta}
+           \label{eq_theta}
 \end{eqnarray}
@@
 The second step determines the relative flows at each stages, solving the linear
-flow equation, \eqref{eq:flow}.
+flow equation, \eqref{eq_flow}.
 The cascade can then be populated with actual machines until the maximum number
@@
 %\caption{caption needed!}
-\label{eq:flow}
+\label{eq_flow}
 \end{equation}
@@
 The tuning method A does not re-optimize $\theta_i$ keeping the same flow as the
-ideal configuration. From equation \eqref{eq:alpha}, maintaining $\delta U$, $F$
+ideal configuration. From equation \eqref{eq_alpha}, maintaining $\delta U$, $F$
 and $\theta$ unchanged implies $\alpha$ remains unchanged as well. According to
-equation \eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, if the feed
+equation \eqref{eq_beta}, when $\alpha$ and $\theta$ are fixed, if the feed
 assay ($N$) changes, $\beta$ will change accordingly.  This breaks the
@@
 order to maintain the $\alpha_i$ and $\beta_i$ at their original values
-(equation \eqref{eq:theta}). The cascade remaining ideal, the product and tails
-assay at each stages are easily determined using equations \eqref{eq:alphabeta}.
+(equation \eqref{eq_theta}). The cascade remaining ideal, the product and tails
+assay at each stages are easily determined using equations \eqref{eq_alphabeta}.
 
 As the cut values change, the relative flow rates between the different stages
-are recomputed using equation \eqref{eq:flow}.  Under this model, the flow at
+are recomputed using equation \eqref{eq_flow}.  Under this model, the flow at
 each stage of the original ideal cascade is assumed to be the maximum flow
@@
 $\theta$ remain fixed. 
-From equations \eqref{eq:alphabeta} and the assay conservation equation $N =
+From equations \eqref{eq_alphabeta} and the assay conservation equation $N =
 \theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
 the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
-order equation \eqref{eq:gamma_p}:
+order equation \eqref{eq_gamma_p}:
 
-\begin{equation}\label{eq:gamma_p}
+\begin{equation}\label{eq_gamma_p}
     \theta(\gamma-1)N'^2+((N+\theta)(\gamma-1)+1)N'-N\gamma = 0
@@
 following :
-\begin{equation}\label{eq:model_b_sol}
+\begin{equation}\label{eq_model_b_sol}
     N' = \frac{N+\theta}{2\theta} +
@@
 Once the product assay is known, one can trivially determine the tails assay,
-$\alpha$ and $\beta$ using equations \eqref{eq:alphabeta} and mass
+$\alpha$ and $\beta$ using equations \eqref{eq_alphabeta} and mass
 conservation.
@@
 stage and the tails assay of the next stage using equation
-\eqref{eq:model_b_sol}.
+\eqref{eq_model_b_sol}.
 

### 2019-11-20 abstract.tex
done for the night ?
Added model product-feed plot. Changes to abstract/motivation.

@@
 \begin{abstract}
-
+\begin{itshape}
     This work compares and evaluates different computational approaches for modeling
@@
 design a symmetric enrichment cascade under ideal conditions as a function of the
-theoretical feed, product and tails assays, it is very difficult to find
+theoretical feed, product, and tails assays, it is very difficult to find
 reliable information about the behavior of a given cascade when the feed assay
@@
 the behavior of an enrichment cascade in such circumstances. In addition to the
-cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
-product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
+cut ($\theta$) those methods evaluate the feed to product, feed to tails, and the
+product to tails enrichment ratio, $\alpha$, $\beta$ and $\gamma$, respectively,
 as a function of the cascade feed assay. As those four parameters depend on each
@@
 nuclear fuel cycle simulator, Cyclus.
+\end{itshape}
 

### 2019-11-20 motivation.tex
Added model product-feed plot. Changes to abstract/motivation.

@@
 
-The present work investigates the performance of an enrichment cycle when chaining
+The present work investigates the performance ofs an enrichment cycle when chaining
 gas enrichment cascades tuned for low enrich uranium production from natural
-uranium. As literature on the mater is for obvious reason limited, three
-behavior models have been implemented and used to evaluate the response of an
-enrich cascade when fed with different assays than the design one. This work
-also takes advantage of the Cyclus\cite{cyclus} fuel cycle capabilities to
-evaluate the assay values at equilibrium.
+uranium to instead produce HEU. As literature on the mater is for obvious reason
+limited, three behavior models have been implemented and used to evaluate the
+response of an enrichment cascade when fed with different assays than designed one.
+This work also takes advantage of the Cyclus\cite{cyclus} fuel cycle capabilities
+to evaluate the assay values at equilibrium.

### 2019-11-20 theory.tex
Added model product-feed plot. Changes to abstract/motivation.

@@
 $F$.
+
+These models inherently result in differing amounts of diminishing returns
+as can be seen in Figure \ref{fig:model_comparison}. As the product assay
+weight percent increases, the required increase in feed assay to achieve the
+same rate of increase grows. This is particularly true for Models A and C
+compared to Model B.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.4]{ModelComparison}
+    \caption{}
+    \label{fig:model_comparison}
+\end{figure}

### 2019-11-21 theory.tex
Changing Model Comparison description and adding caption to plot.

--- 2018-08-10 theory.tex
@@
 $F$.
+
+The speed at which each models reach a threshold of $90\%$ enrichment is
+illustrated in Figure \ref{fig:model_comparison}. The production curve of
+enrichment for each model is shown. The step functions for each model represent
+the cascade configuration. Each step is one cascade in a chain of cascades and
+the shape of the curve for each model gives an indication of how quickly the model
+can reach the enrichment threshold. The main difference is that Model B reaches
+the threshold faster, whereas Models A and C reach a higher enrichment value.
+This highlights some of the immediate differences that would influence the choice
+of using each model in a breakout scenario.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.4]{ModelComparison}
+    \caption{The curve of resulting product assays for each model is plotted.
+    Since the feed assay of each cascade is fed into the next cascade in the
+    chain, a linear relationship between the product and feed assays is plotted
+    in black. The step function for each model represents the output of the
+    cascade chain (each step is a cascade). While there are four steps for each
+    model, Model B (green) reached the $90\%$ enrichment threshold before
+    Model A (red) or Model C (blue). However, in the same amount of steps, Models
+    A and C are able to achieve a higher enrichment percent than Model B.}
+    \label{fig:model_comparison}
+\end{figure}

### 2020-10-29 theory.tex
Adding parameter detail to Raetz equation

@@
 
-In the following section, one will describe the different equations and
-algorithms used to model the behavior of a symmetric ideal gas centrifuge cascade from the
-individual centrifuge property, and to model the centrifuge behavior when fed
-with a different feed enrichment than the design one.
+In the following section, equations and algorithms used to model the behavior of
+a symmetric ideal gas centrifuge cascade from the individual centrifuge property
+are described. Details will also be provided to model the centrifuge behavior
+when fed with a different feed enrichment than the design one.
 
@@
 As described in \cite{glaser.2008}, the separative power of a single centrifuge
-can be express as an analytical solution R\"aetz \cite{raetz.phd} of the
+can be express as an analytical solution \cite{raetz.phd} of the
 differential equation for the gas centrifuge:
@@
 
-Centrifuge parameters, such as average gas temperature, $T$, peripheral speed,
-$v$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
-counter-current flow ratio, $L/P$, and efficiency, $e$ have been chosen (Table
-\ref{tab:centrifuges}) to match the cascade design describe in
-\cite{glaser.2008} and \cite{walker.2017} using P1-type centrifuges.
+In this equation, the parameters of average gas temperature, $T$, peripheral speed,
+$v_a$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
+counter-current flow ratio, $L/P$, are intrinsic to the centrifuge design.
+To match the cascade design describe in \cite{glaser.2008} and \cite{walker.2017},
+P1-type centrifuge properties have been chosen (Table \ref{tab:centrifuges}).
 
@@
     \caption{Summary of the centrifuge parameters.}
-    \begin{tabular}{cccccccc}
+    \begin{tabular}{ccccccc}
         \toprule
-        $T$[K] & $v$[m/s] & $h$[m] & $d$[m]   & $x$      & $F$[mg/s]  & $L/F$ & $e$  \\
+        $T$[K] & $v$[m/s] & $h$[m] & $d$[m]   & $x$      & $F$[mg/s]  & $L/F$  \\
         \midrule
-        320    & $320$    & $1.8$  & $0.105$  & $10^{3}$ & $13$       & 2     & 1.0  \\
+        320    & $320$    & $1.8$  & $0.105$  & $10^{3}$ & $13$       & 2   \\
         \bottomrule

### 2020-10-29 theory.tex
Theory of Z_p

@@
 $v_a$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
-counter-current flow ratio, $L/P$, are intrinsic to the centrifuge design.
+counter-current flow ratio, $L/F$, are intrinsic to the centrifuge design.
 To match the cascade design describe in \cite{glaser.2008} and \cite{walker.2017},
@@
 \end{table}
+
+The variable $Z_p$ is the rectifier length, or the location of the feed point, has
+an optimal axial location as defined by \cite{raetz.phd}:
+
+\begin{equation}
+    Z_p = \frac{(1-\theta)(1+L/F)}{1-\theta+L/F}Z
+\end{equation}
+
+This optimizes the recitifer length based on the cut, $\theta$, which is an expression
+of the fraction of the centrifuge feed that is output as product, and the counter-current
+flow, $L/F$. In practice, this value is a design parameter that is updated in the model
+during the design of the centrifuge cascade.
 

### 2020-10-29 theory.tex
Adding r1/r2 information

@@
 during the design of the centrifuge cascade.
+
+The parameters $r_1$ and $r_2$ are the separation radii of the enriched material
+(here ${}^{235}\mathrm{U}$ vs. ${}^{238}\mathrm{U}$), $r_1$ being the withdrawal
+radius for the lighter isotope and $r_2$ for the heavier isotope. R\"aetz's
+two-shell model looks for optimal values between these two, as defined from
+the hydrodynamic equations. The radii ratio is optimized using the following relationship:
+
+\begin{equation}
+    \max\{[1-(\frac{r_1}{r_2})^2]^2 \times [ \ln(\frac{r_2}{r_1})]^{-1}\}
+\end{equation}
+
+The ratio can further be constrained by approximating $r_2$ as being very close
+to the inner centrifuge wall with radius $a$:
+
+\begin{equation}
+    (\frac{r_1}{r_2}) \approx (\frac{r_1}{a}) = \sqrt{1 - \frac{2RT}{M}(\ln x)\frac{1}{v_{a}^{2}}}
+\end{equation}
+
+Here the gas constants are mass, $M$, temperature $T$, universal gas constant, $R$,
+and the pressure ratio, $x$ (typically $1000:1$).
+This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
+Otherwise, the relationship can be approximated ${\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380} \frac{\mathrm{m}}{\mathrm{s}}$.
 

### 2020-10-29 theory.tex
Last inclusion of Raetz information.

@@
 \begin{eqnarray}
+    \label{eq:raetz}
     \delta U(L,F,\theta,Z_{p}) &= &\frac{1}{2}
@@
 
-Here the gas constants are mass, $M$, temperature $T$, universal gas constant, $R$,
+Here the gas constants are molar mass, $M$, temperature $T$, universal gas constant, $R$,
 and the pressure ratio, $x$ (typically $1000:1$).
@@
 Otherwise, the relationship can be approximated ${\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380} \frac{\mathrm{m}}{\mathrm{s}}$.
+In order to decompose the ratio into each individual radius, knowledge on one
+of them is required. Glaser \cite{glaser.2008} states that $r_2$ typically ranges
+from 96% to 99% the value of the inner centrifuge wall radius $a$. The exact
+behavior of $r_2$ between these two values in operational conditions is unknown,
+but a linear approximation can be made. It is assumed that $r_2$ is always at
+the midpoint of these two extremes (i.e. $r_2 = 0.975 a$). Then, $r_1$ can be
+found by simply multiplying this value by the ratio.
+
+With this, all parameters of the separative power equation \ref{eq:raetz} are
+defined and a value can be calculated. $\delta U$ has units similar to the feed
+flow, that of $[mg/s]$.
 

### 2020-11-02 theory.tex
Pruning theory wording

@@
 This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
-Otherwise, the relationship can be approximated ${\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380} \frac{\mathrm{m}}{\mathrm{s}}$.
+Otherwise, the relationship can be approximated $\{\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380 \frac{\mathrm{m}}{\mathrm{s}}\}$.
 In order to decompose the ratio into each individual radius, knowledge on one
@@
 
-In order to add clarity to the rest of this work, one will take the time to
-define properly the different notation and the basic equation related to gaseous
-centrifuge. The different enrichment factor, $\alpha$ (feed to product), $\beta$
-(feed to tail) and $\gamma$(tail to product) are defined as the ratio of the
-different abundance ($R = \frac{N}{1-N}$) where $N, N', N''$ respectively
-correspond to the enrichment relative to the feed, the product and the tails:
+The outputs of a centrifuge relative to its input can be described with ratios
+of the abundance ($R = \frac{N}{1-N}$) where the feed, product, and tail are
+$N, N', N''$ respectively. Enrichment factiors of $\alpha$ (feed to product),
+$\beta$ (feed to tail), and $\gamma$ (tail to product) can then be defined:
 
@@
 
-A symmetric cascade is a cascade where a stage is feed, $F$, with the tail, $T$, of the next
-stage, the product, $P$, of the previous one, and for the cascade feeding stage
-an external feed, $F_{ext}$, i.e. :
+A symmetric cascade is a cascade where a stage's feed, $F$, with a tail, $T$, of the next
+stage and product, $P$, of the previous one. For the cascade feeding stage
+an external feed, $F_{ext}$:
 
@@
 \subsubsection{Symmetric Ideal Cascade}
-The cascade is built as a symmetric ideal cascade, with no losses in the
-separative work, which means that the tail assay of the next stage ($N''_{i+1}$)
-is the as the product assay of the previous stage ($N'_{i-1}$), which can be
+This model constructs cascades as symmetrical and ideal, with no losses in
+separative work. This means that the tail assay of the next stage ($N''_{i+1}$)
+is the product assay of the previous stage ($N'_{i-1}$), which can be
 expressed as:
+
 \begin{equation}
@@
 The method used to design a symmetric ideal cascade starts with the feeding
-stage. As all the enrichment factor are equal across all the cascade, the
-feeding stage is used to determine those.
-The feed assay of the feeding stage, $N_{0}$ is fixed by the external feed assay
+stage. As all the enrichment factors are equal across all the cascade, the
+feeding stage is used to determine all subsequent stages.
+The feed assay of the feeding stage, $N_{0}$, is fixed by the external feed assay
 provided as an input.
@@
 
-From the mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
+From mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
 \eqref{eq_alphabeta} it is possible to express $\beta$ as a function of the
@@
 
-As illustrated on figure \ref{fig_a_m_b}, the $\theta$ value to ensure a ideal feeding
-stage to the cascade range 0.45 0.525 depending on the feed assay.
+As illustrated in Fig. \ref{fig_a_m_b}, $\theta$ ensures an ideal feeding
+stage to the cascade ranges between 0.45 and 0.525, depending on the feed assay.
 
@@
 
-The design of the ideal symmetric cascade is performed through 2 steps.  First
-one determines the configuration and number of stages, adding stages until the
+The design of the ideal symmetric cascade is performed through 2 steps. First,
+the configuration and number of stages is determined, adding stages until the
 product assay of the final stage is greater or equal the product targeted assay,
@@
 determines the number of enriching and stripping stages as well as their
-enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).
+enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$).
 

### 2020-11-03 theory.tex
Adding information about ideal stage from ideal cut algorithm

@@
 
-As illustrated in Fig. \ref{fig_a_m_b}, $\theta$ ensures an ideal feeding
-stage to the cascade ranges between 0.45 and 0.525, depending on the feed assay.
+To construct an ideal cascade stage, a stage cut ($\theta$) must first be computed.
+This is found iteratively, searching for the optimal cut value where $\alpha = \beta$
+for a given feed and centrifuge parameters. With a separative power calculated,
+and $\alpha$ and $\beta$ value can be determined for an initial cut guess. This
+model assumes that the ideal cut for a stage should be between 0.1 and 0.9. The
+two enrichment factors are compared, and the higher or lower cut value is chosen
+by which pair of factors are closer. A new cut is determined from the chosen
+factors, a new separative power is computed, and new $\alpha$ and $\beta$ values
+are compared. This process continues until, to some precision, the resulting
+enrichment factors are approximately equal. As illustrated in Fig. \ref{fig_a_m_b},
+for a given input feed assay, the ideal feeding stage typically has a $\theta$
+value between 0.45 and 0.525 when $\alpha = \beta$.
 

### 2020-11-04 theory.tex
Correcting alpha/beta definitions
Adding interim definitions to beta equation

@@
     \begin{equation} \label{eq_alpha_def}
-        \alpha = \frac{N}{1-N}\frac{1-N'}{N'}
+        \alpha = \frac{1-N}{N}\frac{N'}{1-N'}
     \end{equation}
     \begin{equation}\label{eq_beta-def}
-        \beta = \frac{N''}{1-N''}\frac{1-N}{N}
+        \beta = \frac{1-N''}{N''}\frac{N}{1-N}
     \end{equation}
@@
 
-From mass conservation, $N = \theta N' + (1-\theta)N''$, and equations
-\eqref{eq_alphabeta} it is possible to express $\beta$ as a function of the
-feed abundance, $R$, the cut $\theta$ and $\alpha$:
+From equations \eqref{eq_alphabeta}, the product assay can be expressed as:
 
+\begin{equation}\label{eq_product_assay}
+    N' = \frac{\alpha R}{1 + \alpha R}
+\end {equation}
+
+Then, from mass conservation, $N = \theta N' + (1-\theta)N''$, equation
+\eqref{eq_product_assay}, and the definition of the abundance, $R$, it is
+possible to express $\beta$ as a function of only the feed abundance,
+$R$, the cut $\theta$ and $\alpha$:
+
+\begin{subequations}
+    \begin{equation}\label{eq_beta_interim}
+        \beta = \left( 1 - \frac{N - \theta N'}{1-\theta} \right)
+                        \left( \frac{R}{\frac{N - \theta N'}{1 - \theta}} \right)
+    \end{equation}
     \begin{equation}\label{eq_beta}
@@
     \end{equation}
+\end{subequations}
 

### 2020-11-05 theory.tex
Adding machines needed per stage information

@@
 of them is required. Glaser \cite{glaser.2008} states that $r_2$ typically ranges
-from 96% to 99% the value of the inner centrifuge wall radius $a$. The exact
+from $96\%$ to $99\%$ the value of the inner centrifuge wall radius $a$. The exact
 behavior of $r_2$ between these two values in operational conditions is unknown,
@@
 
-Then, from mass conservation, $N = \theta N' + (1-\theta)N''$, equation
-\eqref{eq_product_assay}, and the definition of the abundance, $R$, it is
-possible to express $\beta$ as a function of only the feed abundance,
-$R$, the cut $\theta$ and $\alpha$:
+Then, from mass conservation, $N = \theta N' + (1-\theta)N''$ and equation
+\eqref{eq_product_assay}, it is possible to express $\beta$ as a function of
+only the feed abundance, $R$, the cut $\theta$ and $\alpha$:
 
@@
 
-To construct an ideal cascade stage, a stage cut ($\theta$) must first be computed.
+Finally from equation \eqref{eq_alpha} and \eqref{eq_beta} it is possible to
+determine the cut, $\theta$ required to build an ideal cascade:
+
+\begin{eqnarray}
+    \theta_{i} = \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
+           \dfrac{1}{1 + \beta/R_{i}}}
+           \label{eq_theta}
+\end{eqnarray}
+
+To construct an ideal stage, a cut ($\theta$) must first be computed.
 This is found iteratively, searching for the optimal cut value where $\alpha = \beta$
@@
 
-From equation \eqref{eq_alpha} and \eqref{eq_beta} it is possible to determine
-the cut, $\theta$ required to build an ideal cascade:
+The number of machines required to construct a stage can then be computed using
+equation \eqref{eq_alpha_principle} to solve for the centrifuge feed flow:
 
-\begin{eqnarray}
-    \theta_{i} = \dfrac{N_{i} - \dfrac{1}{1 + \beta/R_{i}}}{ \dfrac{\alpha R_{i}}{1 + \alpha R_{i}} -
-           \dfrac{1}{1 + \beta/R_{i}}}
-           \label{eq_theta}
-\end{eqnarray}
+\begin{equation}\label{eq_cent_feed}
+    F_c = \frac{2 \delta U}{(\alpha - 1)^2} \frac{M}{M_{238}} \frac{1-\theta}{\theta}
+\end{equation}
 
-As $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
-$\theta_{i}$, changes across the different stages of a cascade.  This algorithm
-assumes that the corresponding separative power $\delta U$ (not re-computed) can
-be achieved with the chosen centrifuge design, tuning other operational
-parameter such as the rotation speed, the counter-current flow ratio, etc.  Once
-$\theta_{i}$ is determined, it is possible to compute the product and the tail
-assay.
+Where the molar mass ratio $\frac{M}{M_{238}}$ accounts for the molar mass
+differences between the feed gas, $UF_6$, and the individual uranium isotopes
+being separated. The stage feed flow can then be divided by the individual
+centrifuge feed flow, equation \eqref{eq_cent_feed}, to find the exact number of
+machines needed for the ideal stage. In practice, this number is rounded up to
+account for fractional machines required.
+
+In a cascade, as $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of
+the cut, $\theta_{i}$, changes across the different stages of a cascade.  This
+algorithm assumes that the corresponding separative power $\delta U$ (not
+re-computed) can be achieved with the chosen centrifuge design, tuning other
+operational parameter such as the rotation speed, the counter-current flow
+ratio, etc.  Once $\theta_{i}$ is determined, it is possible to compute the
+product and the tail assay.
 

### 2020-11-06 theory.tex
Proofreading misuse models section

@@
 that is being fed with a feed enrichment that does not match the design
-enrichment. So far 3 different methods have been investigated.
+enrichment. Here, 3 different methods will be investigated.
 
-The first one assumes that no change are been made to the cascade, i.e $\delta
+The first one assumes that no changes are being made to the cascade, i.e $\delta
 U$, $F$ and $\theta$ are fixed across all stages. The second one assumes the cut
@@
 $\alpha$ and $\beta$ remain fixed. The last one, described in \cite{walker.2017}
-assumes the tails to product enriching factor and the cut remain constants ($\gamma =
-\alpha\times\beta$). Models behaviors and assumptions are summarized in Tab.
-\ref{tab:models}.
+assumes the tails to product enrichment factor and the cut remain constants
+(eq. \eqref{eq_gamma-def}: $\gamma = \alpha\beta$). Models behaviors and
+assumptions are summarized in Tab. \ref{tab:models}.
 
@@
 \midrule
-Constant parameters  & $\alpha_i, \theta_i$ & $\alpha_i=\beta_i$ & $\gamma_i=\alpha_i .\beta_i, \theta_i$       \\
+Constant parameters  & $\alpha_i, \theta_i$ & $\alpha_i=\beta_i$ & $\gamma_i=\alpha_i\beta_i, \theta_i$       \\
 Varying parameters   & $\beta_i$            & $\theta_i$         & $\alpha_i, \beta_i$                     \\
@@
 The tuning method A does not re-optimize $\theta_i$ keeping the same flow as the
-ideal configuration. From equation \eqref{eq_alpha}, maintaining $\delta U$, $F$
-and $\theta$ unchanged implies $\alpha$ remains unchanged as well. According to
-equation \eqref{eq_beta}, when $\alpha$ and $\theta$ are fixed, if the feed
-assay ($N$) changes, $\beta$ will change accordingly.  This breaks the
+ideal configuration. From equation \eqref{eq_alpha}, maintaining $\delta U$ and
+$F$ while $\theta$ is unchanged implies $\alpha$ remains unchanged as well.
+According to equation \eqref{eq_beta}, when $\alpha$ and $\theta$ are fixed, if
+the feed assay ($N$) changes, $\beta$ will change accordingly.  This breaks the
 ideal status of the cascade, i.e. $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.
@@
 process is repeated until the sum of the square difference in assays is smaller
-than $10^{-8}$.  As the cut remain fixed at each stage the flows do not need to
-be recomputed.
+than $10^{-8}$.  As the cut remains fixed at each stage, the flows do not need
+to be recomputed.
 
@@
 
-Using the second method, the cut value at each stage $\theta_i$, is retuned in
+Using the second method, the cut value at each stage, $\theta_i$, is retuned in
 order to maintain the $\alpha_i$ and $\beta_i$ at their original values
-(equation \eqref{eq_theta}). The cascade remaining ideal, the product and tails
-assay at each stages are easily determined using equations \eqref{eq_alphabeta}.
+(equation \eqref{eq_theta}). Since the cascade remains ideal, the product and
+tails assay at each stage can easily be determined using equations
+\eqref{eq_alphabeta}.
 
@@
 From equations \eqref{eq_alphabeta} and the assay conservation equation $N =
-\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
-the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
-order equation \eqref{eq_gamma_p}:
+\theta N' + (1-\theta)N''$ it is possible to express the product, $N'$,
+dependent on the feed assay $N$, $\gamma$, and the cut, $\theta$, as one
+solution of the second order equation \eqref{eq_gamma_p}:
 
@@
 following :
+
 \begin{equation}\label{eq_model_b_sol}
@@
 \end{equation}
+
 Once the product assay is known, one can trivially determine the tails assay,
-$\alpha$ and $\beta$ using equations \eqref{eq_alphabeta} and mass
+$\alpha$ and $\beta$, using equations \eqref{eq_alphabeta} and mass
 conservation.
 
-Similar to model A, because the cut values remain constant, the flows don't
-need to be recomputed, and the correct assays, $\alpha$ and $\beta$ are
+Similar to model A, because the cut values remain constant, the flows do not
+need to be recomputed and the correct assays, $\alpha$ and $\beta$, are
 determined through iterative blending of the product assays of the previous
@@
 This model assumes that it is possible to tune the centrifuge separative power
-$\delta U$ in order to maintain, for any feed assay $N$, its tails to product
-enrichment factor $\gamma$, while maintaining its cut $\theta$ and feed flow
-$F$.
+$\delta U$ in order to maintain for any feed assay $N$ and its tails to product
+enrichment factor $\gamma$ while maintaining its cut $\theta$ and feed flow $F$.
 
-The speed at which each models reach a threshold of $90\%$ enrichment is
-illustrated in Figure \ref{fig:model_comparison}. The production curve of
-enrichment for each model is shown. The step functions for each model represent
-the cascade configuration. Each step is one cascade in a chain of cascades and
-the shape of the curve for each model gives an indication of how quickly the model
-can reach the enrichment threshold. The main difference is that Model B reaches
-the threshold faster, whereas Models A and C reach a higher enrichment value.
-This highlights some of the immediate differences that would influence the choice
-of using each model in a breakout scenario.
+%The speed at which each models reach a threshold of $90\%$ enrichment is
+%illustrated in Figure \ref{fig:model_comparison}. The production curve of
+%enrichment for each model is shown. The step functions for each model represent
+%the cascade configuration. Each step is one cascade in a chain of cascades and
+%the shape of the curve for each model gives an indication of how quickly the model
+%can reach the enrichment threshold. The main difference is that Model B reaches
+%the threshold faster, whereas Models A and C reach a higher enrichment value.
+%This highlights some of the immediate differences that would influence the choice
+%of using each model in a breakout scenario.
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[scale=0.4]{ModelComparison}
-    \caption{The curve of resulting product assays for each model is plotted.
-    Since the feed assay of each cascade is fed into the next cascade in the
-    chain, a linear relationship between the product and feed assays is plotted
-    in black. The step function for each model represents the output of the
-    cascade chain (each step is a cascade). While there are four steps for each
-    model, Model B (green) reached the $90\%$ enrichment threshold before
-    Model A (red) or Model C (blue). However, in the same amount of steps, Models
-    A and C are able to achieve a higher enrichment percent than Model B.}
-    \label{fig:model_comparison}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \includegraphics[scale=0.4]{ModelComparison}
+%    \caption{The curve of resulting product assays for each model is plotted.
+%    Since the feed assay of each cascade is fed into the next cascade in the
+%    chain, a linear relationship between the product and feed assays is plotted
+%    in black. The step function for each model represents the output of the
+%    cascade chain (each step is a cascade). While there are four steps for each
+%    model, Model B (green) reached the $90\%$ enrichment threshold before
+%    Model A (red) or Model C (blue). However, in the same amount of steps, Models
+%    A and C are able to achieve a higher enrichment percent than Model B.}
+%    \label{fig:model_comparison}
+%\end{figure}

### 2020-12-08 results.tex
attempting to resize results table
still resizing results table
adding a columnwidth req to results table
shrinking results table with footnotesize
updating numbers in results table

@@
 \begin{table}[h!]
+\footnotesize
 \centering
   \caption{Summary of cascades level population.}
-\begin{tabular}{ccccccccc}
+\resizebox{\columnwidth}{!}{%
+\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} cccccccc}
 \toprule
@@
 Model       &        &                & A/NR     & A/R      & B/NR     & B/R      & C/NR     & C/R       \\
-%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
+%Recycling   &       &                & No       & Yes      & No       & Yes      & No       & Yes        \\
 \midrule                                                                                                 
-        &            & Feed       & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.33w\%$ \\
-Level 0 & Assay      & Product    & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $4.82w\%$ \\
-        &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
-        & Cascades   & Impl. (Ideal)& 25(26.7)  & 25(26.4)  & 25(26.6)  & 24(25.8)  & 25(26.7)  & 25(26.4)  \\
+        &            & Feed $w\%$     & $0.71$   & $1.31$   & $0.71$   & $0.92$   & $0.71$   & $1.30$ \\
+Level 0 & Assay      & Product $w\%$  & $3.97$   & $7.27$   & $3.97$   & $5.10$   & $3.97$   & $7.24$ \\
+        &            & Tails $w\%$    & $0.28$   & $0.52$   & $0.28$   & $0.36$   & $0.28$   & $0.51$ \\
+        & Cascades   & Impl. (Ideal)  & 25(26.5) & 25(26.5) & 25(26.4) & 24(26.3) & 25(26.5) & 25(26.2)  \\
 \midrule                                                                                                 
-        &            & Feed       & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $12.2w\%$ \\
-Level 1 & Assay      & Product    & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $58.5w\%$ \\
-        &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
-        & Cascades   & Impl. (Ideal)& 3(2.9)    & 4(3.2)    & 3(2.9)    & 4(3.4)    & 3(2.9)    & 4(3.2)    \\
+        &            & Feed $w\%$     & $3.97$   & $11.48$  & $3.97$   & $6.29$   & $3.97$   & $11.64$ \\
+Level 1 & Assay      & Product $w\%$  & $21.29$  & $53.30$  & $19.33$  & $27.98$  & $21.41$  & $55.12$ \\
+        &            & Tails $w\%$    & $1.68$   & $5.93$   & $1.58$   & $2.54$   & $1.66$   & $5.88$ \\
+        & Cascades   & Impl. (Ideal)  & 3(3.1)   & 4(3.1)   & 3(3.1)   & 4(3.1)   & 3(3.1)   & 4(3.4)    \\
 \midrule                                                                                                 
-        &            & Feed       & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $58.5w\%$ \\
-Level 2 & Assay      & Product    & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $97.0w\%$ \\
-        &            & Tails      & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
-        & Cascades   & Impl. (Ideal)& 1(0.3)    & 1(0.3)    & 1(0.4)    & 1(0.6)    & 1(0.3)    & 1(0.35)   \\
+        &            & Feed $w\%$     & $21.29$  & $53.3$   & $19.33$  & $31.09$  & $21.41$  & $55.12$ \\
+Level 2 & Assay      & Product $w\%$  & $76.39$  & $94.70$  & $58.10$  & $72.31$  & $79.21$  & $96.37$ \\
+        &            & Tails $w\%$    & $13.98$  & $47.81$  & $8.51$   & $14.91$  & $13.75$  & $49.65$ \\
+        & Cascades   & Impl. (Ideal)  & 1(0.4)   & 1(0.4)   & 1(0.4)   & 1(0.5)   & 1(0.4)   & 1(0.4)   \\
 \midrule                                                                                                 
-        &            & Feed       & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
-Level 3 & Assay      & Product    & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
-        &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
-        & Cascades   & Impl. (Ideal)& 1(0.03)   & N.A.      & 1(0.08)   & 1(0.2)    & 1(0.03)   & N.A.      \\
+        &            & Feed $w\%$     & $76.39$  & N.A.     & $58.10$  & $72.31$  & $79.21$  & N.A.      \\
+Level 3 & Assay      & Product $w\%$  & $98.09$  & N.A.     & $88.92$  & $93.79$  & $98.86$  & N.A.      \\
+        &            & Tails $w\%$    & $73.51$  & N.A.     & $35.01$  & $50.36$  & $76.60$  & N.A.      \\
+        & Cascades   & Impl. (Ideal)  & 1(0.04)  & N.A.     & 1(0.09)  & 1(0.1)   & 1(0.04)  & N.A.      \\
+\midrule                                                                                                 
+        &            & Feed $w\%$     & N.A.     & N.A.     & $88.92$  & N.A.     & N.A.     & N.A.      \\
+Level 4 & Assay      & Product $w\%$  & N.A.     & N.A.     & $97.89$  & N.A.     & N.A.     & N.A.      \\
+        &            & Tails $w\%$    & N.A.     & N.A.     & $75.71$  & N.A.     & N.A.     & N.A.      \\
+        & Cascades   & Impl. (Ideal)  & N.A.     & N.A.     & 1(0.04)  & N.A.     & N.A.     & N.A.      \\
 \bottomrule
-\end{tabular}
+\end{tabular*}
+}
 \label{tab:level}

### 2020-12-08 abstract.tex
formatting abstract and title page
reverting italics abstract
proofreading

@@
 other, determining two of them fully defines the other.  The first approach
-consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
+consists of fixing $\theta$ and $\alpha$, recomputing the corresponding assays at
 each stages of the cascade. The second one maintains the ideal condition of the
 cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
-$\theta$ value at each stage accordingly. Both approaches have been implemented
+$\theta$ values at each stage accordingly. Both approaches have been implemented
 into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes

### 2020-12-08 dis_clusion.tex
proofreading

--- 2018-07-17 dis_clusion.tex
@@
 achieve large increase of the enrichment at each level.  On the contrary, when
-retuning the cut of each centrifuges to maintain the ideal state of the cascades
+retuning the cut of each centrifuge to maintain the ideal state of the cascades
 (Model B) while chaining them, the \gls{HEU} production rate is favored over the
@@
 
-The tails recycling allows each model to achieve a large gain in productivity,
-even for then model B in which the number of levels required to reach $90w\%$ of
-$^{235}$U in the uranium does not change. Even if no cascade chaining options
-achieves the same production rate as direct enrichment, the model B with tail
-recycling reached about $80\%$ of the optimum production rate. Such production
-rate would allow the accumulation of a Significant Quantity of \gls{HEU} in less
-than 8 months\ldots
+The tails recycling allows each model to achieve a large gain in productivity.
+Even if no cascade chaining options achieves the same production rate as direct
+enrichment, all models with tail recycling reached close to $73\%$ of the optimum
+production rate. Such a production rate would allow the accumulation of a
+Significant Quantity of \gls{HEU} in less than 8 months\ldots
 
@@
 cascades that are designed to enrich uranium for commercial reactors in order to
-produce \gls{HEU}, instead. Three methods have been implemented to model enrichment
-cascade behavior when fed with different uranium enrichment than the designed
-enrichment.
+produce \gls{HEU} instead. Three methods have been implemented to model
+symmetric enrichment cascade behavior when fed with different uranium enrichment
+than designed.
 
@@
 %% \gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
-One of these method achieves up to $80\%$ of the production rate of a single
+Each method achieves up to $73\%$ of the production rate of a single
 large enrichment cascade designed specifically for \gls{HEU} production using

### 2020-12-08 experiement.tex
scaling cascade config schematic figure
proofreading

@@
 This work focuses on comparing the different misuse models to a reference
-calculation in which a single large cascade is build and designed to directly
+calculation in which a single large cascade is designed and built to directly
 produce \gls{HEU} from natural uranium.
 This works uses the Cyclus fuel cycle simulator to allow material exchange
-between facilities. The enrichment cascade algorithm have been implemented in
+between facilities. The enrichment cascade algorithm has been implemented in
 the $mbmore$ package \cite{mbmore.2018}.
 In each cases, 5060 centrifuges have been used and spread across up to 30
-different gas centrifuge enrichment cascades.
+different gas centrifuge enrichment cascades. This is inspired by limitations
+placed on the Iranian uranium enrichment program via the Joint Comprehensive
+Plan of Action (JCPoA) \cite{jcpoa}.
 
@@
     \centering
-    \includegraphics[scale=0.45]{flow}
+    \includegraphics[width=\linewidth]{flow}
     \caption{Schematic representation of the chained cascades with three levels,
@@
 
-A flow equation similar to \eqref{eq:flow} is then solved to obtain the optimum
+A flow equation similar to \eqref{eq_flow} is then solved to obtain the optimum
 number of cascade per level. When the tails are not recycled, the $(1-\theta)$
@@
 As it is not possible to assign a fraction of an enrichment cascade, cascade per
-level are rounded up for each level but the first one. The remaining available
-cascades are attributed to the first level.
+level must be rounded and assigned for each level. Again, per the JCPoA, 30
+cascades are distributed to the appropriate number of levels to achieve an
+HEU threshold with the least amount of levels. This optimal assignment is
+manually tested by running many different configurations. In generally, each
+level besides the first is rounded up from its optimal fractional value, with
+the remaining cascades being assigned to the first level.
 

### 2020-12-08 motivation.tex
proofreading

--- 2018-07-17 motivation.tex
@@
 work aims to measure the effectiveness of a symmetric enrichment cascade when
-used outside of its designed scope and quantify the attractiveness of such way
+used outside of its designed scope and quantify the attractiveness of such ways
 to build up significant quantity of \gls{HEU}.
@@
 The present work investigates the performance of an enrichment cycle when chaining
-gas enrichment cascades tuned for low enrich uranium production from natural
-uranium. As literature on the mater is for obvious reason limited, three
-behavior models have been implemented and used to evaluate the response of an
-enrich cascade when fed with different assays than the design one. This work
-also takes advantage of the Cyclus\cite{cyclus} fuel cycle capabilities to
-evaluate the assay values at equilibrium.
+gas enrichment cascades tuned for low enriched uranium (LEU) production from natural
+uranium to instead produce HEU. Literature on the subject is limited due to its
+internationally and politically sensitive nature. Three behavior models have been
+implemented and used to evaluate the response of an enrichment cascade when fed
+with different assays than originally designed. This work also takes advantage
+of the Cyclus \cite{cyclus} fuel cycle simulator's capabilities to evaluate the
+assay values at equilibrium.

### 2020-12-08 results.tex
updating real cascade numbers in results table
incrementing results figure scaling width
scaling results figure
scaling results figure further
scaling third subfigure in results
trying one more scaling feature in results table
proofreading

@@
 \resizebox{\columnwidth}{!}{%
-\begin{tabular*}{\textwidth}{c @{\extracolsep{\fill}} cccccccc}
+\begin{tabular*}{\linewidth}{c @{\extracolsep{\fill}} cccccccc}
 \toprule
@@
         &            & Tails $w\%$    & $0.28$   & $0.52$   & $0.28$   & $0.36$   & $0.28$   & $0.51$ \\
-        & Cascades   & Impl. (Ideal)  & 25(26.5) & 25(26.5) & 25(26.4) & 24(26.3) & 25(26.5) & 25(26.2)  \\
+        & Cascades   & Impl. (Ideal)  & 25(26.5) & 25(26.5) & 24(26.4) & 25(26.3) & 25(26.5) & 25(26.2)  \\
 \midrule                                                                                                 
@@
         &            & Tails $w\%$    & $1.68$   & $5.93$   & $1.58$   & $2.54$   & $1.66$   & $5.88$ \\
-        & Cascades   & Impl. (Ideal)  & 3(3.1)   & 4(3.1)   & 3(3.1)   & 4(3.1)   & 3(3.1)   & 4(3.4)    \\
+        & Cascades   & Impl. (Ideal)  & 3(3.1)   & 4(3.1)   & 3(3.1)   & 3(3.1)   & 3(3.1)   & 4(3.4)    \\
 \midrule                                                                                                 
@@
 \ref{tab:level}, the different models don't have the same effect on the
-cascade behavior. While models A and C, achieve a quick enrichment gain with
-the cascades chaining, 4/23/78/98 and 4/23/82/99, respectively, model B, only
-achieves an enrichment gain of 4/21/61/90.  This table also shows the integer
-number of cascades implemented (Impl.) at each level in the simulation, as well as the
-non-integer number of cascades that would achieve an ideal configuration (Ideal).
+cascade behavior. While models A and C achieve a quick enrichment gain with
+the cascades chaining, 4/21/76/98 and 4/21/79/99, respectively, model B only
+achieves an enrichment gain of 4/19/58/89/98, requiring more levels to even
+achieve HEU enrichment. This table also shows the integer
+number of cascades implemented (Impl.) at each level in the simulation, compared
+to the non-integer number of cascades that would achieve an ideal configuration (Ideal).
 
@@
         \centering
-        \includegraphics[scale=0.2]{feed_assays}
-        \caption{Feed Assays.}
+        \includegraphics[width=\linewidth]{feed_assays}
+        \caption{Feed Assays}
         \label{sfig:feed_assay}
@@
         \centering
-        \includegraphics[scale=0.2]{product_assays}
-        \caption{Product Assays.}
+        \includegraphics[width=\linewidth]{product_assays}
+        \caption{Product Assays}
         \label{sfig:product_assay}
@@
         \centering
-        \includegraphics[scale=0.2]{tails_assays}
-        \caption{Tails Assays.}
+        \includegraphics[width=\linewidth]{tails_assays}
+        \caption{Tails Assays}
         \label{sfig:tails_assay}
@@
 As shown in Figures \ref{fig:assays}, recycling the tails increases the overall product assay at
-all the different levels. As the tails assay of a level $n+1$ is always higher than
+all the different levels, requiring less levels in the configuration to achieve
+the desired enrichment. As the tails assay of a level $n+1$ is always higher than
 the product assay of the level $n-1$, recycling the tails of level $n+1$ will
@@
 Moreover, with an increased feed assay, tails and product assays increase as
-well, increasing de facto the feed assays of respectively cascade levels $n-1$
+well, increasing de facto the feed assays of respective cascade levels $n-1$
 and $n+1$, etc.  This effect reduces the number of cascade levels required to reach
-\gls{HEU} in case A and C.
+\gls{HEU} in all cases.
 
@@
 As shown in Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
-production rate, from $2$ to almost $20$ kg/y when using models A and C, and from
-$17$ to $38$ kg/y with the model B. For the reference calculation where all the
+production rate, from $5$ to almost $45$ kg/y when using models A and C, and from
+$12$ to $45$ kg/y with the model B. For the reference calculation, where all the
 available cascades are used within a single large cascade design for direct
-\gls{HEU} production, the \gls{HEU} production rate is slightly over $50$ kg/y.
+\gls{HEU} production, the \gls{HEU} production rate is slightly over $60$ kg/y.
 
-As models A and C, rely on maintaining the cut values at each stages of the
-cascade and share the same number of levels, have the exact same cascade
+As models A and C rely on maintaining the cut values at each stage of the
+cascade and share the same number of levels, they have the exact same cascade
 repartition across the different levels and the same \gls{HEU} production rate.

### 2020-12-08 theory.tex
attempting to resize matrix
proofreading

@@
 In the following section, equations and algorithms used to model the behavior of
-a symmetric ideal gas centrifuge cascade from the individual centrifuge property
-are described. Details will also be provided to model the centrifuge behavior
-when fed with a different feed enrichment than the design one.
+a symmetric ideal gas centrifuge cascade from individual centrifuge properties
+are described. Details will also be provided to model centrifuge behavior
+when fed with a different feed enrichment than designed.
 
@@
 
-The variable $Z_p$ is the rectifier length, or the location of the feed point, has
-an optimal axial location as defined by \cite{raetz.phd}:
+The variable $Z_p$ is the rectifier length, or the location of the feed point,
+and has an optimal axial location as defined by \cite{raetz.phd}:
 
@@
 of the fraction of the centrifuge feed that is output as product, and the counter-current
-flow, $L/F$. In practice, this value is a design parameter that is updated in the model
+flow, $L/F$. In practice, this value is a design parameter that is defined in the model
 during the design of the centrifuge cascade.
@@
 radius for the lighter isotope and $r_2$ for the heavier isotope. R\"aetz's
-two-shell model looks for optimal values between these two, as defined from
+two-shell model looks for optimal values between these two, as described by
 the hydrodynamic equations. The radii ratio is optimized using the following relationship:
@@
 stage and product, $P$, of the previous one. For the cascade feeding stage
-an external feed, $F_{ext}$:
+and external feed, $F_{ext}$:
 
@@
 express $\alpha$ as a function of the feed rate $F$, the separative performance
-$\delta U(\theta)$ and the cut $\theta$:
+$\delta U$ (a function of $\theta$), and the cut $\theta$:
 
@@
 \eqref{eq_product_assay}, it is possible to express $\beta$ as a function of
-only the feed abundance, $R$, the cut $\theta$ and $\alpha$:
+only the feed abundance, $R$, the cut $\theta$, and $\alpha$:
 
@@
 Finally from equation \eqref{eq_alpha} and \eqref{eq_beta} it is possible to
-determine the cut, $\theta$ required to build an ideal cascade:
+determine the cut, $\theta$, required to build an ideal cascade:
 
@@
 
-To construct an ideal stage, a cut ($\theta$) must first be computed.
+To construct an ideal stage, a cut, $\theta$, must first be computed.
 This is found iteratively, searching for the optimal cut value where $\alpha = \beta$
 for a given feed and centrifuge parameters. With a separative power calculated,
-and $\alpha$ and $\beta$ value can be determined for an initial cut guess. This
+an $\alpha$ and $\beta$ value can be determined for an initial cut guess. This
 model assumes that the ideal cut for a stage should be between 0.1 and 0.9. The
@@
 
-The second step determines the relative flows at each stages, solving the linear
+The second step determines the relative flows at each stage, solving the linear
 flow equation, \eqref{eq_flow}.
 The cascade can then be populated with actual machines until the maximum number
-available of machines is reached.
+of available machines is reached.
 
 \begin{equation}
+\resizebox{\linewidth}{!}{%
+$\displaystyle
 \setcounter{MaxMatrixCols}{20}
@@
 \end{bmatrix}
+$}
 %\caption{caption needed!}
@@
 assumes the tails to product enrichment factor and the cut remain constants
-(eq. \eqref{eq_gamma-def}: $\gamma = \alpha\beta$). Models behaviors and
+(eq. \eqref{eq_gamma-def}: $\gamma = \alpha\beta$). Model behaviors and
 assumptions are summarized in Tab. \ref{tab:models}.
@@
 
-The tuning method A does not re-optimize $\theta_i$ keeping the same flow as the
+The tuning method A does not re-optimize $\theta_i$, keeping the same flow as the
 ideal configuration. From equation \eqref{eq_alpha}, maintaining $\delta U$ and
@@
 
-In order to compute the proper product and tails assay at each stage, the tails
+In order to compute the proper product and tails assay at each stage, the tail
 and the product from the next and the previous stage respectively must be

### 2020-12-09 results.tex
updating figure 1 and 3

@@
         (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
-        in $w\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
-        blue), per model (A/B/C) and without/with tails recycling (NR/R). The
-        black dashed line represents the $90 w\%$ enrichment threshold.}
+        in $w\%$ of $^{235}$U, per cascade level from 0 to 4 (purple, red, green,
+        orange, blue), per model (A/B/C) and without/with tails recycling (NR/R).
+        The black dashed line represents the $90 w\%$ enrichment threshold.}
     \label{fig:assays}

### 2021-02-10 motivation.tex
first review pass from abstract up until 2.5.1

@@
 work aims to measure the effectiveness of a symmetric enrichment cascade when
-used outside of its designed scope and quantify the attractiveness of such ways
-to build up significant quantity of \gls{HEU}.
+used outside of its designed scope and to quantify the attractiveness %Katie: I would be VERY VERY careful using the word attractiveness.
+of such ways
+to build up a \gls{SQ} of \gls{HEU}, defined by the \gls{IAEA} as \(25 \ kilograms\)\cite{noauthor_iaea_2001}.
 
 The present work investigates the performance of an enrichment cycle when chaining
-gas enrichment cascades tuned for low enriched uranium (LEU) production from natural
-uranium to instead produce HEU. Literature on the subject is limited due to its
+gas centrifuge enrichment cascades tuned for \gls{LEU} production from natural uranium to instead produce \gls{HEU}. Literature on the subject is limited due to its
 internationally and politically sensitive nature. Three behavior models have been
@@
 with different assays than originally designed. This work also takes advantage
-of the Cyclus \cite{cyclus} fuel cycle simulator's capabilities to evaluate the
+of the \Cyclus \cite{cyclus} fuel cycle simulator's capabilities to evaluate the
 assay values at equilibrium.

### 2021-02-10 theory.tex
first review pass from abstract up until 2.5.1

@@
 
-As described in \cite{glaser.2008}, the separative power of a single centrifuge
-can be express as an analytical solution \cite{raetz.phd} of the
+As described by Glaser in \cite{glaser.2008}, the separative power of a single centrifuge can be express as an analytical solution \cite{raetz.phd} of the
 differential equation for the gas centrifuge:
@@
 \begin{equation}
-    \max\{[1-(\frac{r_1}{r_2})^2]^2 \times [ \ln(\frac{r_2}{r_1})]^{-1}\}
+    \max \left\{ \left[1-\left(\frac{r_1}{r_2}\right)^2 \right]^2 \times \left[ \ln \left(\frac{r_2}{r_1} \right) \right]^{-1} \right\}
 \end{equation}
 
-The ratio can further be constrained by approximating $r_2$ as being very close
+This ratio can further be constrained by approximating $r_2$ as being very close
 to the inner centrifuge wall with radius $a$:
@@
 \begin{equation}
-    (\frac{r_1}{r_2}) \approx (\frac{r_1}{a}) = \sqrt{1 - \frac{2RT}{M}(\ln x)\frac{1}{v_{a}^{2}}}
+    \left(\frac{r_1}{r_2}\right) \approx \left(\frac{r_1}{a}\right) = \sqrt{1 - \frac{2RT}{M}(\ln x)\frac{1}{v_{a}^{2}}}
 \end{equation}
@@
 Here the gas constants are molar mass, $M$, temperature $T$, universal gas constant, $R$,
-and the pressure ratio, $x$ (typically $1000:1$).
+and the pressure ratio, $x$ (typically $1000:1$) \cite{}. %needs citation?
 This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
@@
 With this, all parameters of the separative power equation \ref{eq:raetz} are
-defined and a value can be calculated. $\delta U$ has units similar to the feed
-flow, that of $[mg/s]$.
+defined and a value can be calculated. Separative power, $\delta U$, has units similar to the feed flow, that of $[mg/s]$.
 
@@
 
-It can be shown \ref{avery} that the separative power of a single centrifuge can be
-derive from the first principle and expressed as a function of the feed to
-product enrichment factor, $\alpha$, the cut, $\theta$, and the feed rate, $F$:
+It can be shown \cite{avery} that the separative power of a single centrifuge can be
+derived from first principles and expressed as a function of the feed-to-product enrichment factor, $\alpha$, the cut, $\theta$, and the feed rate, $F$:
+%I think we should replicate at least some of that here
 
@@
 The outputs of a centrifuge relative to its input can be described with ratios
-of the abundance ($R = \frac{N}{1-N}$) where the feed, product, and tail are
-$N, N', N''$ respectively. Enrichment factiors of $\alpha$ (feed to product),
-$\beta$ (feed to tail), and $\gamma$ (tail to product) can then be defined:
+of the abundance ($R = \frac{N}{1-N}$) where the feed, product, and tail enrichment $N, N', N''$ respectively. Enrichment factors of $\alpha$ (feed-to-product),
+$\beta$ (feed-to-tail), and $\gamma$ (tail-to-product) can then be defined:
 
@@
     \begin{equation}\label{eq_gamma-def}
-        \gamma = \alpha.\beta
+        \gamma = \alpha \, \beta
     \end{equation}
@@
 
-A symmetric cascade is a cascade where a stage's feed, $F$, with a tail, $T$, of the next
-stage and product, $P$, of the previous one. For the cascade feeding stage
-and external feed, $F_{ext}$:
+A symmetric cascade is a cascade where a stage is fed using the tail, $T$, of the next stage and the product, $P$, of the previous one.
+The the cascade feeding stage, $F_{i}$ flow, with external feed, $F_{ext}$, is given by:
 
@@
 
-The method used to design a symmetric ideal cascade starts with the feeding
+Designing a symmetric ideal cascade beings with the feeding
 stage. As all the enrichment factors are equal across all the cascade, the
@@
 From equation \eqref{eq_raetz} and \eqref{eq_alpha_principle} it is possible to
-express $\alpha$ as a function of the feed rate $F$, the separative performance
+express the feed-to-product enrichment factor $\alpha$ as a function of the feed rate $F$, the separative performance
 $\delta U$ (a function of $\theta$), and the cut $\theta$:
@@
 \begin{equation}\label{eq_product_assay}
-    N' = \frac{\alpha R}{1 + \alpha R}
+    N' = \frac{\alpha \frac{N}{1-N}}{1+\alpha \frac{N}{1-N}} = \frac{\alpha R}{1 + \alpha R}
 \end {equation}
@@
 Then, from mass conservation, $N = \theta N' + (1-\theta)N''$ and equation
-\eqref{eq_product_assay}, it is possible to express $\beta$ as a function of
-only the feed abundance, $R$, the cut $\theta$, and $\alpha$:
+\eqref{eq_product_assay}, it is possible to express the feed-to-tail enrichment factor $\beta$ as a function of only the feed abundance, $R$, the cut $\theta$, and the feed-to-product enrichment factor, $\alpha$:
 
@@
 This is found iteratively, searching for the optimal cut value where $\alpha = \beta$
-for a given feed and centrifuge parameters. With a separative power calculated,
+for given feed and centrifuge parameters. With a separative power calculated,
 an $\alpha$ and $\beta$ value can be determined for an initial cut guess. This
@@
 
-In a cascade, as $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of
+In a cascade, as the stage feed-to-product enrichment factor $\alpha_{i}$ and stage feed-to-tail enrichment factor $\beta_{i}$ remain constant, only the value of
 the cut, $\theta_{i}$, changes across the different stages of a cascade.  This
 algorithm assumes that the corresponding separative power $\delta U$ (not
-re-computed) can be achieved with the chosen centrifuge design, tuning other
-operational parameter such as the rotation speed, the counter-current flow
+re-computed) can be achieved with the chosen centrifuge design by tuning other
+operational parameters such as the rotation speed, counter-current flow
 ratio, etc.  Once $\theta_{i}$ is determined, it is possible to compute the
-product and the tail assay.
+product and the tail assays.
 
 The design of the ideal symmetric cascade is performed through 2 steps. First,
-the configuration and number of stages is determined, adding stages until the
-product assay of the final stage is greater or equal the product targeted assay,
-and similarly the tails assay is less or equal the tails desired assay.  This
-determines the number of enriching and stripping stages as well as their
-enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$).
+the configuration and number of stages is determined, adding stages with product assay $N'_i$ calculated using equation \ref{eq_product_assay}, until the
+product assay of the final stage is greater than or equal to the product targeted assay.
+The stage tails assay $N''_i$ is calculated similarly, until it is less than or equal to the tails desired assay.
+This determines the number of enriching and stripping stages as well as their enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$).
 
@@
 
-The first one assumes that no changes are being made to the cascade, i.e $\delta
-U$, $F$ and $\theta$ are fixed across all stages. The second one assumes the cut
-value at each stage is retuned to maintain the ideal state of the cascade,
-$\alpha$ and $\beta$ remain fixed. The last one, described in \cite{walker.2017}
-assumes the tails to product enrichment factor and the cut remain constants
+The first method, A, assumes that no changes are being made to the cascade, i.e $\delta U$, $F$ and $\theta$ are fixed across all stages.
+The second method, B, assumes the cut value $\theta$ is re-tuned at each stage to maintain the ideal state of the cascade, while $\alpha$ and $\beta$ remain fixed.
+The last method, C, described in \cite{walker.2017} assumes the tails-to-product enrichment factor $\gamma$ and the cut $\theta$ remain constants
 (eq. \eqref{eq_gamma-def}: $\gamma = \alpha\beta$). Model behaviors and

### 2021-06-24 theory.tex
Corrected feed typo.
Co-authored-by: Katie Mummah <radioactivekate@gmail.com>
expanding on first principles derivation

@@
 
-It can be shown \cite{avery} that the separative power of a single centrifuge can be
-derived from first principles and expressed as a function of the feed-to-product enrichment factor, $\alpha$, the cut, $\theta$, and the feed rate, $F$:
+Separative power can be written as a function of the change in entropy performed \cite{avery}:
+
+\begin{equation}
+    \delta U = \frac{L}{RN} \frac{\Delta S}{(1-N)}
+\end{equation}
+
+Here, $L$ is the feed flow expressed as moles per second and could be interchangeably expressed as $F$ above.
+Using the Boltzmann definition of entropy, the change in entropy for a mixture of two isotopes is:
+
+\begin{equation}
+    \Delta S(N) = R \left( N \ln(N) + (1-N) \ln(1-N) \right)
+\end{equation}
+
+Using this in the expression for free energy \cite{?} and normalizing for temperature and gas constant,
+a value function can be constructed \cite{?}:
+
+\begin{equation}
+    V(x) = (2x-1) \ln{(\frac{x}{1-x})}
+\end{equation}
+
+Where $x$ here is a concentration for a mass (e.g. $N$). The separative work applied on a feed is then an expression of this value function:
+
+\begin{equation}
+    \delta U = \theta F V(N') + (1-\theta) F V(N'') - F V(N)
+\end{equation}
+
+Conducting a Taylor expansion of $V(N)$ around $N$ and utilizing the definition $N=\theta N' + (1-\theta)N''$ lends a simplification:
+
+\begin{equation}
+    \delta U = \frac{\theta}{1-\theta} \frac{F(\alpha-1)^2}{2} \frac{d^2 V(N)}{dN^2} \left[ N(1-N) \right]^2
+\end{equation}
+
+Finally, specifying the change in value function to be independent of $N$ (?) concludes in an expression for the separative power of a single centrifuge
+in terms of the feed-to-product enrichment factor, $\alpha$, the cut, $\theta$, and the feed rate, $F$ \cite{avery}:
 %I think we should replicate at least some of that here
@@
 \begin{equation} \label{eq_alpha_principle}
-    \delta U = \frac{F}{2}\frac{\theta}{1-\theta}(\alpha-1)^{2}
+    \delta U = \frac{\theta}{1-\theta}\frac{F}{2}(\alpha-1)^{2}
 \end{equation}
@@
 \begin{equation}
-    F_{i} = T_{i+1} + F_{i-1} ~(+ F_{ext})
+    F_{i} = T_{i+1} + P_{i-1} ~(+ F_{ext})
 \end{equation}

### 2021-06-24 abstract.tex

@@
 the behavior of an enrichment cascade in such circumstances. In addition to the
-cut ($\theta$) those methods evaluate the feed to product, feed to tails, and the
-product to tails enrichment ratio, $\alpha$, $\beta$ and $\gamma$, respectively,
+cut, ($\theta$) these methods evaluate the feed-to-product, feed-to-tails, and the
+product-to-tails enrichment ratio, $\alpha$, $\beta$ and $\gamma$, respectively,
 as a function of the cascade feed assay. As those four parameters depend on each
@@
 $\theta$ values at each stage accordingly. Both approaches have been implemented
-into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
+into the \Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
 $\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
@@
 scenarios involving misuse of symmetric enrichment cascades simulated using the dynamic
-nuclear fuel cycle simulator, Cyclus.
+nuclear fuel cycle simulator, \Cyclus.
 \end{itshape}
